### 2019-02-04 paper/paper.tex
Add paper outline

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix2019_v3}

% to be able to draw some self-contained figs
\usepackage{tikz}
\usepackage{amsmath}

\begin{document}

%don't print date
\date{}

% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf Dark Decoys:
  Conjuring Proxies from Unused Address Space}

%for single author (just remove % characters)
%\author{
%{\rm Your N.\ Here}\\
%Your Institution
%\and
%{\rm Second Name}\\
%Second Institution
%% copy the following lines to add more authors
%% \and
%% {\rm Name}\\
%%Name Institution
%} % end author

\maketitle

%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------
Refraction Networking (formerly ``Decoy Routing'') has emrged as a useful tool in circumventing
        Internet censorship. By placing proxies in cooperating Internet Service
        Providers (ISPs) and using connections to existing reachable
        ``decoy'' sites for transport, censors cannot easily block access to
        such proxies without also blocking legitimate sites.

However, existing deployed Refraction Networking schemes such as TapDance suffer
from several problems, including a limited number of decoy sites in realistic
deployments, and an unfavorable tradeoff between performance and observability
by the censor. These problems limit where such proxies can be deloyed, hamper
their effectiveness, and may ultimately make them possible for censors to block.

In this paper, we present Dark Decoys, a deployable Refraction Networking scheme that
overcomes these issues. Dark Decoys leverages the (primarily) unused address
space that is reachable through the deploying ISP. Rather than rely on existing
sites as reachable decoy sites that must be involved in each proxy connection,
Dark Decoys create seemingly legitimate hosts at new IP addresses. These
invented hosts are indistinguishable from normal hosts to the censor, but can
be used by clients as one-time proxies.

We implement our scheme ... and it's just the bee's knees. TODO

\end{abstract}

%-------------------------------------------------------------------------------
\section{Introduction}
%-------------------------------------------------------------------------------
% 1.5-2 pages

Censorship circumvention still important
-More countries blocking
-Existing countries blocking more

Existing circumvention strategies on shaky ground
-domain fronting going away
-active probing of existing proxies
-Cenosrs fingerprinting known protocols

Importance of Refraction Networking
-what it is, how it solves many of the above problems
-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far

Challenges remain in Tapdance:
-Censor can fingerprint decoy sites
-Decoys themselves are limited (e.g. a few dozen in many cases)
-Can't have long-lived connections (performance and observability issue)
-Other performance limits (upload limit, TCP window size)

Dark decoys solve these issues
-Create new decoys from ``dark'' (unused) address space
-Clients register (via TapDance-like or other robust protocol (email, blockchain, whatever))
-Connect to custom IP address, talk whatever protocol client/station agrees on

One-time use address advantages:
-Censor cannot actively probe ahead of time (especially in IPv6), making it hard to fingerprint
-Decoys are now virtually unlimited (or limited only by address space)
-Connection can live as long as we want
-No pesky TCP/TapDance-y limits

Requirements/Challenges
-Censor can't be able to distinguish between dark decoy and legitimate hosts
    (otherwise they block all dark decoys)
    -Includes active probing: censor shouldn't be able to register existing IP
-Disruption avoidence: Want to pickup even for used addresses
    -Otherwise, censor probes to find truly unused address space and blocks
    -But can't disrupt legitimate services
    -Can overcome by limiting pickup to the registering client (but spoofing challenges...)
    -Note: also likely solved by the client-sends-SNI in the Mask site application...

\section{Background}
% 1 page
Background on TLS and Refraction Networking

\section{Threat Model}
% 0.5 page

-Censor can block arbitrary addresses (or networks), but faces a cost in doing so (collateral damage)
-Censor can know what network deploys the dark decoy station
-Censor knows the dark decoy prefixes distributed in the client, but they contain legitimate hosts
-Censor can use the client
-Censor can active probe limited sets, but cannot enumerate the entire prefix (i.e. IPv6 /32)
-Censor can active probe or (p)replay connections it suspects

\section{Architecture}
% 3 pages
-Registration
-Dark decoy selection (seed -> IP)
-Connection to Dark Decoy Application (DD App)
-IPv6 vs IPv4 dark decoys

\subsection{Applications}

Application choices:
-obfs4  (could we test this?)
-Masked sites (implemented)
-TLS 1.3 eSNI

-Takeover of masked site TLS connection (client/server random from masked site, master secret from registration)

-Masked site slection: How do we get the list of masked sites? Alexa list? passive observation?

\section{Implementation}
% 1 page

-ISP-scale implementation, able to handle 10+Gbps
-Language choice (Rust, Go, minimal C)
-Open source (client and station)

\section{Evaluation}
% 1 page

Compare to TapDance performance:
-Connection setup time
-Connection/session lifetime
-Throughput (especially upload vs download)
-Security considerations

\section{Attacks and Defenses}
% 1 page

-Fingerprinting Masked site vs Dark decoy application
-Active probing TLS connection
    -Block access unless from registering source IP
        -cite GFW taking over client IPs for active probing of old obfs
    -Verify knowledge of seed (but how to respond when verification fails?)

\section{Related Work}
% 0.5-0.75 page

MultiFlow, The Waterfall of Liberty, Slitheen, Rebound, TapDance, Cirripede, Telex, Decoy Routing
True Cost of RAD, Routing around Decoys
ISP-scale TapDance

\section{Future Work}
% 0.5 page

\section{Conclusion}
%.25 page

%%-------------------------------------------------------------------------------
%\section*{Availability}
%%-------------------------------------------------------------------------------
%
%USENIX program committees give extra points to submissions that are
%backed by artifacts that are publicly available. If you made your code
%or data available, it's worth mentioning this fact in a dedicated
%section.

%-------------------------------------------------------------------------------
\bibliographystyle{plain}
\bibliography{biblio}

\end{document}

### 2019-02-05 src/lib.rs
add redis to handle multicore registrations

@@ -13,6 +13,9 @@ extern crate radix; // https://github.com/refraction-networking/radix
 extern crate tuntap; // https://github.com/ewust/tuntap.rs
 extern crate zmq;
 
+#[macro_use]
+extern crate redis;
+
 use std::mem::transmute;
 use std::collections::HashMap;
 use time::precise_time_ns;
@@ -60,6 +63,7 @@ pub struct PerCoreGlobal
     pub ip_tree:   PrefixTree,
     // ZMQ socket for sending information to the dark decoy application
     zmq_sock:      zmq::Socket,
+
 }
 
 // Tracking of some pretty straightforward quantities
@@ -194,6 +198,7 @@ impl PerCoreStats
                 0,
                 0);
         */
+        /*
         report!("stats {} pkts ({} v4, {} v6) dark decoy flows {} tracked flows {} tags checked {}",
             self.packets_this_period,
             self.ipv4_packets_this_period,
@@ -201,6 +206,7 @@ impl PerCoreStats
             dark_decoys,
             tracked,
             self.elligator_this_period);
+        */
 
         self.elligator_this_period = 0;
         self.packets_this_period = 0;

### 2019-02-06 paper/paper.tex
Architecture first draft

@@
 In this paper, we present Dark Decoys, a deployable Refraction Networking scheme that
-overcomes these issues. Dark Decoys leverages the (primarily) unused address
+overcomes the limits on decoys and performance. Dark Decoys leverages the (primarily) unused address
 space that is reachable through the deploying ISP. Rather than rely on existing
@@
 % 3 pages
--Registration
--Dark decoy selection (seed -> IP)
--Connection to Dark Decoy Application (DD App)
--IPv6 vs IPv4 dark decoys
+
+Dark Decoys involve three main steps. First, clients \textbf{register} with the
+ISP station,
+and agree on the dark decoy IP address that will be used. Next, the client
+connects to the agreed upon address, which is terminated by an
+\textbf{application} running on the station. Finally, the client \textbf{proves}
+to the application that it was the same entity that registered (and not a censor
+attempting to probe), and is able to use the application as a proxy.
+
+Similar to previous schemes, our design does not require expensive in-line
+flow blocking, and can be accomplished with only a passive tap at the ISP.
+Our architecture is also modular, in that the registration and application steps operate
+independently, allowing a wide range of flexibility to evade censors. We
+describe each of these components.
+
+\subsection{Registration}
+
+Clients can register intent to use the proxy in several covert ways. For
+instance, they could use email or other existing intermitently available proxies
+to register. In this section, we use a form of Refraction Networking similar to
+TapDance to register directly with the station.
+
+Registration is unidirectional (client to server) and does not require any
+acknowledgement of receipt. To ensure receipt, clients can attempt to register
+multiple times (possibly via multiple methods) with the same information, and expect
+that one gets through.
+
+\medskip
+
+To register, clients connect to a \textbf{decoy} site that supports TLS. They
+complete the handshake, and send a normal HTTPS request. In TLS, requests (and
+responses) are encrypted and sent in an \texttt{Application Data} record. During
+registration, the client alters the ciphertext of the \texttt{Application Data} record to
+convey a short \textbf{tag} to the ISP station, on path between the client and
+decoy site.
+
+The tag contains a public key (encoded to be indistinguishable from random using
+Elligator~\cite{elligator}), and a message encrypted under the shared secret
+derived from a key exchange with the station's long-term public key hard-coded
+in the client software. The station uses its private key to compute the same
+shared secret from the (decoded) public key, and decrypts the message in the
+tag. The censor, without knowledge of either the station or client's private
+key, cannot derive the shared secret, preventing it from being able to decrypt
+the message.
+
+Inside the message, the client communicates a random \textbf{seed}, and other
+configuration-specific information, such as flags to signify version, feature
+support, and which set of dark decoy network prefixes the client knows of. The
+client and server use a hash of the provided seed to determine which specific
+dark decoy IP address to register. It may seem intuitive to instead have the client
+send the specific IP address to register, but allowing the client arbitrary
+choice also allows censors to register suspected dark decoys and block them if
+they pick up. By using a hash, the censor would have to pre-image the hash to
+obtain a seed it could use to register for a desired IP address. It also gives a
+secret (the seed) that only the client and station know, even after the client
+connects to the dark decoy address.
+
+% Note on IPv6 space? /32 of IPv6 is 96-bits to select...
+We note that IP addresses are selected from unused but still routed address
+space that passes by the ISP. Traffic to unrouted addresses would produce ICMP
+responses that a censor could observe, and are also easily blocked with knowledge
+of a routing table. Because we support the use of IPv6 addresses, censors will
+also be unable to scan ahead of time to determine if the host has been there
+previously, or what was there before. While they can probe suspected dark decoy
+addresses after clients connect to them, at that point the address has already been
+registered, preventing the censor from identifying differences in behavior
+before and after registration.
+
+Once the dark decoy IP address has been selected, the station watches for
+packets destined to that address, and forwards them onto the dark decoy
+\textbf{application}. The station can also optionally ignore packets not from
+the source IP address of the registering client, so that to a probing censor,
+the dark decoy appears to be firewalled off from all but the client.
 
@@
 
-Application choices:
--obfs4  (could we test this?)
--Masked sites (implemented)
--TLS 1.3 eSNI
+Once the client has registered, packets sent to the dark decoy IP address are
+passed to the \textbf{application} running on the station. The application has
+two main jobs: first, it must look like an innocuous legitimate service to the
+censor, and second must allow the client to use it as a proxy.
 
--Takeover of masked site TLS connection (client/server random from masked site, master secret from registration)
+Any protocol that satisfies these criteria can be used as an application. For
+instance, \texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
+Tor~\cite{tor} that could be
+modified to meet these needs: it requires each endpoint to have knowledge of a
+shared secret (which we can derive from the seed shared by the client and
+station during registration), and attempts to be a protocol with no discernible
+fingerprint. Probing censors that do not have the shared secret receive no
+response, while clients that have the secret can communicate with the proxy.
 
--Masked site slection: How do we get the list of masked sites? Alexa list? passive observation?
+However, even though \texttt{obfs4} is indistinguishable from random, there are
+still known attacks that can differentiate it from other
+traffic~\cite{wang2015seeing}. While we have yet to see evidence of such attacks
+employed in practice by censors, we consider two alternatives built on TLS.
+
+\subsubsection{Mask Sites}
+
+TLS is a natural protocol for dark decoy applications, because it is ubiquitous on
+the Internet (making it difficult for censors to block), while also providing
+strong cryptographic protection against passive and active network adversaries.
+However, there are several challenges to make it robust against censors that
+wish to block a particular service.
+
+This is because TLS sends important server-identifying content in plaintext
+during the TLS handshake. This includes the Server Name Indication (SNI) in the
+Client Hello message that sends the domain name of the server, and the
+X.509 Certificate sent by the server.
+
+To evade censors, we must send a plausible SNI value (sending no SNI is
+uncommon and easily blocked---only 1\% of TLS connections do not carry the
+SNI extension~\cite{tls-fingerprint}), and we must have the server respond with
+a plausible (and corresponding) certificate. Even if we manage to avoid sending
+either in the clear, censors could actively probe the server in a
+way that would normally elicit a certificate.
+
+We therefore attempt to mimic an existing \textbf{mask site}, by relaying
+traffic between the client and a selected mask website. To a censor, this site
+will be indistinguishable from the legitimate mask site, making it difficult for
+them to block without potentially blocking the actual site. TLS connections to the
+application will terminate exactly as connections to the mask site would, with the
+application acting as a transparent proxy between the client and mask site.
+However, this leaves the application unable to introspect on the contents of the
+TLS connection to the mask site, as it does not have the client-site shared
+secrets, and it cannot overtly man-in-the-middle the connection before knowing
+it is communicating with the legitimate client (and not the censor).
+
+To accomplish this, the client changes the shared secret it derives with the
+mask site to something that the application can also derive. The client's first
+\texttt{Application Data} packet is thus encrypted under a different secret than
+the client/mask site secret. Specifically, the client uses the \textbf{seed}
+sent during registration to derive the pre-master secret for the connection.
+This is hashed along with the client and server randoms of the current (mask
+site) TLS connection to obtain the master secret that determines
+encryption/decryption/authentication keys.
+
+The application can determine if the client did this by trial decryption with
+the master secret derived from the known \textbf{seed}. If it succeeds, the
+client has proved knowledge of the \textbf{seed}, and the application can
+respond as a proxy. If not, the application simply continues to forward data
+between the client and the mask site. As the censor does not have knowledge of
+the \textbf{seed} used in registration, it cannot coerce the application to
+appear as anything besides the mask site.
+
+\paragraph{Mask Site Selection}
+How do we get the list of masked sites? Alexa list? passive observation?
+
+\subsubsection{Encrypted SNI}
+
+TLS~1.3....
+
+%-Registration
+%-Dark decoy selection (seed -> IP)
+%-Connection to Dark Decoy Application (DD App)
+%-IPv6 vs IPv4 dark decoys
 

### 2019-02-06 application/main.go
WIP: application now successfully intercepts+cosmetics

@@ -6,127 +6,62 @@ import (
 	"errors"
 	"fmt"
 	"io"
+	"io/ioutil"
+	"log"
 	"net"
+	"os"
 	"sync"
+	"syscall"
 	"time"
 
 	zmq "github.com/pebbe/zmq4"
-	tls "github.com/refraction-networking/utls"
+	"github.com/refraction-networking/utls"
 )
 
-// replayableReaderConn could be replayed once by calling StartReplaying
-type replayableReaderConn struct {
+// bufferedReaderConn allows to combine *bufio.Reader(conn) and *conn into one struct.
+// Implements net.Conn
+type bufferedReaderConn struct {
 	net.Conn
-	R            *bufio.Reader
-	ReplayBuffer []byte
-	ReplayState  uint8
-	Replaying    bool
-	Recording    bool
+	R *bufio.Reader
 }
 
-func (bc *replayableReaderConn) Read(b []byte) (n int, err error) {
-	if bc.Replaying && len(bc.ReplayBuffer) > 0 {
-		n = copy(b, bc.ReplayBuffer)
-		bc.ReplayBuffer = bc.ReplayBuffer[n:]
-	} else {
-		n, err = bc.R.Read(b)
-		if bc.Recording {
-			bc.ReplayBuffer = append(bc.ReplayBuffer, b[:n]...)
-		}
-	}
-	return
+func (bc *bufferedReaderConn) Read(b []byte) (n int, err error) {
+	return bc.R.Read(b)
 }
 
-func (bc *replayableReaderConn) Peek(n int) ([]byte, error) {
+func (bc *bufferedReaderConn) Peek(n int) ([]byte, error) {
 	return bc.R.Peek(n)
 }
 
-func (bc *replayableReaderConn) StartReplaying() {
-	bc.Replaying = true
-	bc.Recording = false
-}
-
-func makeReplayableReaderConn(c net.Conn, r *bufio.Reader) *replayableReaderConn {
-	return &replayableReaderConn{
-		Conn:      c,
-		R:         r,
-		Recording: true,
+func (bc *bufferedReaderConn) CloseWrite() error {
+	if closeWriter, ok := bc.Conn.(interface {
+		CloseWrite() error
+	}); ok {
+		return closeWriter.CloseWrite()
+	} else {
+		return errors.New("not a CloseWriter")
 	}
 }
 
-func parseSNI(b []byte) (string, error) {
-	offset := 43
-	if offset >= len(b) {
[…]

### 2019-02-06 paper/figures.tex

\newcommand{\FigOverview}{
\begin{figure}[ht]
    \centering
    \includegraphics[width=0.9\linewidth,clip]{figures/dark-decoy-overview.png}
    \caption{\textbf{Dark Decoy Overview}\,---\, %
    }
    \label{fig:overview}
\end{figure}
}

### 2019-02-06 paper/paper.tex
parskip bullshit, add tls 1.3 section and address utilization

@@
 \usepackage{tikz}
+%\usepackage{parskip}
 \usepackage{amsmath}
+%\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
+\setlength\parskip{1pt}
+\include{figures}
 
@@
 send the specific IP address to register, but allowing the client arbitrary
-choice also allows censors to register suspected dark decoys and block them if
+choice also allows the censor to register suspected dark decoys and block them if
 they pick up. By using a hash, the censor would have to pre-image the hash to
@@
 
+Once the dark decoy IP address has been selected, the station watches for
+packets destined to that address, and forwards them onto the dark decoy
+\textbf{application}. The station can also optionally ignore packets not from
+the source IP address of the registering client, so that to a probing censor,
+the dark decoy appears to be firewalled off from all but the client.
+
+%-IPv6 vs IPv4 dark decoys subsection?
+
+\subsection{Address utilization}
+
 % Note on IPv6 space? /32 of IPv6 is 96-bits to select...
-We note that IP addresses are selected from unused but still routed address
+Dark decoy IP addresses are selected from unused but still routed address
 space that passes by the ISP. Traffic to unrouted addresses would produce ICMP
@@
 
-Once the dark decoy IP address has been selected, the station watches for
-packets destined to that address, and forwards them onto the dark decoy
-\textbf{application}. The station can also optionally ignore packets not from
-the source IP address of the registering client, so that to a probing censor,
-the dark decoy appears to be firewalled off from all but the client.
+While address utilization in IPv4 is quite high (all blocks have been allocated
+at the RIR level), the fraction of addresses that respond to TCP connections on
+a given port is quite low: even popular ports like 443 (use by TLS) have less
+than 2\% of IPv4 hosts respond to connection requests. This leaves a large
+number of hosts available to use as dark decoys. However, if a client registers
+a dark decoy address that is already happens to be used by an existing host,
+there will be multiple responses when the client tries to connect, and the
+connection will fail. However, this failure is still limited to the registering
+client, as the application only responds to the IP of the client that
+registered. In IPv6, the odds of picking a legitimate host are negligible: with
+a /32 prefix of IPv6, there are $2^{96}$ addresses to choose from.
 
@@
 employed in practice by censors, we consider two alternatives built on TLS.
+
+\FigOverview
 
@@
 \paragraph{Mask Site Selection}
-How do we get the list of masked sites? Alexa list? passive observation?
+
+Selecting which sites to masquerade as must be done carefully to avoid censors
+being able to detect obvious choices. For example, if a small university network
+has a dark decoy in their network that appears to be \texttt{apple.com}, it
+would be easy for a censor to block as a likely non-legitimate host. Likewise,
+if a dark decoy at an IP address pretends to be a domain (\texttt{example.com}) that
+globally resolves to a single different IP address, the censor could also
+identify and block the dark decoy.
+
+\smallskip
+\noindent
+\emph{Nearby sites} - One strategy for selecting mask sites to mimic is to pick websites that are
+legitimately hosted in or near the network of the dark decoy addresses. This
+effectively creates copies of legitimate sites, with the censor unable to
+determine which copies are real and which are the dark decoys. However, as
+mentioned, other signals such as DNS may reveal the true mask site.
+
+\smallskip
+\noindent
+\emph{Alexa sites} -
+An alternative strategy is to use popular sites, such as those from the Alexa
+top million~\cite{alexa} list. As mentioned previously, it may be wise to avoid
+sites that are obviously not hosted in the dark decoy address range, such as
+large companies that run their own datacenters and own their own ASN.
+The list could also be filtered to domains that resolve to different IP
+addresses from different vantage points, making it harder for a censor to know
+if a dark decoy corresponds to a domain's IP.
+
+\smallskip
+\noindent
+\emph{Passive observation} -
+The ISP tap could also collect sites by passively observing DNS requests, TLS
+SNI, or certificates that pass by. This would allow for building a realistic set
+of sites that are plausibly in the vicinity of the dark decoy addresses
+that pass by the tap. It also has the added bonus of being able to discover
+IPv6 addresses that could be used as decoys (for registration), where active
+scanning would be infeasible.
+
+In practice, clients can often try multiple dark decoys/mask sites over
+several attempts, as blocking the client outright may negatively impact other
+unrelated users behind the same network (e.g. in the case of NAT). Thus, even a
+censor that can block most (but not all) mask site only delays access, and
+doesn't prevent it outright.
 
@@
 
-TLS~1.3....
+TLS~1.3~\cite{tls13} offers several features that may greatly simplify dark
+decoy application design. For instance, TLS~1.3 handshakes include encrypted
+certificates, potentially obviating the need to impersonate mask sites.
+Unfortunately, TLS~1.3 currently still sends the SNI in the (plaintext) Client
+Hello, meaning we would still have to choose a realistic domain to fool a
+censor.
 
-%-Registration
-%-Dark decoy selection (seed -> IP)
-%-Connection to Dark Decoy Application (DD App)
-%-IPv6 vs IPv4 dark decoys
+However, there are proposals to encrypt the SNI in the Client Hello~\cite{esni},
+though none have been implemented or deployed as of early 2019. Nonetheless,
+if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for dark
+decoy applications by allowing the domain to remain hidden from the censor.
+While the censor could still try to actively probe with guesses for the SNI,
+servers could respond with generic ``Unknown SNI'' errors. If such responses
+were common for incorrect SNI, the censor's efforts to identify dark decoys
+would be frustrated.
 

### 2019-02-07 application/main.go
WIP: fix non-intercept case

@@ -279,8 +279,6 @@ func handleNewConn(clientConn *net.TCPConn) {
 	finalTargetConn = serverBufConn
 	finalClientConn = clientBufConn
 
-	switchToForgedConnSuccess := false
-
 	decryptedFirstAppData, err := ioutil.ReadAll(inMemTlsConn)
 	if err != nil || len(decryptedFirstAppData) == 0 {
 		logger.Printf("not tagged: %s", err)
@@ -292,23 +290,12 @@ func handleNewConn(clientConn *net.TCPConn) {
 		} else {
 			logger.Printf("flow is tagged")
 			defer targetConn.Close()
-			switchToForgedConnSuccess = true
+			serverBufConn.Close()
 			forgedTlsConn := tls.MakeConnWithCompleteHandshake(
 				clientBufConn, tls.VersionTLS12,
 				cipherSuite, masterSecret, clientRandom[:], serverRandom[:], false)
 			finalClientConn = forgedTlsConn
 			finalTargetConn = targetConn
-		}
-	}
-
-	if switchToForgedConnSuccess {
-		serverBufConn.Close()
-	} else {
-		// send first appdata we read from client to the mask site
-		_, err = serverBufConn.Write(firstAppData)
-		if err != nil {
-			logger.Printf("failed to send appdata to masked host: %v", err)
-			return
 		}
 	}
 

### 2019-02-08 application/main.go
First actually working prototype

@@ -2,6 +2,7 @@ package main
 
 import (
 	"bufio"
+	"bytes"
 	"encoding/binary"
 	"errors"
 	"fmt"
@@ -90,20 +91,17 @@ const (
 	TlsHandshakeTypeNextProtocol       = byte(67)
 )
 
-func getOriginalDst(fd uintptr) (string, error) {
+func getOriginalDst(fd uintptr) (net.IP, error) {
 	const SO_ORIGINAL_DST = 80
-	fmt.Println("[DEBUG] getSockOpt variants:")
-	sockOpt, err := syscall.GetsockoptIPv6Mreq(int(fd), syscall.IPPROTO_IPV6, SO_ORIGINAL_DST)
-	fmt.Println("  ", sockOpt, fd, err)
-	sockOpt2, err := syscall.GetsockoptIPv6Mreq(int(fd), syscall.IPPROTO_IP, SO_ORIGINAL_DST)
-	fmt.Println("  ", sockOpt2, fd, err)
-	sockOpt3, err := syscall.GetsockoptIPMreq(int(fd), syscall.IPPROTO_IP, SO_ORIGINAL_DST)
-	fmt.Println("  ", sockOpt3, fd, err)
-	sockOpt4, err := syscall.GetsockoptIPMreq(int(fd), syscall.IPPROTO_IP, SO_ORIGINAL_DST)
-	fmt.Println("  ", sockOpt4, fd, err)
-
-	// TODO: parse the original dst and return
-	return "", err
+	if sockOpt, err := syscall.GetsockoptIPv6Mreq(int(fd), syscall.IPPROTO_IP, SO_ORIGINAL_DST); err == nil {
+		// parse ipv4
+		return net.IPv4(sockOpt.Multiaddr[4], sockOpt.Multiaddr[5], sockOpt.Multiaddr[6], sockOpt.Multiaddr[7]), nil
+	} else if mtuinfo, err := syscall.GetsockoptIPv6MTUInfo(int(fd), syscall.IPPROTO_IPV6, SO_ORIGINAL_DST); err == nil {
+		// parse ipv6
+		return net.IP(mtuinfo.Addr.Addr[:]), nil
+	} else {
+		return nil, err
+	}
 }
 
 func handleNewConn(clientConn *net.TCPConn) {
@@ -111,27 +109,39 @@ func handleNewConn(clientConn *net.TCPConn) {
 
 	fd, err := clientConn.File()
 	if err != nil {
[…]

### 2019-02-08 src/elligator.rs

@@ -1,16 +1,14 @@
-use std::{mem,panic};
+use std::panic;
 
 use c_api;
 
 extern crate crypto;
 
-use std::error;
 use std::error::Error;
 use util::HKDFKeys;
 use elligator::crypto::aes_gcm::AesGcm;
 use elligator::crypto::aead::AeadDecryptor;
 use elligator::crypto::aes;
-use std::fmt::Debug;
 
 //pub mod rust_tapdance;
 
@@ -29,14 +27,14 @@ fn extract_stego_bytes(in_buf: &[u8], out_buf: &mut [u8])
     assert!(in_buf.len() == 4);
     assert!(out_buf.len() == 3);
 
-    let x = ((in_buf[0] & 0x3f) as u32) * (64*64*64) +
-            ((in_buf[1] & 0x3f) as u32) * (64*64) +
-            ((in_buf[2] & 0x3f) as u32) * (64) +
-            ((in_buf[3] & 0x3f) as u32);
+    let x = ((in_buf[0] & 0x3f) as u32) * (64 * 64 * 64) +
+        ((in_buf[1] & 0x3f) as u32) * (64 * 64) +
+        ((in_buf[2] & 0x3f) as u32) * (64) +
+        ((in_buf[3] & 0x3f) as u32);
 
     out_buf[0] = ((x >> 16) & 0xff) as u8;
-    out_buf[1] = ((x >> 8 ) & 0xff) as u8;
-    out_buf[2] = ((x      ) & 0xff) as u8;
+    out_buf[1] = ((x >> 8) & 0xff) as u8;
+    out_buf[2] = ((x) & 0xff) as u8;
 }
 
 //out: &mut [u8; STEGO_DATA_LEN]) -> i32
@@ -51,66 +49,96 @@ pub fn extract_payloads(secret_key: &[u8], tls_record: &[u8]) -> (Result<(HKDFKe
 
     // This fn indexes a lot of slices with computed offsets; panics possible!
     let result = panic::catch_unwind(||
-    {
-        // TLS record: 1 byte of 'content type', 2 of 'version', 2 of 'length',
-        //               and then [length] bytes of 'payload'
-        //======================================================================
-        //let content_type = tls_record[0];
-        //let tls_version = u8u8_to_u16(tls_record[1], tls_record[2]);
-
-        let tls_payload = &tls_record[5..tls_record.len()];
-        //======================================================================
-        // Starting from 92 byte from the end of the TLS payload extract
[…]

### 2019-02-08 src/flow_tracker.rs

@@ -91,17 +91,6 @@ impl FlowNoSrcPort {
     pub fn from_flow(f: &Flow) -> FlowNoSrcPort {FlowNoSrcPort{src_ip: f.src_ip, dst_ip: f.dst_ip, dst_port: f.dst_port}}
 }
 
-#[derive(Copy, Clone)]
-enum FlowState
-{
-    InTLSHandshake,
-    // After SYN, before first app packet (might signal us)
-    ActiveTag(u64),     // Upon a signal, we create the specified flow
-    // client -> client-specified dark decoy
-    // and tag it with this.
-    // The u64 is the time (ns) that this times out.
-}
-
 pub struct SchedEvent
 {
     // Nanoseconds since an unspecified epoch (precise_time_ns()).

### 2019-02-08 src/lib.rs

@@ -12,7 +12,7 @@ extern crate errno;
 extern crate radix; // https://github.com/refraction-networking/radix
 extern crate tuntap; // https://github.com/ewust/tuntap.rs
 extern crate zmq;
-
+extern crate protobuf;
 #[macro_use]
 extern crate redis;
 
@@ -37,6 +37,7 @@ pub mod flow_tracker;
 pub mod process_packet;
 pub mod util;
 pub mod session;
+pub mod signalling;
 
 use session::SessionState;
 

### 2019-02-08 src/process_packet.rs

@@ -9,13 +9,17 @@ use pnet::packet::ip::IpNextHeaderProtocols;
 use pnet::packet::ipv4::Ipv4Packet;
 use pnet::packet::ipv6::Ipv6Packet;
 use pnet::packet::tcp::{TcpPacket,TcpFlags};
-use std::net::{IpAddr,Ipv6Addr,Ipv4Addr};
+use std::net::IpAddr;
 
+use std::u8;
 //use elligator;
 use flow_tracker::{Flow, FlowNoSrcPort};
 use PerCoreGlobal;
 use util::{IpPacket, DDIpSelector};
 use elligator;
+use protobuf;
+use signalling::ClientToStation;
+
 
 const TLS_TYPE_APPLICATION_DATA: u8 = 0x17;
 //const SQUID_PROXY_ADDR: &'static str = "127.0.0.1";
@@ -188,9 +192,6 @@ impl PerCoreGlobal
         }
 
         let dd_flow = FlowNoSrcPort::from_flow(&flow);
-        if flow.src_ip == IpAddr::from([128u8, 138u8, 244u8, 42u8]) {
-            debug!("dd_flow {} {:?}", dd_flow, self.flow_tracker.dark_decoy_flows);
-        }
         if self.flow_tracker.is_registered_dark_decoy(&dd_flow) {
             // Tagged flow! Forward packet to whatever
             debug!("Tagged flow packet {}", flow);
@@ -267,7 +268,7 @@ impl PerCoreGlobal
         match elligator::extract_payloads(&self.priv_key, &tcp_pkt.payload()) {
             Ok(res) => {
                 let dd_ip_selector = match DDIpSelector::new(&vec![String::from("192.122.190.0/24"),
-                                                                String::from("2001:48a8:687f:1::/64")]) {
+                                                                   String::from("2001:48a8:687f:1::/64")]) {
                     // TODO: move this initialization up
                     Ok(dd) => dd,
                     Err(e) => {
@@ -284,12 +285,32 @@ impl PerCoreGlobal
                     }
                 };
 
-                // Send dark_decoy_seed / dst_ip to ZMQ
-                //pub dark_decoy_seed: [u8; 16],
-                let mut msg = vec![0; 16+16];
-                msg[..16].clone_from_slice(&res.0.dark_decoy_seed);
+                let mut c2s = match protobuf::parse_from_bytes::<ClientToStation>
+                    (&res.2) {
+                    Ok(pb) => pb,
+                    Err(e) => {
[…]

### 2019-02-08 src/signalling.rs

@@ -1,0 +1,3223 @@
+// This file is generated. Do not edit
+// @generated
+
+// https://github.com/Manishearth/rust-clippy/issues/702
+#![allow(unknown_lints)]
+#![allow(clippy)]
+
+#![cfg_attr(rustfmt, rustfmt_skip)]
+
+#![allow(box_pointers)]
+#![allow(dead_code)]
+#![allow(missing_docs)]
+#![allow(non_camel_case_types)]
+#![allow(non_snake_case)]
+#![allow(non_upper_case_globals)]
+#![allow(trivial_casts)]
+#![allow(unsafe_code)]
+#![allow(unused_imports)]
+#![allow(unused_results)]
+
+use protobuf::Message as Message_imported_for_functions;
+use protobuf::ProtobufEnum as ProtobufEnum_imported_for_functions;
+
+#[derive(PartialEq,Clone,Default)]
+pub struct PubKey {
+    // message fields
+    key: ::protobuf::SingularField<::std::vec::Vec<u8>>,
+    field_type: ::std::option::Option<KeyType>,
+    // special fields
+    unknown_fields: ::protobuf::UnknownFields,
+    cached_size: ::protobuf::CachedSize,
+}
+
+// see codegen.rs for the explanation why impl Sync explicitly
+unsafe impl ::std::marker::Sync for PubKey {}
+
+impl PubKey {
+    pub fn new() -> PubKey {
+        ::std::default::Default::default()
+    }
+
+    pub fn default_instance() -> &'static PubKey {
+        static mut instance: ::protobuf::lazy::Lazy<PubKey> = ::protobuf::lazy::Lazy {
+            lock: ::protobuf::lazy::ONCE_INIT,
+            ptr: 0 as *const PubKey,
+        };
+        unsafe {
+            instance.get(PubKey::new)
+        }
+    }
+
+    // optional bytes key = 1;
+
+    pub fn clear_key(&mut self) {
+        self.key.clear();
+    }
+
+    pub fn has_key(&self) -> bool {
+        self.key.is_some()
+    }
+
+    // Param is passed by value, moved
+    pub fn set_key(&mut self, v: ::std::vec::Vec<u8>) {
+        self.key = ::protobuf::SingularField::some(v);
+    }
+
+    // Mutable pointer to the field.
+    // If field is not initialized, it is initialized with default value first.
+    pub fn mut_key(&mut self) -> &mut ::std::vec::Vec<u8> {
+        if self.key.is_none() {
+            self.key.set_default();
+        }
[…]

### 2019-02-08 src/util.rs

@@ -145,6 +145,7 @@ pub struct HKDFKeys
     pub fsp_iv: [u8; 12],
     pub vsp_key: [u8; 16],
     pub vsp_iv: [u8; 12],
+    pub new_master_secret: [u8; 48],
     pub dark_decoy_seed: [u8; 16],
 }
 
@@ -157,22 +158,24 @@ impl HKDFKeys
         let kdf = hkdf::Hkdf::<sha2::Sha256>::extract(Some(salt), shared_secret);
         let info = [0u8; 0];
 
-        let mut output = [0u8; 72];
+        let mut output = [0u8; 120];
         kdf.expand(&info, &mut output)?;
 
         let mut fsp_key = [0u8; 16];
         let mut fsp_iv = [0u8; 12];
         let mut vsp_key = [0u8; 16];
         let mut vsp_iv = [0u8; 12];
+        let mut new_master_secret = [0u8; 48];
         let mut dark_decoy_seed = [0u8; 16];
 
         fsp_key.copy_from_slice(&output[0..16]);
         fsp_iv.copy_from_slice(&output[16..28]);
         vsp_key.copy_from_slice(&output[28..44]);
         vsp_iv.copy_from_slice(&output[44..56]);
-        dark_decoy_seed.copy_from_slice(&output[56..72]);
+        new_master_secret.copy_from_slice(&output[56..104]);
+        dark_decoy_seed.copy_from_slice(&output[104..120]);
 
-        Ok(HKDFKeys { fsp_key, fsp_iv, vsp_key, vsp_iv, dark_decoy_seed }) // syntax is very edgy and not at all confusing
+        Ok(HKDFKeys { fsp_key, fsp_iv, vsp_key, vsp_iv, new_master_secret, dark_decoy_seed }) // syntax is very edgy and not at all confusing
     }
 }
 

### 2019-02-08 src/flow_tracker.rs
increase dd timeout

@@ -118,7 +118,7 @@ pub struct FlowTracker
 
 // Amount of time that we timeout all flows
 const TIMEOUT_TRACKED_NS: u64 = 30 * 1000 * 1000 * 1000;
-const TIMEOUT_DARK_DECOYS_NS: u64 = 30 * 1000 * 1000 * 1000;
+const TIMEOUT_DARK_DECOYS_NS: u64 = 300 * 1000 * 1000 * 1000;
 //const FIN_TIMEOUT_NS: u64 = 2*1000*1000*1000;
 
 fn get_redis_conn() -> redis::Connection

### 2019-02-10 paper/paper.tex
intro first draft

@@
 
-Censorship circumvention still important
--More countries blocking
--Existing countries blocking more
+%Censorship circumvention still important
+%-More countries blocking
+%-Existing countries blocking more
+Internet censorship continues to hamper social progress throughout the world.
+Over half of the global Internet population
+now live in countries that block political, social, or religious content
+online~\cite{fotn2018} as governments continue to expand their censorship
+policies and programs.
 
-Existing circumvention strategies on shaky ground
--domain fronting going away
--active probing of existing proxies
--Cenosrs fingerprinting known protocols
+%Existing circumvention strategies on shaky ground
+%-domain fronting going away
+%-active probing of existing proxies
+%-Cenosrs fingerprinting known protocols
+Meanwhile, strategies to circumvent censorship using proxies have suffered many
+recent setbacks. Many previously popular proxies are no longer functional due to
+censors evolving new ways to block them~\cite{ensafi-tor,great-cannon},
+or because they rely on temperamental
+infrastructure. For example, domain fronting was a popular circumvention
+strategy used by meek (in Tor), as well as the Signal secure messaging app to
+get around censorship in countries it was
+blocked~\cite{domain-fronting,signal,signal-domain-fronting}.
+But in May~2018, Google and Amazon made both technical and policy changes to
+their cloud infrastructures that removed support for domain
+fronting~\cite{aws-front}. While meek
+continues to use other cloud providers that (for now) continue to allow domain
+fronting, Signal abandoned the strategy altogether~\cite{signal-back-on-front}.
+%Combined with censors' constant improvements in discovery and blocking
+%techniques~\cite{ensafi-tor,great-cannon}, ...
 
-Importance of Refraction Networking
--what it is, how it solves many of the above problems
--acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
+%Importance of Refraction Networking
+%-what it is, how it solves many of the above problems
+%-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
+One emerging technique is Refraction Networking (also known as ``Decoy
+Routing''), which places proxies at cooperating Internet Service Providers
+(ISPs) outside censoring countries~\cite{refraction-site}. Clients access the
+proxies by connecting to unblocked ``decoy'' sites such that the packets pass by
+the ISP proxy, which intercepts and injects responses as the decoy site.
+Censors cannot easily block access without also blocking
+legitimate connections to the decoy sites, which may be costly for the censor.
+However, deploying such schemes in practice is more difficult than existing proxies:
+convincing ISPs to deploy proxies in their production network is a significant
+operational hurdle. To date, only one of six Refraction
+Networking schemes has been deployed in practice by a large ISP:
+TapDance~\cite{tadance}, a
+Refraction Networking protocol that removes the need for inline
+flow-blocking~\cite{frolov2017isp}.
 
-Challenges remain in Tapdance:
--Censor can fingerprint decoy sites
--Decoys themselves are limited (e.g. a few dozen in many cases)
--Can't have long-lived connections (performance and observability issue)
--Other performance limits (upload limit, TCP window size)
+%Challenges remain in Tapdance:
+%-Censor can fingerprint decoy sites
+%-Decoys themselves are limited (e.g. a few dozen in many cases)
+%-Can't have long-lived connections (performance and observability issue)
+%-Other performance limits (upload limit, TCP window size)
+But in order to be deployed, TapDance makes an aggressive tradeoff
+between observability by censors for the sake of ease of deployment.
+For instance, TapDance's passive ``on the side'' architecture
+does not resist active probing attacks, where the censor can send packets that
+confirm whether or not a suspected connection is indeed a TapDance connection.
+The use of real-world decoy sites also presents practical problems: If
+decoys are limited or not particularly important, it may be easy for a
+censor to block them altogether without much collateral damage. In addition, 
+TapDance has several performance limitations due to its interaction with
+real decoys. For example, TapDance clients' individual connection duration and upload
+capacities are limited due to the interaction with the decoy's TCP and TLS stack
+behavior. This forces TapDance to multiplex long-lived proxy connections over
+several repeated shorter-duration decoy connections, which increases overhead and may
+produce a connection pattern that is visible to censors.
 
-Dark decoys solve these issues
--Create new decoys from ``dark'' (unused) address space
--Clients register (via TapDance-like or other robust protocol (email, blockchain, whatever))
--Connect to custom IP address, talk whatever protocol client/station agrees on
+\medskip
 
-One-time use address advantages:
--Censor cannot actively probe ahead of time (especially in IPv6), making it hard to fingerprint
--Decoys are now virtually unlimited (or limited only by address space)
--Connection can live as long as we want
--No pesky TCP/TapDance-y limits
+%Dark decoys solve these issues
+%-Create new decoys from ``dark'' (unused) address space
+%-Clients register (via TapDance-like or other robust protocol (email, blockchain, whatever))
+%-Connect to custom IP address, talk whatever protocol client/station agrees on
+In this paper, we present Dark Decoys, a new Refraction Networking protocol that
+solves these issues, while maintaining the easy-to-deploy model of TapDance
+(i.e. a passive network tap). In our scheme, clients register new fictitious
+decoys in the ``dark'' or unused address space of the deploying ISP. Once
+registered, clients can connect to these dark decoy IP addresses as if they were
+real hosts. The ISP station acts as the other end of these connections, and responds as
+if it were a legitimate site or service. To the censor, these dark decoys appear
+as legitimate sites or services, and even active probes won't reveal
+information that would allow the censor to block them.
 
-Requirements/Challenges
--Censor can't be able to distinguish between dark decoy and legitimate hosts
-    (otherwise they block all dark decoys)
-    -Includes active probing: censor shouldn't be able to register existing IP
--Disruption avoidence: Want to pickup even for used addresses
-    -Otherwise, censor probes to find truly unused address space and blocks
-    -But can't disrupt legitimate services
-    -Can overcome by limiting pickup to the registering client (but spoofing challenges...)
-    -Note: also likely solved by the client-sends-SNI in the Mask site application...
+%One-time use address advantages:
+%-Censor cannot actively probe ahead of time (especially in IPv6), making it hard to fingerprint
+%-Decoys are now virtually unlimited (or limited only by address space)
+%-Connection can live as long as we want
+%-No pesky TCP/TapDance-y limits
+Dark decoys are cheap to create, allowing for discardable \textbf{one-time use}
+addresses to be used by clients. This greatly increases the cost for censors to
+block, as they must detect and block in real time. Meanwhile, even a censor that
+can detect 90\% of dark decoys does not significantly increase the cost to the
+circumvention system, giving dark decoys an advantage in the censor/circumventor
+cat-and-mouse game.
+We support both IPv4 and IPv6 dark decoys, though we note they are especially
+powerful in IPv6 where censors cannot exhaustively scan ahead of time to
+identify addresses that change behavior.
+Because we fully control the server side, dark decoy connections can live as
+long as needed, without the upload or timing limits faced by TapDance.
+
+%TODO:
+%Requirements/Challenges
+%-Censor can't be able to distinguish between dark decoy and legitimate hosts
+%    (otherwise they block all dark decoys)
+%    -Includes active probing: censor shouldn't be able to register existing IP
+%-Disruption avoidence: Want to pickup even for used addresses
+%    -Otherwise, censor probes to find truly unused address space and blocks
+%    -But can't disrupt legitimate services
+%    -Can overcome by limiting pickup to the registering client (but spoofing challenges...)
+%    -Note: also likely solved by the client-sends-SNI in the Mask site application...
+
+% We implement it, it works...
+We implement our dark decoy protocol under the same model as TapDance using
+only a passive tap at an ISP. Furthermore, our protocol also works with
+asymmetric routing (i.e. when the tap can only see packets from but not to the
+client). We test our deployment on a 10~Gbps real-world ISP testbed similar to the
+TapDance deployment~\cite{frolov2017isp}, and evaluate the performance and
+observability compared to TapDance.
 

### 2019-02-10 paper/paper.tex
add threat model

@@
 \section{Threat Model}
-% 0.5 page
+% 0.25 page
 
--Censor can block arbitrary addresses (or networks), but faces a cost in doing so (collateral damage)
--Censor can know what network deploys the dark decoy station
--Censor knows the dark decoy prefixes distributed in the client, but they contain legitimate hosts
--Censor can use the client
--Censor can active probe limited sets, but cannot enumerate the entire prefix (i.e. IPv6 /32)
--Censor can active probe or (p)replay connections it suspects
+Our deployment model is identical to that of TapDance: we only require a passive
+tap at the deploying ISP, and the ability to inject (spoofed) traffic from dark
+decoy sites. However, we assume a stronger threat model for the adversary than
+TapDance, as our design resists active attacks.
+
+We assume the censor can block arbitrary IP addresses and networks, but faces a
+cost in doing so if it blocks potentially useful resources. In particular, we
+assume it is difficult for the censor to have complete knowledge of legitimate
+addresses used, and so instead resorts to a blacklist approach to blocking
+proxies and objectionable content.
+Whitelists are expensive for censors to maintain and can stifle
+innovation, and are rarely employed by censors.
+
+We assume that the censor can know what network the dark decoy station(s) are
+deployed in and the prefixes dark decoys are selected from, but that blocking those
+networks outright brings a collateral
+damage the censor is unwilling to suffer. Instead, the censor aims to identify
+the addresses that are dark decoys, and block only those.
+
+We assume the censor can use the client to register and access its own dark
+decoys, but that these will not reveal the dark decoys of other users. The
+censor can also actively probe addresses that it sees users accessing, but can
+not enumerate the entire dark decoy prefix (e.g. a /32 IPv6 prefix contains
+$2^{96} addresses$).
+
+Finally, we assume the censor can replay or preplay any connections that it
+suspects involve dark decoys (or their registration) in an attempt to confirm.
+However, the censor wishes to avoid disrupting any connections before it
+knows for certain they are dark decoy ones, lest they disrupt legitimate
+connections. This means that injecting false data or corrupting TLS sessions is
+outside the scope of the censor, but that the censor can send non-disruptive
+probes (such as stale TCP acknowledgements or other packets that would normally
+be ignored). We emphasize that TapDance is observable by censors that can send
+TCP packets in suspected connections, but that our protocol is robust against
+this class of censor.
+
+%-Censor can block arbitrary addresses (or networks), but faces a cost in doing so (collateral damage)
+%-Censor can know what network deploys the dark decoy station
+%-Censor knows the dark decoy prefixes distributed in the client, but they contain legitimate hosts
+%-Censor can use the client
+%-Censor can active probe limited sets, but cannot enumerate the entire prefix (i.e. IPv6 /32)
+%-Censor can active probe or (p)replay connections it suspects
 

### 2019-02-11 paper/figures.tex
add high level figure

@@
 }
+
+\newcommand{\FigHighLevel}{
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.9\linewidth,clip]{figures/high-level.png}
+    \caption{\textbf{Dark Decoys}\,---\, %
+    After registering, clients connect to unused (``dark'') addresses that pass
+        by a cooperating ISP proxy station. The station communicates with the client
+        as if it were a host at the particular address. To the censor, this
+        communication appears to be a legitimate connection to a real host,
+        making it difficult to distinguish from real hosts and block.
+    }
+    \label{fig:overview}
+\end{figure}
+}

### 2019-02-11 paper/figures.tex
add comparison table

--- 2019-02-06 paper/figures.tex
@@
 }
+
+\newcommand{\FigHighLevel}{
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.9\linewidth,clip]{figures/high-level.png}
+    \caption{\textbf{Dark Decoys}\,---\, %
+    After registration, clients connect to unused (``dark'') addresses that pass
+        by a cooperating ISP proxy station. The station communicates with the client
+        as if it were the host at that address. To the censor, this
+        connection appears to be with a legitimate one to a real host,
+        making it difficult to distinguish from real hosts and block.
+    }
+    \label{fig:overview}
+\end{figure}
+}
+
+\newcommand{\yes}{\CIRCLE}
+\newcommand{\no}{\Circle}
+\newcommand{\maybe}{\LEFTcircle}
+
+\newcommand{\TabCompare}{
+\begin{table*}[ht]
+    \centering
+    \begin{tabular}{l|cccccccc}
+            % Multiflow? Waterfall?
+            & \rot{Telex~\cite{telex}} &
+            \rot{Cirripede~\cite{cirripede}} &
+            \rot{Decoy Routing~\cite{curveball}} &
+            \rot{TapDance~\cite{tapdance}} & \rot{Rebound~\cite{rebound}} & \rot{Slitheen~\cite{slitheen}} & \rot{Waterfall~\cite{waterfall}} & \rot{\textbf{Dark Decoys}} \\
+            \hline
+                                      %Telex Cirr  DR     TD      RB    Slth   Water  DD
+            No inline blocking        & \no & \no  & \yes & \no  & \no  & \no  & \no  & \yes \\
+            Handles asym. routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
+            Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
+            Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
+            Traffic analysis resitant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
+            Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
+    \end{tabular}
+    %\caption{\textbf{Refraction Networking schemes}\,---\,}
+    \label{tab:compare}
+\end{table*}
+}

### 2019-02-12 paper/paper.tex
add comparison table
add compare section

@@
 \usepackage{amsmath}
+\usepackage{wasysym}
 %\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
 \setlength\parskip{1pt}
+\usepackage{graphicx} % http://ctan.org/pkg/graphicx
+\usepackage{booktabs} % http://ctan.org/pkg/booktabs
+\usepackage{xparse}   % http://ctan.org/pkg/xparse%don't print date
+\NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
 \include{figures}
@@
 
-%don't print date
 \date{}
@@
 produce a connection pattern that is visible to censors.
+
+\FigHighLevel
 
@@
 
+\subsubsection{WebRTC}
+
+Dark Decoys could also pretend to be clients instead of servers. This may
+potentially give censors less to block on, as actively probing clients is common
+to return few or no open ports. Nonetheless, a censor may be hesitant to block
+client-to-client communication, as it could block peer-to-peer applications as
+well as many video conferencing protocols. WebRTC is a
+natural choice for a client-to-client protocol in censorship circumvention,
+and is used in existing censorship circumvention schemes like
+Snowflake~\cite{snowflake}. Dark decoy applications could also use WebRTC as the
+application protocol, convincing the censor that two clients are communicating.
+
 \section{Implementation}
@@
 
-\section{Attacks and Defenses}
+\section{Discussion}
+
+\subsection{Comparison to Prior Schemes}
+
+Since 2011, there have been several proposed Refraction Networking schemes.
+Telex~\cite{telex}, Cirripede~\cite{cirripede} and Decoy
+Routing~\cite{curveball} are ``first generation'' protocols with nearly
+identical features. These designs require inline flow blocking at the ISP to
+allow the station to intercept flows with detected tags and act as the decoy
+host for them. However, inline-blocking is difficult for ISPs to deploy, as it
+requires special-purpose hardware to be placed inline with production traffic,
+introducing risk of failures and outages that may be expensive for the ISP
+and potentially violate their contractual obligations (SLAs).
+
+TapDance~\cite{tapdance} solves the issue of inline-blocking by coercing the
+decoy into staying silent, and allowing the station to respond instead. However,
+as previously described, this trick comes at a cost: the decoy only stays silent
+for a short timeout (typically 30-120 seconds), and limits the amount of data
+the client can send before it responds. TapDance clients must keep connections
+short and repeatedly reconnect to decoys, increasing overhead and potentially
+alerting censors with this pattern. Dark Decoys addresses this issue and allows
+clients to maintain long-lived connections to the dark decoy.
+
+Rebound~\cite{rebound} and Waterfall~\cite{waterfall} both focus on routing
+asymmetries and routing attacks by the censor. Rebound modifies the client's
+packets on the way to the decoy, and uses error pages on the decoy site to
+reflect data back to the client. Waterfall only observes and modifies the
+decoy-to-client traffic, similarly using error pages on the decoy to reflect
+communication from the client to the station. These schemes also provide some
+resistance to traffic analysis, as they use the real decoy to reflect data to
+the user. Thus, the TCP/TLS behavior seen by the censor more closely matches
+that of a legitimate decoy connection. However, latency and other packet-timing
+characteristics may be observable, and both schemes require some form of inline
+flow blocking.
+
+Slitheen~\cite{slitheen} focuses on addressing observability by replacing
+data in packets sent by the legitimate decoy. Thus, even the packet timings and
+sizes of a Slitheen connection match that of a legitimate decoy connection.
+However, Slitheen also requires inline-blocking, and introduces a large overhead
+as it has to wait for the subset of data-carrying packets from the decoy that
+Slitheen can safely replace. We note that the Slitheen model of mimicry is
+compatible with Dark Decoys, as we could use Slitheen as the application
+protocol. Despite using a passive tap, our scheme is effectively inline to the
+dark decoy (which won't otherwise respond).
+
+Dark Decoys allow a large amount of flexibility compare to previous schemes.
+Because we have significant degrees of freedom in choosing the specific
+application the dark decoy will mimic or talk, our scheme can combine the best
+of existing Refraction Networking protocols to achieve high performance, be easy
+to deploy, and
+also be resistant to active attacks such as replaying or probing by the censor.
+Table~\ref{tab:compare} lists the existing Refraction Networking schemes and
+their features, as compared to Dark Decoys.
+
+\TabCompare
+
+\subsection{Attacks and Defenses}
 % 1 page
@@
     -Verify knowledge of seed (but how to respond when verification fails?)
+-ICMP
 

### 2019-02-12 paper/paper.tex
minor comments

--- 2019-02-10 paper/paper.tex
@@
 \usepackage{usenix2019_v3}
+
+% For submission make this a noop
+\newcommand{\note}[2]{\textit{[#1: #2]}}
+\newcommand{\nikita}[1]{\note{nikita}{#1}}
 
@@
 
-%Censorship circumvention still important
-%-More countries blocking
-%-Existing countries blocking more
-Internet censorship continues to hamper social progress throughout the world.
-Over half of the global Internet population
-now live in countries that block political, social, or religious content
-online~\cite{fotn2018} as governments continue to expand their censorship
-policies and programs.
+Censorship circumvention still important
+-More countries blocking
+-Existing countries blocking more
 
-%Existing circumvention strategies on shaky ground
-%-domain fronting going away
-%-active probing of existing proxies
-%-Cenosrs fingerprinting known protocols
-Meanwhile, strategies to circumvent censorship using proxies have suffered many
-recent setbacks. Many previously popular proxies are no longer functional due to
-censors evolving new ways to block them~\cite{ensafi-tor,great-cannon},
-or because they rely on temperamental
-infrastructure. For example, domain fronting was a popular circumvention
-strategy used by meek (in Tor), as well as the Signal secure messaging app to
-get around censorship in countries it was
-blocked~\cite{domain-fronting,signal,signal-domain-fronting}.
-But in May~2018, Google and Amazon made both technical and policy changes to
-their cloud infrastructures that removed support for domain
-fronting~\cite{aws-front}. While meek
-continues to use other cloud providers that (for now) continue to allow domain
-fronting, Signal abandoned the strategy altogether~\cite{signal-back-on-front}.
-%Combined with censors' constant improvements in discovery and blocking
-%techniques~\cite{ensafi-tor,great-cannon}, ...
+Existing circumvention strategies on shaky ground
+-domain fronting going away
+-active probing of existing proxies
+-Cenosrs fingerprinting known protocols
 
-%Importance of Refraction Networking
-%-what it is, how it solves many of the above problems
-%-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
-One emerging technique is Refraction Networking (also known as ``Decoy
-Routing''), which places proxies at cooperating Internet Service Providers
-(ISPs) outside censoring countries~\cite{refraction-site}. Clients access the
-proxies by connecting to unblocked ``decoy'' sites such that the packets pass by
-the ISP proxy, which intercepts and injects responses as the decoy site.
-Censors cannot easily block access without also blocking
-legitimate connections to the decoy sites, which may be costly for the censor.
-However, deploying such schemes in practice is more difficult than existing proxies:
-convincing ISPs to deploy proxies in their production network is a significant
-operational hurdle. To date, only one of six Refraction
-Networking schemes has been deployed in practice by a large ISP:
-TapDance~\cite{tadance}, a
-Refraction Networking protocol that removes the need for inline
-flow-blocking~\cite{frolov2017isp}.
+Importance of Refraction Networking
+-what it is, how it solves many of the above problems
+-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
 
-%Challenges remain in Tapdance:
-%-Censor can fingerprint decoy sites
-%-Decoys themselves are limited (e.g. a few dozen in many cases)
-%-Can't have long-lived connections (performance and observability issue)
-%-Other performance limits (upload limit, TCP window size)
-But in order to be deployed, TapDance makes an aggressive tradeoff
-between observability by censors for the sake of ease of deployment.
-For instance, TapDance's passive ``on the side'' architecture
-does not resist active probing attacks, where the censor can send packets that
-confirm whether or not a suspected connection is indeed a TapDance connection.
-The use of real-world decoy sites also presents practical problems: If
-decoys are limited or not particularly important, it may be easy for a
-censor to block them altogether without much collateral damage. In addition, 
-TapDance has several performance limitations due to its interaction with
-real decoys. For example, TapDance clients' individual connection duration and upload
-capacities are limited due to the interaction with the decoy's TCP and TLS stack
-behavior. This forces TapDance to multiplex long-lived proxy connections over
-several repeated shorter-duration decoy connections, which increases overhead and may
-produce a connection pattern that is visible to censors.
+Challenges remain in Tapdance:
+-Censor can fingerprint decoy sites
+-Decoys themselves are limited (e.g. a few dozen in many cases)
+-Can't have long-lived connections (performance and observability issue)
+-Other performance limits (upload limit, TCP window size)
 
-\medskip
+Dark decoys solve these issues
+-Create new decoys from ``dark'' (unused) address space
+-Clients register (via TapDance-like or other robust protocol (email, blockchain, whatever))
+-Connect to custom IP address, talk whatever protocol client/station agrees on
 
-%Dark decoys solve these issues
-%-Create new decoys from ``dark'' (unused) address space
-%-Clients register (via TapDance-like or other robust protocol (email, blockchain, whatever))
-%-Connect to custom IP address, talk whatever protocol client/station agrees on
-In this paper, we present Dark Decoys, a new Refraction Networking protocol that
-solves these issues, while maintaining the easy-to-deploy model of TapDance
-(i.e. a passive network tap). In our scheme, clients register new fictitious
-decoys in the ``dark'' or unused address space of the deploying ISP. Once
-registered, clients can connect to these dark decoy IP addresses as if they were
-real hosts. The ISP station acts as the other end of these connections, and responds as
-if it were a legitimate site or service. To the censor, these dark decoys appear
-as legitimate sites or services, and even active probes won't reveal
-information that would allow the censor to block them.
+One-time use address advantages:
+-Censor cannot actively probe ahead of time (especially in IPv6), making it hard to fingerprint
+-Decoys are now virtually unlimited (or limited only by address space)
+-Connection can live as long as we want
+-No pesky TCP/TapDance-y limits
 
-%One-time use address advantages:
-%-Censor cannot actively probe ahead of time (especially in IPv6), making it hard to fingerprint
-%-Decoys are now virtually unlimited (or limited only by address space)
-%-Connection can live as long as we want
-%-No pesky TCP/TapDance-y limits
-Dark decoys are cheap to create, allowing for discardable \textbf{one-time use}
-addresses to be used by clients. This greatly increases the cost for censors to
-block, as they must detect and block in real time. Meanwhile, even a censor that
-can detect 90\% of dark decoys does not significantly increase the cost to the
-circumvention system, giving dark decoys an advantage in the censor/circumventor
-cat-and-mouse game.
-We support both IPv4 and IPv6 dark decoys, though we note they are especially
-powerful in IPv6 where censors cannot exhaustively scan ahead of time to
-identify addresses that change behavior.
-Because we fully control the server side, dark decoy connections can live as
-long as needed, without the upload or timing limits faced by TapDance.
-
-%TODO:
-%Requirements/Challenges
-%-Censor can't be able to distinguish between dark decoy and legitimate hosts
-%    (otherwise they block all dark decoys)
-%    -Includes active probing: censor shouldn't be able to register existing IP
-%-Disruption avoidence: Want to pickup even for used addresses
-%    -Otherwise, censor probes to find truly unused address space and blocks
-%    -But can't disrupt legitimate services
-%    -Can overcome by limiting pickup to the registering client (but spoofing challenges...)
-%    -Note: also likely solved by the client-sends-SNI in the Mask site application...
-
-% We implement it, it works...
-We implement our dark decoy protocol under the same model as TapDance using
-only a passive tap at an ISP. Furthermore, our protocol also works with
-asymmetric routing (i.e. when the tap can only see packets from but not to the
-client). We test our deployment on a 10~Gbps real-world ISP testbed similar to the
-TapDance deployment~\cite{frolov2017isp}, and evaluate the performance and
-observability compared to TapDance.
+Requirements/Challenges
+-Censor can't be able to distinguish between dark decoy and legitimate hosts
+    (otherwise they block all dark decoys)
+    -Includes active probing: censor shouldn't be able to register existing IP
+-Disruption avoidence: Want to pickup even for used addresses
+    -Otherwise, censor probes to find truly unused address space and blocks
+    -But can't disrupt legitimate services
+    -Can overcome by limiting pickup to the registering client (but spoofing challenges...)
+    -Note: also likely solved by the client-sends-SNI in the Mask site application...
 
@@
 key, cannot derive the shared secret, preventing it from being able to decrypt
-the message.
+the message, or learn of its existence.
 
@@
 they pick up. By using a hash, the censor would have to pre-image the hash to
-obtain a seed it could use to register for a desired IP address. It also gives a
+obtain a seed it could use to register for a desired IP address. \nikita{Are we claiming that this kind of enumeration is hard to do in IPv4?} It also gives a
 secret (the seed) that only the client and station know, even after the client
@@
 a /32 prefix of IPv6, there are $2^{96}$ addresses to choose from.
+\nikita{/32 is pretty big, e.g. UIUC only has a /48}
 
@@
 To evade censors, we must send a plausible SNI value (sending no SNI is
-uncommon and easily blocked---only 1\% of TLS connections do not carry the
+uncommon and easily blocked---only 1\% of TLS connections\nikita{qualify this as being true in a particular sample} do not carry the
 SNI extension~\cite{tls-fingerprint}), and we must have the server respond with

### 2019-02-12 paper/paper.tex
add attack section, needs more

--- 2019-02-12 paper/paper.tex
@@
 \subsection{Address utilization}
+% TODO:Can be better: story for v4, these are some problems, here's what it
+% looks like in v6
 
@@
 
--Fingerprinting Masked site vs Dark decoy application
--Active probing TLS connection
-    -Block access unless from registering source IP
-        -cite GFW taking over client IPs for active probing of old obfs
-    -Verify knowledge of seed (but how to respond when verification fails?)
--ICMP
+There are many attacks a censor might attempt to either prevent dark decoys from
+being registered or used.
+
+\paragraph{Blocking registration}
+To make registration more difficult, censors could block TLS connections to all of the
+limited decoys available in a deployment. Using TapDance's current deployment,
+this would involve blocking over 1500 sites. We note that such an attack would
+completely disable all existing Refraction Networking schemes, as none work
+without being able to access legitimate decoys past the station. In dark decoys,
+this would only block new registrations, and would not impact users that
+previously registered. Furthermore, registrations could also occur over email,
+or over lower-bandwidth covert channels, such as port (or even IP) knocking past
+the station, that would be more difficult for the censor to block.
+%Cirripede previously used a registration protocol that sent covert information via initial
+%sequence numbers in arbitrary TCP connections, though we note this solution
+%generally requires clients to have root access to their device to control the
+%initial sequence numbers. Since most mobile users do not have such control, we
+%suggest other methods be used instead.
+
+\paragraph{Scanning masked sites}
+The censor could also attempt to fingerprint the masked site and compare it to a
+suspected dark decoy application. For instance, if a dark decoy IP responds as
+pretending to be \texttt{example.com}, the censor could scan or probe real instances
+of \texttt{example.com} on different ports and see how it responds. Then, the
+censor can probe the dark decoy IP, and see if it responds similarly (e.g. with
+the same set of open ports and payloads for certain kinds of probes). To defend
+against this, we forward \emph{all} traffic destined to the dark decoy to the
+masked site, including ports that are not relevant to the proxy application
+(e.g. non 443). This ensures that above the TCP layer, we appear to be the mask
+site. However, there may be differences in TCP/IP implementations, for instance,
+how IP IDs are incremented, or how TCP timestamps are incremented (or supported
+at all) that may be different from the mask site. To combat this, we can filter
+mask sites by those that have identical TCP/IP stacks to ours, as we use a
+common Linux implementation. We also note that this attack only applies when we
+use the mask site as an application, and that Dark Decoys can support other
+applications (e.g. obfsproxy, WebRTC, etc) that do not have this issue.
+
+\paragraph{Website Fingerprinting}
+Dark Decoy applications that mimic websites (e.g. mask sites) may be vulnerable
+to website fingerprinting, where the censor observes that clients accessing
+suspected dark decoy IPs are receiving payloads or packet timings that differ
+from legitimate connections to the mask site. This attack is difficult for
+censors to carry out because it has high uncertainty: even a small false
+positive rate means blocking mostly legitimate connections (due to the base rate
+of normal traffic), and false negatives could allow clients to retry until they
+gain access. More importantly, unlike previous Refraction Networking protocols,
+Dark Decoy applications are not limited to mimicking websites, and can support
+any (or even a combination of) protocols.
+
+%\paragraph{Probing Dark Decoys}
+%-Active probing TLS connection
+%    -Block access unless from registering source IP
+%        -cite GFW taking over client IPs for active probing of old obfs
+%    -Verify knowledge of seed (but how to respond when verification fails?)
+
+\paragraph{ICMP}
+Censors can use ping or traceroute utilities (via ICMP) to probe potential dark
+decoys. Because there is (usually) no host at the dark decoy address, these
+probes will timeout and produce no response. They might also produce
+``Destination Unreachable'' responses from routers depending on how they are
+configured.
+% we scanned a random sample of v6 addresses and found...x%
+% responded with ICMP dest unreach
+Many legitimate hosts and routers do not respond to or forward ICMP packets, and
+it is common for firewalls to block traceroutes from penetrating inside
+networks. Thus, simply ignoring ICMP messages (or low TTL packets that might be
+used by traceroute) may be a viable strategy. % We should evaluate this claim...
+Alternatively, we could spoof responses to convince an adversary that a dark
+decoy is part of a particular network. However, this strategy requires careful
+consideration of what network makes sense for a mask site to be in. Also, the
+censor may try to probe for addresses around the dark decoy (but still likely to
+be in the same network), which must also be responded to.
+
+%-Fingerprinting Masked site vs Dark decoy application
+%-ICMP
 

### 2019-02-13 paper/background.tex
background section

\section{Background}

Refraction networking fundamentally operates by injecting covert communication inside a client's HTTPS connection with a reachable site, also known as a decoy site. In a regular HTTPS session, a client establishes a TCP connection, performs a TLS connection with a destination site, sends an encrypted web request, and receives an encrypted response. In refraction routing, at least one direction of this exchange is observed by a \emph{refraction station} (RS), deployed at some Internet service provider (ISP). The RS watches for a covert signal from the client that this connection is to be used for censorship circumvention. Upon seeing the signal, the RS will take over the HTTPS session at some point, and establish a proxy session with the client that can then be used for covert communication.

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/refraction-v1}
    \caption{First generation refraction networking designs operated as an inline transparent proxy.}
    \label{fig:refraction-v1}
\end{figure}

\begin{figure}
    \includegraphics[width=\columnwidth]{figures/tapdance}
    \caption{TapDance operates without flow blocking by using a mirror
    port to receive a copy of traffic.}
    \label{fig:tapdance}
  \end{figure}

  \begin{figure}
    \includegraphics[width=\columnwidth]{figures/dark-decoys}
    \caption{Dark decoys uses two sessions: a registration one which is passively observed by the refraction station, and a dark session which is proxied by the RS in its entirety.}
    \label{fig:dark-decoys}
\end{figure}

One of the key challenges for refraction networking is in taking over a session. The RS must start responding to the client's traffic as if it were the decoy destination, and at the same time prevent the destination from sending its own responses back to the client. A simple approach is to have the refraction station act as an inline transparent proxy (\cref{fig:refraction-v1}) that forwards the traffic between the client and the decoy site. After a TLS handshake has been completed, the RS terminates the connection with the decoy site by sending a TCP reset and takes over the session with the client.

An inline element, however, can significantly affect the reliability and performance of the regular, non-refraction traffic of an ISP. Cirripede~\cite{cirripede} and Telex~\cite{telex} attempted to mitigate this by dynamically adding router rules to forward only a subset of traffic from a registered client or an active session through the element, but this nevertheless presented a deployability challenge.

TapDance~\cite{tapdance} offered an alternative design that did not require the blocking or redirection of traffic, but used a mirror port instead (\cref{fig:tapdance}). In TapDance a client sends an incomplete HTTP request, which causes the decoy site to pause waiting for more data while the RS takes over the connection in its place. After a client would receive a packet initiated by the RS, its TCP sequence numbers would become desynchronized with the decoy site, causing the decoy to ignore the packets sent by the client.

This approach reduced the barriers to deployment and TapDance was used in production during a pilot study, serving upwards of 50\,000 real-world users~\cite{tapdance-foci17}. \nikita{worth mentioning that it's being used in production again? we don't have a public ref for that though.} The tap-based approach, however, has some disadvantages. A decoy site will only ignore packets as long as the sequence numbers stay within its TCP window, and will terminate the connection after a timeout. Frolov et al.\ report that in their pilot, they eliminated roughly a third of potential decoy sites due to their measured window or timeout values being too small~\cite{tapdance-foci17}. Even so, sessions that try to upload non-trivial data amounts (in excess of about 15\,KB) or last longer than the timeout value (ranging from 30--120\,s) require the user to create new refraction connections, adding overhead, complexity, and opportunities for errors. Additionally, keeping the connections to the decoy site open for tens of seconds uses up the site's resources; Frolov et al.\ found that a default configuration of the Apache web server would only keep 150 simultaneous connections open, while pilot deployment would often result in dozens of connections to the same decoy site, creating a scaling concern.

Dark decoys are able to avoid these problems by splitting up the traffic between a registration session and a dark session \nikita{are these good terms?} (\cref{fig:dark-decoys}). The registration session is used to send a signal to the RS to let RS know that the client plans to use dark sessions and to establish a seed to be used in future communications (\cref{XXX}); the RS only passively observes this connection without any interference. The dark session connects to a dark address that is not routed to any host; the RS instead acts as a remote endpoint for the entirety of the connection, starting with the TCP handshake. This design obviates the need for taking over a session already in progress, which both simplifies the implementation and eliminates certain attacks, as we will discuss in \cref{XXX}.

\paragraph{Registration Signal} In all implementations of refraction networking, a client must send a covert signal to the RS to initiate communication. This covert signal is  embedded inside communication fields that must be indistinguishable from random by a censor without access to a secret/private key available to the station. Past implementations have used TCP initial sequence numbers~\cite{cirripede}, the ClientRandom field inside a TLS handshake~\cite{decoy-routing,telex}, and the encrypted body of an HTTPS request~\cite{tapdance}. In principle dark decoys can use any of these mechanisms for registration, but n our prototype we used the HTTPS request body as it offers the greatest flexibiity for the amount of data that can be sent with the registration.

### 2019-02-13 paper/paper.tex
add scan
background section

@@
 \include{figures}
+\usepackage{subcaption}
+\usepackage{cleveref}
 
@@
 \section{Background}
+
+\input{background.tex}
 % 1 page
@@
 ``Destination Unreachable'' responses from routers depending on how they are
-configured.
-% we scanned a random sample of v6 addresses and found...x%
-% responded with ICMP dest unreach
+configured. We performed a scan of 10~million IPv6 addresses in a routable /32
+prefix to see if it is common to respond with such tell-tale ICMP messages for
+unused messages. We found only 0.016\% of addresses responded with any ICMP
+messages (a combination of ``Time Exceeded'' and ``Destination Unreachable'').
+
 Many legitimate hosts and routers do not respond to or forward ICMP packets, and

### 2019-02-13 paper/paper.tex
WIP: implementation

@@
 \subsubsection{Encrypted SNI}
+\label{esni}
 
@@
 \section{Implementation}
-% 1 page
+In order to scale up to 10Gbps and beyond,
+one has to utilize multiple cores and employ load balancing.
+We use PF\_RING built-in load balancer \it{zbalance} to efficiently
+distribute load between 4 cores.
+Our timeout is based on last IP address usage time, which prevents us from
+balancing load based on source IP address,
+as censor would be able to observe
+same destination IP address picking or not picking up
+depending on source IP address.
+To avoid such unusual behavior we balance on destination IP.
+Since PF\_RING does not feature load balancing based only on destination
+IP address, we made a custom implementation of this zbalance policy.
 
--ISP-scale implementation, able to handle 10+Gbps
+TODO: say it's tested on 10 Gbps
+
+Implementation of the protocol includes 3 components:
+dark decoy detector, proxy application, and client.
+Dark decoy detector will parse the traffic, searching for registrations in
+tagged messages. After detector observes a registration, and negotiates with client
+a dark decoy IP,
+all packets, that are sent to that dark decoy IP,
+will be forwarded into a proxy application.
+
+\subsection{Registration phase}
+
+Each Dark Decoy connection has 2 phases: registration, and usage of a dark decoy.
+Registration starts with a handshake that is similar to a TapDance handshake,
+but initial HTTP request is complete.
+This allows a reachable site to provide a genuine response
+to a HTTP GET request of its index page.
+Since station does not need to produce a response,
+which significantly reduces complexity of a detector,
+that does not need to decrypt and inject packets into a TLS connection between
+client and a reachable site, as opposed to original TapDance.
+
+Client begins registation by establishing TLS connection
+to one of the reachable websites,
+path to which passes by our tap.
+Client uses a Chosen-Ciphertext Steganography technique~\cite{tapdance} to manupulate
+plaintext of a first application data HTTP request
+to get desired ciphertext,
+and exchange keys with the station.
+After client writes Elligator-encoded~\cite{elligator} representative into the ciphertext at a static offset of 92 bytes from the end,
+that could be decoded using station's private key,
+to negotiate a 32 byte Eligator-encoded~\cite{elligator} shared secret between the client and the station.
+That shared secret is used as a seed of SHA-256 based key derivation function (HKDF),
+allowing station and client to derive an unlimited amount of shared secrets.
+
+Elligator representative on the wire is immidiately followed by a 6 bytes long AES-GCM-encrypted
+fixed size payload(FSP), that holds flags and the size of the variable size payload(VSP).
+IV and key for encrypted of both FSP and VSP will be derived from HKDF.
+Once FSP is decrypted and the size of VSP is known, station can decrypt the VSP as well.
+VSP itself is a protobuf, which allows us to easily change the contents of VSP without risk of version mismatch, and currently contains 3 fields: version of configuration(which includes list of decoys), SNI of mask site, and a presumably blocked target host that client would like to get connected to.
+
+Client will sleep a short randomized period of time before attempting to establish connection to dark decoy.
+This is done for 2 reasons: to break potentially observable interflow dependency with a dark decoy connection being established right after a first application layer data packet sent to decoy,
+and to give station time.
+TODO: why does it need time?
+
+\subsection{Application phase}
+Client and station will use HKDF to derive 16 random bytes and use them to
+agree on a dark decoy IP address, by applying a simple selection algorithm.
+Algorithm is as follows: first, flatten a list of pre-shared avaliable IP
+addresses in various subnets into a single indexed list, then make a 128-bit
+integer out of 16 random bytes and divide it by the length
+of the flattened list, and use the remainder of this division as an index
+of the list to pick an IP address.
+
+To thwart active probing attacks, this application will then confirm
+that connecting client knows a secret, negotiated during the registration.
+If connecting client does know that secret, application will set up proxying,
+otherwise it may give censor a response, that acts like that this IP address
+is not an open proxy.
+
+TODO: describe MakeConnWithCompleteHandshake?
+
+Note that dark decoy detector and proxy application are only loosely coupled with each other,
+making it simple to replace one of them.
+We plan to take advantage of encrypted SNI, when it gets widely adopted,
+and replace our current proxy implementation with one that uses encrypted SNI
+and achieve improved unobservability properties, described in section~\ref{esni}.
+
+\subsection{Languages and LOC counts} % TODO: rename/restructure and complete section
+Client is written in Golang and follows the same API as standard TapDance does,
+which allows us to reuse existing TapDance CLI wrapper and Android application.
+
 -Language choice (Rust, Go, minimal C)
--Open source (client and station)
+-Open source (client, station and application)
 

### 2019-02-13 paper/background.tex
remove dup background sections

@@
 
-Refraction networking fundamentally operates by injecting covert communication inside a client's HTTPS connection with a reachable site, also known as a decoy site.
-In a regular HTTPS session, a client establishes a TCP connection, performs a TLS connection with a destination site, sends an encrypted web request, and receives an encrypted response.
-In refraction routing, at least one direction of this exchange is observed by a \emph{refraction station} (RS), deployed at some Internet service provider (ISP).
-The RS watches for a covert signal from the client that this connection is to be used for censorship circumvention.
-Upon seeing the signal, the RS will take over the HTTPS session at some point, and establish a proxy session with the client that can then be used for covert communication.
+Refraction networking operates by injecting covert communication inside a
+client's HTTPS connection with a reachable site, also known as a decoy site. In
+a regular HTTPS session, a client establishes a TCP connection, performs a TLS
+handshake with a destination site, sends an encrypted web request, and
+receives an encrypted response. In refraction routing, at least one direction
+of this exchange is observed by a \emph{refraction station} (RS), deployed at
+some Internet service provider (ISP). The RS watches for a covert signal from
+the client that this connection is to be used for censorship circumvention.
+Upon seeing the signal, the RS will take over the HTTPS session,
+and establish a proxy session with the client that can then be used for covert
+communication.
 

### 2019-02-14 paper/paper.tex
remove dup background sections
Formatting
Implementation pass

@@
 
-\section{Background}
-
 \input{background.tex}
-% 1 page
-Background on TLS and Refraction Networking
 
@@
 \section{Implementation}
+
+We implemented the Dark Decoy protocol and tested it in a 10~Gbps ISP testbed
+with real traffic. Similar to TapDance~\cite{tapdance}, we used PF\_RING to
+consume the 10~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
+detector processes all packets and watches for new registrations. It also
+forwards all packets sent to a (registered) dark decoy's address to the local
+\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
+allowing the application to accept and respond to connections using the native
+operating system's interface. Figure~\ref{fig:implementation} shows the overall
+architecture of our implementation, which we describe next.
+% Along with the client?
+
+\FigImplementation
+
+\subsection{Detector}
+
+Our detector is a modified fork of the open source TapDance
+implementation~\cite{tapdance-source}.
+We implemented our detector in approximately 1,800 lines of Rust (compared to
+over 5,000 lines for TapDance)\footnote{excluding (from both) about 3,000 lines
+of auto-generated protobuf code}.
+
+We used PF\_RING to load balance the 10~Gbps link over 4~CPU cores. PF\_RING
+supports balancing across cores based on flow (5-tuple) or source and
+destination IPs. However, both of these options present challenges for our Dark
+Decoy detector. One issue is that registrations could be processed on a
+different core than the packets sent to that specific dark decoy address. For
+instance, a client could have its registration handled by Core 1, while its
+packets to the dark decoy address end up on Core 3, which doesn't know about the
+original registration.
+
+To address this, we used Redis~\cite{redis} to allow each process to announce
+(publish) newly registered decoys to the other cores so they can
+add them to their local list of registered dark decoy addresses.
+However, this introduces two new problems. First, a core might add a
+registration \emph{after} it has already received and processed packets destined
+for the specified dark decoy. This typically isn't a problem when running on a
+single core, as packets are processed sequentially. Second, each core may
+timeout each dark decoy at different times, potentially leading to differing
+behavior that is visible to a censor. For instance, if we used the
+source/destination IPs to load balance, a censor's packets to a dark decoy could
+be processed by a different core than the client. If the censor waits for the
+known timeout before sending a probe, its core may have timed out that dark
+decoy, while the client's core has refreshed the timeout of the dark decoy due
+to active use.
+
+To address the first issue, we force the client to delay sending its connection
+to the dark decoy until a short time after registration. In practice, we force
+the client to wait until the registration decoy responds before starting a
+connection with the registered dark decoy.
+
+To address the second issue, we implemented a new load-balancing algorithm in
+PF\_RING to select the core based solely on the destination IP address of the
+packet. This still means we must use Redis to tell all of the cores of new
+registrations, but that only one core will be responsible for processing all of
+the packets sent to a given dark decoy, regardless of who or when it is sent.
+
+\subsection{Application}
+
+We implemented our application in about 500~lines of Golang. Though we note
+other protocols (e.g. obfsproxy or WebRTC) could be used as the application, we
+implemented a mask site mimicking application, that pretends to be a mask site
+when actively probed by the censor.
+
+The application accepts connections to dark decoy addresses forwarded by the
+detector and rewritten to the local address using \texttt{iptables}.
+The application also receives out-of-band information about registrations from the
+detector via a ZMQ~\cite{zmq} connection, which informs the application of the
+registering client's IP address, the secret seed, and other configuration
+information passed by the client.
+
+Once the application accepts a connection, it initially acts as a transparent
+proxy to the mask site specified by the client during registration. The
+application parses the handshake, forwarding packets back and forth between
+client and mask site without modification, and extracting the server and client
+randoms. The application attempts to decrypt the first application data record
+from the client using a key derived from the secret seed, and client and server
+randoms. We use the uTLS library~\cite{utls} on both the application and client
+to allow us to change the TLS secrets being used after the handshake.
+
+If the decryption is successful, the application switches to forwarding
+(decrypted) data back and forth with a client-specified endpoint, such as a
+SOCKS proxy, which can multiplex multiple client connections over the single
+connection to the dark decoy.
+
+\subsection{Client}
+
+Our client is also written in Golang, and uses a TapDance-like protocol for
+registration. We note that this protocol should be harder for censors to observe
+because it consists of only a single (complete) request, and the station does
+not have to spoof packets as the decoy used during registration, only passively
+observe them.
+
+After registering, the client connects to the derived dark decoy address, and
+switches secrets after the handshake. At this point, a local application (e.g.
+SOCKS client) can connect to the client, and it will transparently be connected to
+the remote end via the encrypted dark decoy connection.
+
+\if0
 In order to scale up to 10Gbps and beyond,
 one has to utilize multiple cores and employ load balancing.
-We use PF\_RING built-in load balancer \it{zbalance} to efficiently
+We use PF\_RING built-in load balancer \emph{zbalance} to efficiently
 distribute load between 4 cores.
@@
 -Open source (client, station and application)
+\fi
 

### 2019-02-14 paper/paper.tex
Revise abstract

@@
 % For submission make this a noop
-\newcommand{\note}[2]{\textit{[#1: #2]}}
-\newcommand{\nikita}[1]{\note{nikita}{#1}}
 
@@
 \usepackage{cleveref}
+\usepackage{microtype}
+
+\usepackage{xspace}
+\usepackage{soul}
+\newcommand{\note}[2]{\hl{[\textbf{#1:} #2]}\xspace}
+\newcommand{\nikita}[1]{\note{nikita}{#1}}
+
+% Slight JAH fix to stop URLs from breaking after ``http:''
+\def\UrlBreaks{\do-\do\.\do\@\do\\\do\!\do\_\do\|\do\;\do\>\do\]%
+ \do\)\do\,\do\?\do\'\do+\do\=\do\#}
+\def\UrlBigBreaks{\do\:\do\/}%
+\urlstyle{rm}
 
@@
 %-------------------------------------------------------------------------------
-Refraction Networking (formerly ``Decoy Routing'') has emrged as a useful tool in circumventing
-        Internet censorship. By placing proxies in cooperating Internet Service
-        Providers (ISPs) and using connections to existing reachable
-        ``decoy'' sites for transport, censors cannot easily block access to
-        such proxies without also blocking legitimate sites.
+Refraction Networking (formerly known as ``Decoy Routing'') has
+emerged as a promising next-generation approach for circumventing
+Internet censorship. Rather than trying to hide individual
+circumvention proxy servers from censors, proxy functionality is
+implemented in the core of the network, at cooperating ISPs in
+friendly countries.  Any connection that traverses these ISPs could be
+a conduit for the free flow of information, so censors cannot easily
+block access without also blocking many legitimate sites.  While one
+Refraction scheme, TapDance, has recently been deployed at ISP-scale,
+it suffers from several problems: a limited number of ``decoy'' sites
+in realistic deployments, high technical complexity, and undesirable
+tradeoffs between performance and observability by the censor. These
+problems may impede broader deployment and ultimately allow censors to
+block such techniques.
 
-However, existing deployed Refraction Networking schemes such as TapDance suffer
-from several problems, including a limited number of decoy sites in realistic
-deployments, and an unfavorable tradeoff between performance and observability
-by the censor. These problems limit where such proxies can be deloyed, hamper
-their effectiveness, and may ultimately make them possible for censors to block.
-
-In this paper, we present Dark Decoys, a deployable Refraction Networking scheme that
-overcomes the limits on decoys and performance. Dark Decoys leverages the (primarily) unused address
-space that is reachable through the deploying ISP. Rather than rely on existing
-sites as reachable decoy sites that must be involved in each proxy connection,
-Dark Decoys create seemingly legitimate hosts at new IP addresses. These
-invented hosts are indistinguishable from normal hosts to the censor, but can
-be used by clients as one-time proxies.
-
-We implement our scheme ... and it's just the bee's knees. TODO
+We present Dark Decoys, an improved Refraction Networking approach
+that overcomes these limitations by leveraging unused address space at
+deploying ISPs. Instead of using real websites as the decoy destinations
+for proxy connections, our scheme creates seemingly legitimate hosts
+on demand, at IP addresses where no web server exists.
+These phantom hosts are difficult for a censor to distinguish from
+ones, but can be used by clients as proxies.  We define the
+Dark Decoys protocol, analyze its security, and evaluate a
+prototype on IPv4 and IPv6 networks.
+Our results suggest that Dark Decoys can be as difficult to block
+as TapDance, is simpler to maintain and deploy,
+and offers substantially better network performance.
 
@@
 %-------------------------------------------------------------------------------
+
 \bibliographystyle{plain}
+\small
 \bibliography{biblio}

### 2019-02-14 paper/figures.tex
add compare section
Implementation pass
Move overview to front page

@@
     \centering
-    \includegraphics[width=0.9\linewidth,clip]{figures/high-level.png}
-    \caption{\textbf{Dark Decoys}\,---\, %
-    After registration, clients connect to unused (``dark'') addresses that pass
-        by a cooperating ISP proxy station. The station communicates with the client
-        as if it were the host at that address. To the censor, this
-        connection appears to be with a legitimate one to a real host,
-        making it difficult to distinguish from real hosts and block.
+    \includegraphics[width=\linewidth,clip]{figures/high-level.png}
+    \caption{\textbf{Overview}---%
+      When deployed at an ISP, \scheme observes a mirror of inbound and outbound traffic.
+      Users request service by embedding a steganographic registration message in a TLS handshake with any reachable site at the ISP\@. Then, the client connects to a random unused (``dark'')
+      address in the ISP's AS, and \scheme communicates with the client as if it were that host.
     }
@@
                                       %Telex Cirr  DR     TD      RB    Slth   Water  DD
-            No inline blocking        & \no & \no  & \yes & \no  & \no  & \no  & \no  & \yes \\
+            No inline blocking        & \no & \no  & \no & \yes  & \no  & \no  & \no  & \yes \\
             Handles asym. routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
@@
 }
+
+\newcommand{\FigImplementation}{
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.7\linewidth,clip]{figures/implementation.png}
+    \caption{\textbf{Station Architecture}\,---\, %
+    }
+    \label{fig:implementation}
+\end{figure}
+}

### 2019-02-14 paper/paper.tex
Move overview to front page

@@
 %\usepackage{parskip}
+\usepackage{mathptmx}\renewcommand{\ttdefault}{cmtt}
 \usepackage{amsmath}
@@
 %\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
-\setlength\parskip{1pt}
+%\setlength\parskip{1pt}
 \usepackage{graphicx} % http://ctan.org/pkg/graphicx
@@
 \usepackage{microtype}
-
+\SetExtraKerning{encoding=*,font=*}{\textemdash={120,120}} % Add space around emdashes
+\usepackage[font=small]{caption}
+\microtypecontext{spacing=nonfrench}
 \usepackage{xspace}
@@
 \urlstyle{rm}
+
+\renewcommand{\paragraph}[1]{\smallskip\noindent\textbf{#1\quad}}
 
@@
 
+%\newcommand{\scheme}{Conjure\xspace}
+\newcommand{\scheme}{Dark Decoys\xspace}
+
 %-------------------------------------------------------------------------------
@@
 
-We present Dark Decoys, an improved Refraction Networking approach
+We present \scheme, an improved Refraction Networking approach
 that overcomes these limitations by leveraging unused address space at
@@
 ones, but can be used by clients as proxies.  We define the
-Dark Decoys protocol, analyze its security, and evaluate a
-prototype on IPv4 and IPv6 networks.
-Our results suggest that Dark Decoys can be as difficult to block
+\scheme protocol, analyze its security, and evaluate a
+prototype using an ISP testbed.
+Our results suggest that \scheme can be as difficult to block
 as TapDance, is simpler to maintain and deploy,
@@
 \end{abstract}
+
+\FigHighLevel
 
@@
 produce a connection pattern that is visible to censors.
-
-\FigHighLevel
 

### 2019-02-14 paper/figures.tex
Small edit

@@
       Users request service by embedding a steganographic registration message in a TLS handshake with any reachable site at the ISP\@. Then, the client connects to a random unused (``dark'')
-      address in the ISP's AS, and \scheme communicates with the client as if it were that host.
+      address in the ISP's AS, and \scheme communicates with the client as if it were a proxy at that address.
     }

### 2019-02-14 paper/paper.tex
address entropy?

--- 2019-02-14 paper/paper.tex
@@
 \usepackage{cleveref}
+\usepackage{microtype}
+
+% Slight JAH fix to stop URLs from breaking after ``http:''
+\def\UrlBreaks{\do-\do\.\do\@\do\\\do\!\do\_\do\|\do\;\do\>\do\]%
+ \do\)\do\,\do\?\do\'\do+\do\=\do\#}
+\def\UrlBigBreaks{\do\:\do\/}%
+\urlstyle{rm}
 
@@
 
+\if0
+\paragraph{Address entropy}
+Addresses in IPv6 are commonly shortened, as many of the 128-bits in the address are set to 0.
+For instance, google.com has the address
+\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
+\texttt{2607:f8b0:400f:806::2004}). Only 24 bits are set to 1 in this address,
+giving censors a possible feature to filter on: addresses that have too much
+entropy could be suspicious as servers.
+\fi
+
 \section{Related Work}

### 2019-02-14 paper/background.tex
Improve evolution figures

@@
 
-\begin{figure}
-    \includegraphics[width=\columnwidth]{figures/refraction-v1}
-    \caption{First generation refraction networking designs operated as an inline transparent proxy.}
-    \label{fig:refraction-v1}
-\end{figure}
-
-\begin{figure}
-    \includegraphics[width=\columnwidth]{figures/tapdance}
-    \caption{TapDance operates without flow blocking by using a mirror
-    port to receive a copy of traffic.}
-    \label{fig:tapdance}
-  \end{figure}
-
-  \begin{figure}
-    \includegraphics[width=\columnwidth]{figures/dark-decoys}
-    \caption{Dark decoys uses two sessions: a registration one which is passively observed by the refraction station, and a dark session which is proxied by the RS in its entirety.}
-    \label{fig:dark-decoys}
-\end{figure}
+\FigEvolution
 

### 2019-02-14 paper/figures.tex
Improve evolution figures

@@
 \newcommand{\FigOverview}{
-\begin{figure}[ht]
+\begin{figure*}[t]
     \centering
-    \includegraphics[width=0.9\linewidth,clip]{figures/dark-decoy-overview.png}
+    \includegraphics[width=0.60\linewidth,clip]{figures/dark-decoy-overview.png}
     \caption{\textbf{Dark Decoy Overview}\,---\, %
@@
     \label{fig:overview}
-\end{figure}
+\end{figure*}
 }
@@
     \end{tabular}
-    %\caption{\textbf{Refraction Networking schemes}\,---\,}
+    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,}
     \label{tab:compare}
@@
 }
+
+\newcommand{\FigEvolution}{
+\begin{figure}
+  \centering
+  \begin{subfigure}{\columnwidth}
+    \includegraphics[width=\columnwidth]{figures/refraction-v1}
+    \vspace{-7pt}
+
+    \caption{\textbf{First generation systems} for Refraction Networking, such as Telex and Cirrepede, operated as inline network elements, with the ability to observe traffic and block specific flows.
+ISPs worried that if the inline element failed, it could bring down the network.\looseness=-1}
+    \label{fig:refraction-v1}
+  \end{subfigure}
+  \vspace{12pt}
+
+  \begin{subfigure}{\columnwidth}
+    \includegraphics[width=\columnwidth]{figures/tapdance}
+    \vspace{-7pt}
+
+    \caption{\textbf{TapDance} is a second-generation Refraction Network scheme that operates without flow blocking, needing only to passively observe traffic and inject packets.
+TapDance has recently been deployed at a mid-size ISP, but the techniques used to silence the decoy site and participate in the client--decoy TCP connection mid-stream add significant complexity, performance bottlenecks, and detection risk.}
+    \label{fig:tapdance}
+  \end{subfigure}
+  \vspace{12pt}
+
+  \begin{subfigure}{\columnwidth}
+    \includegraphics[width=\columnwidth]{figures/dark-decoys}
+    \vspace{-7pt}
+
+    \caption{\textbf{\scheme}, our third-generation Refraction Networking design, overcomes these limitations.
+It uses two sessions.
+First, the client connects to a decoy site and embeds a steganographic registration message, which the station receives using only a passive tap.
+Second, the client connects to a ``dark address'' where there is no running server, and the station proxies the connection in its entirety.}
+    \label{fig:dark-decoys}
+  \end{subfigure}
+  \caption{\textbf{Evolution of Refraction Networking Approaches}}
+\end{figure}
+}

### 2019-02-14 paper/background.tex
Minor fixes

@@
 An inline element, however, can significantly affect the reliability and performance of the regular, non-refraction traffic of an ISP.
-Cirripede~\cite{cirripede} and Telex~\cite{telex} attempted to mitigate this by dynamically adding router rules to forward only a subset of traffic from a registered client or an active session through the element, but this nevertheless presented a deployability challenge.
+Cirripede~\cite{cirripede11} and Telex~\cite{telex11} attempted to mitigate this by dynamically adding router rules to forward only a subset of traffic from a registered client or an active session through the element, but this nevertheless presented a deployability challenge.
 
-TapDance~\cite{tapdance} offered an alternative design that did not require the blocking or redirection of traffic, but used a mirror port instead (\cref{fig:tapdance}).
+TapDance~\cite{tapdance14} offered an alternative design that did not require the blocking or redirection of traffic, but used a mirror port instead (\cref{fig:tapdance}).
 In TapDance a client sends an incomplete HTTP request, which causes the decoy site to pause waiting for more data while the RS takes over the connection in its place.
@@
 
-This approach reduced the barriers to deployment and TapDance was used in production during a pilot study, serving upwards of 50\,000 real-world users~\cite{tapdance-foci17}.
+This approach reduced the barriers to deployment and TapDance was used in production during a pilot study, serving upwards of 50\,000 real-world users~\cite{frolov2017isp}.
 \nikita{worth mentioning that it's being used in production again?
@@
 A decoy site will only ignore packets as long as the sequence numbers stay within its TCP window, and will terminate the connection after a timeout.
-Frolov et al.\ report that in their pilot, they eliminated roughly a third of potential decoy sites due to their measured window or timeout values being too small~\cite{tapdance-foci17}.
+Frolov et al.\ report that in their pilot, they eliminated roughly a third of potential decoy sites due to their measured window or timeout values being too small~\cite{frolov2017isp}.
 Even so, sessions that try to upload non-trivial data amounts (in excess of about 15\,KB) or last longer than the timeout value (ranging from 30--120\,s) require the user to create new refraction connections, adding overhead, complexity, and opportunities for errors.
@@
 This covert signal is  embedded inside communication fields that must be indistinguishable from random by a censor without access to a secret/private key available to the station.
-Past implementations have used TCP initial sequence numbers~\cite{cirripede}, the ClientRandom field inside a TLS handshake~\cite{decoy-routing,telex}, and the encrypted body of an HTTPS request~\cite{tapdance}.
+Past implementations have used TCP initial sequence numbers~\cite{cirripede11}, the ClientRandom field inside a TLS handshake~\cite{curveball11,telex11}, and the encrypted body of an HTTPS request~\cite{tapdance14}.
 In principle dark decoys can use any of these mechanisms for registration, but n our prototype we used the HTTPS request body as it offers the greatest flexibiity for the amount of data that can be sent with the registration.

### 2019-02-14 paper/figures.tex
Minor fixes

@@
     \centering
+    \vspace{-0.5in}
     \includegraphics[width=\linewidth,clip]{figures/high-level.png}
@@
             % Multiflow? Waterfall?
-            & \rot{Telex~\cite{telex}} &
-            \rot{Cirripede~\cite{cirripede}} &
-            \rot{Decoy Routing~\cite{curveball}} &
-            \rot{TapDance~\cite{tapdance}} & \rot{Rebound~\cite{rebound}} & \rot{Slitheen~\cite{slitheen}} & \rot{Waterfall~\cite{waterfall}} & \rot{\textbf{Dark Decoys}} \\
+            & \rot{Telex~\cite{telex11}} &
+            \rot{Cirripede~\cite{cirripede11}} &
+            \rot{Decoy Routing~\cite{curveball11}} &
+            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall}} & \rot{\textbf{Dark Decoys}} \\
             \hline
@@
     \includegraphics[width=\columnwidth]{figures/refraction-v1}
-    \vspace{-7pt}
+    \vspace{-3pt}
 
-    \caption{\textbf{First generation systems} for Refraction Networking, such as Telex and Cirrepede, operated as inline network elements, with the ability to observe traffic and block specific flows.
+    \caption{\textbf{First generation systems} for Refraction Networking, such as Telex and Cirripede, operated as inline network elements, with the ability to observe traffic and block specific flows.
 ISPs worried that if the inline element failed, it could bring down the network.\looseness=-1}
@@
   \end{subfigure}
-  \vspace{12pt}
+  \vspace{16pt}
 
@@
     \includegraphics[width=\columnwidth]{figures/tapdance}
-    \vspace{-7pt}
+    \vspace{-3pt}
 
@@
     \includegraphics[width=\columnwidth]{figures/dark-decoys}
-    \vspace{-7pt}
+    \vspace{-3pt}
 
@@
   \end{subfigure}
+
+  \vspace{12pt}
   \caption{\textbf{Evolution of Refraction Networking Approaches}}

### 2019-02-14 paper/paper.tex
Improve evolution figures
Minor fixes

--- 2019-02-14 paper/paper.tex
@@
 \microtypecontext{spacing=nonfrench}
+\usepackage{subcaption}
 \usepackage{xspace}
@@
 get around censorship in countries it was
-blocked~\cite{domain-fronting,signal,signal-domain-fronting}.
+blocked~\cite{meek,signal,signal-domain-fronting}.
 But in May~2018, Google and Amazon made both technical and policy changes to
@@
 Networking schemes has been deployed in practice by a large ISP:
-TapDance~\cite{tadance}, a
+TapDance~\cite{tadance14}, a
 Refraction Networking protocol that removes the need for inline
@@
 Since 2011, there have been several proposed Refraction Networking schemes.
-Telex~\cite{telex}, Cirripede~\cite{cirripede} and Decoy
-Routing~\cite{curveball} are ``first generation'' protocols with nearly
+Telex~\cite{telex11}, Cirripede~\cite{cirripede11} and Decoy
+Routing~\cite{curveball11} are ``first generation'' protocols with nearly
 identical features. These designs require inline flow blocking at the ISP to
@@
 
-TapDance~\cite{tapdance} solves the issue of inline-blocking by coercing the
+TapDance~\cite{tapdance14} solves the issue of inline-blocking by coercing the
 decoy into staying silent, and allowing the station to respond instead. However,
@@
 
-Rebound~\cite{rebound} and Waterfall~\cite{waterfall} both focus on routing
+Rebound~\cite{rebound15} and Waterfall~\cite{waterfall} both focus on routing
 asymmetries and routing attacks by the censor. Rebound modifies the client's
@@
 
-Slitheen~\cite{slitheen} focuses on addressing observability by replacing
+Slitheen~\cite{slitheen16} focuses on addressing observability by replacing
 data in packets sent by the legitimate decoy. Thus, even the packet timings and

### 2019-02-15 paper/paper.tex
Revise first half intro

@@
 \newcommand{\nikita}[1]{\note{nikita}{#1}}
+\newcommand{\TODO}[1]{\hl{TODO: #1}\xspace}
+\newcommand{\TK}{\hl{TK}\xspace}
 
@@
 
-%\newcommand{\scheme}{Conjure\xspace}
-\newcommand{\scheme}{Dark Decoys\xspace}
+\newcommand{\scheme}{Conjure\xspace}
+%\newcommand{\scheme}{Dark Decoys\xspace}
 
@@
 tradeoffs between performance and observability by the censor. These
-problems may impede broader deployment and ultimately allow censors to
+challenges may impede broader deployment and ultimately allow censors to
 block such techniques.
@@
 %-Existing countries blocking more
-Internet censorship continues to hamper social progress throughout the world.
-Over half of the global Internet population
+%Internet censorship continues to hamper social progress throughout the world.
+
+Over half of Internet users globally
 now live in countries that block political, social, or religious content
-online~\cite{fotn2018} as governments continue to expand their censorship
-policies and programs.
-
+online~\cite{fotn2018}.
 %Existing circumvention strategies on shaky ground
@@
 %-Cenosrs fingerprinting known protocols
-Meanwhile, strategies to circumvent censorship using proxies have suffered many
-recent setbacks. Many previously popular proxies are no longer functional due to
-censors evolving new ways to block them~\cite{ensafi-tor,great-cannon},
-or because they rely on temperamental
-infrastructure. For example, domain fronting was a popular circumvention
-strategy used by meek (in Tor), as well as the Signal secure messaging app to
-get around censorship in countries it was
-blocked~\cite{meek,signal,signal-domain-fronting}.
+Meanwhile, many popular tools and techniques for circumventing such censorship
+have ceased to function, because censors have evolved new ways to block them~\cite{ensafi-tor,great-cannon}
+or infrastructure they rely on has become unavailable.
+
+For example, domain fronting~\cite{meek} was a popular circumvention
+strategy used by Meek (in Tor), as well as by the Signal secure messaging app to
+get around censorship in countries where it was
+blocked~\cite{signal,signal-domain-fronting}.
 But in May~2018, Google and Amazon made both technical and policy changes to
@@
 fronting, Signal abandoned the strategy altogether~\cite{signal-back-on-front}.
+There is an urgent need for new, more robust approaches to circumvention.
+
 %Combined with censors' constant improvements in discovery and blocking
@@
 %-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
-One emerging technique is Refraction Networking (also known as ``Decoy
-Routing''), which places proxies at cooperating Internet Service Providers
-(ISPs) outside censoring countries~\cite{refraction-site}. Clients access the
-proxies by connecting to unblocked ``decoy'' sites such that the packets pass by
-the ISP proxy, which intercepts and injects responses as the decoy site.
-Censors cannot easily block access without also blocking
-legitimate connections to the decoy sites, which may be costly for the censor.
+A family of techniques called Refraction Networking~\cite{refraction-site,telex11,cirripede11,curveball11,tapdance14,rebound15,slitheen16,waterfall17}, formerly known
+as Decoy Routing, has made promising steps towards that goal.
+These techniques operate in the network's core, at cooperating Internet Service Providers
+(ISPs) outside censoring countries.
+Clients access circumvention service by connecting to a ``decoy site''---any uncensored website for which the connection travels over a participating ISP\@.
+Upon recognizing a steganographic signal from the client, the ISP modifies the connection response to return censored content requested by the user.
+Censors cannot easily block access without also blocking legitimate connections to the decoy sites---collateral damage that may be prohibitively costly for the censor~\cite{robinson2013collateral}.
+
 However, deploying such schemes in practice is more difficult than existing proxies:
@@
 Networking schemes has been deployed in practice by a large ISP:
-TapDance~\cite{tadance14}, a
+TapDance~\cite{tapdance14}, a
 Refraction Networking protocol that removes the need for inline
@@
 %-Connect to custom IP address, talk whatever protocol client/station agrees on
-In this paper, we present Dark Decoys, a new Refraction Networking protocol that
+In this paper, we present \scheme, a new Refraction Networking protocol that
 solves these issues, while maintaining the easy-to-deploy model of TapDance
@@
 real hosts. The ISP station acts as the other end of these connections, and responds as
-if it were a legitimate site or service. To the censor, these dark decoys appear
+if it were a legitimate site or service. To the censor, these phantom hosts appear
 as legitimate sites or services, and even active probes won't reveal
@@
 We implemented the Dark Decoy protocol and tested it in a 10~Gbps ISP testbed
-with real traffic. Similar to TapDance~\cite{tapdance}, we used PF\_RING to
+with real traffic. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to
 consume the 10~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
@@
 path to which passes by our tap.
-Client uses a Chosen-Ciphertext Steganography technique~\cite{tapdance} to manupulate
+Client uses a Chosen-Ciphertext Steganography technique~\cite{tapdance14} to manupulate
 plaintext of a first application data HTTP request
@@
 
+\TODO{Write (1 page)}
+
 Compare to TapDance performance:
@@
 
-Rebound~\cite{rebound15} and Waterfall~\cite{waterfall} both focus on routing
+Rebound~\cite{rebound15} and Waterfall~\cite{waterfall17} both focus on routing
 asymmetries and routing attacks by the censor. Rebound modifies the client's
@@
 
+\TODO{Write (0.5--0.75 page)}
+
 MultiFlow, The Waterfall of Liberty, Slitheen, Rebound, TapDance, Cirripede, Telex, Decoy Routing
@@
 
+\TODO{Write (0.5 page)}
+
 \section{Conclusion}
 %.25 page
+
+\TODO{Write (0.25 page}
 

### 2019-02-15 script/analyze.sh
add scripts for ip bit counting

@@ -1,0 +1,16 @@
+#!/bin/bash
+
+#python gen-addrs.py 100000 | python count-v6-bits.py | sort -n > rand.pdf
+#cat rand.pdf | cdf > rand.cdf
+
+cat all-by-pkt.out | grep '^2001:48a8:' | sort | uniq | python count-v6-bits.py | sort -n > merit-observed.pdf
+cat merit-observed.pdf | cdf > merit-observed.cdf
+
+#cat merit-observed.pdf | sort -n | uniq -c > merit-observed.counts
+
+cat all-by-pkt.out | sort | uniq | python count-v6-bits.py | sort -n > all-observed.pdf
+
+cat all-observed.pdf | cdf > all-observed.cdf
+
+gnuplot bits.gnuplot
+

### 2019-02-15 paper/figures.tex

@@
     \includegraphics[width=0.60\linewidth,clip]{figures/dark-decoy-overview.png}
-    \caption{\textbf{Dark Decoy Overview}\,---\, %
+    \caption{\textbf{\scheme Overview}\,---\, %
     }
@@
     \caption{\textbf{Overview}---%
-      When deployed at an ISP, \scheme observes a mirror of inbound and outbound traffic.
+      When deployed at ISPs, \scheme monitors a passive network tap.
       Users request service by embedding a steganographic registration message in a TLS handshake with any reachable site at the ISP\@. Then, the client connects to a random unused (``dark'')
-      address in the ISP's AS, and \scheme communicates with the client as if it were a proxy at that address.
+      address in the ISP's AS, and \scheme injects packets to communicates with the client as if it were a proxy server at that address.
     }
@@
             \rot{Decoy Routing~\cite{curveball11}} &
-            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall}} & \rot{\textbf{Dark Decoys}} \\
+            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall}} & \rot{\textbf{\scheme}} \\
             \hline

### 2019-02-15 paper/figures.tex
+entropy attack fig and text, and a hand-wavy defense

@@
     \label{fig:overview}
+\end{figure}
+}
+
+\newcommand{\FigIpBits}{
+\begin{figure}[t]
+    \centering
+    \vspace{-0.5in}
+    \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
+    \caption{\textbf{IPv6 Entropy}---%
+        We observed 30 minutes of IPv6 traffic on our tap to the /32 of the ISP's network.
+        In each address observed, we counted the number of bits set, and compared this to
+        randomly generated addresses. If the 96 non-network bits
+        of each address were chosen randomly, we would expect to see a normal distribution
+        (shown as Random). In practice, the distribution of observed IP addresses has much fewer
+        bits set, suggesting that censors might be able to distinguish between dark decoy addresses
+        and legitimate ones.
+        %We note there are several /64 subnets that had many
+        %addresses that appeared random (visibly overlapping the random distribution).
+    }
+    \label{fig:ipbits}
 \end{figure}

### 2019-02-15 paper/paper.tex
+entropy attack fig and text, and a hand-wavy defense

@@
 
-\if0
+\FigIpBits
+
 \paragraph{Address entropy}
@@
 giving censors a possible feature to filter on: addresses that have too much
-entropy could be suspicious as servers.
-\fi
+entropy (or even simply bits set) could be suspicious as dark decoys. To demonstrate and quantify
+this problem, we measured 30 minutes of IPv6 traffic to our ISP's /32 network prefix.
+Figure~\ref{fig:ipbits} shows a histogram of bits set in the addresses we observed, which are
+notably skewed to less than expected if addresses were randomly generated. However, there
+are still a significant number of networks that appear to have random-looking addresses,
+making it difficult for censors to block these addresses outright. For a specific deployment,
+operators should be careful to observe the distribution of addresses in the subnets they use,
+and possibly limit to randomizing ``realistic'' bits (e.g. the middle and/or last 32 bits).
 

### 2019-02-15 paper/figures.tex
Edits throughout intro

--- 2019-02-15 paper/figures.tex
@@
     \caption{\textbf{Overview}---%
-      When deployed at ISPs, \scheme monitors a passive network tap.
-      Users request service by embedding a steganographic registration message in a TLS handshake with any reachable site at the ISP\@. Then, the client connects to a random unused (``dark'')
-      address in the ISP's AS, and \scheme injects packets to communicates with the client as if it were a proxy server at that address.
+      \scheme is deployed at an ISP using a passive network tap.
+      Clients request service by embedding a steganographic registration message in a TLS connection with any reachable site at the ISP\@. The client selects
+      an unused (``dark'') address in the client's AS, and \scheme
+      injects packets to communicate with the client as if it were a proxy server at that address.
     }
-    \label{fig:overview}
+    \label{fig:highlevel}
 \end{figure}

### 2019-02-15 paper/paper.tex
Edits throughout intro

--- 2019-02-15 paper/paper.tex
@@
 \usepackage{subcaption}
+\usepackage{paralist}
 \usepackage{xspace}
@@
   Conjuring Proxies from Unused Address Space}
+\title{\Large \bf Conjure: Summoning Proxies from Unused Address Space}
 
@@
 These phantom hosts are difficult for a censor to distinguish from
-ones, but can be used by clients as proxies.  We define the
+real ones, but can be used by clients as proxies.  We define the
 \scheme protocol, analyze its security, and evaluate a
 prototype using an ISP testbed.
-Our results suggest that \scheme can be as difficult to block
-as TapDance, is simpler to maintain and deploy,
+Our results suggest that \scheme can be harder to block
+than TapDance, is simpler to maintain and deploy,
 and offers substantially better network performance.
@@
 %-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
-A family of techniques called Refraction Networking~\cite{refraction-site,telex11,cirripede11,curveball11,tapdance14,rebound15,slitheen16,waterfall17}, formerly known
+A family of techniques called Refraction Networking~\cite{telex11,cirripede11,curveball11,tapdance14,rebound15,slitheen16,waterfall17}, formerly known
 as Decoy Routing, has made promising steps towards that goal.
 These techniques operate in the network's core, at cooperating Internet Service Providers
-(ISPs) outside censoring countries.
+(ISPs) outside censoring countries~\cite{refraction-site}.
 Clients access circumvention service by connecting to a ``decoy site''---any uncensored website for which the connection travels over a participating ISP\@.
 Upon recognizing a steganographic signal from the client, the ISP modifies the connection response to return censored content requested by the user.
-Censors cannot easily block access without also blocking legitimate connections to the decoy sites---collateral damage that may be prohibitively costly for the censor~\cite{robinson2013collateral}.
+Censors cannot easily block access without also blocking legitimate connections to the decoy sites---collateral damage that may be prohibitive for censors if Refraction is widely deployed~\cite{robinson2013collateral}.
 
-However, deploying such schemes in practice is more difficult than existing proxies:
-convincing ISPs to deploy proxies in their production network is a significant
-operational hurdle. To date, only one of six Refraction
-Networking schemes has been deployed in practice by a large ISP:
-TapDance~\cite{tapdance14}, a
-Refraction Networking protocol that removes the need for inline
-flow-blocking~\cite{frolov2017isp}.
+However, deploying such schemes is more difficult than with most
+edge-based circumvention techniques, since ISPs must be convinced to
+operate the systems in their production networks.  To date, only
+TapDance~\cite{tapdance14}, one of six Refraction Networking
+proposals, has been deployed at ISP scale~\cite{frolov2017isp}.
+
+TapDance was designed for ease of deployment.
+Instead of in-line network devices required by earlier schemes, it
+calls for only a passive tap.
+This ``on-the-side'' approach, though much friendlier from an ISP's
+perspective, leads to major challenges when interposing in an ongoing
+client-to--decoy connection:
+\begin{compactitem}
+\item Implementation is complex and error-prone, requiring kernel
+  patches or a custom TCP stack. 
+\item To avoid detection, the system must carefully mimmick
+  subtle features of each decoy's TCP and TLS behavior.
+\item The architecture cannot resist active probing attacks, where the
+  censor sends specially crafted packets to determine whether a
+  suspected connection is using TapDance.
+\item Interactions with the decoy's network stack limit the length and
+  duration of each connection, forcing TapDance to multiplex
+  long-lived proxy connections over many shorter decoy
+  connections. This adds overhead and creates a traffic pattern
+  that is challenging to conceal. 
+\end{compactitem}
 
@@
 %-Other performance limits (upload limit, TCP window size)
-But in order to be deployed, TapDance makes an aggressive tradeoff
-between observability by censors for the sake of ease of deployment.
-For instance, TapDance's passive ``on the side'' architecture
-does not resist active probing attacks, where the censor can send packets that
-confirm whether or not a suspected connection is indeed a TapDance connection.
-The use of real-world decoy sites also presents practical problems: If
-decoys are limited or not particularly important, it may be easy for a
-censor to block them altogether without much collateral damage. In addition,
-TapDance has several performance limitations due to its interaction with
-real decoys. For example, TapDance clients' individual connection duration and upload
-capacities are limited due to the interaction with the decoy's TCP and TLS stack
-behavior. This forces TapDance to multiplex long-lived proxy connections over
-several repeated shorter-duration decoy connections, which increases overhead and may
-produce a connection pattern that is visible to censors.
 
-\medskip
+%% AH: I'm not sure I buy this limited decoys argument. If there are
+%% few decoys, there is little collateral damage of blocking
+%% everything in the AS, and \scheme is at a big disadvantage too.
+%The use of real-world decoy sites also presents practical problems: If
+%decoys are limited or not particularly important, it may be easy for a
+%censor to block them altogether without much collateral damage.
 
@@
 %-Connect to custom IP address, talk whatever protocol client/station agrees on
-In this paper, we present \scheme, a new Refraction Networking protocol that
-solves these issues, while maintaining the easy-to-deploy model of TapDance
-(i.e. a passive network tap). In our scheme, clients register new fictitious
-decoys in the ``dark'' or unused address space of the deploying ISP. Once
-registered, clients can connect to these dark decoy IP addresses as if they were
-real hosts. The ISP station acts as the other end of these connections, and responds as
-if it were a legitimate site or service. To the censor, these phantom hosts appear
-as legitimate sites or services, and even active probes won't reveal
-information that would allow the censor to block them.
+
+\smallskip
+
+In this paper, we present \textbf{\scheme}, a Refraction
+Networking protocol that overcomes these challenges while retaining
+TapDance's ISP-friendly deployment requirements.
+Our key innovation is an architecture that avoids
+having to actively participate in client-to-decoy connections.
+
+\TODO{more precise:}
+In our scheme (Figure~\ref{fig:highlevel}), clients 
+request the creation of phantom hosts in the ``dark''
+or unused address space of the deploying ISP. Once registered, clients
+can connect to these phantom hosts IP addresses as if they were real
+proxy servers. The ISP station acts as the other end of these connections, and
+responds as if it were a legitimate site or service. To the censor,
+these phantom hosts appear as legitimate sites or services, and even
+active probes will not reveal information that would allow the censor to
+block them.
+
+%% requests service
+%% by embedding a steganographic registration message in a TLS handshake
+%% with a decoy site. This message, which the ISP station can passively
+%% observe using a private key, uniquely determines an IP address within
+%% the ISP's address space. If there is no server running at that address,
 
@@
 %-No pesky TCP/TapDance-y limits
-Dark decoys are cheap to create, allowing for discardable \textbf{one-time use}
-addresses to be used by clients. This greatly increases the cost for censors to
+
+Phantom hosts are cheap to create, allowing for discardable \textbf{one-time use}
+proxy servers to be used by clients. This greatly increases the cost for censors to
 block, as they must detect and block in real time. Meanwhile, even a censor that
-can detect 90\% of dark decoys does not significantly increase the cost to the
-circumvention system, giving dark decoys an advantage in the censor/circumventor
+can detect 90\% of phantom hosts does not significantly increase the cost to the
+circumvention system, giving \scheme an advantage in the censor/circumventor
 cat-and-mouse game.
-We support both IPv4 and IPv6 dark decoys, though we note they are especially
-powerful in IPv6 where censors cannot exhaustively scan ahead of time to
-identify addresses that change behavior.
-Because we fully control the server side, dark decoy connections can live as
-long as needed, without the upload or timing limits faced by TapDance.
+\scheme supports both IPv4 and IPv6, though we note that the technique is especially
+powerful in IPv6, where censors cannot exhaustively scan the address space
+ahead of time to identify addresses that change behavior.
+Because we fully control the transport connection, connections can live as
+long as needed, without the complexity faced by TapDance.
 
@@
 % We implement it, it works...
-We implement our dark decoy protocol under the same model as TapDance using
-only a passive tap at an ISP. Furthermore, our protocol also works with
-asymmetric routing (i.e. when the tap can only see packets from but not to the
-client). We test our deployment on a 10~Gbps real-world ISP testbed similar to the
-TapDance deployment~\cite{frolov2017isp}, and evaluate the performance and
-observability compared to TapDance.
+
+We introduce the \scheme protocol (Section~\ref{sec:architecture})
+and analyze its security, finding that it resists a broader
+range of detection attacks than TapDance.
+We have implemented a prototype implementation (Section~\ref{sec:implementation})
+and deployed it on a 10~Gbps testbed similar to the TapDance
+deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
+\scheme has reduced complexity and substantially improved performance
+(Section~\ref{sec:evaluation}).
 
@@
 tap at the deploying ISP, and the ability to inject (spoofed) traffic from dark
-decoy sites. However, we assume a stronger threat model for the adversary than
+decoy sites.
+Furthermore, we assume
+asymmetric routing (i.e. that the tap can sometimes only see packets from but not to the
+client).
+However, we assume a stronger threat model for the adversary than
 TapDance, as our design resists active attacks.
@@
 \section{Architecture}
+\label{sec:architecture}
 % 3 pages
@@
 \section{Implementation}
+\label{sec:implementation}
 
@@
 \section{Evaluation}
+\label{sec:evaluation}
 % 1 page

### 2019-02-15 paper/figures.tex

@@
     \label{fig:highlevel}
+\end{figure}
+}
+
+\newcommand{\FigIpBits}{
+\begin{figure}[t]
+    \centering
+    \vspace{-0.5in}
+    \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
+    \caption{\textbf{IPv6 Entropy}---%
+        We observed 30 minutes of IPv6 traffic on our tap to the /32 of the ISP's network.
+        In each address observed, we counted the number of bits set, and compared this to
+        randomly generated addresses. If the 96 non-network bits
+        of each address were chosen randomly, we would expect to see a normal distribution
+        (shown as Random). In practice, the distribution of observed IP addresses has much fewer
+        bits set, suggesting that censors might be able to distinguish between dark decoy addresses
+        and legitimate ones.
+        %We note there are several /64 subnets that had many
+        %addresses that appeared random (visibly overlapping the random distribution).
+    }
+    \label{fig:ipbits}
 \end{figure}

### 2019-02-15 paper/paper.tex

@@
 
+\FigIpBits
+
+\paragraph{Address entropy}
+Addresses in IPv6 are commonly shortened, as many of the 128-bits in the address are set to 0.
+For instance, google.com has the address
+\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
+\texttt{2607:f8b0:400f:806::2004}). Only 24 bits are set to 1 in this address,
+giving censors a possible feature to filter on: addresses that have too much
+entropy (or even simply bits set) could be suspicious as dark decoys. To demonstrate and quantify
+this problem, we measured 30 minutes of IPv6 traffic to our ISP's /32 network prefix.
+Figure~\ref{fig:ipbits} shows a histogram of bits set in the addresses we observed, which are
+notably skewed to less than expected if addresses were randomly generated. However, there
+are still a significant number of networks that appear to have random-looking addresses,
+making it difficult for censors to block these addresses outright. For a specific deployment,
+operators should be careful to observe the distribution of addresses in the subnets they use,
+and possibly limit to randomizing ``realistic'' bits (e.g. the middle and/or last 32 bits).
+
 \section{Related Work}

### 2019-02-15 paper/figures.tex
Fix name
add up/download figs

@@
     \label{fig:highlevel}
+\end{figure}
+}
+
+\newcommand{\FigUpload}{
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.90\linewidth,clip]{figures/bandwidth-up.pdf}
+    \caption{\textbf{Upload Performance}\,---\, %
+        We used iperf to measure the upload bandwidth for a direct connection, TapDance, and \scheme.
+        As expected, TapDance's upload performance is several orders of magnitude lower than
+        the link capacity, due to the overhead of frequent reconnects to the decoy.
+    }
+    \label{fig:upload}
+\end{figure}
+}
+
+\newcommand{\FigDownload}{
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.90\linewidth,clip]{figures/bandwidth-down.pdf}
+    \caption{\textbf{Download Performance}\,---\, %
+        Using iperf, we compare the download performance of a direct connection, TapDance, and \scheme.
+        While TapDance can achieve link capacity download, it still has to occasionally reconnect
+        to the decoy, as seen by the periodic dips. These reconnects are more common the more data
+        the client sends (e.g. requests or any upload data).
+    }
+    \label{fig:download}
 \end{figure}
@@
 \newcommand{\TabCompare}{
-\begin{table*}[ht]
+\begin{table*}[t]
     \centering

### 2019-02-15 script/analyze.sh

@@ -3,12 +3,12 @@
 #python gen-addrs.py 100000 | python count-v6-bits.py | sort -n > rand.pdf
 #cat rand.pdf | cdf > rand.cdf
 
-cat all-by-pkt.out | grep '^2001:48a8:' | sort | uniq | python count-v6-bits.py | sort -n > merit-observed.pdf
+cat ./data/all-by-pkt.out | grep '^2001:48a8:' | sort | uniq | python count-v6-bits.py | sort -n > merit-observed.pdf
 cat merit-observed.pdf | cdf > merit-observed.cdf
 
 #cat merit-observed.pdf | sort -n | uniq -c > merit-observed.counts
 
-cat all-by-pkt.out | sort | uniq | python count-v6-bits.py | sort -n > all-observed.pdf
+cat ./data/all-by-pkt.out | sort | uniq | python count-v6-bits.py | sort -n > all-observed.pdf
 
 cat all-observed.pdf | cdf > all-observed.cdf
 

### 2019-02-15 paper/paper.tex
Fix name
add up/download figs
eval section

@@
   Conjuring Proxies from Unused Address Space}
-\title{\Large \bf Conjure: Summoning Proxies from Unused Address Space}
+%\title{\Large \bf Conjure: Summoning Proxies from Unused Address Space}
 
@@
 
-\newcommand{\scheme}{Conjure\xspace}
-%\newcommand{\scheme}{Dark Decoys\xspace}
+%\newcommand{\scheme}{Conjure\xspace}
+\newcommand{\scheme}{Dark Decoys\xspace}
 
@@
 
-\TODO{Write (1 page)}
+%\TODO{Write (1 page)}
 
-Compare to TapDance performance:
--Connection setup time
--Connection/session lifetime
--Throughput (especially upload vs download)
--Security considerations
+\FigTapBandwidth
+
+\FigUpload
+
+\FigDownload
+
+To evaluate our \scheme implementation, we compare its bandwidth
+to that of TapDance in a realistic ISP setting. We used a full duplex 10~Gbps
+network tap at a mid-sized ISP and run both implementations on a 1U server with
+an 8-core Intel Xeon E5-2640 CPU, 64GB of RAM, and a dual-port Intel X710 10GbE SFP+
+network interface. A typical week of bandwidth seen on the tap is
+shown in Figure~\ref{fig:tap-bandwidth}, ranging from 2.4~Gbps to peaks above
+17~Gbps.
+
+We evaluated the performance of a client from a Singapore-based VPS,
+Figures~\ref{fig:upload} and~\ref{fig:download} show the upload and download as
+measured by iperf for TapDance, our \scheme implementation, and a direct
+connection to our iperf server in the ISP's network.
+
+TapDance must reconnect if the amount of data sent by the client
+exceeds a short TCP window (typically on the order of 32~KBytes) or the
+connection persists until a timeout (18-120 seconds). At each reconnect, the
+TapDance client naively blocks until a new TLS connection to the decoy and
+station has been established. Thus, when uploading files, TapDance has to create
+a new TLS connection for every 32~KBytes of data it sends, limiting its average
+upload bandwidth to less than 1~Mbps due to the high overhead. In contrast,
+our \scheme implementation is
+able to maintain the same connection during large uploads, and achieves
+performance inline with the direct connection.
+
+During download-only workloads, TapDance is able to better utilize the network,
+but must still reconnect before the decoy times out. In our tests, we see
+TapDance reconnect every 25 seconds, which can negatively impact the performance of
+downloads or any real-time streaming applications. Again, our \scheme
+implementation is able to maintain a single connection and provide the maximum
+download rate without interruption.
+
+%Compare to TapDance performance:
+%-Connection setup time
+%-Connection/session lifetime
+%-Throughput (especially upload vs download)
+%-Security considerations
 

### 2019-02-15 paper/paper.tex
minor comments, edits

--- 2019-02-15 paper/paper.tex
@@
 % For submission make this a noop
+\newcommand{\note}[2]{\textit{[#1: #2]}}
+\newcommand{\nikita}[1]{\note{nikita}{#1}}
 
@@
 %\usepackage{parskip}
-\usepackage{mathptmx}\renewcommand{\ttdefault}{cmtt}
 \usepackage{amsmath}
@@
 %\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
-%\setlength\parskip{1pt}
+\setlength\parskip{1pt}
 \usepackage{graphicx} % http://ctan.org/pkg/graphicx
@@
 \usepackage{cleveref}
-\usepackage{microtype}
-\SetExtraKerning{encoding=*,font=*}{\textemdash={120,120}} % Add space around emdashes
-\usepackage[font=small]{caption}
-\microtypecontext{spacing=nonfrench}
-\usepackage{subcaption}
-\usepackage{paralist}
-\usepackage{xspace}
-\usepackage{soul}
-\newcommand{\note}[2]{\hl{[\textbf{#1:} #2]}\xspace}
-\newcommand{\nikita}[1]{\note{nikita}{#1}}
-\newcommand{\TODO}[1]{\hl{TODO: #1}\xspace}
-\newcommand{\TK}{\hl{TK}\xspace}
-
-% Slight JAH fix to stop URLs from breaking after ``http:''
-\def\UrlBreaks{\do-\do\.\do\@\do\\\do\!\do\_\do\|\do\;\do\>\do\]%
- \do\)\do\,\do\?\do\'\do+\do\=\do\#}
-\def\UrlBigBreaks{\do\:\do\/}%
-\urlstyle{rm}
-
-\renewcommand{\paragraph}[1]{\smallskip\noindent\textbf{#1\quad}}
 
@@
   Conjuring Proxies from Unused Address Space}
-\title{\Large \bf Conjure: Summoning Proxies from Unused Address Space}
 
@@
 
-\newcommand{\scheme}{Conjure\xspace}
-%\newcommand{\scheme}{Dark Decoys\xspace}
-
 %-------------------------------------------------------------------------------
@@
 %-------------------------------------------------------------------------------
-Refraction Networking (formerly known as ``Decoy Routing'') has
-emerged as a promising next-generation approach for circumventing
-Internet censorship. Rather than trying to hide individual
-circumvention proxy servers from censors, proxy functionality is
-implemented in the core of the network, at cooperating ISPs in
-friendly countries.  Any connection that traverses these ISPs could be
-a conduit for the free flow of information, so censors cannot easily
-block access without also blocking many legitimate sites.  While one
-Refraction scheme, TapDance, has recently been deployed at ISP-scale,
-it suffers from several problems: a limited number of ``decoy'' sites
-in realistic deployments, high technical complexity, and undesirable
-tradeoffs between performance and observability by the censor. These
-challenges may impede broader deployment and ultimately allow censors to
-block such techniques.
+Refraction Networking (formerly ``Decoy Routing'') has emerged as a useful tool in circumventing
+        Internet censorship. By placing proxies in cooperating Internet Service
+        Providers (ISPs) and using connections to existing reachable
+        ``decoy'' sites for transport, censors cannot easily block access to
+        such proxies without also blocking legitimate sites.
 
-We present \scheme, an improved Refraction Networking approach
-that overcomes these limitations by leveraging unused address space at
-deploying ISPs. Instead of using real websites as the decoy destinations
-for proxy connections, our scheme creates seemingly legitimate hosts
-on demand, at IP addresses where no web server exists.
-These phantom hosts are difficult for a censor to distinguish from
-real ones, but can be used by clients as proxies.  We define the
-\scheme protocol, analyze its security, and evaluate a
-prototype using an ISP testbed.
-Our results suggest that \scheme can be harder to block
-than TapDance, is simpler to maintain and deploy,
-and offers substantially better network performance.
+However, existing deployed Refraction Networking schemes such as TapDance \nikita{TapDance is the only deployed scheme} suffer
+from several problems, including a limited number of decoy sites in realistic
+deployments, and an unfavorable tradeoff between performance and observability
+by the censor. These problems limit where such proxies can be deloyed, hamper
+their effectiveness, and may ultimately make them possible for censors to block.
+
+In this paper, we present Dark Decoys, a deployable Refraction Networking scheme that
+overcomes the limits on decoys and performance. Dark Decoys leverages the (primarily) unused address
+space that is reachable through the deploying ISP. Rather than rely on existing
+sites as reachable decoy sites that must be involved in each proxy connection,
+Dark Decoys create seemingly legitimate hosts at new IP addresses. These
+invented hosts are indistinguishable from normal hosts to the censor, but can
+be used by clients as one-time proxies.
+
+We implement our scheme ... and it's just the bee's knees. TODO
 
 \end{abstract}
-
-\FigHighLevel
 
@@
 %-Existing countries blocking more
-%Internet censorship continues to hamper social progress throughout the world.
+Internet censorship continues to hamper social progress throughout the world.
+Over half of the global Internet population
+now live in countries that block political, social, or religious content
+online~\cite{fotn2018} as governments continue to expand their censorship
+policies and programs.
 
-Over half of Internet users globally
-now live in countries that block political, social, or religious content
-online~\cite{fotn2018}.
 %Existing circumvention strategies on shaky ground
@@
 %-Cenosrs fingerprinting known protocols
-Meanwhile, many popular tools and techniques for circumventing such censorship
-have ceased to function, because censors have evolved new ways to block them~\cite{ensafi-tor,great-cannon}
-or infrastructure they rely on has become unavailable.
-
-For example, domain fronting~\cite{meek} was a popular circumvention
-strategy used by Meek (in Tor), as well as by the Signal secure messaging app to
-get around censorship in countries where it was
-blocked~\cite{signal,signal-domain-fronting}.
+Meanwhile, strategies to circumvent censorship using proxies have suffered many
+recent setbacks. Many previously popular proxies are no longer functional due to
+censors evolving new ways to block them~\cite{ensafi-tor,great-cannon},
+or because they rely on temperamental
+infrastructure. For example, domain fronting was a popular circumvention
+strategy used by meek (in Tor), as well as the Signal secure messaging app to
+get around censorship in countries it was
+blocked~\cite{domain-fronting,signal,signal-domain-fronting}.
 But in May~2018, Google and Amazon made both technical and policy changes to
@@
 fronting, Signal abandoned the strategy altogether~\cite{signal-back-on-front}.
-There is an urgent need for new, more robust approaches to circumvention.
-
 %Combined with censors' constant improvements in discovery and blocking
@@
 %-acknowledge challenge of ISP deployment, cite TapDance deployment as only refraction technology that has overcome this challenge so far
-A family of techniques called Refraction Networking~\cite{telex11,cirripede11,curveball11,tapdance14,rebound15,slitheen16,waterfall17}, formerly known
-as Decoy Routing, has made promising steps towards that goal.
-These techniques operate in the network's core, at cooperating Internet Service Providers
-(ISPs) outside censoring countries~\cite{refraction-site}.
-Clients access circumvention service by connecting to a ``decoy site''---any uncensored website for which the connection travels over a participating ISP\@.
-Upon recognizing a steganographic signal from the client, the ISP modifies the connection response to return censored content requested by the user.
-Censors cannot easily block access without also blocking legitimate connections to the decoy sites---collateral damage that may be prohibitive for censors if Refraction is widely deployed~\cite{robinson2013collateral}.
-
-However, deploying such schemes is more difficult than with most
-edge-based circumvention techniques, since ISPs must be convinced to
-operate the systems in their production networks.  To date, only
-TapDance~\cite{tapdance14}, one of six Refraction Networking
-proposals, has been deployed at ISP scale~\cite{frolov2017isp}.
-
-TapDance was designed for ease of deployment.
-Instead of in-line network devices required by earlier schemes, it
-calls for only a passive tap.
-This ``on-the-side'' approach, though much friendlier from an ISP's
-perspective, leads to major challenges when interposing in an ongoing
-client-to--decoy connection:
-\begin{compactitem}
-\item Implementation is complex and error-prone, requiring kernel
-  patches or a custom TCP stack. 
-\item To avoid detection, the system must carefully mimmick
-  subtle features of each decoy's TCP and TLS behavior.
-\item The architecture cannot resist active probing attacks, where the
-  censor sends specially crafted packets to determine whether a
-  suspected connection is using TapDance.
-\item Interactions with the decoy's network stack limit the length and
-  duration of each connection, forcing TapDance to multiplex
-  long-lived proxy connections over many shorter decoy
-  connections. This adds overhead and creates a traffic pattern
-  that is challenging to conceal. 
-\end{compactitem}
+One emerging technique is Refraction Networking (also known as ``Decoy
+Routing''), which places proxies at cooperating Internet Service Providers
+(ISPs) outside censoring countries~\cite{refraction-site}. Clients access the
+proxies by connecting to unblocked ``decoy'' sites such that the packets pass by
+the ISP proxy, which intercepts and injects responses as the decoy site.
+Censors cannot easily block access without also blocking
+legitimate connections to the decoy sites, which may be costly for the censor.
+However, deploying such schemes in practice is more difficult than existing proxies:
+convincing ISPs to deploy proxies in their production network is a significant
+operational hurdle. To date, only one of six Refraction
+Networking schemes has been deployed in practice by a large ISP:
+TapDance~\cite{tadance}, a
+Refraction Networking protocol that removes the need for inline
+flow-blocking~\cite{frolov2017isp}.
 
@@
 %-Other performance limits (upload limit, TCP window size)
+But in order to be deployed, TapDance makes an aggressive tradeoff
+between observability by censors for the sake of ease of deployment.
+For instance, TapDance's passive ``on the side'' architecture
+does not resist active probing attacks, where the censor can send packets that
+confirm whether or not a suspected connection is indeed a TapDance connection.
+The use of real-world decoy sites also presents practical problems: If
+decoys are limited or not particularly important, it may be easy for a
+censor to block them altogether without much collateral damage. In addition,
+TapDance has several performance limitations due to its interaction with
+real decoys. For example, TapDance clients' individual connection duration and upload
+capacities are limited due to the interaction with the decoy's TCP and TLS stack
+behavior. This forces TapDance to multiplex long-lived proxy connections over
+several repeated shorter-duration decoy connections, which increases overhead and may
+produce a connection pattern that is visible to censors.
 
-%% AH: I'm not sure I buy this limited decoys argument. If there are
-%% few decoys, there is little collateral damage of blocking
-%% everything in the AS, and \scheme is at a big disadvantage too.
-%The use of real-world decoy sites also presents practical problems: If
-%decoys are limited or not particularly important, it may be easy for a
-%censor to block them altogether without much collateral damage.
+\FigHighLevel
+
+\medskip
 
@@
 %-Connect to custom IP address, talk whatever protocol client/station agrees on
-
-\smallskip
-
-In this paper, we present \textbf{\scheme}, a Refraction
-Networking protocol that overcomes these challenges while retaining
-TapDance's ISP-friendly deployment requirements.
-Our key innovation is an architecture that avoids
-having to actively participate in client-to-decoy connections.
-
-\TODO{more precise:}
-In our scheme (Figure~\ref{fig:highlevel}), clients 
-request the creation of phantom hosts in the ``dark''
-or unused address space of the deploying ISP. Once registered, clients
-can connect to these phantom hosts IP addresses as if they were real
-proxy servers. The ISP station acts as the other end of these connections, and
-responds as if it were a legitimate site or service. To the censor,
-these phantom hosts appear as legitimate sites or services, and even
-active probes will not reveal information that would allow the censor to
-block them.
-
-%% requests service
-%% by embedding a steganographic registration message in a TLS handshake
-%% with a decoy site. This message, which the ISP station can passively
-%% observe using a private key, uniquely determines an IP address within
-%% the ISP's address space. If there is no server running at that address,
+In this paper, we present Dark Decoys, a new Refraction Networking protocol that
+solves these issues, while maintaining the easy-to-deploy model of TapDance
+(i.e. a passive network tap). In our scheme, clients register new fictitious
+decoys in the ``dark'' or unused address space of the deploying ISP. Once
+registered, clients can connect to these dark decoy IP addresses as if they were
+real hosts. The ISP station acts as the other end of these connections, and responds as
+if it were a legitimate site or service. To the censor, these dark decoys appear
+as legitimate sites or services, and even active probes won't reveal
+information that would allow the censor to block them.
 
@@
 %-No pesky TCP/TapDance-y limits
-
-Phantom hosts are cheap to create, allowing for discardable \textbf{one-time use}
-proxy servers to be used by clients. This greatly increases the cost for censors to
+Dark decoys are cheap to create, allowing for discardable \textbf{one-time use}
+addresses to be used by clients. This greatly increases the cost for censors to
 block, as they must detect and block in real time. Meanwhile, even a censor that
-can detect 90\% of phantom hosts does not significantly increase the cost to the
-circumvention system, giving \scheme an advantage in the censor/circumventor
+can detect 90\% of dark decoys does not significantly increase the cost to the
+circumvention system, giving dark decoys an advantage in the censor/circumventor
 cat-and-mouse game.
-\scheme supports both IPv4 and IPv6, though we note that the technique is especially
-powerful in IPv6, where censors cannot exhaustively scan the address space
-ahead of time to identify addresses that change behavior.
-Because we fully control the transport connection, connections can live as
-long as needed, without the complexity faced by TapDance.
+We support both IPv4 and IPv6 dark decoys, though we note they are especially
+powerful in IPv6 where censors cannot exhaustively scan ahead of time to
+identify addresses that change behavior.
+Because we fully control the server side, dark decoy connections can live as
+long as needed, without the upload or timing limits faced by TapDance.
 
@@
 % We implement it, it works...
-
-We introduce the \scheme protocol (Section~\ref{sec:architecture})
-and analyze its security, finding that it resists a broader
-range of detection attacks than TapDance.
-We have implemented a prototype implementation (Section~\ref{sec:implementation})
-and deployed it on a 10~Gbps testbed similar to the TapDance
-deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
-\scheme has reduced complexity and substantially improved performance
-(Section~\ref{sec:evaluation}).
+We implement our dark decoy protocol under the same model as TapDance using
+only a passive tap at an ISP. Furthermore, our protocol also works with
+asymmetric routing (i.e. when the tap can only see packets from but not to the
+client). We test our deployment on a 10~Gbps real-world ISP testbed similar to the
+TapDance deployment~\cite{frolov2017isp}, and evaluate the performance and
+observability compared to TapDance.
 
@@
 tap at the deploying ISP, and the ability to inject (spoofed) traffic from dark
-decoy sites.
-Furthermore, we assume
-asymmetric routing (i.e. that the tap can sometimes only see packets from but not to the
-client).
-However, we assume a stronger threat model for the adversary than
+decoy sites. However, we assume a stronger threat model for the adversary than
 TapDance, as our design resists active attacks.
@@
 \section{Architecture}
-\label{sec:architecture}
 % 3 pages
@@
 \section{Implementation}
-\label{sec:implementation}
-
-We implemented the Dark Decoy protocol and tested it in a 10~Gbps ISP testbed
-with real traffic. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to
-consume the 10~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
-detector processes all packets and watches for new registrations. It also
-forwards all packets sent to a (registered) dark decoy's address to the local
-\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
-allowing the application to accept and respond to connections using the native
-operating system's interface. Figure~\ref{fig:implementation} shows the overall
-architecture of our implementation, which we describe next.
-% Along with the client?
-
-\FigImplementation
-
-\subsection{Detector}
-
-Our detector is a modified fork of the open source TapDance
-implementation~\cite{tapdance-source}.
-We implemented our detector in approximately 1,800 lines of Rust (compared to
-over 5,000 lines for TapDance)\footnote{excluding (from both) about 3,000 lines
-of auto-generated protobuf code}.
-
-We used PF\_RING to load balance the 10~Gbps link over 4~CPU cores. PF\_RING
-supports balancing across cores based on flow (5-tuple) or source and
-destination IPs. However, both of these options present challenges for our Dark
-Decoy detector. One issue is that registrations could be processed on a
-different core than the packets sent to that specific dark decoy address. For
-instance, a client could have its registration handled by Core 1, while its
-packets to the dark decoy address end up on Core 3, which doesn't know about the
-original registration.
-
-To address this, we used Redis~\cite{redis} to allow each process to announce
-(publish) newly registered decoys to the other cores so they can
-add them to their local list of registered dark decoy addresses.
-However, this introduces two new problems. First, a core might add a
-registration \emph{after} it has already received and processed packets destined
-for the specified dark decoy. This typically isn't a problem when running on a
-single core, as packets are processed sequentially. Second, each core may
-timeout each dark decoy at different times, potentially leading to differing
-behavior that is visible to a censor. For instance, if we used the
-source/destination IPs to load balance, a censor's packets to a dark decoy could
-be processed by a different core than the client. If the censor waits for the
-known timeout before sending a probe, its core may have timed out that dark
-decoy, while the client's core has refreshed the timeout of the dark decoy due
-to active use.
-
-To address the first issue, we force the client to delay sending its connection
-to the dark decoy until a short time after registration. In practice, we force
-the client to wait until the registration decoy responds before starting a
-connection with the registered dark decoy.
-
-To address the second issue, we implemented a new load-balancing algorithm in
-PF\_RING to select the core based solely on the destination IP address of the
-packet. This still means we must use Redis to tell all of the cores of new
-registrations, but that only one core will be responsible for processing all of
-the packets sent to a given dark decoy, regardless of who or when it is sent.
-
-\subsection{Application}
-
-We implemented our application in about 500~lines of Golang. Though we note
-other protocols (e.g. obfsproxy or WebRTC) could be used as the application, we
-implemented a mask site mimicking application, that pretends to be a mask site
-when actively probed by the censor.
-
-The application accepts connections to dark decoy addresses forwarded by the
-detector and rewritten to the local address using \texttt{iptables}.
-The application also receives out-of-band information about registrations from the
-detector via a ZMQ~\cite{zmq} connection, which informs the application of the
-registering client's IP address, the secret seed, and other configuration
-information passed by the client.
-
-Once the application accepts a connection, it initially acts as a transparent
-proxy to the mask site specified by the client during registration. The
-application parses the handshake, forwarding packets back and forth between
-client and mask site without modification, and extracting the server and client
-randoms. The application attempts to decrypt the first application data record
-from the client using a key derived from the secret seed, and client and server
-randoms. We use the uTLS library~\cite{utls} on both the application and client
-to allow us to change the TLS secrets being used after the handshake.
-
-If the decryption is successful, the application switches to forwarding
-(decrypted) data back and forth with a client-specified endpoint, such as a
-SOCKS proxy, which can multiplex multiple client connections over the single
-connection to the dark decoy.
-
-\subsection{Client}
-
-Our client is also written in Golang, and uses a TapDance-like protocol for
-registration. We note that this protocol should be harder for censors to observe
-because it consists of only a single (complete) request, and the station does
-not have to spoof packets as the decoy used during registration, only passively
-observe them.
-
-After registering, the client connects to the derived dark decoy address, and
-switches secrets after the handshake. At this point, a local application (e.g.
-SOCKS client) can connect to the client, and it will transparently be connected to
-the remote end via the encrypted dark decoy connection.
-
-\if0
 In order to scale up to 10Gbps and beyond,
 one has to utilize multiple cores and employ load balancing.
-We use PF\_RING built-in load balancer \emph{zbalance} to efficiently
+We use PF\_RING built-in load balancer \textit{zbalance} to efficiently
 distribute load between 4 cores.
@@
 path to which passes by our tap.
-Client uses a Chosen-Ciphertext Steganography technique~\cite{tapdance14} to manupulate
+Client uses a Chosen-Ciphertext Steganography technique~\cite{tapdance} to manupulate
 plaintext of a first application data HTTP request
@@
 -Open source (client, station and application)
-\fi
 
 \section{Evaluation}
-\label{sec:evaluation}
 % 1 page
-
-\TODO{Write (1 page)}
 
@@
 Since 2011, there have been several proposed Refraction Networking schemes.
-Telex~\cite{telex11}, Cirripede~\cite{cirripede11} and Decoy
-Routing~\cite{curveball11} are ``first generation'' protocols with nearly
+Telex~\cite{telex}, Cirripede~\cite{cirripede} and Decoy
+Routing~\cite{curveball} are ``first generation'' protocols with nearly
 identical features. These designs require inline flow blocking at the ISP to
@@
 
-TapDance~\cite{tapdance14} solves the issue of inline-blocking by coercing the
+TapDance~\cite{tapdance} solves the issue of inline-blocking by coercing the
 decoy into staying silent, and allowing the station to respond instead. However,
@@
 
-Rebound~\cite{rebound15} and Waterfall~\cite{waterfall17} both focus on routing
+Rebound~\cite{rebound} and Waterfall~\cite{waterfall} both focus on routing
 asymmetries and routing attacks by the censor. Rebound modifies the client's
@@
 
-Slitheen~\cite{slitheen16} focuses on addressing observability by replacing
+Slitheen~\cite{slitheen} focuses on addressing observability by replacing
 data in packets sent by the legitimate decoy. Thus, even the packet timings and
@@
 
-\TODO{Write (0.5--0.75 page)}
-
 MultiFlow, The Waterfall of Liberty, Slitheen, Rebound, TapDance, Cirripede, Telex, Decoy Routing
@@
 
-\TODO{Write (0.5 page)}
-
 \section{Conclusion}
 %.25 page
-
-\TODO{Write (0.25 page}
 
@@
 %-------------------------------------------------------------------------------
-
 \bibliographystyle{plain}
-\small
 \bibliography{biblio}

### 2019-02-15 paper/paper.tex
updated WF text

--- 2019-02-15 paper/paper.tex
@@
 \paragraph{Website Fingerprinting}
-Dark Decoy applications that mimic websites (e.g. mask sites) may be vulnerable
-to website fingerprinting, where the censor observes that clients accessing
-suspected dark decoy IPs are receiving payloads or packet timings that differ
-from legitimate connections to the mask site. This attack is difficult for
-censors to carry out because it has high uncertainty: even a small false
+
+Website Fingerprinting~\cite{kNN,kFP,DLFP} (WF) uses the patterns of encrypted traffic to identify which website a client is connected to.
+WF uses a classifier to label the traffic as belonging to one of several known websites, or (in some variants), an unknown or background class.
+Though WF is commonly studied in the context of anonymous web browsing, a censor could also use WF to detect refraction networking by distinguishing known traffic patterns of legitimate uses of a decoy site from the traffic generated by refraction networking (unknown class).
+Alternatively, the censor could monitor all traffic for patterns consistent with a set of blocked websites.
+
+Dark Decoy applications that mimic specific websites (e.g., mask sites) are likewise susceptible to WF.
+To date, however, censors have not been observed using WF and similar techniques, possibly due to the significant uncertainty resulting from even the best algorithms: even a small false
 positive rate means blocking mostly legitimate connections (due to the base rate
 of normal traffic), and false negatives could allow clients to retry until they
-gain access. More importantly, unlike previous Refraction Networking protocols,
+gain access.
+
+More importantly, Dark Decoy applications offer great flexibility in deploying traffic analysis defenses; for example, traffic shaping strategies such as implemented in Slitheen~\cite{slitheen16} could be easily employed in Dark Decoys.
+Furthermore,
 Dark Decoy applications are not limited to mimicking websites, and can support
 any (or even a combination of) protocols.
-
-%\paragraph{Probing Dark Decoys}
-%-Active probing TLS connection
-%    -Block access unless from registering source IP
-%        -cite GFW taking over client IPs for active probing of old obfs
-%    -Verify knowledge of seed (but how to respond when verification fails?)
+Finally, if encrypted SNI can be used (\cref{esni}), the censor would not be able to build up a traffic profile of a legitimate site since its identity would be encrypted.
 

### 2019-02-15 paper/figures.tex
binomial, not normal distribution
Add bandwidth fig

@@
 
+\newcommand{\FigTapBandwidth}{
+\begin{figure*}[t]
+    \centering
+    \includegraphics[width=0.90\linewidth,clip]{figures/decoy-tap-bandwidth.png}
+    \caption{\textbf{Tap Bandwidth}\,---\, %
+        We deployed our \scheme implementation in a realistic ISP testbed on a
+        (full duplex) tap of a 10~Gbps router. As shown in a typical week, traffic
+        ranges from 2-17~Gbps.
+    }
+    \label{fig:tap-bandwidth}
+\end{figure*}
+}
+
 \newcommand{\FigIpBits}{
@@
         randomly generated addresses. If the 96 non-network bits
-        of each address were chosen randomly, we would expect to see a normal distribution
+        of each address were chosen randomly, we would expect to see a Binomial distribution
         (shown as Random). In practice, the distribution of observed IP addresses has much fewer

### 2019-02-15 paper/paper.tex
related work section

@@
 
-\subsection{Comparison to Prior Schemes}
-
-Since 2011, there have been several proposed Refraction Networking schemes.
-Telex~\cite{telex11}, Cirripede~\cite{cirripede11} and Decoy
-Routing~\cite{curveball11} are ``first generation'' protocols with nearly
-identical features. These designs require inline flow blocking at the ISP to
-allow the station to intercept flows with detected tags and act as the decoy
-host for them. However, inline-blocking is difficult for ISPs to deploy, as it
-requires special-purpose hardware to be placed inline with production traffic,
-introducing risk of failures and outages that may be expensive for the ISP
-and potentially violate their contractual obligations (SLAs).
-
-TapDance~\cite{tapdance14} solves the issue of inline-blocking by coercing the
-decoy into staying silent, and allowing the station to respond instead. However,
-as previously described, this trick comes at a cost: the decoy only stays silent
-for a short timeout (typically 30-120 seconds), and limits the amount of data
-the client can send before it responds. TapDance clients must keep connections
-short and repeatedly reconnect to decoys, increasing overhead and potentially
-alerting censors with this pattern. Dark Decoys addresses this issue and allows
-clients to maintain long-lived connections to the dark decoy.
-
-Rebound~\cite{rebound15} and Waterfall~\cite{waterfall17} both focus on routing
-asymmetries and routing attacks by the censor. Rebound modifies the client's
-packets on the way to the decoy, and uses error pages on the decoy site to
-reflect data back to the client. Waterfall only observes and modifies the
-decoy-to-client traffic, similarly using error pages on the decoy to reflect
-communication from the client to the station. These schemes also provide some
-resistance to traffic analysis, as they use the real decoy to reflect data to
-the user. Thus, the TCP/TLS behavior seen by the censor more closely matches
-that of a legitimate decoy connection. However, latency and other packet-timing
-characteristics may be observable, and both schemes require some form of inline
-flow blocking.
-
-Slitheen~\cite{slitheen16} focuses on addressing observability by replacing
-data in packets sent by the legitimate decoy. Thus, even the packet timings and
-sizes of a Slitheen connection match that of a legitimate decoy connection.
-However, Slitheen also requires inline-blocking, and introduces a large overhead
-as it has to wait for the subset of data-carrying packets from the decoy that
-Slitheen can safely replace. We note that the Slitheen model of mimicry is
-compatible with Dark Decoys, as we could use Slitheen as the application
-protocol. Despite using a passive tap, our scheme is effectively inline to the
-dark decoy (which won't otherwise respond).
-
-Dark Decoys allow a large amount of flexibility compare to previous schemes.
-Because we have significant degrees of freedom in choosing the specific
-application the dark decoy will mimic or talk, our scheme can combine the best
-of existing Refraction Networking protocols to achieve high performance, be easy
-to deploy, and
-also be resistant to active attacks such as replaying or probing by the censor.
-Table~\ref{tab:compare} lists the existing Refraction Networking schemes and
-their features, as compared to Dark Decoys.
-
-\TabCompare
-
 \subsection{Attacks and Defenses}
@@
 
-\section{Related Work}
+\input{related}
 % 0.5-0.75 page
-
-\TODO{Write (0.5--0.75 page)}
-
-MultiFlow, The Waterfall of Liberty, Slitheen, Rebound, TapDance, Cirripede, Telex, Decoy Routing
-True Cost of RAD, Routing around Decoys
-ISP-scale TapDance
 

### 2019-02-15 paper/related.tex
related work section

\section{Related Work}

We first compare Dark Decoys with other Refraction Networking schemes and then discuss other related work.

\subsection{Prior Refraction Networking Schemes}

Since 2011, there have been several proposed Refraction Networking schemes.
Telex~\cite{telex11}, Cirripede~\cite{cirripede11} and Decoy
Routing (aka Curveball)~\cite{curveball11} are ``first generation'' protocols with nearly
identical features. These designs require inline flow blocking at the ISP to
allow the station to intercept flows with detected tags and act as the decoy
host for them. However, inline blocking is difficult for ISPs to deploy, as it
requires special-purpose hardware to be placed inline with production traffic,
introducing risk of failures and outages that may be expensive for the ISP
and potentially violate their contractual obligations (SLAs).

TapDance~\cite{tapdance14} solves the issue of inline-blocking by coercing the
decoy into staying silent, and allowing the station to respond instead. However,
as previously described, this trick comes at a cost: the decoy only stays silent
for a short timeout (typically 30-120 seconds), and limits the amount of data
the client can send before it responds. TapDance clients must keep connections
short and repeatedly reconnect to decoys, increasing overhead and potentially
alerting censors with this pattern. Dark Decoys addresses this issue and allows
clients to maintain long-lived connections to the dark decoy.

Rebound~\cite{rebound15} and Waterfall~\cite{waterfall17} both focus on routing
asymmetries and routing attacks by the censor. Rebound modifies the client's
packets on the way to the decoy, and uses error pages on the decoy site to
reflect data back to the client. Waterfall only observes and modifies the
decoy-to-client traffic, similarly using error pages on the decoy to reflect
communication from the client to the station. These schemes also provide some
resistance to traffic analysis, as they use the real decoy to reflect data to
the user. Thus, the TCP/TLS behavior seen by the censor more closely matches
that of a legitimate decoy connection. However, latency and other packet-timing
characteristics may be observable, and both schemes require some form of inline
flow blocking.

Slitheen~\cite{slitheen16} focuses on addressing observability by replacing
data in packets sent by the legitimate decoy. Thus, even the packet timings and
sizes of a Slitheen connection match that of a legitimate decoy connection.
However, Slitheen also requires inline-blocking, and introduces a large overhead
as it has to wait for the subset of data-carrying packets from the decoy that
Slitheen can safely replace. We note that the Slitheen model of mimicry is
compatible with Dark Decoys, as we could use Slitheen as the application
protocol. Despite using a passive tap, our scheme is effectively inline to the
dark decoy (which won't otherwise respond).

Bocovich and Goldberg propose an asymmetric gossip scheme~\cite{secureasymmetry} that combines a passive monitor on the forward path from the client to the decoy with an inline blocking element on the return path. These elements work in concert to allow schemes such as Telex and Slitheen to work on asymmetric connections. This approach, however, still requires inline blocking on one direction, and further complicates deployment by requiring the installation of more components and potentially complex coordination between them. MultiFlow~\cite{multiflow} uses refraction networking only as a forward mechanism to communicate a web request to the station, and then uses a bulletin board or email to deliver the response back. It does not require inline flow blocking as it does not modify users' traffic at all, but it fundamentally relies on a separate data delivery mechanism, similar to other cloud- or email-based circumvention tools~\cite{SWEET-ToN,CloudTransport}.

Dark Decoys allow a large amount of flexibility compared to previous schemes.
Because we have significant degrees of freedom in choosing the specific
application the dark decoy will mimic or talk, our scheme can combine the best
of existing Refraction Networking protocols to achieve high performance, be easy
to deploy, and
also be resistant to active attacks such as replaying or probing by the censor.
Table~\ref{tab:compare} lists the existing Refraction Networking schemes and
their features, as compared to Dark Decoys.

\TabCompare

\subsection{Decoy Placement and Routing Attacks}

Houmansadr et al.~\cite{cirripede11} found that placing refraction proxies in a handful of Tier 1 networks would be sufficient for them to be usable by the majority of the Internet population. Cesareo et al.~\cite{decoy-placement} developed an algorithm for optimizing the placement of proxies based on AS-level Internet topology data. Schuchard et al.~\cite{rad} suggested that a censor may actively change its routes to ensure traffic leaving its country avoids the proxies, but Houmansadr et al.~\cite{true-cost-rad} suggested that real-world constraints on routing make this attack difficult to carry out in practice. Nevertheless, Nasr et al.~\cite{game-of-decoys} propose a game-theoretic framework to optimize proxy placement in an adversarial setting, and the design of Waterfall~\cite{waterfall17} is in part motivated by resilience to routing attacks, as it is more difficult for the censor to control the return path from a decoy site, rather than the forward path.

In practice, deployment of refraction networking has so far been at access, rather than transit ISPs~\cite{frolov2017isp}. This may be in part because a transit ISP has a large number of routers and points-of-presence, significantly raising the costs of deployment~\cite{devil-details}.\footnote{We
note that Gosain et al.~\cite{devil-details} use an estimate of \$885\,000 USD/proxy, while Frolov et al.~\cite{frolov2017isp} report line-rate TapDance deployment using commodity hardware that cost only several thousand dollars.} Likewise, we expect Dark Decoys to use address space announced by the ISP, rather than addresses relayed by it, which mitigates routing-based attacks. Depending on the size of the ISP, however, a censor may decide to block the entirety of its address space, which would incur smaller collateral damage than blocking all addresses seen by a transit ISP.

\subsection{Avoiding Destination Blocking}

Traditionally, proxies deployed for censorship are eventually identified and blocked by the censor. Several proposals have been made to carefully control  the distribution of proxy addresses, using social connections and reputation~\cite{proximax,rbridge,salmon}. Nevertheless, keeping this information secret is challenging; additonally, censors often employ active scanning techniques to discover proxies~\cite{Dunna2018a}. Refraction networking generally assumes that clients have no secret information, and instead relies on the  collateral damage that would result from blocking all the potential decoy destinations. Dark Decoys further this goal by creating a large number of destinations out of the dark space. A similar approach was taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large set of dummy destinations. CensorSpoofer, however, could only send information in one direction---to the client---and had to rely on a separate out-of-band channel for client-to-proxy communication. As an alternative approach, FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to run Flash- or WebRTC-based proxies within their browser to allow censored users to connect to the Tor network with the potential to greatly increase the number. In practice, these proxies served a very small number of users, as compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}

### 2019-02-15 paper/paper.tex
Fill in missing refs

@@
 To evade censors, we must send a plausible SNI value (sending no SNI is
-uncommon and easily blocked---only 1\% of TLS connections\nikita{qualify this as being true in a particular sample} do not carry the
+uncommon and easily blocked---study conducted using Colorado University network
+infrastructure shows that only 1\% of all TLS connections coming in and out of 
+campus do not carry the
 SNI extension~\cite{tls-fingerprint}), and we must have the server respond with
@@
 \noindent
-\emph{Alexa sites} -
+\emph{Popular sites} -
 An alternative strategy is to use popular sites, such as those from the Alexa
-top million~\cite{alexa} list. As mentioned previously, it may be wise to avoid
+top site~\cite{alexa-top500} list. As mentioned previously, it may be wise to avoid
 sites that are obviously not hosted in the dark decoy address range, such as
@@
 
-Website Fingerprinting~\cite{kNN,kFP,DLFP} (WF) uses the patterns of encrypted traffic to identify which website a client is connected to.
+Website Fingerprinting~\cite{wang2014effective,hayes2016k,sirinam2018deep} (WF) uses the patterns of encrypted traffic to identify which website a client is connected to.
 WF uses a classifier to label the traffic as belonging to one of several known websites, or (in some variants), an unknown or background class.

### 2019-02-15 paper/paper.tex
edit arch section to emphasize ipv6

--- 2019-02-15 paper/paper.tex
@@
 \textbf{application} running on the station. Finally, the client \textbf{proves}
-to the application that it was the same entity that registered (and not a censor
+to the application that it was the same client that registered (and not a censor
 attempting to probe), and is able to use the application as a proxy.
@@
 To register, clients connect to a \textbf{decoy} site that supports TLS. They
-complete the handshake, and send a normal HTTPS request. In TLS, requests (and
-responses) are encrypted and sent in an \texttt{Application Data} record. During
-registration, the client alters the ciphertext of the \texttt{Application Data} record to
-convey a short \textbf{tag} to the ISP station, on path between the client and
-decoy site.
+complete the handshake, and send a normal HTTPS request that embeds a special
+steganographic \textbf{tag} in the ciphertext of the request. We use
+the same technique used in TapDance's covert ciphertext channel\footnote{Section 3 in
+TapDance~\cite{tapdance14}} to embed the tag, but we purposefully have the client
+send a complete request (rather than incomplete), allowing the decoy server to respond.
+The steganographic tag is only visible to the ISP station, which can see the tag using its
+private key. Unlike in TapDance, the \scheme station can passively observe
+the tag, and does not need to respond to it (which requires mimicking the
+decoy)
 
@@
 key, cannot derive the shared secret, preventing it from being able to decrypt
-the message, or learn of its existence.
+the message, or even learn of its existence.
 
@@
 configuration-specific information, such as flags to signify version, feature
-support, and which set of dark decoy network prefixes the client knows of. The
-client and server use a hash of the provided seed to determine which specific
-dark decoy IP address to register. It may seem intuitive to instead have the client
+support, and a set of IPv6 network prefixes that the client knows can be used
+for dark decoys (previously distributed publicly).
+The client and server hash the seed to determine which specific
+IPv6 address from the set of prefixes will be used and registered as a dark
+decoy. It may seem intuitive to instead have the client
 send the specific IP address to register, but allowing the client arbitrary
 choice also allows the censor to register suspected dark decoys and block them if
-they pick up. By using a hash, the censor would have to pre-image the hash to
-obtain a seed it could use to register for a desired IP address. \nikita{Are we claiming that this kind of enumeration is hard to do in IPv4?} It also gives a
+they pick up. 
+By using a hash of a seed, the censor would have to pre-image the hash to
+obtain a seed it could use to register for a desired IP address.
+It also gives a
 secret (the seed) that only the client and station know, even after the client
@@
 \textbf{application}. The station can also optionally ignore packets not from
-the source IP address of the registering client, so that to a probing censor,
-the dark decoy appears to be firewalled off from all but the client.
+the source IP address of the registering client, so that to a probing censor
+from a different IP address,
+the dark decoy appears to be firewalled off from all but the client. We note
+this is not a robust solution: censors have previously been observed taking over
+IP addresses of clients~\cite{ensafi-tor}. We instead address active probing in
+the application.
 
-%-IPv6 vs IPv4 dark decoys subsection?
+\subsubsection{IPv6 vs IPv4 dark decoys}
 
-\subsection{Address utilization}
-% TODO:Can be better: story for v4, these are some problems, here's what it
-% looks like in v6
+Dark decoy IP addresses must be derived from network blocks that are routed (so they pass
+the ISP station) and contain other legitimate hosts (so that censors cannot
+block the entire network without collateral damage).
+Because of the large number of IPv6 addresses, even
+relatively small network prefixes have astronomical numbers of addresses: a
+single /32 prefix has $2^{96}$ possible addresses. Therefore, client-chosen
+seeds have negligible probability of corresponding to addresses that are already
+being used by legitimate hosts. This allows us to select dark decoy addresses
+from network prefixes that contain
+legitimate hosts---crucial to discouraging the censor from blocking them
+outright---without worry that registrations could interfere with legitimate
+services.
 
-% Note on IPv6 space? /32 of IPv6 is 96-bits to select...
-Dark decoy IP addresses are selected from unused but still routed address
-space that passes by the ISP. Traffic to unrouted addresses would produce ICMP
-responses that a censor could observe, and are also easily blocked with knowledge
-of a routing table. Because we support the use of IPv6 addresses, censors will
-also be unable to scan ahead of time to determine if the host has been there
-previously, or what was there before. While they can probe suspected dark decoy
-addresses after clients connect to them, at that point the address has already been
-registered, preventing the censor from identifying differences in behavior
-before and after registration.
+In addition, the use of IPv6 prevents censors from exhaustively probing
+potential dark decoy network prefixes ahead of time to learn the full set of
+legitimate sites in the network.
 
-While address utilization in IPv4 is quite high (all blocks have been allocated
-at the RIR level), the fraction of addresses that respond to TCP connections on
-a given port is quite low: even popular ports like 443 (use by TLS) have less
-than 2\% of IPv4 hosts respond to connection requests. This leaves a large
-number of hosts available to use as dark decoys. However, if a client registers
-a dark decoy address that is already happens to be used by an existing host,
-there will be multiple responses when the client tries to connect, and the
-connection will fail. However, this failure is still limited to the registering
-client, as the application only responds to the IP of the client that
-registered. In IPv6, the odds of picking a legitimate host are negligible: with
-a /32 prefix of IPv6, there are $2^{96}$ addresses to choose from.
-\nikita{/32 is pretty big, e.g. UIUC only has a /48}
+\paragraph{IPv4}
+While \scheme composes well with IPv6, we can also support IPv4,
+at the cost of being vulnerable to active probing by the censor.
+We emphasize that TapDance is already
+vulnerable to active probing attacks~\cite{tapdance14} that \scheme defends
+against when using IPv6. However, in IPv4, there are substantially fewer
+addresses, allowing censors to easily enumerate network prefixes that pass by
+the ISP station and measure legitimate sites. Furthermore, the small address
+space makes it much easier to pre-image the hash used to derive IP addresses
+from the seed. Registering a specific IPv4 address in an IPv4 /16 subnet will
+take only an expected $2^{16}$ hashes for the censor to achieve. This would let
+attackers register legitimate hosts as dark decoys, potentially disrupting
+legitimate service. If the station refused to pick up for addresses that
+correspond to legitimate hosts (measured by scanning during registration), then
+censors could use this as an oracle for distinguishing legitimate sites from
+dark decoys. Still, IPv4 \scheme offers many performance, flexibility, and
+simplicity benefits over TapDance, though they are both vulnerable to active
+probing attacks.
+
+%While address utilization in IPv4 is quite high (all blocks have been allocated
+%at the RIR level), the fraction of addresses that respond to TCP connections on
+%a given port is quite low: even popular ports like 443 (use by TLS) have less
+%than 2\% of IPv4 hosts respond to connection requests. This leaves a large
+%number of hosts available to use as dark decoys. However, if a client registers
+%a dark decoy address that is already happens to be used by an existing host,
+%there will be multiple responses when the client tries to connect, and the
+%connection will fail. However, this failure is still limited to the registering
+%client, as the application only responds to the IP of the client that
+%registered. In IPv6, the odds of picking a legitimate host are negligible: with
+%a /32 prefix of IPv6, there are $2^{96}$ addresses to choose from.
+%\nikita{/32 is pretty big, e.g. UIUC only has a /48}
 

### 2019-02-15 paper/paper.tex
Figure

--- 2019-02-15 paper/paper.tex
@@
 % make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-\title{\Large \bf Dark Decoys:
-  Conjuring Proxies from Unused Address Space}
-%\title{\Large \bf Conjure: Summoning Proxies from Unused Address Space}
+%\title{\Large \bf Dark Decoys:
+%  Conjuring Proxies from Unused Address Space}
+\title{\Large \bf Conjure: Summoning Proxies from Unused Address Space}
 
@@
 
-%\newcommand{\scheme}{Conjure\xspace}
-\newcommand{\scheme}{Dark Decoys\xspace}
+%\newcommand{\scheme}{Dark Decoys\xspace}
+\newcommand{\scheme}{Conjure\xspace}
 
@@
 To evade censors, we must send a plausible SNI value (sending no SNI is
-uncommon and easily blocked---study conducted using Colorado University network
-infrastructure shows that only 1\% of all TLS connections coming in and out of 
-campus do not carry the
+uncommon and easily blocked---only 1\% of TLS connections\nikita{qualify this as being true in a particular sample} do not carry the
 SNI extension~\cite{tls-fingerprint}), and we must have the server respond with
@@
 \noindent
-\emph{Popular sites} -
+\emph{Alexa sites} -
 An alternative strategy is to use popular sites, such as those from the Alexa
-top site~\cite{alexa-top500} list. As mentioned previously, it may be wise to avoid
+top million~\cite{alexa} list. As mentioned previously, it may be wise to avoid
 sites that are obviously not hosted in the dark decoy address range, such as
@@
 
-Website Fingerprinting~\cite{wang2014effective,hayes2016k,sirinam2018deep} (WF) uses the patterns of encrypted traffic to identify which website a client is connected to.
+Website Fingerprinting~\cite{kNN,kFP,DLFP} (WF) uses the patterns of encrypted traffic to identify which website a client is connected to.
 WF uses a classifier to label the traffic as belonging to one of several known websites, or (in some variants), an unknown or background class.

### 2019-02-15 paper/figures.tex

@@
     \centering
-    \vspace{-0.5in}
+    \vspace{-0.525in}
     \includegraphics[width=\linewidth,clip]{figures/high-level.png}
     \caption{\textbf{Overview}---%
-      \scheme is deployed at an ISP using a passive network tap.
-      Clients request service by embedding a steganographic registration message in a TLS connection with any reachable site at the ISP\@. The client selects
-      an unused (``dark'') address in the client's AS, and \scheme
-      injects packets to communicate with the client as if it were a proxy server at that address.
+      An ISP deploys a \scheme station, which sees a passive tap of network traffic.
+      Clients request service by embedding a steganographic message in a TLS connection with any reachable site at the ISP\@. The client then connects
+      to an unused IP address in the client's AS, and the station
+      injects packets to communicate with the client as if there were a proxy server at that address.
     }
@@
             \rot{Decoy Routing~\cite{curveball11}} &
-            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall}} & \rot{\textbf{\scheme}} \\
+            \rot{TapDance~\cite{tapdance14}} & \rot{Rebound~\cite{rebound15}} & \rot{Slitheen~\cite{slitheen16}} & \rot{Waterfall~\cite{waterfall17}} & \rot{\textbf{\scheme}} \\
             \hline

### 2019-02-15 paper/figures.tex
Figures

@@
 \newcommand{\FigOverview}{
-\begin{figure*}[t]
+\begin{figure}[t]
     \centering
-    \includegraphics[width=0.60\linewidth,clip]{figures/dark-decoy-overview.png}
-    \caption{\textbf{\scheme Overview}\,---\, %
+    \includegraphics[width=\linewidth,clip]{figures/dark-decoy-overview.png}
+    \caption{\textbf{\scheme Operations}\,---\,%
+      \TODO{Caption}
     }
     \label{fig:overview}
-\end{figure*}
+\end{figure}
 }
@@
     \centering
-    \vspace{-0.525in}
+    \vspace{-0.54in}
     \includegraphics[width=\linewidth,clip]{figures/high-level.png}
-    \caption{\textbf{Overview}---%
-      An ISP deploys a \scheme station, which sees a passive tap of network traffic.
-      Clients request service by embedding a steganographic message in a TLS connection with any reachable site at the ISP\@. The client then connects
-      to an unused IP address in the client's AS, and the station
-      injects packets to communicate with the client as if there were a proxy server at that address.
+    \caption{\textbf{\scheme Overview}---%
+      An ISP deploys a \scheme station, which sees a passive tap of passing traffic.
+      Following a steganographic registration process, a client can connect
+      to an unused IP address in the ISP's AS, and the station will
+      inject packets to communicate with the client as if there were a proxy server at that address.
     }
@@
 \newcommand{\FigImplementation}{
-\begin{figure}[ht]
+\begin{figure}[t]
     \centering
     \includegraphics[width=0.7\linewidth,clip]{figures/implementation.png}
-    \caption{\textbf{Station Architecture}\,---\, %
+    \caption{\textbf{Station Architecture}\,---\,%
+      \TODO{Caption}
     }

### 2019-02-15 paper/figures.tex
add future work

--- 2019-02-15 paper/figures.tex
@@
             Handles asym. routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
-            Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
+            %Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
             Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
             Traffic analysis resitant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
-            Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
+            %Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\
+            Unlimited Session Length  &\yes & \yes & \yes & \no  & \no  & \no  & \no  & \yes \\
+            %Multicore Implementation  &\no  & \no  & \no  & \yes & \no  & \no  & \no  & \yes \\
     \end{tabular}

### 2019-02-15 paper/paper.tex
add future work

--- 2019-02-15 paper/paper.tex
@@
 \subsubsection{WebRTC}
+\label{sec:webrtc}
 
@@
 
-\TODO{Write (0.5 page)}
+\scheme provides a much larger degree of engineering flexibility than previous
+Refraction Networking schemes. Due to its modular design, different registration
+protocols and applications can be used. One obvious direction is to further
+study such alternatives. For instance, while we use a TapDance-like
+registration, we could potentially cut down on the overhead of one-time
+registration by using port-knocking or using a Telex-style~\cite{telex11} tag (in the Client
+Hello rather than Application Data).
+
+\paragraph{Client-side applications}
+On the application side, \scheme provides an interesting opportunity to explore
+\emph{client mimicking} dark decoys. Rather than pretend to be a server (e.g.
+mask site), our application could connect back to a client after registration
+from the dark decoy address. Protocols like WebRTC mentioned in
+Section~\ref{sec:webrtc} or other peer-to-peer protocols such as BitTorrent,
+Skype, or Bitcoin.
+
+\paragraph{Traffic Analysis}
+\scheme could also support applications that tradeoff performance for
+observability. While Slitheen offers ideal mimicry of decoys, it comes at a high
+cost of overhead. \scheme mask site applications could implement Slitheen
+in order to perfectly mimic the mask site's latency, packet timings, and payload
+sizes. In addition, careful choice of mask sites may allow for higher
+performance, as sites with more replaceable content can carry more covert data.
+
+\paragraph{Long-term Deployment}
+Ultimately, the goal for Refraction Networking protocols is to be useful in
+circumventing censorship. While it has taken many years for research
+protocols to mature, we are excited to see schemes like TapDance deployed in
+practice~\cite{frolov2017isp}. We believe \scheme can be even easier to deploy
+at scale, and hope to leverage the existing success of TapDance to place \scheme
+stations in real-world ISPs.
 

### 2019-02-15 paper/figures.tex
Placement

@@
     \centering
-    \vspace{-0.5in}
     \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
@@
         bits set, suggesting that censors might be able to distinguish between dark decoy addresses
-        and legitimate ones.
+        and legitimate ones.\looseness=-1
         %We note there are several /64 subnets that had many
@@
   \vspace{12pt}
-  \caption{\textbf{Evolution of Refraction Networking Approaches}}
+  \caption{\textbf{Evolution of Refraction Networking}}
 \end{figure}

### 2019-02-15 paper/background.tex
\scheme

@@
 
-Dark decoys are able to avoid these problems by splitting up the traffic between a registration session and a dark session \nikita{are these good terms?} (\cref{fig:dark-decoys}).
+\scheme is able to avoid these problems by splitting up the traffic between a registration session and a dark session \nikita{are these good terms?} (\cref{fig:dark-decoys}).
 The registration session is used to send a signal to the RS to let RS know that the client plans to use dark sessions and to establish a seed to be used in future communications (\cref{XXX}); the RS only passively observes this connection without any interference.
@@
 Past implementations have used TCP initial sequence numbers~\cite{cirripede11}, the ClientRandom field inside a TLS handshake~\cite{curveball11,telex11}, and the encrypted body of an HTTPS request~\cite{tapdance14}.
-In principle dark decoys can use any of these mechanisms for registration, but n our prototype we used the HTTPS request body as it offers the greatest flexibiity for the amount of data that can be sent with the registration.
+In principle \scheme can use any of these mechanisms for registration, but in our prototype we used the HTTPS request body as it offers the greatest flexibiity for the amount of data that can be sent with the registration.

### 2019-02-15 paper/related.tex
Placement
\scheme

@@
+\TabCompare
+
 \section{Related Work}
 
-We first compare Dark Decoys with other Refraction Networking schemes and then discuss other related work.
+We first compare \scheme with other Refraction Networking schemes and then discuss other related work.
 
@@
 short and repeatedly reconnect to decoys, increasing overhead and potentially
-alerting censors with this pattern. Dark Decoys addresses this issue and allows
+alerting censors with this pattern. \scheme addresses this issue and allows
 clients to maintain long-lived connections to the dark decoy.
@@
 Slitheen can safely replace. We note that the Slitheen model of mimicry is
-compatible with Dark Decoys, as we could use Slitheen as the application
+compatible with \scheme, as we could use Slitheen as the application
 protocol. Despite using a passive tap, our scheme is effectively inline to the
@@
 
-Dark Decoys allow a large amount of flexibility compared to previous schemes.
+\scheme allow a large amount of flexibility compared to previous schemes.
 Because we have significant degrees of freedom in choosing the specific
@@
 Table~\ref{tab:compare} lists the existing Refraction Networking schemes and
-their features, as compared to Dark Decoys.
-
-\TabCompare
+their features, as compared to \scheme.
 
@@
 This may be in part because a transit ISP has a large number of routers and points-of-presence, significantly raising the costs of deployment~\cite{devil-details}.\footnote{We
-note that Gosain et al.~\cite{devil-details} use an estimate of \$885\,000 USD/proxy, while Frolov et al.~\cite{frolov2017isp} report line-rate TapDance deployment using commodity hardware that cost only several thousand dollars.} Likewise, we expect Dark Decoys to use address space announced by the ISP, rather than addresses relayed by it, which mitigates routing-based attacks.
+note that Gosain et al.~\cite{devil-details} use an estimate of \$885\,000 USD/proxy, while Frolov et al.~\cite{frolov2017isp} report line-rate TapDance deployment using commodity hardware that cost only several thousand dollars.} Likewise, we expect \scheme to use address space announced by the ISP, rather than addresses relayed by it, which mitigates routing-based attacks.
 Depending on the size of the ISP, however, a censor may decide to block the entirety of its address space, which would incur smaller collateral damage than blocking all addresses seen by a transit ISP.
@@
 Refraction networking generally assumes that clients have no secret information, and instead relies on the  collateral damage that would result from blocking all the potential decoy destinations.
-Dark Decoys further this goal by creating a large number of destinations out of the dark space.
+\scheme further this goal by creating a large number of destinations out of the dark space.
 A similar approach was taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large set of dummy destinations.

### 2019-02-16 paper/paper.tex
\scheme
Section formatting

@@
 
-Dark Decoys involve three main steps. First, clients \textbf{register} with the
+\scheme involve three main steps. First, clients \textbf{register} with the
 ISP station,
@@
 
-\paragraph{Mask Site Selection}
+\subsubsection{Mask Site Selection}
 
@@
 
-\smallskip
-\noindent
-\emph{Nearby sites} - One strategy for selecting mask sites to mimic is to pick websites that are
+\paragraph{Nearby sites.}
+One strategy for selecting mask sites to mimic is to pick websites that are
 legitimately hosted in or near the network of the dark decoy addresses. This
@@
 
-\smallskip
-\noindent
-\emph{Popular sites} -
+\paragraph{Popular sites.}
 An alternative strategy is to use popular sites, such as those from the Alexa
@@
 
-\smallskip
-\noindent
-\emph{Passive observation} -
+\paragraph{Passive observation.}
 The ISP tap could also collect sites by passively observing DNS requests, TLS
@@
 \paragraph{Website Fingerprinting}
-
 Website Fingerprinting~\cite{wang2014effective,hayes2016k,sirinam2018deep} (WF) uses the patterns of encrypted traffic to identify which website a client is connected to.

### 2019-02-16 paper/paper.tex
background pass
Terminology

@@
 Our deployment model is identical to that of TapDance: we only require a passive
-tap at the deploying ISP, and the ability to inject (spoofed) traffic from dark
-decoy sites.
+tap at the deploying ISP, and the ability to inject (spoofed) traffic from phantom
+hosts.
 Furthermore, we assume
@@
 
-We assume that the censor can know what network the dark decoy station(s) are
-deployed in and the prefixes dark decoys are selected from, but that blocking those
+We assume that the censor can know what network the \scheme station(s) are
+deployed in and the prefixes phantom hosts are selected from, but that blocking those
 networks outright brings a collateral
 damage the censor is unwilling to suffer. Instead, the censor aims to identify
-the addresses that are dark decoys, and block only those.
+the addresses that are phantom hosts, and block only those.
 
-We assume the censor can use the client to register and access its own dark
-decoys, but that these will not reveal the dark decoys of other users. The
+We assume the censor can use the client to register and access its own phantom
+hosts, but that these will not reveal the phantom hosts of other users. The
 censor can also actively probe addresses that it sees users accessing, but can
-not enumerate the entire dark decoy prefix (e.g. a /32 IPv6 prefix contains
+not enumerate the entire ISP prefix (e.g. a /32 IPv6 prefix contains
 $2^{96} addresses$).
@@
 Finally, we assume the censor can replay or preplay any connections that it
-suspects involve dark decoys (or their registration) in an attempt to confirm.
+suspects involve phantom hosts (or their registration) in an attempt to confirm.
 However, the censor wishes to avoid disrupting any connections before it
-knows for certain they are dark decoy ones, lest they disrupt legitimate
+knows for certain they are from \scheme clients, lest they disrupt legitimate
 connections. This means that injecting false data or corrupting TLS sessions is
@@
 ISP station,
-and agree on the dark decoy IP address that will be used. Next, the client
+and agree on the phantom host IP address that will be used. Next, the client
 connects to the agreed upon address, which is terminated by an
@@
 support, and a set of IPv6 network prefixes that the client knows can be used
-for dark decoys (previously distributed publicly).
+for phantom hosts (previously distributed publicly).
 The client and server hash the seed to determine which specific
-IPv6 address from the set of prefixes will be used and registered as a dark
-decoy. It may seem intuitive to instead have the client
+IPv6 address from the set of prefixes will be used and registered as a phantom host. It may seem intuitive to instead have the client
 send the specific IP address to register, but allowing the client arbitrary
-choice also allows the censor to register suspected dark decoys and block them if
+choice also allows the censor to register suspected phantom hosts and block them if
 they pick up. 
@@
 secret (the seed) that only the client and station know, even after the client
-connects to the dark decoy address.
+connects to the phantom host address.
 
-Once the dark decoy IP address has been selected, the station watches for
-packets destined to that address, and forwards them onto the dark decoy
+Once the phantom host IP address has been selected, the station watches for
+packets destined to that address, and forwards them onto the phantom host
 \textbf{application}. The station can also optionally ignore packets not from
@@
 from a different IP address,
-the dark decoy appears to be firewalled off from all but the client. We note
+the phantom host appears to be firewalled off from all but the client. We note
 this is not a robust solution: censors have previously been observed taking over
@@
 
-\subsubsection{IPv6 vs IPv4 dark decoys}
+\subsubsection{IPv6 vs IPv4 phantom hosts}
 
-Dark decoy IP addresses must be derived from network blocks that are routed (so they pass
+Phantom host IP addresses must be derived from network blocks that are routed (so they pass
 the ISP station) and contain other legitimate hosts (so that censors cannot
@@
 seeds have negligible probability of corresponding to addresses that are already
-being used by legitimate hosts. This allows us to select dark decoy addresses
+being used by legitimate hosts. This allows us to select phantom host addresses
 from network prefixes that contain
@@
 In addition, the use of IPv6 prevents censors from exhaustively probing
-potential dark decoy network prefixes ahead of time to learn the full set of
+potential phantom host network prefixes ahead of time to learn the full set of
 legitimate sites in the network.
@@
 take only an expected $2^{16}$ hashes for the censor to achieve. This would let
-attackers register legitimate hosts as dark decoys, potentially disrupting
+attackers register legitimate hosts as phantom hosts, potentially disrupting
 legitimate service. If the station refused to pick up for addresses that
@@
 censors could use this as an oracle for distinguishing legitimate sites from
-dark decoys. Still, IPv4 \scheme offers many performance, flexibility, and
+phantom hosts. Still, IPv4 \scheme offers many performance, flexibility, and
 simplicity benefits over TapDance, though they are both vulnerable to active
@@
 
-Once the client has registered, packets sent to the dark decoy IP address are
+Once the client has registered, packets sent to the phantom host IP address are
 passed to the \textbf{application} running on the station. The application has
@@
 
-TLS is a natural protocol for dark decoy applications, because it is ubiquitous on
+TLS is a natural protocol for \scheme applications, because it is ubiquitous on
 the Internet (making it difficult for censors to block), while also providing
@@
 being able to detect obvious choices. For example, if a small university network
-has a dark decoy in their network that appears to be \texttt{apple.com}, it
+has a phantom host in their network that appears to be \texttt{apple.com}, it
 would be easy for a censor to block as a likely non-legitimate host. Likewise,
-if a dark decoy at an IP address pretends to be a domain (\texttt{example.com}) that
+if a phantom host at an IP address pretends to be a domain (\texttt{example.com}) that
 globally resolves to a single different IP address, the censor could also
-identify and block the dark decoy.
+identify and block the phantom host.
 
@@
 One strategy for selecting mask sites to mimic is to pick websites that are
-legitimately hosted in or near the network of the dark decoy addresses. This
+legitimately hosted in or near the network of the phantom host addresses. This
 effectively creates copies of legitimate sites, with the censor unable to
-determine which copies are real and which are the dark decoys. However, as
+determine which copies are real and which are the phantom hosts. However, as
 mentioned, other signals such as DNS may reveal the true mask site.
@@
 top site~\cite{alexa-top500} list. As mentioned previously, it may be wise to avoid
-sites that are obviously not hosted in the dark decoy address range, such as
+sites that are obviously not hosted in the phantom host address range, such as
 large companies that run their own datacenters and own their own ASN.
@@
 addresses from different vantage points, making it harder for a censor to know
-if a dark decoy corresponds to a domain's IP.
+if a phantom host corresponds to a domain's IP.
 
@@
 SNI, or certificates that pass by. This would allow for building a realistic set
-of sites that are plausibly in the vicinity of the dark decoy addresses
+of sites that are plausibly in the vicinity of the phantom host addresses
 that pass by the tap. It also has the added bonus of being able to discover
@@
 
-In practice, clients can often try multiple dark decoys/mask sites over
+In practice, clients can often try phantom hosts/mask sites over
 several attempts, as blocking the client outright may negatively impact other
@@
 
-TLS~1.3~\cite{tls13} offers several features that may greatly simplify dark
-decoy application design. For instance, TLS~1.3 handshakes include encrypted
+TLS~1.3~\cite{tls13} offers several features that may greatly simplify 
+\scheme application design. For instance, TLS~1.3 handshakes include encrypted
 certificates, potentially obviating the need to impersonate mask sites.
@@
 though none have been implemented or deployed as of early 2019. Nonetheless,
-if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for dark
-decoy applications by allowing the domain to remain hidden from the censor.
+if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
+\scheme applications by allowing the domain to remain hidden from the censor.
 While the censor could still try to actively probe with guesses for the SNI,
 servers could respond with generic ``Unknown SNI'' errors. If such responses
-were common for incorrect SNI, the censor's efforts to identify dark decoys
+were common for incorrect SNI, the censor's efforts to identify phantom hosts
 would be frustrated.
@@
 
-Dark Decoys could also pretend to be clients instead of servers. This may
+Phantom hosts could also pretend to be clients instead of servers. This may
 potentially give censors less to block on, as actively probing clients is common
@@
 and is used in existing censorship circumvention schemes like
-Snowflake~\cite{snowflake}. Dark decoy applications could also use WebRTC as the
+Snowflake~\cite{snowflake}. \scheme could also use WebRTC as the
 application protocol, convincing the censor that two clients are communicating.
@@
 
-We implemented the Dark Decoy protocol and tested it in a 10~Gbps ISP testbed
+We implemented the \scheme protocol and tested it in a 10~Gbps ISP testbed
 with real traffic. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to
@@
 detector processes all packets and watches for new registrations. It also
-forwards all packets sent to a (registered) dark decoy's address to the local
+forwards all packets sent to a (registered) phantom host address to the local
 \textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
@@
 supports balancing across cores based on flow (5-tuple) or source and
-destination IPs. However, both of these options present challenges for our Dark
-Decoy detector. One issue is that registrations could be processed on a
-different core than the packets sent to that specific dark decoy address. For
+destination IPs. However, both of these options present challenges for our 
+implementation. One issue is that registrations could be processed on a
+different core than the packets sent to that specific phantom host address. For
 instance, a client could have its registration handled by Core 1, while its
-packets to the dark decoy address end up on Core 3, which doesn't know about the
+packets to the phantom host address end up on Core 3, which doesn't know about the
 original registration.
@@
 (publish) newly registered decoys to the other cores so they can
-add them to their local list of registered dark decoy addresses.
+add them to their local list of registered phantom host addresses.
 However, this introduces two new problems. First, a core might add a
 registration \emph{after} it has already received and processed packets destined
-for the specified dark decoy. This typically isn't a problem when running on a
+for the specified phantom host. This typically isn't a problem when running on a
 single core, as packets are processed sequentially. Second, each core may
-timeout each dark decoy at different times, potentially leading to differing
+timeout each phantom host at different times, potentially leading to differing
 behavior that is visible to a censor. For instance, if we used the
-source/destination IPs to load balance, a censor's packets to a dark decoy could
+source/destination IPs to load balance, a censor's packets to a phantom host could
 be processed by a different core than the client. If the censor waits for the
-known timeout before sending a probe, its core may have timed out that dark
-decoy, while the client's core has refreshed the timeout of the dark decoy due
+known timeout before sending a probe, its core may have timed out that phantom host, while the client's core has refreshed the timeout of the phantom host due
 to active use.
@@
 To address the first issue, we force the client to delay sending its connection
-to the dark decoy until a short time after registration. In practice, we force
+to the phantom host until a short time after registration. In practice, we force
 the client to wait until the registration decoy responds before starting a
-connection with the registered dark decoy.
+connection with the registered phantom host.
 
@@
 registrations, but that only one core will be responsible for processing all of
-the packets sent to a given dark decoy, regardless of who or when it is sent.
+the packets sent to a given phantom host, regardless of who or when it is sent.
 
@@
 
-The application accepts connections to dark decoy addresses forwarded by the
+The application accepts connections to phantom host addresses forwarded by the
 detector and rewritten to the local address using \texttt{iptables}.
@@
 SOCKS proxy, which can multiplex multiple client connections over the single
-connection to the dark decoy.
+connection to the phantom host.
 
@@
 
-After registering, the client connects to the derived dark decoy address, and
+After registering, the client connects to the derived phantom host address, and
 switches secrets after the handshake. At this point, a local application (e.g.
 SOCKS client) can connect to the client, and it will transparently be connected to
-the remote end via the encrypted dark decoy connection.
+the remote end via the encrypted phantom host connection.
 
@@
 Implementation of the protocol includes 3 components:
-dark decoy detector, proxy application, and client.
-Dark decoy detector will parse the traffic, searching for registrations in
+detector, proxy application, and client.
+Detector will parse the traffic, searching for registrations in
 tagged messages. After detector observes a registration, and negotiates with client
-a dark decoy IP,
-all packets, that are sent to that dark decoy IP,
+a phantom host IP,
+all packets, that are sent to that phantom host IP,
 will be forwarded into a proxy application.
@@
 
-Each Dark Decoy connection has 2 phases: registration, and usage of a dark decoy.
+Each \scheme connection has 2 phases: registration, and usage of a phantom host.
 Registration starts with a handshake that is similar to a TapDance handshake,
@@
 
-Client will sleep a short randomized period of time before attempting to establish connection to dark decoy.
-This is done for 2 reasons: to break potentially observable interflow dependency with a dark decoy connection being established right after a first application layer data packet sent to decoy,
+Client will sleep a short randomized period of time before attempting to establish connection to phantom host.
+This is done for 2 reasons: to break potentially observable interflow dependency with a phantom host connection being established right after a first application layer data packet sent to decoy,
 and to give station time.
@@
 Client and station will use HKDF to derive 16 random bytes and use them to
-agree on a dark decoy IP address, by applying a simple selection algorithm.
+agree on a phantom host IP address, by applying a simple selection algorithm.
 Algorithm is as follows: first, flatten a list of pre-shared avaliable IP
@@
 
-Note that dark decoy detector and proxy application are only loosely coupled with each other,
+Note that the detector and proxy application are only loosely coupled with each other,
 making it simple to replace one of them.
@@
 % 1 page
+\label{sec:attacks}
 
-There are many attacks a censor might attempt to either prevent dark decoys from
+There are many attacks a censor might attempt to either prevent phantom hosts from
 being registered or used.
@@
 completely disable all existing Refraction Networking schemes, as none work
-without being able to access legitimate decoys past the station. In dark decoys,
+without being able to access legitimate decoys past the station. In \scheme,
 this would only block new registrations, and would not impact users that
@@
 The censor could also attempt to fingerprint the masked site and compare it to a
-suspected dark decoy application. For instance, if a dark decoy IP responds as
+suspected \scheme application. For instance, if a phantom host IP responds as
 pretending to be \texttt{example.com}, the censor could scan or probe real instances
 of \texttt{example.com} on different ports and see how it responds. Then, the
-censor can probe the dark decoy IP, and see if it responds similarly (e.g. with
+censor can probe the phantom host IP, and see if it responds similarly (e.g. with
 the same set of open ports and payloads for certain kinds of probes). To defend
-against this, we forward \emph{all} traffic destined to the dark decoy to the
+against this, we forward \emph{all} traffic destined to the phantom host to the
 masked site, including ports that are not relevant to the proxy application
@@
 common Linux implementation. We also note that this attack only applies when we
-use the mask site as an application, and that Dark Decoys can support other
+use the mask site as an application, and that \scheme can support other
 applications (e.g. obfsproxy, WebRTC, etc) that do not have this issue.
@@
 
-Dark Decoy applications that mimic specific websites (e.g., mask sites) are likewise susceptible to WF.
+\scheme applications that mimic specific websites (e.g., mask sites) are likewise susceptible to WF.
 To date, however, censors have not been observed using WF and similar techniques, possibly due to the significant uncertainty resulting from even the best algorithms: even a small false
@@
 
-More importantly, Dark Decoy applications offer great flexibility in deploying traffic analysis defenses; for example, traffic shaping strategies such as implemented in Slitheen~\cite{slitheen16} could be easily employed in Dark Decoys.
+More importantly, \scheme applications offer great flexibility in deploying traffic analysis defenses; for example, traffic shaping strategies such as implemented in Slitheen~\cite{slitheen16} could be easily employed in \scheme.
 Furthermore,
-Dark Decoy applications are not limited to mimicking websites, and can support
+\scheme applications are not limited to mimicking websites, and can support
 any (or even a combination of) protocols.
@@
 \paragraph{ICMP}
-Censors can use ping or traceroute utilities (via ICMP) to probe potential dark
-decoys. Because there is (usually) no host at the dark decoy address, these
+Censors can use ping or traceroute utilities (via ICMP) to probe potential phantom
+hosts. Because there is (usually) no host at the phantom host address, these
 probes will timeout and produce no response. They might also produce
@@
 used by traceroute) may be a viable strategy. % We should evaluate this claim...
-Alternatively, we could spoof responses to convince an adversary that a dark
-decoy is part of a particular network. However, this strategy requires careful
+Alternatively, we could spoof responses to convince an adversary that a 
+phantom host is part of a particular network. However, this strategy requires careful
 consideration of what network makes sense for a mask site to be in. Also, the
-censor may try to probe for addresses around the dark decoy (but still likely to
+censor may try to probe for addresses around the phantom host (but still likely to
 be in the same network), which must also be responded to.
@@
 giving censors a possible feature to filter on: addresses that have too much
-entropy (or even simply bits set) could be suspicious as dark decoys. To demonstrate and quantify
+entropy (or even simply bits set) could be suspicious as phantom hosts. To demonstrate and quantify
 this problem, we measured 30 minutes of IPv6 traffic to our ISP's /32 network prefix.
@@
 On the application side, \scheme provides an interesting opportunity to explore
-\emph{client mimicking} dark decoys. Rather than pretend to be a server (e.g.
+\emph{client mimicking} phantom hosts. Rather than pretend to be a server (e.g.
 mask site), our application could connect back to a client after registration
-from the dark decoy address. Protocols like WebRTC mentioned in
+from the phantom host address. Protocols like WebRTC mentioned in
 Section~\ref{sec:webrtc} or other peer-to-peer protocols such as BitTorrent,

### 2019-02-16 paper/figures.tex

@@
         (shown as Random). In practice, the distribution of observed IP addresses has much fewer
-        bits set, suggesting that censors might be able to distinguish between dark decoy addresses
+        bits set, suggesting that censors might be able to distinguish between phantom host addresses
         and legitimate ones.\looseness=-1
@@
 First, the client connects to a decoy site and embeds a steganographic registration message, which the station receives using only a passive tap.
-Second, the client connects to a ``dark address'' where there is no running server, and the station proxies the connection in its entirety.}
+Second, the client connects to a ``phantom host'' where there is no running server, and the station proxies the connection in its entirety.}
     \label{fig:dark-decoys}

### 2019-02-16 paper/background.tex

@@
 receives an encrypted response. In refraction routing, at least one direction
-of this exchange is observed by a \emph{refraction station} (RS), deployed at
-some Internet service provider (ISP). The RS watches for a covert signal from
+of this exchange is observed by a \emph{refraction station}, deployed at
+some Internet service provider (ISP). The station watches for a covert signal from
 the client that this connection is to be used for censorship circumvention.
-Upon seeing the signal, the RS will take over the HTTPS session,
+Upon seeing the signal, the station will take over the HTTPS session,
 and establish a proxy session with the client that can then be used for covert
@@
 One of the key challenges for refraction networking is in taking over a session.
-The RS must start responding to the client's traffic as if it were the decoy destination, and at the same time prevent the destination from sending its own responses back to the client.
+The station must start responding to the client's traffic as if it were the decoy destination, and at the same time prevent the destination from sending its own responses back to the client.
 A simple approach is to have the refraction station act as an inline transparent proxy (\cref{fig:refraction-v1}) that forwards the traffic between the client and the decoy site.
-After a TLS handshake has been completed, the RS terminates the connection with the decoy site by sending a TCP reset and takes over the session with the client.
+After a TLS handshake has been completed, the station terminates the connection with the decoy site by sending a TCP reset and takes over the session with the client.
 
@@
 TapDance~\cite{tapdance14} offered an alternative design that did not require the blocking or redirection of traffic, but used a mirror port instead (\cref{fig:tapdance}).
-In TapDance a client sends an incomplete HTTP request, which causes the decoy site to pause waiting for more data while the RS takes over the connection in its place.
-After a client would receive a packet initiated by the RS, its TCP sequence numbers would become desynchronized with the decoy site, causing the decoy to ignore the packets sent by the client.
+In TapDance a client sends an incomplete HTTP request, which causes the decoy site to pause waiting for more data while the station takes over the connection in its place.
+After a client would receive a packet initiated by the station, its TCP sequence numbers would become desynchronized with the decoy site, causing the decoy to ignore the packets sent by the client.
 
 This approach reduced the barriers to deployment and TapDance was used in production during a pilot study, serving upwards of 50\,000 real-world users~\cite{frolov2017isp}. 
-\nikita{worth mentioning that it's being used in production again?
-we don't have a public ref for that though.} The tap-based approach, however, has some disadvantages.
+%\nikita{worth mentioning that it's being used in production again? we don't have a public ref for that though.} 
+The tap-based approach, however, has some disadvantages.
 A decoy site will only ignore packets as long as the sequence numbers stay within its TCP window, and will terminate the connection after a timeout.
 Frolov et al.\ report that in their pilot, they eliminated roughly a third of potential decoy sites due to their measured window or timeout values being too small~\cite{frolov2017isp}.
-Even so, sessions that try to upload non-trivial data amounts (in excess of about 15\,KB) or last longer than the timeout value (ranging from 30--120\,s) require the user to create new refraction connections, adding overhead, complexity, and opportunities for errors.
-Additionally, keeping the connections to the decoy site open for tens of seconds uses up the site's resources; Frolov et al.\ found that a default configuration of the Apache web server would only keep 150 simultaneous connections open, while pilot deployment would often result in dozens of connections to the same decoy site, creating a scaling concern.
+Even so, sessions that try to upload non-trivial data amounts (in excess of about 15\,KB) or last longer than the timeout value (ranging from 20--120\,s) require the user to create new refraction connections, adding overhead, complexity, and opportunities for errors.
+Additionally, keeping the connections to the decoy site open for tens of seconds uses up the site's resources; Frolov et al.\ found that a default configuration of the Apache web server would only keep 150 simultaneous connections open, while the pilot deployment would often result in dozens of connections to the same decoy site, creating a scaling concern.
 
-\scheme is able to avoid these problems by splitting up the traffic between a registration session and a dark session \nikita{are these good terms?} (\cref{fig:dark-decoys}).
-The registration session is used to send a signal to the RS to let RS know that the client plans to use dark sessions and to establish a seed to be used in future communications (\cref{XXX}); the RS only passively observes this connection without any interference.
+\scheme is able to avoid these problems by creating proxies at unused IP addresses, allowing the station full control over a host it has created, rather than forcing it to mimic an already existing decoy (\cref{fig:dark-decoys}).
+%The registration session is used to send a signal to the station to let RS know that the client plans to use dark sessions and to establish a seed to be used in future communications (\cref{XXX}); the RS only passively observes this connection without any interference.
 The dark session connects to a dark address that is not routed to any host; the RS instead acts as a remote endpoint for the entirety of the connection, starting with the TCP handshake.
-This design obviates the need for taking over a session already in progress, which both simplifies the implementation and eliminates certain attacks, as we will discuss in \cref{XXX}.
+This design obviates the need for taking over a session already in progress, which both simplifies the implementation and eliminates certain attacks, as we will discuss in Section~\ref{sec:attacks}.
 
-\paragraph{Registration Signal} In all implementations of refraction networking, a client must send a covert signal to the RS to initiate communication.
+\paragraph{Registration Signal} In all implementations of refraction networking, a client must send a covert signal to the station to initiate communication.
 This covert signal is  embedded inside communication fields that must be indistinguishable from random by a censor without access to a secret/private key available to the station.

### 2019-02-16 paper/related.tex

@@
 alerting censors with this pattern. \scheme addresses this issue and allows
-clients to maintain long-lived connections to the dark decoy.
+clients to maintain long-lived connections to the phantom host.
 
@@
 protocol. Despite using a passive tap, our scheme is effectively inline to the
-dark decoy (which won't otherwise respond).
+phantom host (which won't otherwise respond).
 
@@
 Because we have significant degrees of freedom in choosing the specific
-application the dark decoy will mimic or talk, our scheme can combine the best
+application the phantom host will mimic or talk, our scheme can combine the best
 of existing Refraction Networking protocols to achieve high performance, be easy

### 2019-02-16 paper/paper.tex
Fix future work

@@
 
-\subsubsection{IPv6 vs IPv4 phantom hosts}
+\subsubsection{IPv6 vs.\ IPv4 Phantom Hosts}
 
@@
 
-\paragraph{Website Fingerprinting}
+\paragraph{Website fingerprinting}
 Website Fingerprinting~\cite{wang2014effective,hayes2016k,sirinam2018deep} (WF) uses the patterns of encrypted traffic to identify which website a client is connected to.
@@
 study such alternatives. For instance, while we use a TapDance-like
-registration, we could potentially cut down on the overhead of one-time
-registration by using port-knocking or using a Telex-style~\cite{telex11} tag (in the Client
-Hello rather than Application Data).
+covert channel for registration, we could potentially cut down on the overhead of one-time
+registration by using port-knocking or using a Telex-style~\cite{telex11} tag (in the Client Hello rather than Application Data).
 
@@
 On the application side, \scheme provides an interesting opportunity to explore
-\emph{client mimicking} phantom hosts. Rather than pretend to be a server (e.g.
-mask site), our application could connect back to a client after registration
-from the phantom host address. Protocols like WebRTC mentioned in
-Section~\ref{sec:webrtc} or other peer-to-peer protocols such as BitTorrent,
+\emph{client mimicking} phantom hosts. Rather than pretend to be a server (e.g.,
+a mask site), our application could connect back to a client after registration
+from the phantom host address. Possible protocols could include WebRTC, mentioned in
+Section~\ref{sec:webrtc}, or other peer-to-peer protocols such as BitTorrent,
 Skype, or Bitcoin.
 
-\paragraph{Traffic Analysis}
+\paragraph{Traffic analysis}
 \scheme could also support applications that tradeoff performance for
@@
 
-\paragraph{Long-term Deployment}
+\paragraph{Long-term deployment}
 Ultimately, the goal for Refraction Networking protocols is to be useful in
@@
 practice~\cite{frolov2017isp}. We believe \scheme can be even easier to deploy
-at scale, and hope to leverage the existing success of TapDance to place \scheme
-stations in real-world ISPs.
+at scale, and we hope to leverage the existing success of TapDance to place \scheme
+stations at real ISPs.
 

### 2019-02-16 paper/background.tex
Spelling

@@
 Past implementations have used TCP initial sequence numbers~\cite{cirripede11}, the ClientRandom field inside a TLS handshake~\cite{curveball11,telex11}, and the encrypted body of an HTTPS request~\cite{tapdance14}.
-In principle \scheme can use any of these mechanisms for registration, but in our prototype we used the HTTPS request body as it offers the greatest flexibiity for the amount of data that can be sent with the registration.
+In principle \scheme can use any of these mechanisms for registration, but in our prototype we used the HTTPS request body as it offers the greatest flexibility for the amount of data that can be sent with the registration.

### 2019-02-16 paper/paper.tex
Spelling

@@
   patches or a custom TCP stack.
-\item To avoid detection, the system must carefully mimmick
+\item To avoid detection, the system must carefully mimic
   subtle features of each decoy's TCP and TLS behavior.
@@
 Clients can register intent to use the proxy in several covert ways. For
-instance, they could use email or other existing intermitently available proxies
+instance, they could use email or other existing intermittently available proxies
 to register. In this section, we use a form of Refraction Networking similar to
@@
 sites that are obviously not hosted in the phantom host address range, such as
-large companies that run their own datacenters and own their own ASN.
+large companies that run their own data centers and own their own ASN.
 The list could also be filtered to domains that resolve to different IP
@@
 
-Client begins registation by establishing TLS connection
+Client begins registration by establishing TLS connection
 to one of the reachable websites,
 path to which passes by our tap.
-Client uses a Chosen-Ciphertext Steganography technique~\cite{tapdance14} to manupulate
+Client uses a Chosen-Ciphertext Steganography technique~\cite{tapdance14} to manipulate
 plaintext of a first application data HTTP request
@@
 that could be decoded using station's private key,
-to negotiate a 32 byte Eligator-encoded~\cite{elligator} shared secret between the client and the station.
+to negotiate a 32 byte Elligator-encoded~\cite{elligator} shared secret between the client and the station.
 That shared secret is used as a seed of SHA-256 based key derivation function (HKDF),
@@
 
-Elligator representative on the wire is immidiately followed by a 6 bytes long AES-GCM-encrypted
+Elligator representative on the wire is immediately followed by a 6 bytes long AES-GCM-encrypted
 fixed size payload(FSP), that holds flags and the size of the variable size payload(VSP).
@@
 agree on a phantom host IP address, by applying a simple selection algorithm.
-Algorithm is as follows: first, flatten a list of pre-shared avaliable IP
+Algorithm is as follows: first, flatten a list of pre-shared available IP
 addresses in various subnets into a single indexed list, then make a 128-bit

### 2019-02-16 paper/related.tex
Spelling

@@
 This may be in part because a transit ISP has a large number of routers and points-of-presence, significantly raising the costs of deployment~\cite{devil-details}.\footnote{We
-note that Gosain et al.~\cite{devil-details} use an estimate of \$885\,000 USD/proxy, while Frolov et al.~\cite{frolov2017isp} report line-rate TapDance deployment using commodity hardware that cost only several thousand dollars.} Likewise, we expect \scheme to use address space announced by the ISP, rather than addresses relayed by it, which mitigates routing-based attacks.
+note that Gosain et al.~\cite{devil-details} use an estimate of \$885,000/proxy, while Frolov et al.~\cite{frolov2017isp} report line-rate TapDance deployment using commodity hardware that costs only several thousand dollars.} Likewise, we expect \scheme to use address space announced by the ISP, rather than addresses relayed by it, which mitigates routing-based attacks.
 Depending on the size of the ISP, however, a censor may decide to block the entirety of its address space, which would incur smaller collateral damage than blocking all addresses seen by a transit ISP.
@@
 Several proposals have been made to carefully control  the distribution of proxy addresses, using social connections and reputation~\cite{proximax,rbridge,salmon}.
-Nevertheless, keeping this information secret is challenging; additonally, censors often employ active scanning techniques to discover proxies~\cite{Dunna2018a}.
+Nevertheless, keeping this information secret is challenging; additionally, censors often employ active scanning techniques to discover proxies~\cite{Dunna2018a}.
 Refraction networking generally assumes that clients have no secret information, and instead relies on the  collateral damage that would result from blocking all the potential decoy destinations.

### 2019-02-16 paper/figures.tex
Spelling

@@
             Replay attack resistant   &\yes & \yes & \yes & \no  & \yes & \yes & \yes & \yes \\
-            Traffic analysis resitant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
+            Traffic analysis resistant &\no  & \no  & \no  & \no  &\maybe& \yes &\maybe& \no \\
             %Uses unused addresses     & \no & \no  & \no  & \no  & \no  & \no  & \no  & \yes \\

### 2019-02-16 paper/figures.tex
figures pass

--- 2019-02-16 paper/figures.tex
@@
     \caption{\textbf{\scheme Operations}\,---\,%
-      \TODO{Caption}
+        Clients first register by sending a secret seed in a steganographic tag past the station in a
+        normal TLS connection to a Decoy site. Clients then connect to an address derived from the seed,
+        which the station responds as a phantom host. If the client can prove knowledge of the
+        seed used during registration, they are allowed access to the proxy. Otherwise,
+        their traffic is forwarded to a Mask Site to make it difficult for censors to distinguish
+        phantom hosts from legitimate ones.
     }
@@
     \end{tabular}
-    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,}
+    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,
+        ``No inline blocking'' corresponds to schemes that can operate as a passive tap on the side
+        without needing an inline element in the ISP network.
+        ``Handles asymmetric routes'' refers to schemes that work when only one direction (either client to decoy or decoy to server) is seen by the station.
+        ``Replay attacks'' refers to censors who may replay/preplay previous messages or actively probe
+        the protocol.
+        ``Traffic analysis'' includes latency, inter-packet timing, and website fingerprinting.
+        ``Unlimited Sessions'' shows schemes that do not need to repeatedly reconnect to download
+        or upload arbitrarily large content.}
     \label{tab:compare}
@@
     \caption{\textbf{Station Architecture}\,---\,%
-      \TODO{Caption}
+        We used PF\_RING to receive packets from a 10~Gbps packet tap, which we load balance
+        across 4~CPU cores. The detector process identifies and processes registrations, and forwards
+        packets destined to registered dark decoy addreses to a local application. The application
+        determines if the client is legitimate (using a seed shared during registration) and forwards
+        their traffic to a proxy. Otherwise, the application responds as if it were the mask site.
     }

### 2019-02-16 paper/paper.tex
Remove todo

@@
 
-\TODO{more precise:}
+%\TODO{more precise:}
 In our scheme (Figure~\ref{fig:highlevel}), clients
@@
 
-\scheme involve three main steps. First, clients \textbf{register} with the
+\scheme involves three main steps. First, clients \textbf{register} with the
 ISP station,
@@
 observability. While Slitheen offers ideal mimicry of decoys, it comes at a high
-cost of overhead. \scheme mask site applications could implement Slitheen
+cost of overhead. \scheme applications could implement Slitheen
 in order to perfectly mimic the mask site's latency, packet timings, and payload

### 2019-02-16 paper/paper.tex
Fix intro

@@
 
-Phantom hosts are cheap to create, allowing for discardable \textbf{one-time use}
-proxy servers to be used by clients. This greatly increases the cost for censors to
+Phantom hosts are cheap to create, allowing for discardable or even one-time-use
+proxy servers. This greatly increases the cost for censors to
 block, as they must detect and block in real time. Meanwhile, even a censor that
@@
 \scheme has reduced complexity and substantially improved performance
-(Section~\ref{sec:evaluation}).
+(Section~\ref{sec:evaluation}).  We believe that these advantages
+make \scheme a strong choice for future Refraction Networking deployments.
 

### 2019-02-16 paper/figures.tex
Placement

@@
     \centering
-    \includegraphics[width=0.90\linewidth,clip]{figures/bandwidth-up.pdf}
+    \includegraphics[width=0.95\linewidth,clip]{figures/bandwidth-up.pdf}
     \caption{\textbf{Upload Performance}\,---\, %
@@
     \centering
-    \includegraphics[width=0.90\linewidth,clip]{figures/bandwidth-down.pdf}
+    \includegraphics[width=0.95\linewidth,clip]{figures/bandwidth-down.pdf}
     \caption{\textbf{Download Performance}\,---\, %
@@
 \newcommand{\FigTapBandwidth}{
-\begin{figure*}[t]
+\begin{figure*}[ht]
     \centering
-    \includegraphics[width=0.90\linewidth,clip]{figures/decoy-tap-bandwidth.png}
+    \includegraphics[width=0.75\linewidth,clip]{figures/decoy-tap-bandwidth.png}
     \caption{\textbf{Tap Bandwidth}\,---\, %

### 2019-02-16 paper/figures.tex
Spelling

@@
             No inline blocking        & \no & \no  & \no & \yes  & \no  & \no  & \no  & \yes \\
-            Handles asym. routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
+            Handles asym.\ routing     & \no & \yes & \no  & \yes & \yes & \no  & \yes & \yes \\
             %Currently deployed        & \no & \no  & \no  & \yes & \no  & \no  & \no  & \no \\
@@
         across 4~CPU cores. The detector process identifies and processes registrations, and forwards
-        packets destined to registered dark decoy addreses to a local application. The application
+        packets destined to registered dark decoy addresses to a local application. The application
         determines if the client is legitimate (using a seed shared during registration) and forwards

### 2019-02-16 paper/paper.tex
Placement
Conclusion
Fix broken ref

@@
 
-However, there are proposals to encrypt the SNI in the Client Hello~\cite{esni},
+However, there are proposals to encrypt the SNI in the Client Hello~\cite{ietf-tls-esni-02},
 though none have been implemented or deployed as of early 2019. Nonetheless,
@@
 to allow us to change the TLS secrets being used after the handshake.
+
+\FigTapBandwidth
 
@@
 
-\FigTapBandwidth
-
-\FigUpload
-
-\FigDownload
-
 To evaluate our \scheme implementation, we compare its bandwidth
@@
 being registered or used.
+
+\FigUpload
+\FigDownload
 
@@
 
-\section{Future Work}
+\section{Conclusion and Future Work}
 % 0.5 page
@@
 
-\section{Conclusion}
+%\section{Conclusion}
 %.25 page
 
-\TODO{Write (0.25 page}
+%\TODO{Write (0.25 page}
 

### 2019-02-16 paper/background.tex
minor fix

@@
 The station must start responding to the client's traffic as if it were the decoy destination, and at the same time prevent the destination from sending its own responses back to the client.
-A simple approach is to have the refraction station act as an inline transparent proxy (\cref{fig:refraction-v1}) that forwards the traffic between the client and the decoy site.
+A simple approach is to have the refraction station act as an inline transparent proxy (Figure~\ref{fig:refraction-v1}) that forwards the traffic between the client and the decoy site.
 After a TLS handshake has been completed, the station terminates the connection with the decoy site by sending a TCP reset and takes over the session with the client.
@@
 
-TapDance~\cite{tapdance14} offered an alternative design that did not require the blocking or redirection of traffic, but used a mirror port instead (\cref{fig:tapdance}).
+TapDance~\cite{tapdance14} offered an alternative design that did not require the blocking or redirection of traffic, but used a mirror port instead (Figure~\ref{fig:tapdance}).
 In TapDance a client sends an incomplete HTTP request, which causes the decoy site to pause waiting for more data while the station takes over the connection in its place.
@@
 
-\scheme is able to avoid these problems by creating proxies at unused IP addresses, allowing the station full control over a host it has created, rather than forcing it to mimic an already existing decoy (\cref{fig:dark-decoys}).
+\scheme is able to avoid these problems by creating proxies at unused IP addresses, allowing the station full control over a host it has created, rather than forcing it to mimic an already existing decoy (Figure~\ref{fig:dark-decoys}).
 %The registration session is used to send a signal to the station to let RS know that the client plans to use dark sessions and to establish a seed to be used in future communications (\cref{XXX}); the RS only passively observes this connection without any interference.

### 2019-02-16 paper/figures.tex
dark decoy -> phantom host

@@
         across 4~CPU cores. The detector process identifies and processes registrations, and forwards
-        packets destined to registered dark decoy addresses to a local application. The application
+        packets destined to registered phantom host addresses to a local application. The application
         determines if the client is legitimate (using a seed shared during registration) and forwards

### 2019-05-07 paper/related.tex

@@
 
-\scheme allow a large amount of flexibility compared to previous schemes.
+\scheme allows a large amount of flexibility compared to previous schemes.
 Because we have significant degrees of freedom in choosing the specific
@@
 Refraction networking generally assumes that clients have no secret information, and instead relies on the  collateral damage that would result from blocking all the potential decoy destinations.
-\scheme further this goal by creating a large number of destinations out of the dark space.
+\scheme furthers this goal by creating a large number of destinations out of the dark space.
 A similar approach was taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large set of dummy destinations.

### 2019-05-13 application/main.go
app: downgrade 3-way-proxy with 2-way-proxy

@@ -11,6 +11,7 @@ import (
 	"log"
 	"net"
 	"os"
+	"strings"
 	"sync"
 	"syscall"
 	"time"
@@ -104,28 +105,7 @@ func getOriginalDst(fd uintptr) (net.IP, error) {
 	}
 }
 
-func handleNewConn(clientConn *net.TCPConn) {
-	defer clientConn.Close()
-
-	fd, err := clientConn.File()
-	if err != nil {
-		logger.Printf("failed to get file descriptor on clientConn: %v\n", err)
-		return
-	}
-
-	// TODO: if NOT mPort 443: just forward things and return
-
-	originalDstIP, err := getOriginalDst(fd.Fd())
-	if err != nil {
-		logger.Println("failed to getOriginalDst from fd:", err)
-		return
-	}
-
-	reg := registeredDecoys.CheckRegistration(originalDstIP)
-	if reg == nil {
-		logger.Printf("registration for %v not found", originalDstIP)
-		return
-	}
+func threeWayProxy(reg *decoyRegistration, clientConn *net.TCPConn, originalDstIP net.IP) {
 	maskHostPort := reg.mask
 	if _, mPort, err := net.SplitHostPort(maskHostPort); err != nil {
 		maskHostPort = net.JoinHostPort(maskHostPort, "443")
@@ -312,38 +292,14 @@ func handleNewConn(clientConn *net.TCPConn) {
 	wg := sync.WaitGroup{}
 	oncePrintErr := sync.Once{}
 	wg.Add(2)
-	halfProxy := func(src, dst net.Conn) {
-		buf := bufferPool.Get().([]byte)
-		_, err = io.CopyBuffer(dst, src, buf)
-		oncePrintErr.Do(
-			func() {
-				if err == nil {
-					logger.Printf("gracefully stopping forwarding from %v", src.RemoteAddr())
-				} else {
-					logger.Printf("stopping forwarding from %v due to error: %v", src.RemoteAddr(), err)
-				}
-			})
-		//if closeWriter, ok := dst.(interface {
-		//	CloseWrite() error
-		//}); ok {
-		//	closeWriter.CloseWrite()
-		//}
-		//
-		//if closeReader, ok := src.(interface {
-		//	CloseRead() error
-		//}); ok {
-		//	closeReader.CloseRead()
-		//}
-		wg.Done()
-	}
 
-	go halfProxy(finalClientConn, finalTargetConn)
[…]

### 2019-05-13 src/lib.rs
Print stats

@@ -199,7 +199,6 @@ impl PerCoreStats
                 0,
                 0);
         */
-        /*
         report!("stats {} pkts ({} v4, {} v6) dark decoy flows {} tracked flows {} tags checked {}",
             self.packets_this_period,
             self.ipv4_packets_this_period,
@@ -207,7 +206,6 @@ impl PerCoreStats
             dark_decoys,
             tracked,
             self.elligator_this_period);
-        */
 
         self.elligator_this_period = 0;
         self.packets_this_period = 0;

### 2019-05-13 src/process_packet.rs
Stop printing every tagged pkt

@@ -175,18 +175,6 @@ impl PerCoreGlobal
 
         let flow = Flow::new(&ip_pkt, &tcp_pkt);
 
-
-        // Test if this is to a prefix we care about
-        /*
-        if let IpPacket::V4(pkt) = &ip_pkt {
-            if !self.ip_tree.contains_addr_v4(pkt.get_destination()) {
-                self.stats.not_in_tree_this_period += 1;
-                return;
-            }
-        }
-        self.stats.in_tree_this_period += 1;
-        */
-
         if panic::catch_unwind(||{ tcp_pkt.payload(); }).is_err() {
             return;
         }
@@ -194,7 +182,7 @@ impl PerCoreGlobal
         let dd_flow = FlowNoSrcPort::from_flow(&flow);
         if self.flow_tracker.is_registered_dark_decoy(&dd_flow) {
             // Tagged flow! Forward packet to whatever
-            debug!("Tagged flow packet {}", flow);
+            //debug!("Tagged flow packet {}", flow);
 
             // Update expire time
             self.flow_tracker.mark_dark_decoy(&dd_flow);

### 2019-05-13 src/process_packet.rs
Stop requiring client to provide masked site
Masked site address is mandatory for 3-way-proxy,
but we downgraded to 2-way-proxy.

@@ -285,10 +285,6 @@ impl PerCoreGlobal
                     error!("ClientToStation has no covert: {:?}", c2s);
                     return None;
                 }
-                if !c2s.has_masked_decoy_server_name() {
-                    error!("ClientToStation has no masked decoy: {:?}", c2s);
-                    return None;
-                }
 
                 let covert_bytes = c2s.get_covert_address().as_bytes();
                 let masked_decoy_bytes = c2s.get_masked_decoy_server_name().as_bytes();

### 2019-05-13 application/main.go
Fix PROXY header: send host only, not host:port

@@ -549,15 +549,19 @@ func main() {
 	}
 }
 
-func writePROXYHeader(conn net.Conn, originalIP string) error {
-	if len(originalIP) == 0 {
+func writePROXYHeader(conn net.Conn, originalIPPort string) error {
+	if len(originalIPPort) == 0 {
 		return errors.New("can't write PROXY header: empty IP")
 	}
 	transportProtocol := "TCP4"
-	if !strings.Contains(originalIP, ".") {
+	if !strings.Contains(originalIPPort, ".") {
 		transportProtocol = "TCP6"
 	}
-	proxyHeader := fmt.Sprintf("PROXY %s %s 127.0.0.1 1111 1234\r\n", transportProtocol, originalIP)
-	_, err := conn.Write([]byte(proxyHeader))
+	host, port, err := net.SplitHostPort(originalIPPort)
+	if err != nil {
+		return err
+	}
+	proxyHeader := fmt.Sprintf("PROXY %s %s 127.0.0.1 %s 1234\r\n", transportProtocol, host, port)
+	_, err = conn.Write([]byte(proxyHeader))
 	return err
 }

### 2019-05-14 paper/paper.tex
Format fix
CCS ACM format
pass up to implementation

@@
-\documentclass[letterpaper,twocolumn,10pt]{article}
-\usepackage{usenix2019_v3}
-
-% For submission make this a noop
+\documentclass[sigconf]{acmart}
+%\usepackage{usenix2019_v3}
+
+\AtBeginDocument{%
+  \providecommand\BibTeX{{%
+    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
+
+%% Rights management information.  This information is sent to you
+%% when you complete the rights form.  These commands have SAMPLE
+%% values in them; it is your responsibility as an author to replace
+%% the commands and values with those provided to you when you
+%% complete the rights form.
+\setcopyright{acmcopyright}
+\copyrightyear{2019}
+\acmYear{2019}
+\acmDOI{10.1145/1122445.1122456}
+
+%% These commands are for a PROCEEDINGS abstract or paper.
+\acmConference[CCS '19]{CCS '19: ACM Conference on Computer and Communications
+Security}{November 11--15, 2019}{London, UK}
+\acmBooktitle{CCS '19: ACM Symposium on Computer and Communications Security,
+  November 11--15, 2019, London, UK}
+\acmPrice{0.00}
+\acmISBN{978-1-4503-9999-9/18/06}
 
@@
 
+\widowpenalty=10000
+\clubpenalty=10000
+
 \renewcommand{\paragraph}[1]{\smallskip\noindent\textbf{#1\quad}}
@@
 
+%\author{Anonymized for review}
 %for single author (just remove % characters)
@@
 %} % end author
-
-\maketitle
 
@@
 
-\FigHighLevel
+\keywords{anticensorship, proxies, network security}
+
+\maketitle
 
@@
 % 1.5-2 pages
+
+\FigHighLevel
 
@@
 For example, domain fronting~\cite{meek} was a popular circumvention
-strategy used by Meek (in Tor), as well as by the Signal secure messaging app to
+strategy used by meek (in Tor), as well as by the Signal secure messaging app to
 get around censorship in countries where it was
@@
 cat-and-mouse game.
+%TODO: don't need to hedge on IPv4 anymore..?
 \scheme supports both IPv4 and IPv6, though we note that the technique is especially
@@
 
+% TODO: modularity?
+
 We introduce the \scheme protocol (Section~\ref{sec:architecture})
@@
 \scheme has reduced complexity and substantially improved performance
-(Section~\ref{sec:evaluation}).  We believe that these advantages
+(Section~\ref{sec:evaluation}).  In addition, \scheme provides significantly
+more flexibility than existing Refraction protocols, allowing maintainers to
+respond to future censor techniques.
+We believe that these advantages
 make \scheme a strong choice for future Refraction Networking deployments.
@@
 Furthermore, we assume
-asymmetric routing (i.e. that the tap can sometimes only see packets from but not to the
+asymmetric routing (i.e. that the tap might only see packets from but not to the
 client).
@@
 Whitelists are expensive for censors to maintain and can stifle
-innovation, and are rarely employed by censors.
+innovation, and are rarely employed by country-level censors.
+%TODO: cite OONI? censored planet?
 
@@
 damage the censor is unwilling to suffer. Instead, the censor aims to identify
-the addresses that are phantom hosts, and block only those.
+the addresses that are phantom hosts, and block only those. We note this
+assumption supposes that the deployment is large enough to deter routing around
+decoy attacks~\cite{rad12,true-cost-rad}.
 
@@
 hosts, but that these will not reveal the phantom hosts of other users. The
-censor can also actively probe addresses that it sees users accessing, but can
-not enumerate the entire ISP prefix (e.g. a /32 IPv6 prefix contains
-$2^{96} addresses$).
+censor can also actively probe addresses that it sees users accessing, and can
+employ tools such as ZMap~\cite{zmap13} to scan large network blocks, excepting
+large IPv6 prefixes (e.g. a /32 IPv6 prefix contains $2^{96}$ addresses).
 
@@
 outside the scope of the censor, but that the censor can send non-disruptive
-probes (such as stale TCP acknowledgements or other packets that would normally
-be ignored). We emphasize that TapDance is observable by censors that can send
+probes (such as stale TCP acknowledgements) that would normally
+be ignored. We emphasize that TapDance is observable by censors that can send
 TCP packets in suspected connections, but that our protocol is robust against
@@
 
-\scheme involves three main steps. First, clients \textbf{register} with the
+\scheme involves two high-level steps. First, clients \textbf{register} with the
 ISP station,
-and agree on the phantom host IP address that will be used. Next, the client
-connects to the agreed upon address, which is terminated by an
-\textbf{application} running on the station. Finally, the client \textbf{proves}
-to the application that it was the same client that registered (and not a censor
-attempting to probe), and is able to use the application as a proxy.
+and agree on the phantom host IP address that will be used. Then, the client
+connects to the agreed upon phantom address, which relays the client's traffic
+to an \textbf{application}. If the application determines the traffic is from
+the same client that originally registered (and not a probing censor), it
+provides access to the proxy, tunneled through the application's protocol.
 
@@
 independently, allowing a wide range of flexibility to evade censors. We
-describe each of these components.
+describe each of these components, and then describe our implementation and
+deployment in Section~\ref{sec:implementation}.
 
@@
 Clients can register intent to use the proxy in several covert ways. For
-instance, they could use email or other existing intermittently available proxies
+instance, they could use email~\cite{SWEET-ToN} or any other existing intermittently
+available proxies
 to register. In this section, we use a form of Refraction Networking similar to
-TapDance to register directly with the station.
+TapDance to register directly with the station, though note our scheme is simpler and more
+difficult to detect or block compared to vanilla TapDance.
+%We note this form is simpler and more difficult to detect or block than
+%TapDance.
 
@@
 steganographic \textbf{tag} in the ciphertext of the request. We use
-the same technique used in TapDance's covert ciphertext channel\footnote{Section 3 in
+the same technique used in TapDance's covert ciphertext
+channel\footnote{Section~3 in
 TapDance~\cite{tapdance14}} to embed the tag, but we purposefully have the client
@@
 the tag, and does not need to respond to it (which requires mimicking the
-decoy)
+decoy).
+%In addition, more potential decoys can be used than in TapDance, as
+%there is no need to exclude decoys that have timeouts or TCP windows unfavorable
+%for keeping connections open. We estimate in our deployment an increase of 25\%
+%in decoys that could be used.
 
@@
 Elligator~\cite{elligator}), and a message encrypted under the shared secret
-derived from a key exchange with the station's long-term public key hard-coded
+derived from a Diffie-Hellman key exchange with the station's long-term public key hard-coded
 in the client software. The station uses its private key to compute the same
-shared secret from the (decoded) public key, and decrypts the message in the
+shared secret from the (decoded) client public key, and decrypts the message in the
 tag. The censor, without knowledge of either the station or client's private
@@
 configuration-specific information, such as flags to signify version, feature
-support, and a set of IPv6 network prefixes that the client knows can be used
+support, and a set of network prefixes that the client knows can be used
 for phantom hosts (previously distributed publicly).
 The client and server hash the seed to determine which specific
-IPv6 address from the set of prefixes will be used and registered as a phantom host. It may seem intuitive to instead have the client
+IP address from the set of prefixes will be used and registered as a phantom host.
+It may seem intuitive to instead have the client
 send the specific IP address to register, but allowing the client arbitrary
@@
 It also gives a
-secret (the seed) that only the client and station know, even after the client
-connects to the phantom host address.
+secret (the seed) that only the client and station know, which can
+later be used to verify a client connecting to the phantom host address is the
+original registering client.
 
@@
 packets destined to that address, and forwards them onto the phantom host
-\textbf{application}. The station can also optionally ignore packets not from
+\textbf{application}. The station ignores packets that are not from
 the source IP address of the registering client, so that to a probing censor
@@
 the phantom host appears to be firewalled off from all but the client. We note
-this is not a robust solution: censors have previously been observed taking over
-IP addresses of clients~\cite{ensafi-tor}. We instead address active probing in
-the application.
+that this does not address censors that send follow-up probes, as censors could
+take over the IP address of suspected clients for these
+probes~\cite{ensafi-tor}. However, it does prevent censors from enumerating the
+address space before hand, as they would have to do so from every potential
+client IP address. Simply scanning the prefixes with ZMap~\cite{zmap13} from a
+single vantage point would not reveal hosts that only respond to specific IPs
+(e.g. are firewalled off).
+%We instead address active probing in the application.
 
@@
 
-In addition, the use of IPv6 prevents censors from exhaustively probing
-potential phantom host network prefixes ahead of time to learn the full set of
-legitimate sites in the network.
+%In addition, the use of IPv6 prevents censors from exhaustively probing
+%potential phantom host network prefixes ahead of time to learn the full set of
+%legitimate sites in the network, even from a single vantage point.
+%Therefore, IPv6 phantom hosts could choose
+%to respond to any client, and not just the original registering client.
 
 \paragraph{IPv4}
-While \scheme composes well with IPv6, we can also support IPv4,
-at the cost of being vulnerable to active probing by the censor.
-We emphasize that TapDance is already
-vulnerable to active probing attacks~\cite{tapdance14} that \scheme defends
-against when using IPv6. However, in IPv4, there are substantially fewer
-addresses, allowing censors to easily enumerate network prefixes that pass by
-the ISP station and measure legitimate sites. Furthermore, the small address
-space makes it much easier to pre-image the hash used to derive IP addresses
-from the seed. Registering a specific IPv4 address in an IPv4 /16 subnet will
-take only an expected $2^{16}$ hashes for the censor to achieve. This would let
-attackers register legitimate hosts as phantom hosts, potentially disrupting
-legitimate service. If the station refused to pick up for addresses that
-correspond to legitimate hosts (measured by scanning during registration), then
-censors could use this as an oracle for distinguishing legitimate sites from
-phantom hosts. Still, IPv4 \scheme offers many performance, flexibility, and
-simplicity benefits over TapDance, though they are both vulnerable to active
-probing attacks.
+While \scheme composes well with IPv6, we can also support IPv4, with some
+careful caveats. First, in IPv4, there are substaintially fewer addresses,
+allowing censors to easily \textbf{enumerate network prefxies} that pass by the ISP
+station to look for legitimate sites to whitelist. However, as previously noted,
+having phantom hosts pretend to be firewalled off from all but the registered
+client forces censors to have to enumerate from all potential client vantage
+points to measure the state of hosts before registration. This whitelist
+approach for a censor would also overblock new services that came online after
+their scan.
+Additionally, for IPv4 \scheme, we dynamically generate the TCP port of the phantom host
+during registration (along with its IP), which further makes exhaustive scans infeasible:
+a censor that must enumerate from the vantage point of a /10 of client IPs (4~million IPs)
+to a /16 (65K IPs) of potential phantom proxies on each of 65K potential ports would take nearly
+50~years of scanning with ZMap at 10~Gbps.
+
+A second problem in IPv4 \scheme is that the limited range of IPs (and ports)
+makes it possible for a censor to \textbf{pre-image the hash} used to derive the phantom
+address from the seed. Even with the /16 of IPs and all 65K ports, a censor need
+only test an expecated $2^{32}$ possible seeds to find one that would allow it
+to register for that phantom address. The censor could then register a suspected
+address, and see if it provides proxy access. If it does, the censor learns
+there is no legitimate service there, and can block it. To combat this, we
+allow only a single client to register for a particular phantom address at a
+time. A censor could attempt to register all addresses in an attempt to deny
+proxy service to legitimate users, but this would be easily observed at the
+registration system, where rate limits via client puzzles or account-based fees
+could be enforced.
+
+Finally, legitimate \textbf{IPv4 addresses density} is much higher than IPv6,
+increasing the potential for users to accidentally register seeds that derive
+phantom addresses corresponding to live hosts. To address this, the station
+sends probes to potential phantom hosts during registration, and ignores the
+registration if a real host responds.
+
+%We emphasize that TapDance is already
+%vulnerable to active probing attacks~\cite{tapdance14} that \scheme defends
+%against when using IPv6. However, in IPv4, there are substantially fewer
+%addresses, allowing censors to easily enumerate network prefixes that pass by
+%the ISP station and measure legitimate sites. Furthermore, the small address
+%space makes it much easier to pre-image the hash used to derive IP addresses
+%from the seed. Registering a specific IPv4 address in an IPv4 /16 subnet will
+%take only an expected $2^{16}$ hashes for the censor to achieve. This would let
+%attackers register legitimate hosts as phantom hosts, potentially disrupting
+%legitimate service. If the station refused to pick up for addresses that
+%correspond to legitimate hosts (measured by scanning during registration), then
+%censors could use this as an oracle for distinguishing legitimate sites from
+%phantom hosts. Still, IPv4 \scheme offers many performance, flexibility, and
+%simplicity benefits over TapDance, though they are both vulnerable to active
+%probing attacks.
 
@@
 passed to the \textbf{application} running on the station. The application has
-two main jobs: first, it must look like an innocuous legitimate service to the
-censor, and second must allow the client to use it as a proxy.
+two main requirements: first, the protocol it uses to communicate with the
+client must be difficult for the censor to passively detect and block by traffic
+inspection. Second, the application must resist active probes by the censor (who
+does not know the registration seed).
 
@@
 instance, \texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
-Tor~\cite{tor} that could be
-modified to meet these needs: it requires each endpoint to have knowledge of a
-shared secret (which we can derive from the seed shared by the client and
-station during registration), and attempts to be a protocol with no discernible
+Tor~\cite{tor} that is designed to address both of these requirements:
+it requires each endpoint to have knowledge of a
+shared secret (which we can derive from the registration seed),
+and attempts to be a protocol with no discernible
 fingerprint. Probing censors that do not have the shared secret receive no
@@
 
-However, even though \texttt{obfs4} is indistinguishable from random, there are
-still known attacks that can differentiate it from other
-traffic~\cite{wang2015seeing}. While we have yet to see evidence of such attacks
-employed in practice by censors, we consider two alternatives built on TLS.
+%However, even though \texttt{obfs4} is indistinguishable from random, there are
+%still known attacks that can differentiate it from other
+%traffic~\cite{wang2015seeing}. While we have yet to see evidence of such attacks
+%employed in practice by censors, we consider two alternatives built on TLS.
+
+Besides obfs4, we next describe in detail several alternative application
+protocols based on SSH, TLS, and WebRTC. These
+alternatives neatly demonstrate the flexibility of \scheme in allowing deployments
+to support multiple application protocols. Should censors develop ways to
+identify and block one protocol, others can still be used to provide proxy
+access.
 
 \FigOverview
+
+\subsubsection{Obfuscated SSH}
+
+Obfuscated SSH~\cite{ossh} is a protocol that attempts to mask the Secure Shell
+(SSH) protocol in a thin
+layer of encryption. This makes it difficult for censors to identify using a
+regular expression, as there are no identifying headers or fields for a censor
+to search for. Instead, Obfuscated SSH clients first send a 16-byte seed, which
+is then used to derive a symmetric key that encrypts the rest of the
+communication. While this can be passively observable by censors (who can also
+derive the key and deobfuscate the protocol), the key derivation is deliberately
+slowed by an iterated hash to make such identifcation
+expensive (though not impossible) at high speeds.
+
+Obfuscated SSH also does not protect against active probing, as the censor can
+easily create their own connections and confirm the server is using the
+protocol. Nonetheless, this protocol is used successfully in deployed censorship
+circumvention systems~\cite{psiphon}. Obfuscated SSH could also be used as a \scheme
+application protocol, though we note it provides no active probing or passive
+identifcation resistance.
 
@@
 
-This is because TLS sends important server-identifying content in plaintext
+One challenge is that TLS sends important server-identifying content in plaintext
 during the TLS handshake. This includes the Server Name Indication (SNI) in the
@@
 To evade censors, we must send a plausible SNI value (sending no SNI is
-uncommon and easily blocked---study conducted using Colorado University network
-infrastructure shows that only 1\% of all TLS connections coming in and out of 
-campus do not carry the
-SNI extension~\cite{tls-fingerprint}), and we must have the server respond with
+uncommon and easily blocked---only 1\% of TLS connections
+do not send the SNI extension~\cite{tls-fingerprint}), and we must have the server respond with
 a plausible (and corresponding) certificate. Even if we manage to avoid sending
-either in the clear, censors could actively probe the server in a
-way that would normally elicit a certificate.
-
-We therefore attempt to mimic an existing \textbf{mask site}, by relaying
+either in the clear (e.g. using session resumption), censors could actively probe
+the server in a way that would normally elicit a certificate.
+
+We therefore attempt to mimic an existing \textbf{mask site} by relaying
 traffic between the client and a selected mask website. To a censor, this site
@@
 
-To accomplish this, the client changes the shared secret it derives with the
+To covertly signal to the relaying application, the client changes the shared secret
+it derives with the
 mask site to something that the application can also derive. The client's first
@@
 However, there are proposals to encrypt the SNI in the Client Hello~\cite{ietf-tls-esni-02},
-though none have been implemented or deployed as of early 2019. Nonetheless,
+though none have been implemented or deployed as of 2019. Nonetheless,
 if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
@@
 
-We implemented the \scheme protocol and tested it in a 10~Gbps ISP testbed
+We implemented the \scheme protocol and deployed it at a 10~Gbps ISP
 with real traffic. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to

### 2019-05-15 paper/figures.tex
update application overview fig

@@
     \centering
-    \includegraphics[width=\linewidth,clip]{figures/dark-decoy-overview.png}
+    \includegraphics[width=\linewidth,clip]{figures/conjure-overview.png}
     \caption{\textbf{\scheme Operations}\,---\,%
@@
         normal TLS connection to a Decoy site. Clients then connect to an address derived from the seed,
-        which the station responds as a phantom host. If the client can prove knowledge of the
+        which the station responds as a phantom host application. If the client can prove knowledge of the
         seed used during registration, they are allowed access to the proxy. Otherwise,
-        their traffic is forwarded to a Mask Site to make it difficult for censors to distinguish
-        phantom hosts from legitimate ones.
+        the phantom host application pretends to be a benign host by staying silent or forwarding traffic
+        to a mask site to make it difficult for censors to distinguish phantom hosts from legitimate ones.
     }
@@
 \newcommand{\FigHighLevel}{
-\begin{figure}[t]
+\begin{figure}[]
     \centering
-    \vspace{-0.54in}
+    %\vspace{-0.54in}
     \includegraphics[width=\linewidth,clip]{figures/high-level.png}

### 2019-05-15 paper/paper.tex
pass through implementation and related work

@@
 %TODO: don't need to hedge on IPv4 anymore..?
-\scheme supports both IPv4 and IPv6, though we note that the technique is especially
+\scheme supports both IPv4 and IPv6,
+though we note that the technique is especially
 powerful in IPv6, where censors cannot exhaustively scan the address space
@@
 range of detection attacks than TapDance.
-We have implemented a prototype implementation (Section~\ref{sec:implementation})
-and deployed it on a 10~Gbps testbed similar to the TapDance
+We have implemented Conjure (Section~\ref{sec:implementation})
+and deployed it on a 20~Gbps ISP testbed similar to the TapDance
 deployment~\cite{frolov2017isp}.  Compared to TapDance, we find that
@@
 \subsection{Registration}
-
+\label{sec:registration}
 Clients can register intent to use the proxy in several covert ways. For
@@
 packets destined to that address, and forwards them onto the phantom host
-\textbf{application}. The station ignores packets that are not from
-the source IP address of the registering client, so that to a probing censor
-from a different IP address,
-the phantom host appears to be firewalled off from all but the client. We note
-that this does not address censors that send follow-up probes, as censors could
-take over the IP address of suspected clients for these
-probes~\cite{ensafi-tor}. However, it does prevent censors from enumerating the
+\textbf{application}. The station only forwards packets that originate from the
+IP address of the registering client, making the phantom host appear as
+firewalled off to everyone but the client.
+We note that censors have been observed taking over client IP
+addresses for follow-up probing~\cite{ensafi-tor}, which would allow censors to
+still communicate with registered phantom hosts despite this filter.
+However, filtering in this way does prevent censors from enumerating the
 address space before hand, as they would have to do so from every potential
@@
 Once the client has registered, packets sent to the phantom host IP address are
-passed to the \textbf{application} running on the station. The application has
-two main requirements: first, the protocol it uses to communicate with the
-client must be difficult for the censor to passively detect and block by traffic
-inspection. Second, the application must resist active probes by the censor (who
+passed to the \textbf{application} running on the station, which provides
+proxy access to the client. The application has
+two main requirements: first, the protocol it uses with the client 
+must be difficult for the censor to \emph{passively detect} and block by traffic
+inspection. Second, the application must resist \emph{active probes} by the censor (who
 does not know the registration seed).
 
-Any protocol that satisfies these criteria can be used as an application. For
-instance, \texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
-Tor~\cite{tor} that is designed to address both of these requirements:
-it requires each endpoint to have knowledge of a
-shared secret (which we can derive from the registration seed),
-and attempts to be a protocol with no discernible
-fingerprint. Probing censors that do not have the shared secret receive no
-response, while clients that have the secret can communicate with the proxy.
+Any protocol that satisfies these criteria can be used as an application. In
+this section, we describe existing protocols (obfs4 and obfuscated SSH) as well
+as introduce our own (Mask sites, TLS 1.3 eSNI, and phantom WebRTC clients) that
+can be used in \scheme, and evaluate how each meet the necessary requirements.
+Figure~\ref{fig:overview} describes a high-level overview of the \scheme
+registration and application behavior.
+
+\FigOverview
+
+\subsubsection{obfs4}
+
+\texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
+Tor~\cite{tor} designed to resist both passive detection and active probing.
+Traffic is obfuscated by encrypting it and sending headerless ciphertext
+messages, and clients can only connect to \texttt{obfs4}
+servers by proving knowledge of a secret. Probing censors that do not have the
+secret get no response from \texttt{obfs4} servers, making it difficult for
+censors to confirm if a host is a proxy. Server IPs and their corresponding secrets
+are normally distributed out-of-band through Tor's bridge distribution system.
+
+We can adopt \texttt{obfs4} for use as a \scheme application, with minimal
+modification. During
+registration, the \scheme client and station can use the registration seed to
+derive the \texttt{obfs4} secrets (NODE\_ID and server private/public keys)
+needed for the client to connect. The station then launches an \texttt{obfs4} server
+instance at the registered phantom address, and the client can connect to it using the
+derived secrets. If a censor attempts to connect to the phantom address (even
+using the client's IP), it will not receive a response, as it does not know the
+registration seed used to derive the \texttt{obfs4} secrets.
+
+Using \texttt{obfs4} as a \scheme application has the added benefit that servers
+and secrets do not need to be distributed out-of-band, eliminating one of the
+main ways censors currently block existing \texttt{obfs4}
+instances~\cite{tor-bridge-blocking-blog}. Instead, each \scheme \texttt{obfs4}
+instance is private to its registering client, and there is no public service
+that censors can use to discover them.
 
@@
 
-Besides obfs4, we next describe in detail several alternative application
-protocols based on SSH, TLS, and WebRTC. These
-alternatives neatly demonstrate the flexibility of \scheme in allowing deployments
-to support multiple application protocols. Should censors develop ways to
-identify and block one protocol, others can still be used to provide proxy
-access.
-
-\FigOverview
+%Besides obfs4, we next describe in detail several alternative application
+%protocols based on SSH, TLS, and WebRTC. These
+%alternatives neatly demonstrate the flexibility of \scheme in allowing deployments
+%to support multiple application protocols. Should censors develop ways to
+%identify and block one protocol, others can still be used to provide proxy
+%access.
 
 \subsubsection{Obfuscated SSH}
+\label{sec:ossh}
 
@@
 (SSH) protocol in a thin
-layer of encryption. This makes it difficult for censors to identify using a
-regular expression, as there are no identifying headers or fields for a censor
+layer of encryption. This makes it difficult for censors to identify using basic
+packet filters, as there are no identifying headers or fields
 to search for. Instead, Obfuscated SSH clients first send a 16-byte seed, which
 is then used to derive a symmetric key that encrypts the rest of the
-communication. While this can be passively observable by censors (who can also
+communication. While this can passively detected by censors (who can also
 derive the key and deobfuscate the protocol), the key derivation is deliberately
@@
 easily create their own connections and confirm the server is using the
-protocol. Nonetheless, this protocol is used successfully in deployed censorship
-circumvention systems~\cite{psiphon}. Obfuscated SSH could also be used as a \scheme
+protocol. Nonetheless, this protocol is still used successfully in deployed censorship
+circumvention systems~\cite{psiphon}. Obfuscated SSH can also be used as a \scheme
 application protocol, though we note it provides no active probing or passive
@@
 \subsubsection{Mask Sites}
+\label{sec:mask-sites}
 
@@
 
-\subsubsection{WebRTC}
+\subsubsection{Phantom WebRTC Clients}
 \label{sec:webrtc}
@@
 
-We implemented the \scheme protocol and deployed it at a 10~Gbps ISP
-with real traffic. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to
-consume the 10~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
+We implemented the \scheme protocol and deployed a station at a
+20~Gbps router in a mid-sized transit ISP. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to
+consume the 20~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
 detector processes all packets and watches for new registrations. It also
@@
 
-We used PF\_RING to load balance the 10~Gbps link over 4~CPU cores. PF\_RING
+To achieve high-performance necessary to operate at 20~Gbps, we used
+PF\_RING~\cite{pfring} to load balance incoming packets over 4~CPU cores. PF\_RING
 supports balancing across cores based on flow (5-tuple) or source and
-destination IPs. However, both of these options present challenges for our 
-implementation. One issue is that registrations could be processed on a
+destination IPs. However, both of these options present engineering challenges
+for \scheme that we must overcome.
+One issue is that registrations could be processed on a
 different core than the packets sent to that specific phantom host address. For
@@
 
-To address this, we used Redis~\cite{redis} to allow each process to announce
+To address this, we used Redis~\cite{redis} to allow each process to broadcast
 (publish) newly registered decoys to the other cores so they can
@@
 
-To address the first issue, we force the client to delay sending its connection
+To address the first issue of asynchronous cores, we force the client to delay sending its connection
 to the phantom host until a short time after registration. In practice, we force
 the client to wait until the registration decoy responds before starting a
-connection with the registered phantom host.
-
-To address the second issue, we implemented a new load-balancing algorithm in
+connection with the registered phantom host. While the decoy response is
+unrelated to the station's processing, it serves as a conservative way to know
+the registration has had time to reach the station.
+
+To address the second issue of differing core timeouts, we implemented a new
+load-balancing algorithm in
 PF\_RING to select the core based solely on the destination IP address of the
-packet. This still means we must use Redis to tell all of the cores of new
-registrations, but that only one core will be responsible for processing all of
+packet. We still must use Redis to tell all of the cores of new
+registrations, but only one core will be ultimately responsible for processing all of
 the packets sent to a given phantom host, regardless of who or when it is sent.
@@
 
-Our client is also written in Golang, and uses a TapDance-like protocol for
+%TODO: how many registration requests do we make? how long does it take?
+We created a \scheme client and integrated it with the Psiphon~\cite{psiphon}
+anticensorship client. Psiphon has millions of users in censored countries, and
+we are in the early stages of rolling \scheme out to real-world users.
+
+Our \scheme client is written in Golang, and uses the TapDance-like protocol
+(Section~\ref{sec:registration}) for
 registration. We note that this protocol should be harder for censors to observe
-because it consists of only a single (complete) request, and the station does
+than normal TapDance because it consists of only a single (complete) request, and the station does
 not have to spoof packets as the decoy used during registration, only passively
@@
 
-After registering, the client connects to the derived phantom host address, and
-switches secrets after the handshake. At this point, a local application (e.g.
-SOCKS client) can connect to the client, and it will transparently be connected to
-the remote end via the encrypted phantom host connection.
+We implemented two of the applications in our client: Obfuscated SSH used by
+Psiphon
+(Section~\ref{sec:ossh}) and our Mask Site protocol
+(Section~\ref{sec:mask-sites}). Our client signals which application it will use
+in the registration tag. After registration, the client connects to the derived
+phantom host address, and speaks the specified application protocol, which
+tunnels a SOCKS connection between the client and Psiphon's backend servers,
+which proxy the client's connections.
 
 \if0
-In order to scale up to 10Gbps and beyond,
+In order to scale up to 20Gbps and beyond,
 one has to utilize multiple cores and employ load balancing.
@@
 
-TODO: say it's tested on 10 Gbps
+TODO: say it's tested on 20 Gbps
 
@@
 To evaluate our \scheme implementation, we compare its bandwidth
-to that of TapDance in a realistic ISP setting. We used a full duplex 10~Gbps
+to that of TapDance in a realistic ISP setting. We used a 20~Gbps
 network tap at a mid-sized ISP and run both implementations on a 1U server with
@@
 unused messages. We found only 0.016\% of addresses responded with any ICMP
-messages (a combination of ``Time Exceeded'' and ``Destination Unreachable'').
+messages (mainly ``Time Exceeded'' and ``Destination Unreachable'').
 
@@
 For instance, google.com has the address
-\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
-\texttt{2607:f8b0:400f:806::2004}). Only 24 bits are set to 1 in this address,
+%\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
+\texttt{2607:f8b0:400f:806::2004}. Only 24~bits are set to 1 in this address,
 giving censors a possible feature to filter on: addresses that have too much

### 2019-05-15 paper/related.tex
pass through implementation and related work

@@
 
-Traditionally, proxies deployed for censorship are eventually identified and blocked by the censor.
-Several proposals have been made to carefully control  the distribution of proxy addresses, using social connections and reputation~\cite{proximax,rbridge,salmon}.
-Nevertheless, keeping this information secret is challenging; additionally, censors often employ active scanning techniques to discover proxies~\cite{Dunna2018a}.
-Refraction networking generally assumes that clients have no secret information, and instead relies on the  collateral damage that would result from blocking all the potential decoy destinations.
-\scheme furthers this goal by creating a large number of destinations out of the dark space.
-A similar approach was taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large set of dummy destinations.
-CensorSpoofer, however, could only send information in one direction---to the client---and had to rely on a separate out-of-band channel for client-to-proxy communication.
-As an alternative approach, FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to run Flash- or WebRTC-based proxies within their browser to allow censored users to connect to the Tor network with the potential to greatly increase the number.
-In practice, these proxies served a very small number of users, as compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}
+Traditionally, proxies deployed for censorship are eventually identified and
+blocked by the censor. Several proposals have been made to carefully control
+the distribution of proxy addresses, using social connections and
+reputation~\cite{proximax,rbridge,salmon}. Nevertheless, keeping this
+information secret is challenging; additionally, censors often employ active
+scanning techniques to discover proxies~\cite{Dunna2018a}. Refraction
+networking generally assumes that clients have no secret information, and
+instead relies on the  collateral damage that would result from blocking all
+the potential decoy destinations. \scheme furthers this goal by creating a
+large number of destinations out of the dark space. A similar approach was
+conceptualized in DEFIANCE~\cite{lincoln2012}, where censored Tor clients
+connect to pools of addresses that are volunteered to run Tor bridge nodes.
+Unlike \scheme, DEFIANCE requires network admins that own the IP blocks to
+participate and operate proxies on their addresses, allowing censors to block
+the IP ranges involved once discovered. In contrast, \scheme can be
+deployed at transit ISPs, and censors face a large risk of collateral
+over-blocking if they block the network blocks used.
+Another similar approach was
+taken by CensorSpoofer~\cite{censorspoofer}, which spoofed traffic from a large
+set of dummy destinations. CensorSpoofer, however, could only send information
+in one direction---to the client---and had to rely on a separate out-of-band
+channel for client-to-proxy communication. As an alternative approach,
+FlashProxy~\cite{flash-proxies} and Snowflake~\cite{snowflake} allow users to
+run Flash- or WebRTC-based proxies within their browser to allow censored users
+to connect to the Tor network with the potential to greatly increase the
+number. In practice, these proxies served a very small number of users, as
+compared with other Tor bridge transports.\footnote{\url{https://metrics.torproject.org/userstats-bridge-transport.html?start=2017-01-01&end=2019-02-15&transport=!<OR>&transport=websocket&transport=snowflake}}

### 2019-05-15 paper/figures.tex
adding entropy figures.

@@
     \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
+    \includegraphics[width=\linewidth,clip]{figures/entropy_curveball_1hr.png}
     \caption{\textbf{IPv6 Entropy}---%
-        We observed 30 minutes of IPv6 traffic on our tap to the /32 of the ISP's network.
-        In each address observed, we counted the number of bits set, and compared this to
-        randomly generated addresses. If the 96 non-network bits
+        \textit{(Top)} In 30 minutes of IPv6 traffic observed on a /32 tap in 
+        the ISP's network we counted the number of bits set in each address, and compared this to
+        addresses generated from a uniform distribution. If the 96 non-network bits
         of each address were chosen randomly, we would expect to see a Binomial distribution
         (shown as Random). In practice, the distribution of observed IP addresses has much fewer
-        bits set, suggesting that censors might be able to distinguish between phantom host addresses
-        and legitimate ones.\looseness=-1
+        bits set. \textit{(Bottom)} To further investigate this we captured one hour of IPv6 
+        traffic at the same network tap and evaluated the entropy and aggregate count ratio 
+        (ACR) across each nybble for the set of IPv6 addresses observed~\cite{foremski2016entropy}.
+        The low entropy and high ACR in the upper nybbles can be attributed to the commonality 
+        of the addresses associated with the specific /32 on which we captured. Overall the
+        moderate entropy in most positions suggests that there is a relative structure to the way 
+        IPv6 addresses are used but no rigid positions that would betray an individual IPv6 address. 
+        Furthermore we can take consideration of that relative entropy when generating phantom 
+        addresses.\looseness=-1
+        % suggesting that censors might be able to distinguish between phantom host addresses
+        % and legitimate ones.
         %We note there are several /64 subnets that had many

### 2019-05-15 paper/paper.tex
adding entropy figures.

@@
 are still a significant number of networks that appear to have random-looking addresses,
-making it difficult for censors to block these addresses outright. For a specific deployment,
-operators should be careful to observe the distribution of addresses in the subnets they use,
-and possibly limit to randomizing ``realistic'' bits (e.g. the middle and/or last 32 bits).
+making it difficult for censors to block these addresses outright.
+
+Using one hour of collected traffic from the same tap we evaluated the entropy seen at
+each nybble in a set of IPv6 addresses~\cite{foremski2016entropy}. The entropy and aggregate 
+count ratio (ACR) for each position are used to group adjacent nybbles into probabilistically
+related segments. We can see that all segments display at least moderate entropy 
+suggesting that there is a structure to be mirrored in the way that IPv6 addresses are 
+assigned. However, we note that in the dataset that we collected there is no position 
+(outside of the upper bits related to the specific /32) that exhibited such low entropy
+so as to be a signal to a censor on their own when evaluating a single suspect IPv6 address.
+
+For a specific deployment, operators should be careful to observe the distribution of
+addresses in the subnets they use, and possibly limit to randomizing ``realistic'' 
+bits (e.g. the upper and/or last 32 bits within the given /32).
 

### 2019-05-15 paper/figures.tex
update address selection subsection

@@
 
-\newcommand{\FigIpBits}{
+\newcommand{\FigIpEntropy}{
 \begin{figure}[t]
     \centering
-    \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
-    \includegraphics[width=\linewidth,clip]{figures/entropy_curveball_1hr.png}
-    \caption{\textbf{IPv6 Entropy}---%
-        \textit{(Top)} In 30 minutes of IPv6 traffic observed on a /32 tap in 
-        the ISP's network we counted the number of bits set in each address, and compared this to
-        addresses generated from a uniform distribution. If the 96 non-network bits
-        of each address were chosen randomly, we would expect to see a Binomial distribution
-        (shown as Random). In practice, the distribution of observed IP addresses has much fewer
-        bits set. \textit{(Bottom)} To further investigate this we captured one hour of IPv6 
+    %\includegraphics[width=\linewidth,clip]{figures/entropy_curveball_1hr.png}
+    \includegraphics[width=\linewidth,clip]{figures/entropy-ip-16hr.png}
+    \caption{\textbf{IPv6 Entropy}---%,
+    To further investigate this we captured one hour of IPv6 
         traffic at the same network tap and evaluated the entropy and aggregate count ratio 
@@
         Furthermore we can take consideration of that relative entropy when generating phantom 
-        addresses.\looseness=-1
+        addresses.%\looseness=-1
+        }
+    \label{fig:ipentropy}
+\end{figure}
+}
+
+\newcommand{\FigIpBits}{
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
+    \caption{\textbf{IPv6 bits set}---%
+        In 16 hours of IPv6 traffic observed on a /32 tap in 
+        the ISP's network we counted the number of bits set in each address, and compared this to
+        addresses generated from a uniform distribution. If the 96 non-network bits
+        of each address were chosen randomly, we would expect to see a Binomial distribution
+        (shown as Random). In practice, the distribution of observed IP addresses has much fewer
+        bits set. Nonetheless, the significant overlap of these distributions
+        would make it difficult for censors to block any individual phantom hosts
+        without collateral risk of blocking legitimate services.
        % suggesting that censors might be able to distinguish between phantom host addresses

### 2019-05-15 paper/paper.tex
update address selection subsection

--- 2019-05-15 paper/paper.tex
@@
 original registering client.
+We discuss the intricacies of phantom IP address selection in
+Section~\ref{sec:addr-selection}.
 
@@
 
-\subsubsection{IPv6 vs.\ IPv4 Phantom Hosts}
+\subsection{Applications}
+
+Once the client has registered, packets sent to the phantom host IP address are
+passed to the \textbf{application} running on the station, which provides
+proxy access to the client. The application has
+two main requirements: first, the protocol it uses with the client 
+must be difficult for the censor to \emph{passively detect} and block by traffic
+inspection. Second, the application must resist \emph{active probes} by the censor (who
+does not know the registration seed).
+
+Any protocol that satisfies these criteria can be used as an application. In
+this section, we describe existing protocols (obfs4 and obfuscated SSH) as well
+as introduce our own (Mask sites, TLS 1.3 eSNI, and phantom WebRTC clients) that
+can be used in \scheme, and evaluate how each meet the necessary requirements.
+Figure~\ref{fig:overview} describes a high-level overview of the \scheme
+registration and application behavior.
+
+\FigOverview
+
+\subsubsection{obfs4}
+
+\texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
+Tor~\cite{tor} designed to resist both passive detection and active probing.
+Traffic is obfuscated by encrypting it and sending headerless ciphertext
+messages, and clients can only connect to \texttt{obfs4}
+servers by proving knowledge of a secret. Probing censors that do not have the
+secret get no response from \texttt{obfs4} servers, making it difficult for
+censors to confirm if a host is a proxy. Server IPs and their corresponding secrets
+are normally distributed out-of-band through Tor's bridge distribution system.
+
+We can adopt \texttt{obfs4} for use as a \scheme application, with minimal
+modification. During
+registration, the \scheme client and station can use the registration seed to
+derive the \texttt{obfs4} secrets (NODE\_ID and server private/public keys)
+needed for the client to connect. The station then launches an \texttt{obfs4} server
+instance at the registered phantom address, and the client can connect to it using the
+derived secrets. If a censor attempts to connect to the phantom address (even
+using the client's IP), it will not receive a response, as it does not know the
+registration seed used to derive the \texttt{obfs4} secrets.
+
+Using \texttt{obfs4} as a \scheme application has the added benefit that servers
+and secrets do not need to be distributed out-of-band, eliminating one of the
+main ways censors currently block existing \texttt{obfs4}
+instances~\cite{tor-bridge-blocking-blog}. Instead, each \scheme \texttt{obfs4}
+instance is private to its registering client, and there is no public service
+that censors can use to discover them.
+
+%However, even though \texttt{obfs4} is indistinguishable from random, there are
+%still known attacks that can differentiate it from other
+%traffic~\cite{wang2015seeing}. While we have yet to see evidence of such attacks
+%employed in practice by censors, we consider two alternatives built on TLS.
+
+%Besides obfs4, we next describe in detail several alternative application
+%protocols based on SSH, TLS, and WebRTC. These
+%alternatives neatly demonstrate the flexibility of \scheme in allowing deployments
+%to support multiple application protocols. Should censors develop ways to
+%identify and block one protocol, others can still be used to provide proxy
+%access.
+
+\subsubsection{Obfuscated SSH}
+\label{sec:ossh}
+
+Obfuscated SSH~\cite{ossh} is a protocol that attempts to mask the Secure Shell
+(SSH) protocol in a thin
+layer of encryption. This makes it difficult for censors to identify using basic
+packet filters, as there are no identifying headers or fields
+to search for. Instead, Obfuscated SSH clients first send a 16-byte seed, which
+is then used to derive a symmetric key that encrypts the rest of the
+communication. While this can passively detected by censors (who can also
+derive the key and deobfuscate the protocol), the key derivation is deliberately
+slowed by an iterated hash to make such identifcation
+expensive (though not impossible) at high speeds.
+
+Obfuscated SSH also does not protect against active probing, as the censor can
+easily create their own connections and confirm the server is using the
+protocol. Nonetheless, this protocol is still used successfully in deployed censorship
+circumvention systems~\cite{psiphon}. Obfuscated SSH can also be used as a \scheme
+application protocol, though we note it provides no active probing or passive
+identifcation resistance.
+
+\subsubsection{Mask Sites}
+\label{sec:mask-sites}
+
+TLS is a natural protocol for \scheme applications, because it is ubiquitous on
+the Internet (making it difficult for censors to block), while also providing
+strong cryptographic protection against passive and active network adversaries.
+However, there are several challenges to make it robust against censors that
+wish to block a particular service.
+
+One challenge is that TLS sends important server-identifying content in plaintext
+during the TLS handshake. This includes the Server Name Indication (SNI) in the
+Client Hello message that sends the domain name of the server, and the
+X.509 Certificate sent by the server.
+
+To evade censors, we must send a plausible SNI value (sending no SNI is
+uncommon and easily blocked---only 1\% of TLS connections
+do not send the SNI extension~\cite{tls-fingerprint}), and we must have the server respond with
+a plausible (and corresponding) certificate. Even if we manage to avoid sending
+either in the clear (e.g. using session resumption), censors could actively probe
+the server in a way that would normally elicit a certificate.
+
+We therefore attempt to mimic an existing \textbf{mask site} by relaying
+traffic between the client and a selected mask website. To a censor, this site
+will be indistinguishable from the legitimate mask site, making it difficult for
+them to block without potentially blocking the actual site. TLS connections to the
+application will terminate exactly as connections to the mask site would, with the
+application acting as a transparent proxy between the client and mask site.
+However, this leaves the application unable to introspect on the contents of the
+TLS connection to the mask site, as it does not have the client-site shared
+secrets, and it cannot overtly man-in-the-middle the connection before knowing
+it is communicating with the legitimate client (and not the censor).
+
+To covertly signal to the relaying application, the client changes the shared secret
+it derives with the
+mask site to something that the application can also derive. The client's first
+\texttt{Application Data} packet is thus encrypted under a different secret than
+the client/mask site secret. Specifically, the client uses the \textbf{seed}
+sent during registration to derive the pre-master secret for the connection.
+This is hashed along with the client and server randoms of the current (mask
+site) TLS connection to obtain the master secret that determines
+encryption/decryption/authentication keys.
+
+The application can determine if the client did this by trial decryption with
+the master secret derived from the known \textbf{seed}. If it succeeds, the
+client has proved knowledge of the \textbf{seed}, and the application can
+respond as a proxy. If not, the application simply continues to forward data
+between the client and the mask site. As the censor does not have knowledge of
+the \textbf{seed} used in registration, it cannot coerce the application to
+appear as anything besides the mask site.
+
+\subsubsection{Mask Site Selection}
+
+Selecting which sites to masquerade as must be done carefully to avoid censors
+being able to detect obvious choices. For example, if a small university network
+has a phantom host in their network that appears to be \texttt{apple.com}, it
+would be easy for a censor to block as a likely non-legitimate host. Likewise,
+if a phantom host at an IP address pretends to be a domain (\texttt{example.com}) that
+globally resolves to a single different IP address, the censor could also
+identify and block the phantom host.
+
+\paragraph{Nearby sites.}
+One strategy for selecting mask sites to mimic is to pick websites that are
+legitimately hosted in or near the network of the phantom host addresses. This
+effectively creates copies of legitimate sites, with the censor unable to
+determine which copies are real and which are the phantom hosts. However, as
+mentioned, other signals such as DNS may reveal the true mask site.
+
+\paragraph{Popular sites.}
+An alternative strategy is to use popular sites, such as those from the Alexa
+top site~\cite{alexa-top500} list. As mentioned previously, it may be wise to avoid
+sites that are obviously not hosted in the phantom host address range, such as
+large companies that run their own data centers and own their own ASN.
+The list could also be filtered to domains that resolve to different IP
+addresses from different vantage points, making it harder for a censor to know
+if a phantom host corresponds to a domain's IP.
+
+\paragraph{Passive observation.}
+The ISP tap could also collect sites by passively observing DNS requests, TLS
+SNI, or certificates that pass by. This would allow for building a realistic set
+of sites that are plausibly in the vicinity of the phantom host addresses
+that pass by the tap. It also has the added bonus of being able to discover
+IPv6 addresses that could be used as decoys (for registration), where active
+scanning would be infeasible.
+
+In practice, clients can often try phantom hosts/mask sites over
+several attempts, as blocking the client outright may negatively impact other
+unrelated users behind the same network (e.g. in the case of NAT). Thus, even a
+censor that can block most (but not all) mask site only delays access, and
+doesn't prevent it outright.
+
+\subsubsection{Encrypted SNI}
+\label{esni}
+
+TLS~1.3~\cite{tls13} offers several features that may greatly simplify 
+\scheme application design. For instance, TLS~1.3 handshakes include encrypted
+certificates, potentially obviating the need to impersonate mask sites.
+Unfortunately, TLS~1.3 currently still sends the SNI in the (plaintext) Client
+Hello, meaning we would still have to choose a realistic domain to fool a
+censor.
+
+However, there are proposals to encrypt the SNI in the Client Hello~\cite{ietf-tls-esni-02},
+though none have been implemented or deployed as of 2019. Nonetheless,
+if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
+\scheme applications by allowing the domain to remain hidden from the censor.
+While the censor could still try to actively probe with guesses for the SNI,
+servers could respond with generic ``Unknown SNI'' errors. If such responses
+were common for incorrect SNI, the censor's efforts to identify phantom hosts
+would be frustrated.
+
+\subsubsection{Phantom WebRTC Clients}
+\label{sec:webrtc}
+
+Phantom hosts could also pretend to be clients instead of servers. This may
+potentially give censors less to block on, as actively probing clients is common
+to return few or no open ports. Nonetheless, a censor may be hesitant to block
+client-to-client communication, as it could block peer-to-peer applications as
+well as many video conferencing protocols. WebRTC is a
+natural choice for a client-to-client protocol in censorship circumvention,
+and is used in existing censorship circumvention schemes like
+Snowflake~\cite{snowflake}. \scheme could also use WebRTC as the
+application protocol, convincing the censor that two clients are communicating.
+
+\subsection{Address Selection}
+\label{sec:addr-selection}
 
@@
 
-\paragraph{IPv4}
+\subsubsection{IPv4}
 While \scheme composes well with IPv6, we can also support IPv4, with some
-careful caveats. First, in IPv4, there are substaintially fewer addresses,
-allowing censors to easily \textbf{enumerate network prefxies} that pass by the ISP
-station to look for legitimate sites to whitelist. However, as previously noted,
-having phantom hosts pretend to be firewalled off from all but the registered
-client forces censors to have to enumerate from all potential client vantage
-points to measure the state of hosts before registration. This whitelist
-approach for a censor would also overblock new services that came online after
-their scan.
-Additionally, for IPv4 \scheme, we dynamically generate the TCP port of the phantom host
-during registration (along with its IP), which further makes exhaustive scans infeasible:
+careful caveats. First, in IPv4, there are substantially fewer addresses,
+allowing censors to easily \textbf{enumerate network prefixes} that pass by the ISP
+station to look for legitimate sites to whitelist. To address this, \scheme
+phantom hosts are firewalled from all IPs other than the client that registered
+them. Thus, censors would not see them in an enumerating scan from a single
+vantage point before registration (when they do not exist), and blocking hosts
+not seen in such a scan would block legitimate hosts that firewalled themselves
+off from all but a few IPs. % Such firewall behavior is a best practice for...
+Censors could attempt to scan the network from \emph{all} potential client
+vantage points, by co-opting client IPs to perform scans---a behavior previously
+observed by the Great Firewall of China to scan for Tor bridges~\cite{ensafi-tor}.
+To prevent this, for IPv4 \scheme, we dynamically generate the TCP port of the
+phantom host (along with its IP) from the registration seed, which further makes
+exhaustive scans infeasible:
 a censor that must enumerate from the vantage point of a /10 of client IPs (4~million IPs)
 to a /16 (65K IPs) of potential phantom proxies on each of 65K potential ports would take nearly
-50~years of scanning with ZMap at 10~Gbps.
+50~years of scanning with ZMap at 10~Gbps. We note that while the use of
+non-standard ports could potentially be suspicious, several successful
+circumvention tools---including Psiphon~\cite{psiphon} and
+\texttt{obfs4}~\cite{obfs4}---use random ports on their obfuscated protocols.
+Finally, we note that censors that whitelist either standard ports or discovered
+hosts from enumerations scans would over-block new services that came online after
+their scans.
 
@@
 address from the seed. Even with the /16 of IPs and all 65K ports, a censor need
-only test an expecated $2^{32}$ possible seeds to find one that would allow it
+only test an expected $2^{32}$ possible seeds to find one that would allow it
 to register for that phantom address. The censor could then register a suspected
@@
 phantom addresses corresponding to live hosts. To address this, the station
-sends probes to potential phantom hosts during registration, and ignores the
-registration if a real host responds.
+sends probes to potential IPv4 phantom hosts during registration, and ignores the
+registration if a real host responds. Censors that try to register specific
+phantom proxies will be unable to distinguish if another user has registered it
+or a legitimate host is there, as in both cases we ignore the censor's
+registration. This also serves to prevent abuse by attackers that attempt
+to use the \scheme station to interfere with legitimate services.
 
@@
 
-\subsection{Applications}
-
-Once the client has registered, packets sent to the phantom host IP address are
-passed to the \textbf{application} running on the station, which provides
-proxy access to the client. The application has
-two main requirements: first, the protocol it uses with the client 
-must be difficult for the censor to \emph{passively detect} and block by traffic
-inspection. Second, the application must resist \emph{active probes} by the censor (who
-does not know the registration seed).
-
-Any protocol that satisfies these criteria can be used as an application. In
-this section, we describe existing protocols (obfs4 and obfuscated SSH) as well
-as introduce our own (Mask sites, TLS 1.3 eSNI, and phantom WebRTC clients) that
-can be used in \scheme, and evaluate how each meet the necessary requirements.
-Figure~\ref{fig:overview} describes a high-level overview of the \scheme
-registration and application behavior.
-
-\FigOverview
-
-\subsubsection{obfs4}
-
-\texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
-Tor~\cite{tor} designed to resist both passive detection and active probing.
-Traffic is obfuscated by encrypting it and sending headerless ciphertext
-messages, and clients can only connect to \texttt{obfs4}
-servers by proving knowledge of a secret. Probing censors that do not have the
-secret get no response from \texttt{obfs4} servers, making it difficult for
-censors to confirm if a host is a proxy. Server IPs and their corresponding secrets
-are normally distributed out-of-band through Tor's bridge distribution system.
-
-We can adopt \texttt{obfs4} for use as a \scheme application, with minimal
-modification. During
-registration, the \scheme client and station can use the registration seed to
-derive the \texttt{obfs4} secrets (NODE\_ID and server private/public keys)
-needed for the client to connect. The station then launches an \texttt{obfs4} server
-instance at the registered phantom address, and the client can connect to it using the
-derived secrets. If a censor attempts to connect to the phantom address (even
-using the client's IP), it will not receive a response, as it does not know the
-registration seed used to derive the \texttt{obfs4} secrets.
-
-Using \texttt{obfs4} as a \scheme application has the added benefit that servers
-and secrets do not need to be distributed out-of-band, eliminating one of the
-main ways censors currently block existing \texttt{obfs4}
-instances~\cite{tor-bridge-blocking-blog}. Instead, each \scheme \texttt{obfs4}
-instance is private to its registering client, and there is no public service
-that censors can use to discover them.
-
-%However, even though \texttt{obfs4} is indistinguishable from random, there are
-%still known attacks that can differentiate it from other
-%traffic~\cite{wang2015seeing}. While we have yet to see evidence of such attacks
-%employed in practice by censors, we consider two alternatives built on TLS.
-
-%Besides obfs4, we next describe in detail several alternative application
-%protocols based on SSH, TLS, and WebRTC. These
-%alternatives neatly demonstrate the flexibility of \scheme in allowing deployments
-%to support multiple application protocols. Should censors develop ways to
-%identify and block one protocol, others can still be used to provide proxy
-%access.
-
-\subsubsection{Obfuscated SSH}
-\label{sec:ossh}
-
-Obfuscated SSH~\cite{ossh} is a protocol that attempts to mask the Secure Shell
-(SSH) protocol in a thin
-layer of encryption. This makes it difficult for censors to identify using basic
-packet filters, as there are no identifying headers or fields
-to search for. Instead, Obfuscated SSH clients first send a 16-byte seed, which
-is then used to derive a symmetric key that encrypts the rest of the
-communication. While this can passively detected by censors (who can also
-derive the key and deobfuscate the protocol), the key derivation is deliberately
-slowed by an iterated hash to make such identifcation
-expensive (though not impossible) at high speeds.
-
-Obfuscated SSH also does not protect against active probing, as the censor can
-easily create their own connections and confirm the server is using the
-protocol. Nonetheless, this protocol is still used successfully in deployed censorship
-circumvention systems~\cite{psiphon}. Obfuscated SSH can also be used as a \scheme
-application protocol, though we note it provides no active probing or passive
-identifcation resistance.
-
-\subsubsection{Mask Sites}
-\label{sec:mask-sites}
-
-TLS is a natural protocol for \scheme applications, because it is ubiquitous on
-the Internet (making it difficult for censors to block), while also providing
-strong cryptographic protection against passive and active network adversaries.
-However, there are several challenges to make it robust against censors that
-wish to block a particular service.
-
-One challenge is that TLS sends important server-identifying content in plaintext
-during the TLS handshake. This includes the Server Name Indication (SNI) in the
-Client Hello message that sends the domain name of the server, and the
-X.509 Certificate sent by the server.
-
-To evade censors, we must send a plausible SNI value (sending no SNI is
-uncommon and easily blocked---only 1\% of TLS connections
-do not send the SNI extension~\cite{tls-fingerprint}), and we must have the server respond with
-a plausible (and corresponding) certificate. Even if we manage to avoid sending
-either in the clear (e.g. using session resumption), censors could actively probe
-the server in a way that would normally elicit a certificate.
-
-We therefore attempt to mimic an existing \textbf{mask site} by relaying
-traffic between the client and a selected mask website. To a censor, this site
-will be indistinguishable from the legitimate mask site, making it difficult for
-them to block without potentially blocking the actual site. TLS connections to the
-application will terminate exactly as connections to the mask site would, with the
-application acting as a transparent proxy between the client and mask site.
-However, this leaves the application unable to introspect on the contents of the
-TLS connection to the mask site, as it does not have the client-site shared
-secrets, and it cannot overtly man-in-the-middle the connection before knowing
-it is communicating with the legitimate client (and not the censor).
-
-To covertly signal to the relaying application, the client changes the shared secret
-it derives with the
-mask site to something that the application can also derive. The client's first
-\texttt{Application Data} packet is thus encrypted under a different secret than
-the client/mask site secret. Specifically, the client uses the \textbf{seed}
-sent during registration to derive the pre-master secret for the connection.
-This is hashed along with the client and server randoms of the current (mask
-site) TLS connection to obtain the master secret that determines
-encryption/decryption/authentication keys.
-
-The application can determine if the client did this by trial decryption with
-the master secret derived from the known \textbf{seed}. If it succeeds, the
-client has proved knowledge of the \textbf{seed}, and the application can
-respond as a proxy. If not, the application simply continues to forward data
-between the client and the mask site. As the censor does not have knowledge of
-the \textbf{seed} used in registration, it cannot coerce the application to
-appear as anything besides the mask site.
-
-\subsubsection{Mask Site Selection}
-
-Selecting which sites to masquerade as must be done carefully to avoid censors
-being able to detect obvious choices. For example, if a small university network
-has a phantom host in their network that appears to be \texttt{apple.com}, it
-would be easy for a censor to block as a likely non-legitimate host. Likewise,
-if a phantom host at an IP address pretends to be a domain (\texttt{example.com}) that
-globally resolves to a single different IP address, the censor could also
-identify and block the phantom host.
-
-\paragraph{Nearby sites.}
-One strategy for selecting mask sites to mimic is to pick websites that are
-legitimately hosted in or near the network of the phantom host addresses. This
-effectively creates copies of legitimate sites, with the censor unable to
-determine which copies are real and which are the phantom hosts. However, as
-mentioned, other signals such as DNS may reveal the true mask site.
-
-\paragraph{Popular sites.}
-An alternative strategy is to use popular sites, such as those from the Alexa
-top site~\cite{alexa-top500} list. As mentioned previously, it may be wise to avoid
-sites that are obviously not hosted in the phantom host address range, such as
-large companies that run their own data centers and own their own ASN.
-The list could also be filtered to domains that resolve to different IP
-addresses from different vantage points, making it harder for a censor to know
-if a phantom host corresponds to a domain's IP.
-
-\paragraph{Passive observation.}
-The ISP tap could also collect sites by passively observing DNS requests, TLS
-SNI, or certificates that pass by. This would allow for building a realistic set
-of sites that are plausibly in the vicinity of the phantom host addresses
-that pass by the tap. It also has the added bonus of being able to discover
-IPv6 addresses that could be used as decoys (for registration), where active
-scanning would be infeasible.
-
-In practice, clients can often try phantom hosts/mask sites over
-several attempts, as blocking the client outright may negatively impact other
-unrelated users behind the same network (e.g. in the case of NAT). Thus, even a
-censor that can block most (but not all) mask site only delays access, and
-doesn't prevent it outright.
-
-\subsubsection{Encrypted SNI}
-\label{esni}
-
-TLS~1.3~\cite{tls13} offers several features that may greatly simplify 
-\scheme application design. For instance, TLS~1.3 handshakes include encrypted
-certificates, potentially obviating the need to impersonate mask sites.
-Unfortunately, TLS~1.3 currently still sends the SNI in the (plaintext) Client
-Hello, meaning we would still have to choose a realistic domain to fool a
-censor.
-
-However, there are proposals to encrypt the SNI in the Client Hello~\cite{ietf-tls-esni-02},
-though none have been implemented or deployed as of 2019. Nonetheless,
-if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
-\scheme applications by allowing the domain to remain hidden from the censor.
-While the censor could still try to actively probe with guesses for the SNI,
-servers could respond with generic ``Unknown SNI'' errors. If such responses
-were common for incorrect SNI, the censor's efforts to identify phantom hosts
-would be frustrated.
-
-\subsubsection{Phantom WebRTC Clients}
-\label{sec:webrtc}
-
-Phantom hosts could also pretend to be clients instead of servers. This may
-potentially give censors less to block on, as actively probing clients is common
-to return few or no open ports. Nonetheless, a censor may be hesitant to block
-client-to-client communication, as it could block peer-to-peer applications as
-well as many video conferencing protocols. WebRTC is a
-natural choice for a client-to-client protocol in censorship circumvention,
-and is used in existing censorship circumvention schemes like
-Snowflake~\cite{snowflake}. \scheme could also use WebRTC as the
-application protocol, convincing the censor that two clients are communicating.
+\subsubsection{IPv6 address entropy}
+\FigIpBits
+
+In IPv6 \scheme, we no longer need to worry about address enumeration or
+pre-image attacks. Our ISP routes a /32 IPv6 prefix, which provides $2^{96}$ potential
+phantom host IP addresses. However, IPv6 addresses often have long runs of 0
+bits in them, and rarely use all 128-bits equally.
+For instance, google.com has the address
+%\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
+\texttt{2607:f8b0:400f:806::2004}, which only has 24 bits set to 1.
+Censors might try to use this observation and block high entropy IPv6 addresses.
+
+To measure and quantify this problem, we collected and analyzed 16 hours of
+netflow data at our ISP tap. We extracted 4013 IPv6 addresses observed in the /32
+IPv6 prefix routed by the ISP (out of 32,817 total observed). To confirm the
+hypothesis that 0 bits are more common in IPv6 addresses, we counted the number
+of bits set in each address. Figure~\ref{fig:ipbits} shows a histogram of the
+number of bits set and compares it to the histogram of a uniformly random set of
+addresses.\footnote{The random distribution's center is skewed from 64 due to
+the number of set bits in our fixed /32 network prefix.} Although these
+distributions are distinguishable, they do have significant overlap. Given
+enough samples, a censor could trivially tell if the addresses were chosen
+randomly or were legitimate hosts. However, a censor's job is significantly
+harder, and they must tell from a single sample which distribution it comes
+from. The presence of random-looking addresses makes it difficult for censors to
+block such hosts outright.
+
+% 7 bits set in 2001:48a8:: (would expect 16)
+
+\FigIpEntropy
+
+Prior work by Foremski et al.~\cite{foremski2016entropy} has developed models to
+generate likely IPv6 addresses from a set of known addresses, useful for
+discovering new hosts to scan given known ones. We use their Entropy/IP tool to
+analyze the addresses we collected. Figure~\ref{fig:ipentropy} shows the
+normalized entropy of each address 4-bit nibble and the total entropy (18.8 out
+of 32). Nibbles that were constant across all addresses
+(such as the /32 network prefix nibbles) have zero entropy, while those that
+equally span the range of values have maximum entropy (normalized to 1). In our
+addresses, we observe an entropy of over 75~bits, with more entropy in the later
+segments of the address. While not quite the full 96~bits that uniformly random
+would produce, this is still a significant amount for phantom hosts to hide in.
+
+For a specific deployment, operators should be careful to observe the distribution of
+addresses in the subnets they use, and possibly limit to randomizing ``realistic''
+bits (e.g. the upper and/or last 32 bits within the given /32).
+As an improvement, we could also use the Entropy/IP
+tool~\cite{foremski2016entropy} to generate the random IPv6 phantom hosts from
+the registration seed based on the Bayesian Network model created by the tool.
 
@@
 
-\FigIpBits
-
-\paragraph{Address entropy}
-Addresses in IPv6 are commonly shortened, as many of the 128-bits in the address are set to 0.
-For instance, google.com has the address
-%\texttt{2607:f8b0:400f:0806:0000:0000:0000:2004} (which can be shortened to
-\texttt{2607:f8b0:400f:806::2004}. Only 24~bits are set to 1 in this address,
-giving censors a possible feature to filter on: addresses that have too much
-entropy (or even simply bits set) could be suspicious as phantom hosts. To demonstrate and quantify
-this problem, we measured 30 minutes of IPv6 traffic to our ISP's /32 network prefix.
-Figure~\ref{fig:ipbits} shows a histogram of bits set in the addresses we observed, which are
-notably skewed to less than expected if addresses were randomly generated. However, there
-are still a significant number of networks that appear to have random-looking addresses,
-making it difficult for censors to block these addresses outright. For a specific deployment,
-operators should be careful to observe the distribution of addresses in the subnets they use,
-and possibly limit to randomizing ``realistic'' bits (e.g. the middle and/or last 32 bits).
-
 \input{related}

### 2019-05-15 script/analyze.sh

@@ -3,12 +3,15 @@
 #python gen-addrs.py 100000 | python count-v6-bits.py | sort -n > rand.pdf
 #cat rand.pdf | cdf > rand.cdf
 
-cat ./data/all-by-pkt.out | grep '^2001:48a8:' | sort | uniq | python count-v6-bits.py | sort -n > merit-observed.pdf
+
+#cat ./data/all-by-pkt.out | grep '^2001:48a8:' | sort | uniq | python count-v6-bits.py | sort -n > merit-observed.pdf
+cat ./data/ip6-16hr.out | grep '^2001:48a8:' | sort | uniq | python count-v6-bits.py | sort -n > merit-observed.pdf
 cat merit-observed.pdf | cdf > merit-observed.cdf
 
-#cat merit-observed.pdf | sort -n | uniq -c > merit-observed.counts
+cat merit-observed.pdf | sort -n | uniq -c > merit-observed.counts
 
-cat ./data/all-by-pkt.out | sort | uniq | python count-v6-bits.py | sort -n > all-observed.pdf
+#cat ./data/all-by-pkt.out | sort | uniq | python count-v6-bits.py | sort -n > all-observed.pdf
+cat ./data/ip6-16hr.out | sort | uniq | python count-v6-bits.py | sort -n > all-observed.pdf
 
 cat all-observed.pdf | cdf > all-observed.cdf
 

### 2019-05-15 paper/figures.tex
add applications table

--- 2019-05-15 paper/figures.tex
@@
 
+\newcommand{\FigIpEntropy}{
+\begin{figure}[t]
+    \centering
+    %\includegraphics[width=\linewidth,clip]{figures/entropy_curveball_1hr.png}
+    \includegraphics[width=\linewidth,clip]{figures/entropy-ip-16hr.png}
+    \caption{\textbf{IPv6 Entropy}---%,
+        Censors may be able to distinguish random-looking phantom host IPv6 addresses
+        from legitimately used ones based on the address's entropy.
+        We used the Entropy/IP tool~\cite{foremski2016entropy} to analyze the entropy
+        of 4013 IPv6 addresses observed by our tap. This plot from the tool shows the
+        normalized entropy of each nibble in the addresses, which is fairly high
+        for most of the non-network prefix nibbles. In total, these addresses have
+        about 75~bits of entropy (out of 96 expected), and the relatively high entropy
+        present in each nibble would make it difficult for a censor to block without
+        significant false positives / negatives. While distinguishable from random
+        given enough samples,
+        we can also use the Entropy/IP tool to generate addresses from the Bayesian Network
+        model it produces.}
+    \label{fig:ipentropy}
+\end{figure}
+}
+
 \newcommand{\FigIpBits}{
@@
     \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
-    \caption{\textbf{IPv6 Entropy}---%
-        We observed 30 minutes of IPv6 traffic on our tap to the /32 of the ISP's network.
-        In each address observed, we counted the number of bits set, and compared this to
-        randomly generated addresses. If the 96 non-network bits
-        of each address were chosen randomly, we would expect to see a Binomial distribution
-        (shown as Random). In practice, the distribution of observed IP addresses has much fewer
-        bits set, suggesting that censors might be able to distinguish between phantom host addresses
-        and legitimate ones.\looseness=-1
+    \caption{\textbf{IPv6 bits set}---%
+        We measure the number of bits set to 1 in IPv6 addresses in our ISP's /32
+        and observed by our tap,
+        and compare it to the Binomial distribution (Random) we would expect to see
+        if the 96 non-network bits of each address were chosen randomly. In practice,
+        we observe much fewer bits set.
+        Nonetheless, the significant overlap of these distributions
+        would make it difficult for censors to block any individual phantom hosts
+        without collateral risk of blocking legitimate services.
+       % suggesting that censors might be able to distinguish between phantom host addresses
+        % and legitimate ones.
         %We note there are several /64 subnets that had many
@@
             Unlimited Session Length  &\yes & \yes & \yes & \no  & \no  & \no  & \no  & \yes \\
-            %Multicore Implementation  &\no  & \no  & \no  & \yes & \no  & \no  & \no  & \yes \\
+            %ISP Deployment           &\no  & \no  & \no  & \yes & \no  & \no  & \no  & \yes \\
     \end{tabular}
@@
 
+\newcommand{\TabApplications}{
+\begin{table}[t]
+    \centering
+    \begin{tabular}{l|ccccc}
+            & \rot{OSSH~\cite{ossh}} &
+              \rot{\texttt{obfs4}~\cite{obfs4}} &
+              \rot{Mask Sites} &
+              \rot{TLS eSNI} & \rot{WebRTC} \\
+            \hline
+            Active probe resistant  & \no  & \yes & \yes & \yes & \yes \\
+            Randomized or Tunneling & R    & R    & T    &  T   & T \\
+            Known passive attack    & \cite{Fifield2017a} & \cite{wang2015seeing} & - & - & - \\
+            \scheme implementation  & \yes & \no  & \yes  & \no & \no \\
+    \end{tabular}
+    \caption{\textbf{\scheme Applications}\,---\,
+    ``Active probe resistant`` protocols are designed to look innocuous even if scanned by a censor.
+    ``Tunneling`` (T) protocols use another protocol (e.g. TLS) to blend in, while ``Randomized`` (R)
+        ones attempt to have no discernable protocol fingerprint or headers.
+        For existing protocols, we list any known attacks suggested in the literature that let censors
+        passively detect them. We also list if we have implemented the application in our prototype.}
+    \label{tab:applications}
+\end{table}
+}
+
 \newcommand{\FigImplementation}{
@@
         determines if the client is legitimate (using a seed shared during registration) and forwards
-        their traffic to a proxy. Otherwise, the application responds as if it were the mask site.
-    }
+        their traffic to a proxy. Otherwise, the application responds as if it were the mask site.}
     \label{fig:implementation}

### 2019-05-16 paper/paper.tex
add applications table
minor edits

@@
 the same technique used in TapDance's covert ciphertext
-channel\footnote{Section~3 in
-TapDance~\cite{tapdance14}} to embed the tag, but we purposefully have the client
+channel~\cite[\S3]{tapdance14}
+to embed the tag, but we purposefully have the client
 send a complete request (rather than incomplete), allowing the decoy server to respond.
@@
 private key. Unlike in TapDance, the \scheme station can passively observe
-the tag, and does not need to respond to it (which requires mimicking the
-decoy).
-%In addition, more potential decoys can be used than in TapDance, as
-%there is no need to exclude decoys that have timeouts or TCP windows unfavorable
-%for keeping connections open. We estimate in our deployment an increase of 25\%
-%in decoys that could be used.
+the tag, and does not need to respond to it, obviating the need to mimick the decoy.
+In addition, more potential decoys can be used than in TapDance, as
+there is no need to exclude decoys that have timeouts or TCP windows unfavorable
+for keeping connections open. In our ISP deployment, this results in a modest increase
+of 25\% more decoys that could be used than in TapDance.
 
@@
 Figure~\ref{fig:overview} describes a high-level overview of the \scheme
-registration and application behavior.
+registration and application behavior, and Table~\ref{tab:applications} compares the
+application protocols.
 
@@
 
-Obfuscated SSH~\cite{ossh} is a protocol that attempts to mask the Secure Shell
+Obfuscated SSH~\cite{ossh} (OSSH) is a protocol that attempts to mask the Secure Shell
 (SSH) protocol in a thin
@@
 communication. While this can passively detected by censors (who can also
-derive the key and deobfuscate the protocol), the key derivation is deliberately
-slowed by an iterated hash to make such identifcation
+derive the key and de-obfuscate the protocol), the key derivation is deliberately
+slowed by an iterated hash to make such identification
 expensive (though not impossible) at high speeds.
@@
 easily create their own connections and confirm the server is using the
-protocol. Nonetheless, this protocol is still used successfully in deployed censorship
-circumvention systems~\cite{psiphon}. Obfuscated SSH can also be used as a \scheme
+protocol. Nonetheless, this protocol is still used in deployed censorship
+circumvention systems~\cite{psiphon}, though has to deploy proxies at new IP
+addresses when censors inevitably discover and block them.
+Obfuscated SSH can also be used as a \scheme
 application protocol, though we note it provides no active probing or passive
-identifcation resistance.
+identification resistance. However, \scheme OSSH can still make it cheaper to
+rotate to new IP addresses when proxies are found and blocked.
 
@@
 
+\TabApplications
+
 \subsection{Address Selection}
@@
 Because of the large number of IPv6 addresses, even
-relatively small network prefixes have astronomical numbers of addresses: a
+moderately-sized network prefixes have astronomical numbers of addresses: a
 single /32 prefix has $2^{96}$ possible addresses. Therefore, client-chosen

### 2019-05-16 script/parse-td.sh
add latency plot and data

@@ -1,0 +1,13 @@
+#!/bin/bash
+
+#cat data/td.plot | awk '{print $10}' | sort -n | cdf > ./data/td.cdf
+#cat data/dd2.plot | awk '{print $10}' | sort -n | cdf > ./data/dd.cdf
+
+#cat data/td.linear.plot | awk '{print $8}' | sort -n | cdf > ./data/td.cdf
+#cat data/dd.linear.plot | awk '{print $8}' | sort -n | cdf > ./data/dd.cdf
+cat data/td.eric.plot | awk '{print $10}' | sort -n | cdf > ./data/td.cdf
+cat data/dd.eric.plot | awk '{print $10}' | sort -n | cdf > ./data/dd.cdf
+
+gnuplot td-dd.gnuplot
+
+

### 2019-05-16 paper/related.tex
quick citation fix

@@
 
-Bocovich and Goldberg propose an asymmetric gossip scheme~\cite{secureasymmetry} that combines a passive monitor on the forward path from the client to the decoy with an inline blocking element on the return path.
-These elements work in concert to allow schemes such as Telex and Slitheen to work on asymmetric connections.
-This approach, however, still requires inline blocking on one direction, and further complicates deployment by requiring the installation of more components and potentially complex coordination between them.
-MultiFlow~\cite{multiflow} uses refraction networking only as a forward mechanism to communicate a web request to the station, and then uses a bulletin board or email to deliver the response back.
-It does not require inline flow blocking as it does not modify users' traffic at all, but it fundamentally relies on a separate data delivery mechanism, similar to other cloud- or email-based circumvention tools~\cite{SWEET-ToN,CloudTransport}.
+Bocovich and Goldberg propose an asymmetric gossip scheme~\cite{secureasymmetry} 
+that combines a passive monitor on the forward path from the client to the decoy 
+with an inline blocking element on the return path. These elements work in concert 
+to allow schemes such as Telex and Slitheen to work on asymmetric connections. 
+This approach, however, still requires inline blocking on one direction, and 
+further complicates deployment by requiring the installation of more components 
+and potentially complex coordination between them. MultiFlow~\cite{multiflow} 
+uses refraction networking only as a forward mechanism to communicate a web 
+request to the station, and then uses a bulletin board or email to deliver the 
+response back. It does not require inline flow blocking as it does not modify 
+users' traffic at all, but it fundamentally relies on a separate data delivery 
+mechanism, similar to other cloud- or email-based circumvention 
+tools~\cite{SWEET-ToN,CloudTransport}.
 
@@
 
-Houmansadr et al.~\cite{cirripede11} found that placing refraction proxies in a handful of Tier 1 networks would be sufficient for them to be usable by the majority of the Internet population.
-Cesareo et al.~\cite{decoy-placement} developed an algorithm for optimizing the placement of proxies based on AS-level Internet topology data.
-Schuchard et al.~\cite{rad} suggested that a censor may actively change its routes to ensure traffic leaving its country avoids the proxies, but Houmansadr et al.~\cite{true-cost-rad} suggested that real-world constraints on routing make this attack difficult to carry out in practice.
-Nevertheless, Nasr et al.~\cite{game-of-decoys} propose a game-theoretic framework to optimize proxy placement in an adversarial setting, and the design of Waterfall~\cite{waterfall17} is in part motivated by resilience to routing attacks, as it is more difficult for the censor to control the return path from a decoy site, rather than the forward path.
+Houmansadr et al.~\cite{cirripede11} found that placing refraction proxies in a 
+handful of Tier 1 networks would be sufficient for them to be usable by the 
+majority of the Internet population. Cesareo et al.~\cite{decoy-placement} 
+developed an algorithm for optimizing the placement of proxies based on AS-level 
+Internet topology data. Schuchard et al.~\cite{rad12} suggested that a censor may 
+actively change its routes to ensure traffic leaving its country avoids the 
+proxies, but Houmansadr et al.~\cite{true-cost-rad} suggested that real-world 
+constraints on routing make this attack difficult to carry out in practice. 
+Nevertheless, Nasr et al.~\cite{game-of-decoys} propose a game-theoretic 
+framework to optimize proxy placement in an adversarial setting, and the 
+design of Waterfall~\cite{waterfall17} is in part motivated by resilience to 
+routing attacks, as it is more difficult for the censor to control the return 
+path from a decoy site, rather than the forward path.
 
-In practice, deployment of refraction networking has so far been at access, rather than transit ISPs~\cite{frolov2017isp}.
-This may be in part because a transit ISP has a large number of routers and points-of-presence, significantly raising the costs of deployment~\cite{devil-details}.\footnote{We
-note that Gosain et al.~\cite{devil-details} use an estimate of \$885,000/proxy, while Frolov et al.~\cite{frolov2017isp} report line-rate TapDance deployment using commodity hardware that costs only several thousand dollars.} Likewise, we expect \scheme to use address space announced by the ISP, rather than addresses relayed by it, which mitigates routing-based attacks.
-Depending on the size of the ISP, however, a censor may decide to block the entirety of its address space, which would incur smaller collateral damage than blocking all addresses seen by a transit ISP.
+In practice, deployment of refraction networking has so far been at access, 
+rather than transit ISPs~\cite{frolov2017isp}. This may be in part because a 
+transit ISP has a large number of routers and points-of-presence, significantly 
+raising the costs of deployment~\cite{devil-details}.\footnote{We
+note that Gosain et al.~\cite{devil-details} use an estimate of \$885,000/proxy, 
+while Frolov et al.~\cite{frolov2017isp} report line-rate TapDance deployment 
+using commodity hardware that costs only several thousand dollars.} Likewise, 
+we expect \scheme to use address space announced by the ISP, rather than 
+addresses relayed by it, which mitigates routing-based attacks. Depending on 
+the size of the ISP, however, a censor may decide to block the entirety of its 
+address space, which would incur smaller collateral damage than blocking all 
+addresses seen by a transit ISP.
 

### 2019-05-16 paper/figures.tex
add latency figure to paper and explain

@@
     \label{fig:download}
+\end{figure}
+}
+
+\newcommand{\FigLatency}{
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.95\linewidth,clip]{figures/td-dd-latency.pdf}
+    \caption{\textbf{Latency}\,---\, %
+        We compare the CDF of latency for requests between \scheme and TapDance.
+        In each case, we have a long-lived session over which requests are being made
+        using Apache Benchmark (ab). At the median, \scheme has 44~ms (19\%) faster latency than
+        TapDance.
+        In addition, TapDance requests are frequently slowed by its intermittent reconnections
+        to the decoy, as shown in the longer tail of TapDance's latency CDF. \scheme has no such
+        reconnects, and thus has more uniform latency. At the 99th
+        percentile, \scheme is 281~ms (92\%) faster than TapDance.
+    }
+    \label{fig:latency}
 \end{figure}

### 2019-05-16 paper/paper.tex
add latency figure to paper and explain

@@
 
-To evaluate our \scheme implementation, we compare its bandwidth
+\FigUpload
+\FigDownload
+
+To evaluate our \scheme implementation, we compare its bandwidth and latency
 to that of TapDance in a realistic ISP setting. We used a 20~Gbps
@@
 
-We evaluated the performance of a client from a Singapore-based VPS,
+We evaluated the performance of a client from an India-based VPS,
 Figures~\ref{fig:upload} and~\ref{fig:download} show the upload and download as
@@
 
+We also measure the latency of repeated small requests. In both \scheme (using
+the OSSH protocol) and
+TapDance we establish a single session tunnel using our integrated Psiphon
+client, and make 1000 requests through each using Apache Benchmark (ab). We find
+that our India-based VPS throttles TLS but not OSSH, making TapDance twice as slow as
+\scheme. We repeated these tests on a US-based VPS which does not have such
+throttling, and show results in Figure~\ref{fig:latency}. TapDance's frequent
+reconnects adds significant latency to about 10\% of requests. In addition, the
+median latency of \scheme is about 19\% faster, due to the added
+overhead of TLS and the complex path that TapDance data packets take through
+the station compared to \scheme.
+
+\FigLatency
+
 %Compare to TapDance performance:
@@
 being registered or used.
-
-\FigUpload
-\FigDownload
 

### 2019-05-16 paper/figures.tex
minor edits

@@
         We deployed our \scheme implementation in a realistic ISP testbed on a
-        (full duplex) tap of a 10~Gbps router. As shown in a typical week, traffic
+        tap of a 20~Gbps router. As shown in a typical week, traffic
         ranges from 2-17~Gbps.
@@
     \caption{\textbf{Station Architecture}\,---\,%
-        We used PF\_RING to receive packets from a 10~Gbps packet tap, which we load balance
+        We used PF\_RING to receive packets from a 20~Gbps packet tap, which we load balance
         across 4~CPU cores. The detector process identifies and processes registrations, and forwards
@@
         determines if the client is legitimate (using a seed shared during registration) and forwards
-        their traffic to a proxy. Otherwise, the application responds as if it were the mask site.}
+        their traffic to a proxy. Otherwise, the application responds as an innocuous host, such as by
+        forwarding pakcets to a mask site.}
     \label{fig:implementation}

### 2019-05-16 paper/paper.tex
minor edits

@@
 (ISPs) outside censoring countries~\cite{refraction-site}.
-Clients access circumvention service by connecting to a ``decoy site''---any uncensored website for which the connection travels over a participating ISP\@.
+Clients access circumvention services by connecting to a ``decoy site''---any uncensored website for which the connection travels over a participating ISP\@.
 Upon recognizing a steganographic signal from the client, the ISP modifies the connection response to return censored content requested by the user.
@@
 cat-and-mouse game.
-%TODO: don't need to hedge on IPv4 anymore..?
+%TODO: don't need to hedge on IPv4 anymore..? couldcut
 \scheme supports both IPv4 and IPv6,
@@
 \scheme has reduced complexity and substantially improved performance
-(Section~\ref{sec:evaluation}).  In addition, \scheme provides significantly
+(Section~\ref{sec:evaluation}): on average, \scheme has 20\% lower latency,
+14\% faster download bandwidth, and over 1400 times faster upload bandwidth.
+In addition, \scheme provides significantly
 more flexibility than existing Refraction protocols, allowing maintainers to
@@
 make \scheme a strong choice for future Refraction Networking deployments.
+
+%download: dd - td: 5947790000 - 5219112999 = 14% faster down
+% upload:  5088330000/3500000.0 = 1453x upload
+% latency: td avg 297ms, dd avg 237ms = 20% lower latency
 
@@
 choice also allows the censor to register suspected phantom hosts and block them if
-they pick up.
+they can be used as proxies.
 By using a hash of a seed, the censor would have to pre-image the hash to
@@
 Figures~\ref{fig:upload} and~\ref{fig:download} show the upload and download as
-measured by iperf for TapDance, our \scheme implementation, and a direct
-connection to our iperf server in the ISP's network.
+measured by iperf for TapDance, our \scheme implementation (using the mask site application),
+and a direct connection to our iperf server in the ISP's network.
 
@@
 a new TLS connection for every 32~KBytes of data it sends, limiting its average
-upload bandwidth to less than 1~Mbps due to the high overhead. In contrast,
+upload bandwidth to around 0.1~Mbps due to the high overhead. In contrast,
 our \scheme implementation is
 able to maintain the same connection during large uploads, and achieves
-performance inline with the direct connection.
+performance inline with the direct connection, over 1400 times faster.
 
@@
 implementation is able to maintain a single connection and provide the maximum
-download rate without interruption.
+download rate without interruption, 14\% faster than TapDance.
 

### 2019-05-16 paper/related.tex
minor edits

@@
 connect to pools of addresses that are volunteered to run Tor bridge nodes.
-Unlike \scheme, DEFIANCE requires network admins that own the IP blocks to
-participate and operate proxies on their addresses, allowing censors to block
-the IP ranges involved once discovered. In contrast, \scheme can be
-deployed at transit ISPs, and censors face a large risk of collateral
-over-blocking if they block the network blocks used.
+DEFIANCE also requires volunteer web servers to run specialized servers to
+distribute information. Unlike \scheme, DEFIANCE was not designed to run at an
+ISP, and invovles many moving parts that present single points of failure if
+blocked by a censor. In contrast, \scheme has a relatively simple yet flexible
+design, allowing it to easily respond to censors.
 Another similar approach was

### 2019-05-16 paper/figures.tex
Format

@@
     \includegraphics[width=\linewidth,clip]{figures/conjure-overview.png}
-    \caption{\textbf{\scheme Operations}\,---\,%
+    \caption{\textbf{\scheme Operations}\,---\,\rm%
         Clients first register by sending a secret seed in a steganographic tag past the station in a
@@
     \includegraphics[width=\linewidth,clip]{figures/high-level.png}
-    \caption{\textbf{\scheme Overview}---%
+    \caption{\textbf{\scheme Overview}\,---\,\rm%
       An ISP deploys a \scheme station, which sees a passive tap of passing traffic.
@@
     \includegraphics[width=0.95\linewidth,clip]{figures/bandwidth-up.pdf}
-    \caption{\textbf{Upload Performance}\,---\, %
+    \caption{\textbf{Upload Performance}\,---\,\rm%
         We used iperf to measure the upload bandwidth for a direct connection, TapDance, and \scheme.
@@
     \includegraphics[width=0.95\linewidth,clip]{figures/bandwidth-down.pdf}
-    \caption{\textbf{Download Performance}\,---\, %
+    \caption{\textbf{Download Performance}\,---\,\rm%
         Using iperf, we compare the download performance of a direct connection, TapDance, and \scheme.
@@
     \includegraphics[width=0.95\linewidth,clip]{figures/td-dd-latency.pdf}
-    \caption{\textbf{Latency}\,---\, %
+    \caption{\textbf{Latency}\,---\,\rm%
         We compare the CDF of latency for requests between \scheme and TapDance.
@@
     \includegraphics[width=0.75\linewidth,clip]{figures/decoy-tap-bandwidth.png}
-    \caption{\textbf{Tap Bandwidth}\,---\, %
+    \caption{\textbf{Tap Bandwidth}\,---\,\rm%
         We deployed our \scheme implementation in a realistic ISP testbed on a
@@
     \includegraphics[width=\linewidth,clip]{figures/entropy-ip-16hr.png}
-    \caption{\textbf{IPv6 Entropy}---%,
+    \caption{\textbf{IPv6 Entropy}\,---\,\rm%
         Censors may be able to distinguish random-looking phantom host IPv6 addresses
@@
     \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
-    \caption{\textbf{IPv6 bits set}---%
+    \caption{\textbf{IPv6 bits set}\,---\,\rm%
         We measure the number of bits set to 1 in IPv6 addresses in our ISP's /32
@@
     \end{tabular}
-    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,
+    \medskip
+    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,\rm%
         ``No inline blocking'' corresponds to schemes that can operate as a passive tap on the side
@@
     \end{tabular}
-    \caption{\textbf{\scheme Applications}\,---\,
+    \medskip
+    \caption{\textbf{\scheme Applications}\,---\,\rm%
     ``Active probe resistant`` protocols are designed to look innocuous even if scanned by a censor.
@@
     \includegraphics[width=0.7\linewidth,clip]{figures/implementation.png}
-    \caption{\textbf{Station Architecture}\,---\,%
+    \caption{\textbf{Station Architecture}\,---\,\rm%
         We used PF\_RING to receive packets from a 20~Gbps packet tap, which we load balance
@@
 
-    \caption{\textbf{First generation systems} for Refraction Networking, such as Telex and Cirripede, operated as inline network elements, with the ability to observe traffic and block specific flows.
+    \caption{\textbf{First generation systems}\rm for Refraction Networking, such as Telex and Cirripede, operated as inline network elements, with the ability to observe traffic and block specific flows.
 ISPs worried that if the inline element failed, it could bring down the network.\looseness=-1}
@@
 
-    \caption{\textbf{TapDance} is a second-generation Refraction Network scheme that operates without flow blocking, needing only to passively observe traffic and inject packets.
+    \caption{\textbf{TapDance}\rm is a second-generation Refraction Network scheme that operates without flow blocking, needing only to passively observe traffic and inject packets.
 TapDance has recently been deployed at a mid-size ISP, but the techniques used to silence the decoy site and participate in the client--decoy TCP connection mid-stream add significant complexity, performance bottlenecks, and detection risk.}
@@
 
-    \caption{\textbf{\scheme}, our third-generation Refraction Networking design, overcomes these limitations.
+    \caption{\textbf{\scheme}\rm, our third-generation Refraction Networking design, overcomes these limitations.
 It uses two sessions.

### 2019-05-16 paper/paper.tex
Format

@@
 %% complete the rights form.
-\setcopyright{acmcopyright}
-\copyrightyear{2019}
+%% \setcopyright{acmcopyright}
+%% \copyrightyear{2019}
+%% \acmYear{2019}
+%% \acmDOI{10.1145/1122445.1122456}
+
+%% %% These commands are for a PROCEEDINGS abstract or paper.
+%% \acmConference[CCS '19]{CCS '19: ACM Conference on Computer and Communications
+%% Security}{November 11--15, 2019}{London, UK}
+%% \acmBooktitle{CCS '19: ACM Symposium on Computer and Communications Security,
+%%   November 11--15, 2019, London, UK}
+%% \acmPrice{0.00}
+%% \acmISBN{978-1-4503-9999-9/18/06}
+
+\fancyhf{} % Remove fancy page headers                                                                
+\fancyhead[C]{Anonymous submission \#610 to ACM CCS 2019}
+\fancyfoot[C]{\thepage}
+
+\setcopyright{none} % No copyright notice required for submissions                                     
+\acmConference[Anonymous Submission to ACM CCS 2019]{ACM Conference on Computer and Communications Security}{Due 15 May 2019}{London, TBD}
 \acmYear{2019}
-\acmDOI{10.1145/1122445.1122456}
-
-%% These commands are for a PROCEEDINGS abstract or paper.
-\acmConference[CCS '19]{CCS '19: ACM Conference on Computer and Communications
-Security}{November 11--15, 2019}{London, UK}
-\acmBooktitle{CCS '19: ACM Symposium on Computer and Communications Security,
-  November 11--15, 2019, London, UK}
-\acmPrice{0.00}
-\acmISBN{978-1-4503-9999-9/18/06}
+
+\settopmatter{printacmref=false, printccs=true, printfolios=true}
 
@@
 %\usepackage{parskip}
-\usepackage{mathptmx}\renewcommand{\ttdefault}{cmtt}
+%\usepackage{mathptmx}\renewcommand{\ttdefault}{cmtt}
 \usepackage{amsmath}
@@
 \SetExtraKerning{encoding=*,font=*}{\textemdash={120,120}} % Add space around emdashes
-\usepackage[font=small]{caption}
+%\usepackage[font=small]{caption}
 \microtypecontext{spacing=nonfrench}
-\usepackage{subcaption}
+%\usepackage{subcaption}
 \usepackage{paralist}
@@
 %  Conjuring Proxies from Unused Address Space}
-\title{\Large \bf Conjure: Summoning Proxies from Unused Address Space}
+\title{Conjure: Summoning Proxies from Unused Address Space}
 

### 2019-08-29 paper/paper.tex
Format
pass on discussion for ccs resubmission

@@
-\documentclass[sigconf]{acmart}
+\documentclass[sigconf,anonymous]{acmart}
 %\usepackage{usenix2019_v3}
@@
 \SetExtraKerning{encoding=*,font=*}{\textemdash={120,120}} % Add space around emdashes
-%\usepackage[font=small]{caption}
+\usepackage[font=small]{caption}
 \microtypecontext{spacing=nonfrench}
@@
 packet filters, as there are no identifying headers or fields
-to search for. Instead, Obfuscated SSH clients first send a 16-byte seed, which
-is then used to derive a symmetric key that encrypts the rest of the
-communication. While this can passively detected by censors (who can also
-derive the key and de-obfuscate the protocol), the key derivation is deliberately
-slowed by an iterated hash to make such identification
-expensive (though not impossible) at high speeds.
-
-Obfuscated SSH also does not protect against active probing, as the censor can
-easily create their own connections and confirm the server is using the
-protocol. Nonetheless, this protocol is still used in deployed censorship
-circumvention systems~\cite{psiphon}, though has to deploy proxies at new IP
-addresses when censors inevitably discover and block them.
-Obfuscated SSH can also be used as a \scheme
-application protocol, though we note it provides no active probing or passive
-identification resistance. However, \scheme OSSH can still make it cheaper to
-rotate to new IP addresses when proxies are found and blocked.
+to search for. Instead, Obfuscated SSH clients first send a 16-byte random seed, which
+is used to derive a symmetric key that encrypts the rest of the
+communication. Early versions of OSSH were passively detectable by censors, who
+can observe the random seed and derive the key, allowing them to de-obfuscate the protocol.
+These versions also did
+not protect against active probing attacks, as a censor can easily create their
+own connections to confirm if a server supports the protocol.
+
+More recent versions of OSSH, such as those used by Psiphon~\cite{psiphon}, mix a secret
+value into the key derivation, thwarting the naive passive detection/decryption
+attack. The secret is distributed out-of-band along with the proxy's address,
+and is unknown to a passive or active-probing censor. If a client connects and cannot
+demonstrate knowledge of
+the secret, the OSSH server does not respond, making it more difficult for
+censors to discover OSSH servers via active probing attacks.
+
+%While this can passively detected by censors (who can also
+%derive the key and de-obfuscate the protocol), the key derivation is deliberately
+%slowed by an iterated hash to make such identification
+%expensive (though not impossible) at high speeds.
+%
+%
+%% This is wrong...it actually does protect against active probing
+%Obfuscated SSH also does not protect against active probing, as the censor can
+%easily create their own connections and confirm the server is using the
+%protocol. Nonetheless, this protocol is still used in deployed censorship
+%circumvention systems~\cite{psiphon}, though has to deploy proxies at new IP
+%addresses when censors inevitably discover and block them.
+%Obfuscated SSH can also be used as a \scheme
+%application protocol, though we note it provides no active probing or passive
+%identification resistance. However, \scheme OSSH can still make it cheaper to
+%rotate to new IP addresses when proxies are found and blocked.
 
@@
 traffic between the client and a selected mask website. To a censor, this site
-will be indistinguishable from the legitimate mask site, making it difficult for
-them to block without potentially blocking the actual site. TLS connections to the
+will be indistinguishable from the actual site, making it difficult for
+them to block without potentially blocking the real site. TLS connections to the
 application will terminate exactly as connections to the mask site would, with the
-application acting as a transparent proxy between the client and mask site.
+application acting as a transparent TCP-layer proxy between the client and mask site.
 However, this leaves the application unable to introspect on the contents of the
@@
 sent during registration to derive the pre-master secret for the connection.
-This is hashed along with the client and server randoms of the current (mask
-site) TLS connection to obtain the master secret that determines
+The new pre-master secret is hashed along with the client and server randoms of the current
+(mask site) TLS connection to obtain the master secret that determines
 encryption/decryption/authentication keys.
@@
 (Section~\ref{sec:mask-sites}). Our client signals which application it will use
-in the registration tag. After registration, the client connects to the derived
+in the registration tag. The client also sends a flag that indicates if the
+client supports IPv6, to allow IPv4-only clients to only derive IPv4 phantom
+hosts.
+After registration, the client connects to the derived
 phantom host address, and speaks the specified application protocol, which
@@
 
-\section{Discussion}
-
-\subsection{Attacks and Defenses}
+%\section{Discussion}
+
+\section{Attacks and Defenses}
 % 1 page
@@
 
-There are many attacks a censor might attempt to either prevent phantom hosts from
-being registered or used.
-
-\paragraph{Blocking registration}
+In this section, we discuss several attacks a censor might attempt to either
+block phantom hosts from being registered or used.
+
+\subsection{Probing phantom hosts}
+% censors could actively scan phantom hosts...we review how this works for obfs4, OSSH, masked sites individually
+Censors may attempt to actively probe suspected phantom hosts to determine if
+they are proxies or real hosts. China has been observed using exactly this technique to
+discover existing proxies and Tor bridge
+nodes~\cite{tor-bridge-blocking-blog,active-probe,ensafi-tor,china-blocking-tor}.
+In response to China's active probing, Tor and other circumvention tool developers have developed
+\emph{probe-resistant} protocols, such as \texttt{obfs4}~\cite{obfs4}, Obfuscated SSH
+(OSSH)~\cite{ossh}, and Shadowsocks~\cite{shadowsocks}. Each of these protocols
+require the client to know a special secret distributed alongside the original
+proxy address. Without knowledge of this secret, active-probing censors will not
+receive any response from these hosts, making it difficult for censors to tell if
+a server is a proxy or a non-responsive legitimate host.
+
+\paragraph{Obfuscated SSH} Modern OSSH protocols are intended to be
+probe-resistant. Censors that attempt to probe suspected OSSH servers without
+knowledge of the secret receive no data response, making it difficult to
+distinguish them from other non-responsive hosts. To confirm this, we use
+ZMap~\cite{zmap} to scan over 1 billion random IP/port combinations, and sent 25
+random bytes (corresponding to the OSSH handshake) to the approximately 800,000
+servers that responded. We expect very few of these to actually be OSSH
+servers as they are simply random servers on random TCP ports.
+However, over 99.4\% of them did not respond with any data, behavior mirrored by
+OSSH servers.
+Furthermore, 7.42\% of servers closed the connection with a TCP RST
+after we send our random data, a response we also see with OSSH. While there may
+be other ways to differentiate OSSH servers from others online, our tests
+suggest censors could face steep false-positive rates in identifying OSSH
+servers with active probing.
+
+%TODO: how many servers in zmap look like OSSH? e.g. we send them 23 random
+%bytes and then they don't respond with data. 99.46% (793789 out of 798032)
+% If we send 25 bytes (~OSSH handshake size...), OSSH server responds with RST.
+% zmap: 28.42% respond with RST within 4 secs. Only 7.49% within
+
+\paragraph{\texttt{obfs4}}
+Unlike previous versions of obfsproxy, the \texttt{obfs4} protocol is designed to
+be resistant to active probing
+attacks, requiring the client prove knowledge of a secret before the server will
+respond. We verified that naive active probing attacks (where we attempt to
+connect to an \texttt{obfs4} server without knowledge of the secret and see if
+it provides proxy access) do not work
+against \texttt{obfs4}. In addition, although China is effective at blocking
+\texttt{obfs3}, the more recent probe-resistant \texttt{obfs4} remains a viable
+proxy in the country
+
+\paragraph{Mask sites}
+The censor could also attempt to fingerprint a masked site and compare it to a
+suspected \scheme application. For instance, if a phantom host IP responds to a
+censors' probes
+pretending to be \texttt{example.com}, the censor could probe real instances
+of \texttt{example.com} on different ports and see how it responds. Then, the
+censor can probe the phantom host IP, and see if it responds similarly (e.g. with
+the same set of open ports and payloads for certain kinds of probes). To defend
+against this, we forward \emph{all} traffic destined to the phantom host to the
+masked site, including ports that are not relevant to the proxy application
+(e.g. non 443). This ensures that above the TCP layer, we appear to be the mask
+site. However, there may be differences in TCP/IP implementations, for instance,
+how IP IDs are incremented, or how TCP timestamps are incremented (or supported
+at all) that may be different from the mask site. To combat this, we can filter
+mask sites by those that have identical TCP/IP stacks to ours, as we use a
+common Linux implementation. We also note that this attack only applies when we
+use the mask site as an application, and that \scheme can support other
+applications (e.g. obfsproxy, WebRTC, etc) that do not have this issue.
+
+We acknowledge that perfect mimicry of the real site is likely infeasible:
+Houmansadr et al.~\cite{houmansadr-parrot} demonstrated the difficulty in fully
+mimicking known applications, showing that staying fully-feature compatible is
+an expensive and potentially intractable problem for circumvention systems.
+However, their study focuses on \emph{application-specific} mimicry, used by
+circumvention tools like CensorSpoofer, StegoTorus, and Skypemorph. These tools
+generally attempt to mimic a specific protocol used by a complex application
+such as Skype,
+where only one or a handful of official popular clients are used. Houmansadr et
+al.~\cite{houmansadr-parrot} show that such mimicry is difficult in practice due
+to the complexity and opaqueness of specifications, side protocols that
+applications may use, and intra- and inter-dependence on connections and other
+protocols.
+
+In contrast, mask sites have
+the advantage that we can mimic any sites from a large set of heterogeneous real
+websites, making it harder for a censor to fully fingerprint and characterize
+\emph{all} potential mask sites. As websites may themselves use distributed
+or heterogeneous server implementations, it could be more difficult for a
+censor to block all mask site application use.
+Nonetheless, it is still possible for censors to
+use active probing attacks to detect either protocol feature, payload size, or
+timing differences between mask sites and the real sites they attempt to mimic.
+
+%This general issue remains an open problem in censorship circumvention; however,
+%if solved, \scheme can use it to thwart active probing attacks in a useable
+% and flexible system.
+
+\subsection{Passive identification}
+Censors might also attempt to use passive methods to distinguish and block communication
+with registration decoys or phantom hosts. For example, 
+Website Fingerprinting~\cite{wang2014effective,hayes2016k,sirinam2018deep} (WF)
+uses the patterns of encrypted traffic to identify which website a client is
+connected to. WF uses a classifier to label the traffic as belonging to one of
+several known websites, or (in some variants), an unknown or background class.
+Though WF is commonly studied in the context of anonymous web browsing, a censor
+could also use WF to detect \scheme applications by distinguishing known traffic
+patterns of legitimate website use from traffic generated by \scheme (unknown
+class). Alternatively, the censor could monitor traffic for patterns consistent
+with tunneled access to a set of blocked websites.
+
+Wang et al.~\cite{wang2015seeing} demonstrated several effective classifiers
+that can passively distinguish normal traffic from obfuscated circumvention
+protocols including \texttt{obfs3}, \texttt{obfs4}, Format-transforming
+encryption~\cite{fte}, and meek~\cite{meek}. However, despite the low false
+positive rate of these classifiers, Wang et~al.~\cite{wang2015seeing} caution
+that the base rate of normal traffic compared to obfuscated traffic would force
+censors that employ such attacks to suffer significant collateral damage in
+degrading performance and reliability of legitimate traffic.
+Indeed, to date, censors have not been observed using WF or other
+passive techniques, possibly due to the inaccuracy of these identification
+techniques in practice. Even small false positive rates means blocking mostly legitimate
+connections, and false negatives could allow clients to retry until they gain
+access.
+
+More importantly, \scheme applications offer great flexibility in deploying
+traffic analysis defenses; for example, traffic shaping strategies such as
+implemented in Slitheen~\cite{slitheen16} could be easily employed in \scheme.
+\scheme clients could also choose from a large set of potential applications,
+forcing censors to have to block access to all of them to block use.
+%Furthermore, \scheme applications are not limited to mimicking websites, and can
+%support any (or even a combination of) protocols. Finally, if encrypted SNI can
+%be used (\cref{esni}), the censor would not be able to build up a traffic
+%profile of a legitimate site since its identity would be encrypted.
+
+\subsection{Blocking registration}
 To make registration more difficult, censors could block TLS connections to all of the
@@
 
-\paragraph{Scanning masked sites}
-The censor could also attempt to fingerprint the masked site and compare it to a
-suspected \scheme application. For instance, if a phantom host IP responds as
-pretending to be \texttt{example.com}, the censor could scan or probe real instances
-of \texttt{example.com} on different ports and see how it responds. Then, the
-censor can probe the phantom host IP, and see if it responds similarly (e.g. with
-the same set of open ports and payloads for certain kinds of probes). To defend
-against this, we forward \emph{all} traffic destined to the phantom host to the
-masked site, including ports that are not relevant to the proxy application
-(e.g. non 443). This ensures that above the TCP layer, we appear to be the mask
-site. However, there may be differences in TCP/IP implementations, for instance,
-how IP IDs are incremented, or how TCP timestamps are incremented (or supported
-at all) that may be different from the mask site. To combat this, we can filter
-mask sites by those that have identical TCP/IP stacks to ours, as we use a
-common Linux implementation. We also note that this attack only applies when we
-use the mask site as an application, and that \scheme can support other
-applications (e.g. obfsproxy, WebRTC, etc) that do not have this issue.
-
-\paragraph{Website fingerprinting}
-Website Fingerprinting~\cite{wang2014effective,hayes2016k,sirinam2018deep} (WF) uses the patterns of encrypted traffic to identify which website a client is connected to.
-WF uses a classifier to label the traffic as belonging to one of several known websites, or (in some variants), an unknown or background class.
-Though WF is commonly studied in the context of anonymous web browsing, a censor could also use WF to detect refraction networking by distinguishing known traffic patterns of legitimate uses of a decoy site from the traffic generated by refraction networking (unknown class).
-Alternatively, the censor could monitor all traffic for patterns consistent with a set of blocked websites.
-
-\scheme applications that mimic specific websites (e.g., mask sites) are likewise susceptible to WF.
-To date, however, censors have not been observed using WF and similar techniques, possibly due to the significant uncertainty resulting from even the best algorithms: even a small false
-positive rate means blocking mostly legitimate connections (due to the base rate
-of normal traffic), and false negatives could allow clients to retry until they
-gain access.
-
-More importantly, \scheme applications offer great flexibility in deploying traffic analysis defenses; for example, traffic shaping strategies such as implemented in Slitheen~\cite{slitheen16} could be easily employed in \scheme.
-Furthermore,
-\scheme applications are not limited to mimicking websites, and can support
-any (or even a combination of) protocols.
-Finally, if encrypted SNI can be used (\cref{esni}), the censor would not be able to build up a traffic profile of a legitimate site since its identity would be encrypted.
-
-\paragraph{ICMP}
+\subsection{ICMP}
 Censors can use ping or traceroute utilities (via ICMP) to probe potential phantom

### 2019-08-30 paper/figures.tex
quick fix and figure 6 arch redone.

@@
             \hline
-            Active probe resistant  & \no  & \yes & \yes & \yes & \yes \\
+            Active probe resistant  & \yes  & \yes & \yes & \yes & \yes \\
             Randomized or Tunneling & R    & R    & T    &  T   & T \\
@@
     \centering
-    \includegraphics[width=0.7\linewidth,clip]{figures/implementation.png}
+    \includegraphics[width=0.7\linewidth,clip]{figures/dark-decoy-flow1.png}
     \caption{\textbf{Station Architecture}\,---\,\rm%
         We used PF\_RING to receive packets from a 20~Gbps packet tap, which we load balance
-        across 4~CPU cores. The detector process identifies and processes registrations, and forwards
-        packets destined to registered phantom host addresses to a local application. The application
-        determines if the client is legitimate (using a seed shared during registration) and forwards
-        their traffic to a proxy. Otherwise, the application responds as an innocuous host, such as by
-        forwarding pakcets to a mask site.}
+        across 4~CPU cores. The detector process identifies registrations, notifying all
+        cores when a new registration is received (green dashed registration flow). The detector also
+        identifies packets associated with registered flows (by connection 4-tuple) and diverts them
+        to a local application which handles proxying connections(purple dotted flow). The local 
+        application determines which proxy the flow should use based on a parameter specified by 
+        the client in the registration and initializes a goroutine to handle forwarding. 
+        \\\hspace{\textwidth}
+        A censor trying to interfere in this
+        connection would need to co-opt the clients IP address in a precise window (after the 
+        registration but before the client connects to the phantom) and correctly guess the phantom hosts 
+        IP address (or connect to all possible phantom IPs) before the active probe traffic gets to the local application. 
+        At this point their connection will fail in a manor specific to the proxy that the client specified
+        in the registration (e.g. connecting to OSSH without knowledge of the preshared secret).}
     \label{fig:implementation}

### 2019-08-30 paper/related.tex
quick fix and figure 6 arch redone.

@@
 distribute information. Unlike \scheme, DEFIANCE was not designed to run at an
-ISP, and invovles many moving parts that present single points of failure if
+ISP, and involves many moving parts that present single points of failure if
 blocked by a censor. In contrast, \scheme has a relatively simple yet flexible

### 2019-08-31 paper/rebuttal.tex
Added Letter to reviewers / rebuttal appendix

\section{Letter To Reviewers}

We thank the reviewers for their detailed comments and insights. In this resubmission we have modified 
multiple items to address concerns and clarify various ambiguities raised by the previous submission. 
First we have modified sections \ref{sec:architecture} 
and \ref{sec:implementation} to better communicate the construction of the Conjure system, 
the modularity that it affords, and the benefits that we derive from it's properties. We 
have also added section \ref{sec:attacks} to discuss the security benefits and shortcomings 
of Conjure directly.

Reviewers A, C, and D reference the difficulty of correctly mimicking realistic services with
reference to the mask site proxy option. We have added acknowledgement of the inherent difficulty of mimicking 
services in section \ref{sec:attacks} but note that we have multiple strong factors in our
favor. First we do not choose a single service to mimic as other works in the past have 
\cite{stegotorus, skypemorph, censorspoofer} making a fingerprinting attack more difficult to employ by effectively raising the noise
(false positive / false negative) rates on any classifiers. Second, there has been no indication 
of website fingerprinting being employed by censors to detect proxies in nation-state censorship 
efforts due to the cost of overblocking at scale.

We would like to underscore that mimicry is only a feature of a Conjure session when the client 
elects to use the mask site proxy option. A Conjure session that uses OSSH, Obfs4, etc. will 
not employ any mimicking. This heterogeneity is a strength as it allows Conjure to continue
providing secure proxy access to clients even when new active probing attacks are discovered for 
individual transports.

Reviewer D raises a concern about identifying phantom hosts by attempting to connect and
classifying based on the non-response of a host seen previously responding to a possible Conjure client. 
This would not be an effective attack on Conjure for multiple reasons. First, the internet is volatile,
and services come up, go down, or transition addresses regularly. Second, many networks are fire-walled
and require specific authentication and/or source address to access. Finally protocols on the internet
are diverse and may not reply when improperly probed. Simply checking whether a connection can be opened 
from a third party client will not indicate to a censor with reliable confidence that a client is 
contacting a phantom host.

All reviewers voice similar concerns about the incentives present for ISPs to deploy a system like
Conjure, and the burden that this may impose upon them. Conjure already has the cooperation of a 
major state level ISP, and our test bench has demonstrated that this places
no undue burden upon them. Our system does not require any inline blocking or packet modification 
as we operate on packets mirrored to a machine that we host within the ISP's network. 
To clarify, the ISP is not responsible for finding unused addresses, discovering viable mask sites, 
or managing proxied connections -- we perform those operations on our station deployed
at an ISP. They are also not responsible for hosting sites (or managing certificates) at any of the 
phantom hosts, as Conjure does not host any fake services, connections to phantom hosts are 
redirected to the covert destination out of line. The only overhead 
for the ISP is providing our station (hosted locally in their network) with a TAP on the packets that 
pass by, ensuring that we do not create any bottleneck in the service that they provide to their customers.

As for the risk of refraction networking making the ISP a target for malicious activity, they likely already
are a target based on the information and access that they have and they work to make their networks 
secure against those attacks. The motivation of making the internet a more free and open environment,
low overhead of deployment, and the effective demonstration of Conjure in a production environment 
form a strong incentive.

We believe that Conjure represents a significant step forward in the arms race of proxy
discovery and censorship circumvention because we leverage the the unused addresses of the internet
to connect clients to secure, active probe resistant proxies without giving censors a singular 
specific IP address that can be blocked to inexpensively deny proxy access.

### 2019-08-31 paper/paper.tex
Added Letter to reviewers / rebuttal appendix

@@
 
-We assume the censor can use the client to register and access its own phantom
-hosts, but that these will not reveal the phantom hosts of other users. The
+We allow the censor access to the client to register and use its own phantom hosts, 
+so the system should ensure that these will not reveal the phantom hosts of other users. The
 censor can also actively probe addresses that it sees users accessing, and can
@@
 distinguish them from other non-responsive hosts. To confirm this, we use
-ZMap~\cite{zmap} to scan over 1 billion random IP/port combinations, and sent 25
+ZMap~\cite{zmap13} to scan over 1 billion random IP/port combinations, and sent 25
 random bytes (corresponding to the OSSH handshake) to the approximately 800,000
@@
 
+\appendix
+
+\input{rebuttal}
+
 \end{document}

### 2019-09-01 paper/rebuttal.tex
Architecture updates for paper.

@@
 First we have modified sections \ref{sec:architecture} 
-and \ref{sec:implementation} to better communicate the construction of the Conjure system, 
+and \ref{sec:implementation} to better communicate the construction of the \scheme system, 
 the modularity that it affords, and the benefits that we derive from it's properties. We 
 have also added section \ref{sec:attacks} to discuss the security benefits and shortcomings 
-of Conjure directly.
+of \scheme directly.
 
@@
 
-We would like to underscore that mimicry is only a feature of a Conjure session when the client 
-elects to use the mask site proxy option. A Conjure session that uses OSSH, Obfs4, etc. will 
-not employ any mimicking. This heterogeneity is a strength as it allows Conjure to continue
+We would like to underscore that mimicry is only a feature of a \scheme session when the client 
+elects to use the mask site proxy option. A \scheme session that uses OSSH, Obfs4, etc. will 
+not employ any mimicking. This heterogeneity is a strength as it allows \scheme to continue
 providing secure proxy access to clients even when new active probing attacks are discovered for 
@@
 Reviewer D raises a concern about identifying phantom hosts by attempting to connect and
-classifying based on the non-response of a host seen previously responding to a possible Conjure client. 
-This would not be an effective attack on Conjure for multiple reasons. First, the internet is volatile,
+classifying based on the non-response of a host seen previously responding to a possible \scheme client. 
+This would not be an effective attack on \scheme for multiple reasons. First, the internet is volatile,
 and services come up, go down, or transition addresses regularly. Second, many networks are fire-walled
@@
 All reviewers voice similar concerns about the incentives present for ISPs to deploy a system like
-Conjure, and the burden that this may impose upon them. Conjure already has the cooperation of a 
-major state level ISP, and our test bench has demonstrated that this places
+\scheme, and the burden that this may impose upon them. \scheme already has the cooperation of a 
+a mid-sized transit ISP, and our test bench has demonstrated that this places
 no undue burden upon them. Our system does not require any inline blocking or packet modification 
@@
 at an ISP. They are also not responsible for hosting sites (or managing certificates) at any of the 
-phantom hosts, as Conjure does not host any fake services, connections to phantom hosts are 
+phantom hosts, as \scheme does not host any fake services, connections to phantom hosts are 
 redirected to the covert destination out of line. The only overhead 
@@
 secure against those attacks. The motivation of making the internet a more free and open environment,
-low overhead of deployment, and the effective demonstration of Conjure in a production environment 
+low overhead of deployment, and the effective demonstration of \scheme in a production environment 
 form a strong incentive.
 
-We believe that Conjure represents a significant step forward in the arms race of proxy
+We believe that \scheme represents a significant step forward in the arms race of proxy
 discovery and censorship circumvention because we leverage the the unused addresses of the internet

### 2019-09-01 paper/figures.tex
Architecture updates for paper.

@@
     \centering
-    \includegraphics[width=\linewidth,clip]{figures/conjure-overview.png}
+    \includegraphics[width=\linewidth,clip]{figures/dark-decoy-flow2.png}
     \caption{\textbf{\scheme Operations}\,---\,\rm%
-        Clients first register by sending a secret seed in a steganographic tag past the station in a
-        normal TLS connection to a Decoy site. Clients then connect to an address derived from the seed,
-        which the station responds as a phantom host application. If the client can prove knowledge of the
-        seed used during registration, they are allowed access to the proxy. Otherwise,
-        the phantom host application pretends to be a benign host by staying silent or forwarding traffic
-        to a mask site to make it difficult for censors to distinguish phantom hosts from legitimate ones.
+        A \scheme session is constructed in two pieces. First a client registers by sending a tls connection
+        to the Decoy host (see Figure 2c) with a steganographically tagged payload.
+        This registration contains the true address that the client would like to connect to and a seed 
+        which the \scheme station uses to derive the Phantom IP address for the session(green dashed flow). 
+        Second The client derives the same 
+        Phantom IP address and connects directly to it using the proxy protocol (e.g. OSSH) that they specified in
+        their registration (purple dotted flow). The station identifies registered packets by source IP, destination IP,
+        and destination port (client IP, phantom IP, and phantom port respectively). The traffic is passed 
+        to a proxy server handling the specific proxy specified by the client then redirected to the 
+        covert address that the client indicated in their registration. 
+        \\\hspace{\textwidth}
+        Secrets for the individual proxy services are shared out of band or derived from the shared secret 
+        between the client and the station such that an adversary attempting to probe a connection will be
+        unable to connect to the proxy service. 
     }
@@
   \begin{subfigure}{\columnwidth}
+    \label{fig:evolutionconjure}
     \includegraphics[width=\columnwidth]{figures/dark-decoys}

### 2019-09-01 paper/paper.tex
Architecture updates for paper.

@@
 In our scheme (Figure~\ref{fig:highlevel}), clients
-request the creation of phantom hosts in the ``dark''
+register their intentions to connect to phantom hosts in the ``dark''
 or unused address space of the deploying ISP. Once registered, clients
 can connect to these phantom hosts IP addresses as if they were real
-proxy servers. The ISP station acts as the other end of these connections, and
+proxy servers. The \scheme station (deployed at an ISP) acts as the other end of these connections, and
 responds as if it were a legitimate site or service. To the censor,
@@
 %% by embedding a steganographic registration message in a TLS handshake
-%% with a decoy site. This message, which the ISP station can passively
+%% with a decoy site. This message, which the \scheme station can passively
 %% observe using a private key, uniquely determines an IP address within
@@
 
-Phantom hosts are cheap to create, allowing for discardable or even one-time-use
-proxy servers. This greatly increases the cost for censors to
+\TODO{Phantom hosts are cheap to create, allowing for discardable or even one-time-use
+proxy servers}. This greatly increases the cost for censors to
 block, as they must detect and block in real time. Meanwhile, even a censor that
@@
 cat-and-mouse game.
-%TODO: don't need to hedge on IPv4 anymore..? couldcut
+%TODO: don't need to hedge on IPv4 anymore..? could cut
 \scheme supports both IPv4 and IPv6,
@@
 range of detection attacks than TapDance.
-We have implemented Conjure (Section~\ref{sec:implementation})
+We have implemented \scheme (Section~\ref{sec:implementation})
 and deployed it on a 20~Gbps ISP testbed similar to the TapDance
@@
 
-\scheme involves two high-level steps. First, clients \textbf{register} with the
-ISP station,
-and agree on the phantom host IP address that will be used. Then, the client
-connects to the agreed upon phantom address, which relays the client's traffic
-to an \textbf{application}. If the application determines the traffic is from
-the same client that originally registered (and not a probing censor), it
-provides access to the proxy, tunneled through the application's protocol.
+\scheme involves two high-level steps. First, clients \textbf{register} with a 
+\scheme station deployed at an ISP, and derive a phantom host IP address from 
+a seed shared in the registration. Then, clients \textbf{connect} 
+to the agreed upon phantom address, and the station listening on the tap 
+relays the client's traffic to a local application. The application brokers 
+traffic to a proxy application specified by the client in their registration 
+providing a probe resistant tunnel. Figure~\ref{fig:overview} describes a 
+high-level overview of the \scheme registration and connection behavior.
 
 Similar to previous schemes, our design does not require expensive in-line
-flow blocking, and can be accomplished with only a passive tap at the ISP.
-Our architecture is also modular, in that the registration and application steps operate
+flow blocking and is accomplished with only a passive tap at the ISP, imparting
+little to no burden on their infrastructure and service reliability.
+Our architecture is also modular, in that the registration and connection steps operate
 independently, allowing a wide range of flexibility to evade censors. We
@@
 
+\FigOverview
+
 \subsection{Registration}
 \label{sec:registration}
-Clients can register intent to use the proxy in several covert ways. For
-instance, they could use email~\cite{SWEET-ToN} or any other existing intermittently
-available proxies
-to register. In this section, we use a form of Refraction Networking similar to
-TapDance to register directly with the station, though note our scheme is simpler and more
-difficult to detect or block compared to vanilla TapDance.
-%We note this form is simpler and more difficult to detect or block than
-%TapDance.
-
-Registration is unidirectional (client to server) and does not require any
-acknowledgement of receipt. To ensure receipt, clients can attempt to register
-multiple times (possibly via multiple methods) with the same information, and expect
-that one gets through.
+We use a form of refraction networking similar to Tapdance to register directly with
+the station, though \scheme registration is significantly simpler and more difficult
+to detect than vanilla Tapdance. This is because registration flows are unidirectional; 
+a client communicates their intent to register to the station without any 
+response from the station itself. This makes registration flows very difficult to detect as they 
+can be sent to any site hosted behind the ISP, and display no evidence of proxy behavior.
+
+While this model of registration gives the client no definitive indication that their 
+registration was successful, the client can attempt to register
+multiple times concurrently with the same information, 
+and expect that one gets through. Alternatively clients can register intent to use the 
+proxy in other covert ways. For instance, they could use email~\cite{SWEET-ToN} or any 
+other existing intermittently available proxies to register.
 
@@
 
-To register, clients connect to a \textbf{decoy} site that supports TLS. They
-complete the handshake, and send a normal HTTPS request that embeds a special
-steganographic \textbf{tag} in the ciphertext of the request. We use
-the same technique used in TapDance's covert ciphertext
-channel~\cite[\S3]{tapdance14}
-to embed the tag, but we purposefully have the client
-send a complete request (rather than incomplete), allowing the decoy server to respond.
-The steganographic tag is only visible to the ISP station, which can see the tag using its
-private key. Unlike in TapDance, the \scheme station can passively observe
-the tag, and does not need to respond to it, obviating the need to mimick the decoy.
-In addition, more potential decoys can be used than in TapDance, as
-there is no need to exclude decoys that have timeouts or TCP windows unfavorable
-for keeping connections open. In our ISP deployment, this results in a modest increase
-of 25\% more decoys that could be used than in TapDance.
+A registration connection is sent to a \textbf{registration decoy}: any site that 
+supports TLS behind the ISP relative to the client. The client completes the handshake,
+and sends a normal HTTPS request that embeds a ciphertext tag in the payload. 
+\scheme leverages the same steganographic technique as Tapdance to encode the 
+ciphertext~\cite[\S3]{tapdance14}, however we send a complete request allowing the
+registration decoy to respond or close the connection. The tag is encrypted such 
+that it is only visible to the station. The \scheme station passively observes
+tagged flows obviating the need to mimic the decoy. In addition, more potential 
+decoys can be used in comparison to TapDance, as there is no need to exclude decoys that 
+have timeouts or TCP windows unfavorable for keeping connections open. In our 
+deployment, this results in a modest increase of 25\% more decoys that could be 
+used than in TapDance.
 
@@
 derived from a Diffie-Hellman key exchange with the station's long-term public key hard-coded
-in the client software. The station uses its private key to compute the same
+in the client. The station uses its private key to compute the same
 shared secret from the (decoded) client public key, and decrypts the message in the
@@
 
-Inside the message, the client communicates a random \textbf{seed}, and other
-configuration-specific information, such as flags to signify version, feature
-support, and a set of network prefixes that the client knows can be used
-for phantom hosts (previously distributed publicly).
+Inside the message, the client communicates a random seed, the covert address 
+they would like to connect to, the transport protocol they will use, and other
+configuration-specific information, such as flags to signify version, and feature support.
 The client and server hash the seed to determine which specific
-IP address from the set of prefixes will be used and registered as a phantom host.
+IP address from the set of shared CIDR prefixes will be used and registered as a phantom host.
 It may seem intuitive to instead have the client
@@
 obtain a seed it could use to register for a desired IP address.
-It also gives a
-secret (the seed) that only the client and station know, which can
-later be used to verify a client connecting to the phantom host address is the
-original registering client.
 We discuss the intricacies of phantom IP address selection in
@@
 Once the phantom host IP address has been selected, the station watches for
-packets destined to that address, and forwards them onto the phantom host
-\textbf{application}. The station only forwards packets that originate from the
-IP address of the registering client, making the phantom host appear as
-firewalled off to everyone but the client.
+packets with the source address of the original client and the phantom as the destination, 
+and forwards them on to the a local application handling transports. The station only 
+forwards packets that originate from the IP address of the registering client, making the
+ phantom host appear firewalled off to everyone but the client.
 We note that censors have been observed taking over client IP
-addresses for follow-up probing~\cite{ensafi-tor}, which would allow censors to
-still communicate with registered phantom hosts despite this filter.
-However, filtering in this way does prevent censors from enumerating the
+addresses for follow-up probing~\cite{ensafi-tor}. This would allow censors to
+hijack registrations if they can connect within the small window between client 
+registration and connection. However this only 
+allows the censor to communicate to the local application that handles transports, 
+it does not connect them to the covert address that the client indicated in their registration. 
+Filtering by client IP and phantom IP also prevents censors from enumerating the
 address space before hand, as they would have to do so from every potential
@@
 single vantage point would not reveal hosts that only respond to specific IPs
-(e.g. are firewalled off).
-%We instead address active probing in the application.
-
-\subsection{Applications}
+(e.g. firewalled subnets).
+
+\subsection{Transports}
 
 Once the client has registered, packets sent to the phantom host IP address are
-passed to the \textbf{application} running on the station, which provides
-proxy access to the client. The application has
+detected at the station and passed to the local \textbf{application} which provides
+proxy access to the client. A viable \scheme transport has
 two main requirements: first, the protocol it uses with the client 
 must be difficult for the censor to \emph{passively detect} and block by traffic
-inspection. Second, the application must resist \emph{active probes} by the censor (who
-does not know the registration seed).
-
-Any protocol that satisfies these criteria can be used as an application. In
-this section, we describe existing protocols (obfs4 and obfuscated SSH) as well
+inspection. Second, the endpoint must resist \emph{active probes} by the censor (who
+does not know some shared secret).
+
+Any protocol that satisfies these criteria can be used as an effective transport
+with \scheme. In this section, we describe various existing protocols (OSSH and obfuscated Obfs4) as well
 as introduce our own (Mask sites, TLS 1.3 eSNI, and phantom WebRTC clients) that
 can be used in \scheme, and evaluate how each meet the necessary requirements.
-Figure~\ref{fig:overview} describes a high-level overview of the \scheme
-registration and application behavior, and Table~\ref{tab:applications} compares the
-application protocols.
-
-\FigOverview
-
-\subsubsection{obfs4}
-
-\texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
-Tor~\cite{tor} designed to resist both passive detection and active probing.
-Traffic is obfuscated by encrypting it and sending headerless ciphertext
-messages, and clients can only connect to \texttt{obfs4}
-servers by proving knowledge of a secret. Probing censors that do not have the
-secret get no response from \texttt{obfs4} servers, making it difficult for
-censors to confirm if a host is a proxy. Server IPs and their corresponding secrets
-are normally distributed out-of-band through Tor's bridge distribution system.
-
-We can adopt \texttt{obfs4} for use as a \scheme application, with minimal
-modification. During
-registration, the \scheme client and station can use the registration seed to
-derive the \texttt{obfs4} secrets (NODE\_ID and server private/public keys)
-needed for the client to connect. The station then launches an \texttt{obfs4} server
-instance at the registered phantom address, and the client can connect to it using the
-derived secrets. If a censor attempts to connect to the phantom address (even
-using the client's IP), it will not receive a response, as it does not know the
-registration seed used to derive the \texttt{obfs4} secrets.
-
-Using \texttt{obfs4} as a \scheme application has the added benefit that servers
-and secrets do not need to be distributed out-of-band, eliminating one of the
-main ways censors currently block existing \texttt{obfs4}
-instances~\cite{tor-bridge-blocking-blog}. Instead, each \scheme \texttt{obfs4}
-instance is private to its registering client, and there is no public service
-that censors can use to discover them.
-
-%However, even though \texttt{obfs4} is indistinguishable from random, there are
-%still known attacks that can differentiate it from other
-%traffic~\cite{wang2015seeing}. While we have yet to see evidence of such attacks
-%employed in practice by censors, we consider two alternatives built on TLS.
-
-%Besides obfs4, we next describe in detail several alternative application
-%protocols based on SSH, TLS, and WebRTC. These
-%alternatives neatly demonstrate the flexibility of \scheme in allowing deployments
-%to support multiple application protocols. Should censors develop ways to
-%identify and block one protocol, others can still be used to provide proxy
-%access.
+Table~\ref{tab:applications} compares the application protocols. \scheme uses a modular 
+approach to transports because research into proxy detection is ongoing.
+Having a variety of supported transports gives clients a quick way to pivot and 
+maintain proxy access even when new proxy protocol vulnerabilities are discovered.
 
@@
 communication. Early versions of OSSH were passively detectable by censors, who
-can observe the random seed and derive the key, allowing them to de-obfuscate the protocol.
+could observe the random seed and derive the key, allowing them to de-obfuscate the protocol.
 These versions also did
-not protect against active probing attacks, as a censor can easily create their
+not protect against active probing attacks, as a censor could easily create their
 own connections to confirm if a server supports the protocol.
@@
 
-%While this can passively detected by censors (who can also
-%derive the key and de-obfuscate the protocol), the key derivation is deliberately
-%slowed by an iterated hash to make such identification
-%expensive (though not impossible) at high speeds.
-%
-%
-%% This is wrong...it actually does protect against active probing
-%Obfuscated SSH also does not protect against active probing, as the censor can
-%easily create their own connections and confirm the server is using the
-%protocol. Nonetheless, this protocol is still used in deployed censorship
-%circumvention systems~\cite{psiphon}, though has to deploy proxies at new IP
-%addresses when censors inevitably discover and block them.
-%Obfuscated SSH can also be used as a \scheme
-%application protocol, though we note it provides no active probing or passive
-%identification resistance. However, \scheme OSSH can still make it cheaper to
-%rotate to new IP addresses when proxies are found and blocked.
-
-\subsubsection{Mask Sites}
-\label{sec:mask-sites}
+% \TODO{We have implemented OSSH as a transport option by integrating with psiphon.}
+
+\subsubsection{obfs4}
+
+\texttt{obfs4}~\cite{obfs4} is a pluggable transport used by
+Tor~\cite{tor} designed to resist both passive detection and active probing.
+Traffic is obfuscated by encrypting it and sending headerless ciphertext
+messages. Similar to OSSH, clients can only connect to \texttt{obfs4}
+servers by proving knowledge of a secret. Probing censors that do not have the
+secret get no response from \texttt{obfs4} servers, making it difficult for
+censors to confirm if a host is a proxy. Server IPs and their corresponding secrets
+are normally distributed out-of-band through Tor's bridge distribution system.
+
+During registration, the \scheme client and station could use the registration seed to
+derive the \texttt{obfs4} secrets (NODE\_ID and server private/public keys)
+needed for the client to connect. The station could then launch an \texttt{obfs4} server
+instance locally for the client to connect to as a transport using the
+derived secrets. If a censor attempts to connect to the phantom address (even
+using the client's IP), it will not receive a response, as it does not know the
+registration seed used to derive the \texttt{obfs4} secrets.
+
+Using \texttt{obfs4} as a \scheme application has the added benefit that servers
+and secrets do not need to be distributed out-of-band, eliminating one of the
+main ways censors currently block existing \texttt{obfs4}
+instances~\cite{tor-bridge-blocking-blog}. Instead, each \scheme \texttt{obfs4}
+instance is private to its registering client, and there is no public service
+that censors can use to discover them.
+
+\subsubsection{TLS}
 
@@
 during the TLS handshake. This includes the Server Name Indication (SNI) in the
-Client Hello message that sends the domain name of the server, and the
-X.509 Certificate sent by the server.
+Client Hello message that specifies the domain name, and the
+X.509 Certificate of the server.
 
@@
 
-We therefore attempt to mimic an existing \textbf{mask site} by relaying
-traffic between the client and a selected mask website. To a censor, this site
-will be indistinguishable from the actual site, making it difficult for
+\paragraph{Encrypted SNI}
+\label{esni}
+
+TLS~1.3~\cite{tls13} offers several features that may greatly simplify 
+\scheme transport design. For instance, TLS~1.3 handshakes include encrypted
+certificates, removing a strong traffic classification feature.
+Unfortunately, TLS~1.3 currently still sends the SNI in the (plaintext) Client
+Hello, meaning we would have to choose a realistic domain to fool a censor.
+
+However, there are proposals to encrypt the SNI in the Client Hello~\cite{ietf-tls-esni-02},
+though none have been implemented or deployed as of 2019. Nonetheless,
+if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
+\scheme applications by allowing the client to use plain TLS as the transport
+while remaining hidden from the censor.
+Censors could still try to actively probe with guesses for the SNI,
+servers could respond with generic ``Unknown SNI'' errors. If such responses
+were common for incorrect SNI, the censor's efforts to identify phantom hosts
+would be frustrated.
+
+\paragraph{Mask Sites}
+\label{sec:mask-sites}
+
+Working with currently popular implementations of TLS we overcome the active 
+and passive probing challenges by mimicking an existing mask site. To a censor, this site
+will be difficult to distinguish from the actual site, making it expensive for
 them to block without potentially blocking the real site. TLS connections to the
-application will terminate exactly as connections to the mask site would, with the
-application acting as a transparent TCP-layer proxy between the client and mask site.
+\scheme station will terminate exactly as connections to the mask site would, with
+\scheme acting as a transparent TCP-layer proxy between the client and mask site.
 However, this leaves the application unable to introspect on the contents of the
-TLS connection to the mask site, as it does not have the client-site shared
+TLS connection to the mask site, as it does not have the client-side shared
 secrets, and it cannot overtly man-in-the-middle the connection before knowing
@@
 To covertly signal to the relaying application, the client changes the shared secret
-it derives with the
-mask site to something that the application can also derive. The client's first
+it derives with the mask site to something that the \scheme station can also derive. The client's first
 \texttt{Application Data} packet is thus encrypted under a different secret than
@@
 
-The application can determine if the client did this by trial decryption with
-the master secret derived from the known \textbf{seed}. If it succeeds, the
-client has proved knowledge of the \textbf{seed}, and the application can
+The \scheme station can determine if the client did this by trial decryption with
+the master secret derived from the known seed shared at registration. If it succeeds, the
+client has proved knowledge of the seed, and the application can
 respond as a proxy. If not, the application simply continues to forward data
-between the client and the mask site. As the censor does not have knowledge of
+between the client and the mask site, in case a clients IP was taken over by
+a censor after registration. As the censor does not have knowledge of
 the \textbf{seed} used in registration, it cannot coerce the application to
@@
 
-\subsubsection{Mask Site Selection}
+\paragraph{Mask Site Selection}
 
@@
 if a phantom host at an IP address pretends to be a domain (\texttt{example.com}) that
-globally resolves to a single different IP address, the censor could also
+globally resolves to a single IP address, the censor could also trivially
 identify and block the phantom host.
 
-\paragraph{Nearby sites.}
-One strategy for selecting mask sites to mimic is to pick websites that are
-legitimately hosted in or near the network of the phantom host addresses. This
-effectively creates copies of legitimate sites, with the censor unable to
-determine which copies are real and which are the phantom hosts. However, as
-mentioned, other signals such as DNS may reveal the true mask site.
-
-\paragraph{Popular sites.}
-An alternative strategy is to use popular sites, such as those from the Alexa
-top site~\cite{alexa-top500} list. As mentioned previously, it may be wise to avoid
+\textit{Nearby sites --} pick websites that are
+legitimately hosted in or near the network of the phantom host addresses
+effectively creating copies of legitimate sites. However, other signals such as 
+DNS may reveal the true mask site.
+
+\textit{Popular sites --} choose mask sites from a list such as the Alexa
+top site~\cite{alexa-top500} list. Although it may be wise to avoid
 sites that are obviously not hosted in the phantom host address range, such as
@@
 
-\paragraph{Passive observation.}
-The ISP tap could also collect sites by passively observing DNS requests, TLS
-SNI, or certificates that pass by. This would allow for building a realistic set
+\textit{Passive observation --} collect sites by passively observing DNS requests, TLS
+SNI, or certificates that pass by at the network tap. This would allow for building a realistic set
 of sites that are plausibly in the vicinity of the phantom host addresses
-that pass by the tap. It also has the added bonus of being able to discover
-IPv6 addresses that could be used as decoys (for registration), where active
-scanning would be infeasible.
-
-In practice, clients can often try phantom hosts/mask sites over
+that pass by the tap.
+
+In practice, clients can often try multiple phantom hosts/mask sites over
 several attempts, as blocking the client outright may negatively impact other
 unrelated users behind the same network (e.g. in the case of NAT). Thus, even a
-censor that can block most (but not all) mask site only delays access, and
-doesn't prevent it outright.
-
-\subsubsection{Encrypted SNI}
-\label{esni}
-
-TLS~1.3~\cite{tls13} offers several features that may greatly simplify 
-\scheme application design. For instance, TLS~1.3 handshakes include encrypted
-certificates, potentially obviating the need to impersonate mask sites.
-Unfortunately, TLS~1.3 currently still sends the SNI in the (plaintext) Client
-Hello, meaning we would still have to choose a realistic domain to fool a
-censor.
-
-However, there are proposals to encrypt the SNI in the Client Hello~\cite{ietf-tls-esni-02},
-though none have been implemented or deployed as of 2019. Nonetheless,
-if widely adopted, Encrypted SNI (ESNI) would offer a powerful solution for
-\scheme applications by allowing the domain to remain hidden from the censor.
-While the censor could still try to actively probe with guesses for the SNI,
-servers could respond with generic ``Unknown SNI'' errors. If such responses
-were common for incorrect SNI, the censor's efforts to identify phantom hosts
-would be frustrated.
+censor that can block most but not all mask site usage (i.e. by employing 
+website fingerprinting) only delays access, and doesn't prevent it outright.
 
@@
 Phantom hosts could also pretend to be clients instead of servers. This may
-potentially give censors less to block on, as actively probing clients is common
-to return few or no open ports. Nonetheless, a censor may be hesitant to block
+potentially give censors less to block on, as actively probing clients commonly
+returns few or no open ports. A censor may also be hesitant to block
 client-to-client communication, as it could block peer-to-peer applications as
 well as many video conferencing protocols. WebRTC is a
-natural choice for a client-to-client protocol in censorship circumvention,
-and is used in existing censorship circumvention schemes like
+natural choice for a client-to-client transport in censorship circumvention,
+and is already used in existing schemes like
 Snowflake~\cite{snowflake}. \scheme could also use WebRTC as the
-application protocol, convincing the censor that two clients are communicating.
+transport protocol, convincing the censor that two clients are communicating.
 
 \TabApplications
+
+\section{Implementation}
+\label{sec:implementation}
+
+We implemented the \scheme protocol and deployed a station at a
+20~Gbps router in a mid-sized transit ISP. We used PF\_RING to
+consume the 20~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
+detector processes all packets and watches for new registrations. It also
+forwards all packets sent to a (registered) phantom host address to the local
+\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
+allowing the application to accept and respond to connections using the native
+operating system's interface. Figure~\ref{fig:implementation} shows the overall
+architecture of our implementation, which we describe next.
+% Along with the client?
+
+\FigImplementation
+
+\subsection{Detector}
+
+Our detector is a modified fork of the open source TapDance
+implementation~\cite{tapdance-source}.
+We implemented our detector in approximately 1,800 lines of Rust (compared to
+over 5,000 lines for TapDance)\footnote{excluding (from both) about 3,000 lines
+of auto-generated protobuf code}.
+
+To achieve high-performance necessary to operate at 20~Gbps, we used
+PF\_RING~\cite{pfring} to load balance incoming packets over 4~CPU cores. PF\_RING
+supports balancing across cores based on flow (5-tuple) or source and
+destination IPs. However, both of these options present engineering challenges
+for \scheme that we must overcome.
+One issue is that registrations could be processed on a
+different core than the packets sent to that specific phantom host address. For
+instance, a client could have its registration handled by Core 1, while its
+packets to the phantom host address end up on Core 3, which doesn't know about the
+original registration.
+
+To address this, we used Redis~\cite{redis} to allow each process to broadcast
+(publish) newly registered decoys to the other cores so they can
+add them to their local list of registered phantom host addresses.
+However, this introduces two new problems. First, a core might add a
+registration \emph{after} it has already received and processed packets destined
+for the specified phantom host. This typically isn't a problem when running on a
+single core, as packets are processed sequentially. Second, each core may
+timeout each phantom host at different times, potentially leading to differing
+behavior that is visible to a censor. For instance, if we used the
+source/destination IPs to load balance, a censor's packets to a phantom host could
+be processed by a different core than the client. If the censor waits for the
+known timeout before sending a probe, its core may have timed out that phantom host, while the client's core has refreshed the timeout of the phantom host due
+to active use.
+
+To address the first issue of asynchronous cores, we force the client to delay sending its connection
+to the phantom host until a short time after registration. In practice, we force
+the client to wait until the registration decoy responds before starting a
+connection with the registered phantom host. While the decoy response is
+unrelated to the station's processing, it serves as a conservative way to know
+the registration has had time to reach the station.
+
+To address the second issue of differing core timeouts, we implemented a new
+load-balancing algorithm in
+PF\_RING to select the core based solely on the destination IP address of the
+packet. We still must use Redis to tell all of the cores of new
+registrations, but only one core will be ultimately responsible for processing all of
+the packets sent to a given phantom host, regardless of who or when it is sent.
+
+\subsection{Application}
+
+We implemented our application in about 500~lines of Golang. Though we note
+other protocols (e.g. obfsproxy or WebRTC) could be used as the application, we
+implemented a mask site mimicking application, that pretends to be a mask site
+when actively probed by the censor.
+
+The application accepts connections to phantom host addresses forwarded by the
+detector and rewritten to the local address using \texttt{iptables}.
+The application also receives out-of-band information about registrations from the
+detector via a ZMQ~\cite{zmq} connection, which informs the application of the
+registering client's IP address, the secret seed, and other configuration
+information passed by the client.
+
+Once the application accepts a connection, it initially acts as a transparent
+proxy to the mask site specified by the client during registration. The
+application parses the handshake, forwarding packets back and forth between
+client and mask site without modification, and extracting the server and client
+randoms. The application attempts to decrypt the first application data record
+from the client using a key derived from the secret seed, and client and server
+randoms. We use the uTLS library~\cite{utls} on both the application and client
+to allow us to change the TLS secrets being used after the handshake.
+
+\FigTapBandwidth
+
+If the decryption is successful, the application switches to forwarding
+(decrypted) data back and forth with a client-specified endpoint, such as a
+SOCKS proxy, which can multiplex multiple client connections over the single
+connection to the phantom host.
+
+\subsection{Client}
+
+%TODO: how many registration requests do we make? how long does it take?
+We created a \scheme client and integrated it with the Psiphon~\cite{psiphon}
+anticensorship client. Psiphon has millions of users in censored countries, and
+we are in the early stages of rolling \scheme out to real-world users.
+
+Our \scheme client is written in Golang, and uses the TapDance-like protocol
+(Section~\ref{sec:registration}) for
+registration. We note that this protocol should be harder for censors to observe
+than normal TapDance because it consists of only a single (complete) request, and the station does
+not have to spoof packets as the decoy used during registration, only passively
+observe them.
+
+We implemented two of the applications in our client: Obfuscated SSH used by
+Psiphon
+(Section~\ref{sec:ossh}) and our Mask Site protocol
+(Section~\ref{sec:mask-sites}). Our client signals which application it will use
+in the registration tag. The client also sends a flag that indicates if the
+client supports IPv6, to allow IPv4-only clients to only derive IPv4 phantom
+hosts.
+After registration, the client connects to the derived
+phantom host address, and speaks the specified application protocol, which
+tunnels a SOCKS connection between the client and Psiphon's backend servers,
+which proxy the client's connections.
+
+\if0
+In order to scale up to 20Gbps and beyond,
+one has to utilize multiple cores and employ load balancing.
+We use PF\_RING built-in load balancer \emph{zbalance} to efficiently
+distribute load between 4 cores.
+Our timeout is based on last IP address usage time, which prevents us from
+balancing load based on source IP address,
+as censor would be able to observe
+same destination IP address picking or not picking up
+depending on source IP address.
+To avoid such unusual behavior we balance on destination IP.
+Since PF\_RING does not feature load balancing based only on destination
+IP address, we made a custom implementation of this zbalance policy.
+
+TODO: say it's tested on 20 Gbps
+
+Implementation of the protocol includes 3 components:
+detector, proxy application, and client.
+Detector will parse the traffic, searching for registrations in
+tagged messages. After detector observes a registration, and negotiates with client
+a phantom host IP,
+all packets, that are sent to that phantom host IP,
+will be forwarded into a proxy application.
+
+\subsection{Registration phase}
+
+Each \scheme connection has 2 phases: registration, and usage of a phantom host.
+Registration starts with a handshake that is similar to a TapDance handshake,
+but initial HTTP request is complete.
+This allows a reachable site to provide a genuine response
+to a HTTP GET request of its index page.
+Since station does not need to produce a response,
+which significantly reduces complexity of a detector,
+that does not need to decrypt and inject packets into a TLS connection between
+client and a reachable site, as opposed to original TapDance.
+
+Client begins registration by establishing TLS connection
+to one of the reachable websites,
+path to which passes by our tap.
+Client uses a Chosen-Ciphertext Steganography technique~\cite{tapdance14} to manipulate
+plaintext of a first application data HTTP request
+to get desired ciphertext,
+and exchange keys with the station.
+After client writes Elligator-encoded~\cite{elligator} representative into the ciphertext at a static offset of 92 bytes from the end,
+that could be decoded using station's private key,
+to negotiate a 32 byte Elligator-encoded~\cite{elligator} shared secret between the client and the station.
+That shared secret is used as a seed of SHA-256 based key derivation function (HKDF),
+allowing station and client to derive an unlimited amount of shared secrets.
+
+Elligator representative on the wire is immediately followed by a 6 bytes long AES-GCM-encrypted
+fixed size payload(FSP), that holds flags and the size of the variable size payload(VSP).
+IV and key for encrypted of both FSP and VSP will be derived from HKDF.
+Once FSP is decrypted and the size of VSP is known, station can decrypt the VSP as well.
+VSP itself is a protobuf, which allows us to easily change the contents of VSP without risk of version mismatch, and currently contains 3 fields: version of configuration(which includes list of decoys), SNI of mask site, and a presumably blocked target host that client would like to get connected to.
+
+Client will sleep a short randomized period of time before attempting to establish connection to phantom host.
+This is done for 2 reasons: to break potentially observable interflow dependency with a phantom host connection being established right after a first application layer data packet sent to decoy,
+and to give station time.
+TODO: why does it need time?
+
+\subsection{Application phase}
+Client and station will use HKDF to derive 16 random bytes and use them to
+agree on a phantom host IP address, by applying a simple selection algorithm.
+Algorithm is as follows: first, flatten a list of pre-shared available IP
+addresses in various subnets into a single indexed list, then make a 128-bit
+integer out of 16 random bytes and divide it by the length
+of the flattened list, and use the remainder of this division as an index
+of the list to pick an IP address.
+
+To thwart active probing attacks, this application will then confirm
+that connecting client knows a secret, negotiated during the registration.
+If connecting client does know that secret, application will set up proxying,
+otherwise it may give censor a response, that acts like that this IP address
+is not an open proxy.
+
+TODO: describe MakeConnWithCompleteHandshake?
+
+Note that the detector and proxy application are only loosely coupled with each other,
+making it simple to replace one of them.
+We plan to take advantage of encrypted SNI, when it gets widely adopted,
+and replace our current proxy implementation with one that uses encrypted SNI
+and achieve improved unobservability properties, described in section~\ref{esni}.
+
+\subsection{Languages and LOC counts} % TODO: rename/restructure and complete section
+Client is written in Golang and follows the same API as standard TapDance does,
+which allows us to reuse existing TapDance CLI wrapper and Android application.
+
+-Language choice (Rust, Go, minimal C)
+-Open source (client, station and application)
+\fi
+
+\section{Evaluation}
+\label{sec:evaluation}
+% 1 page
+
+%\TODO{Write (1 page)}
+
+\FigUpload
+\FigDownload
+
+To evaluate our \scheme implementation, we compare its bandwidth and latency
+to that of TapDance in a realistic ISP setting. We used a 20~Gbps
+network tap at a mid-sized ISP and run both implementations on a 1U server with
+an 8-core Intel Xeon E5-2640 CPU, 64GB of RAM, and a dual-port Intel X710 10GbE SFP+
+network interface. A typical week of bandwidth seen on the tap is
+shown in Figure~\ref{fig:tap-bandwidth}, ranging from 2.4~Gbps to peaks above
+17~Gbps.
+
+We evaluated the performance of a client from an India-based VPS,
+Figures~\ref{fig:upload} and~\ref{fig:download} show the upload and download as
+measured by iperf for TapDance, our \scheme implementation (using the mask site application),
+and a direct connection to our iperf server in the ISP's network.
+
+TapDance must reconnect if the amount of data sent by the client
+exceeds a short TCP window (typically on the order of 32~KBytes) or the
+connection persists until a timeout (18-120 seconds). At each reconnect, the
+TapDance client naively blocks until a new TLS connection to the decoy and
+station has been established. Thus, when uploading files, TapDance has to create
+a new TLS connection for every 32~KBytes of data it sends, limiting its average
+upload bandwidth to around 0.1~Mbps due to the high overhead. In contrast,
+our \scheme implementation is
+able to maintain the same connection during large uploads, and achieves
+performance inline with the direct connection, over 1400 times faster.
+
+During download-only workloads, TapDance is able to better utilize the network,
+but must still reconnect before the decoy times out. In our tests, we see
+TapDance reconnect every 25 seconds, which can negatively impact the performance of
+downloads or any real-time streaming applications. Again, our \scheme
+implementation is able to maintain a single connection and provide the maximum
+download rate without interruption, 14\% faster than TapDance.
+
+We also measure the latency of repeated small requests. In both \scheme (using
+the OSSH protocol) and
+TapDance we establish a single session tunnel using our integrated Psiphon
+client, and make 1000 requests through each using Apache Benchmark (ab). We find
+that our India-based VPS throttles TLS but not OSSH, making TapDance twice as slow as
+\scheme. We repeated these tests on a US-based VPS which does not have such
+throttling, and show results in Figure~\ref{fig:latency}. TapDance's frequent
+reconnects adds significant latency to about 10\% of requests. In addition, the
+median latency of \scheme is about 19\% faster, due to the added
+overhead of TLS and the complex path that TapDance data packets take through
+the station compared to \scheme.
+
+\FigLatency
 
@@
 Phantom host IP addresses must be derived from network blocks that are routed (so they pass
-the ISP station) and contain other legitimate hosts (so that censors cannot
+the \scheme station) and contain other legitimate hosts (so that censors cannot
 block the entire network without collateral damage).
@@
 %addresses, allowing censors to easily enumerate network prefixes that pass by
-%the ISP station and measure legitimate sites. Furthermore, the small address
+%the \scheme station and measure legitimate sites. Furthermore, the small address
 %space makes it much easier to pre-image the hash used to derive IP addresses
@@
 the registration seed based on the Bayesian Network model created by the tool.
-
-\section{Implementation}
-\label{sec:implementation}
-
-We implemented the \scheme protocol and deployed a station at a
-20~Gbps router in a mid-sized transit ISP. Similar to TapDance~\cite{tapdance14}, we used PF\_RING to
-consume the 20~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
-detector processes all packets and watches for new registrations. It also
-forwards all packets sent to a (registered) phantom host address to the local
-\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
-allowing the application to accept and respond to connections using the native
-operating system's interface. Figure~\ref{fig:implementation} shows the overall
-architecture of our implementation, which we describe next.
-% Along with the client?
-
-\FigImplementation
-
-\subsection{Detector}
-
-Our detector is a modified fork of the open source TapDance
-implementation~\cite{tapdance-source}.
-We implemented our detector in approximately 1,800 lines of Rust (compared to
-over 5,000 lines for TapDance)\footnote{excluding (from both) about 3,000 lines
-of auto-generated protobuf code}.
-
-To achieve high-performance necessary to operate at 20~Gbps, we used
-PF\_RING~\cite{pfring} to load balance incoming packets over 4~CPU cores. PF\_RING
-supports balancing across cores based on flow (5-tuple) or source and
-destination IPs. However, both of these options present engineering challenges
-for \scheme that we must overcome.
-One issue is that registrations could be processed on a
-different core than the packets sent to that specific phantom host address. For
-instance, a client could have its registration handled by Core 1, while its
-packets to the phantom host address end up on Core 3, which doesn't know about the
-original registration.
-
-To address this, we used Redis~\cite{redis} to allow each process to broadcast
-(publish) newly registered decoys to the other cores so they can
-add them to their local list of registered phantom host addresses.
-However, this introduces two new problems. First, a core might add a
-registration \emph{after} it has already received and processed packets destined
-for the specified phantom host. This typically isn't a problem when running on a
-single core, as packets are processed sequentially. Second, each core may
-timeout each phantom host at different times, potentially leading to differing
-behavior that is visible to a censor. For instance, if we used the
-source/destination IPs to load balance, a censor's packets to a phantom host could
-be processed by a different core than the client. If the censor waits for the
-known timeout before sending a probe, its core may have timed out that phantom host, while the client's core has refreshed the timeout of the phantom host due
-to active use.
-
-To address the first issue of asynchronous cores, we force the client to delay sending its connection
-to the phantom host until a short time after registration. In practice, we force
-the client to wait until the registration decoy responds before starting a
-connection with the registered phantom host. While the decoy response is
-unrelated to the station's processing, it serves as a conservative way to know
-the registration has had time to reach the station.
-
-To address the second issue of differing core timeouts, we implemented a new
-load-balancing algorithm in
-PF\_RING to select the core based solely on the destination IP address of the
-packet. We still must use Redis to tell all of the cores of new
-registrations, but only one core will be ultimately responsible for processing all of
-the packets sent to a given phantom host, regardless of who or when it is sent.
-
-\subsection{Application}
-
-We implemented our application in about 500~lines of Golang. Though we note
-other protocols (e.g. obfsproxy or WebRTC) could be used as the application, we
-implemented a mask site mimicking application, that pretends to be a mask site
-when actively probed by the censor.
-
-The application accepts connections to phantom host addresses forwarded by the
-detector and rewritten to the local address using \texttt{iptables}.
-The application also receives out-of-band information about registrations from the
-detector via a ZMQ~\cite{zmq} connection, which informs the application of the
-registering client's IP address, the secret seed, and other configuration
-information passed by the client.
-
-Once the application accepts a connection, it initially acts as a transparent
-proxy to the mask site specified by the client during registration. The
-application parses the handshake, forwarding packets back and forth between
-client and mask site without modification, and extracting the server and client
-randoms. The application attempts to decrypt the first application data record
-from the client using a key derived from the secret seed, and client and server
-randoms. We use the uTLS library~\cite{utls} on both the application and client
-to allow us to change the TLS secrets being used after the handshake.
-
-\FigTapBandwidth
-
-If the decryption is successful, the application switches to forwarding
-(decrypted) data back and forth with a client-specified endpoint, such as a
-SOCKS proxy, which can multiplex multiple client connections over the single
-connection to the phantom host.
-
-\subsection{Client}
-
-%TODO: how many registration requests do we make? how long does it take?
-We created a \scheme client and integrated it with the Psiphon~\cite{psiphon}
-anticensorship client. Psiphon has millions of users in censored countries, and
-we are in the early stages of rolling \scheme out to real-world users.
-
-Our \scheme client is written in Golang, and uses the TapDance-like protocol
-(Section~\ref{sec:registration}) for
-registration. We note that this protocol should be harder for censors to observe
-than normal TapDance because it consists of only a single (complete) request, and the station does
-not have to spoof packets as the decoy used during registration, only passively
-observe them.
-
-We implemented two of the applications in our client: Obfuscated SSH used by
-Psiphon
-(Section~\ref{sec:ossh}) and our Mask Site protocol
-(Section~\ref{sec:mask-sites}). Our client signals which application it will use
-in the registration tag. The client also sends a flag that indicates if the
-client supports IPv6, to allow IPv4-only clients to only derive IPv4 phantom
-hosts.
-After registration, the client connects to the derived
-phantom host address, and speaks the specified application protocol, which
-tunnels a SOCKS connection between the client and Psiphon's backend servers,
-which proxy the client's connections.
-
-\if0
-In order to scale up to 20Gbps and beyond,
-one has to utilize multiple cores and employ load balancing.
-We use PF\_RING built-in load balancer \emph{zbalance} to efficiently
-distribute load between 4 cores.
-Our timeout is based on last IP address usage time, which prevents us from
-balancing load based on source IP address,
-as censor would be able to observe
-same destination IP address picking or not picking up
-depending on source IP address.
-To avoid such unusual behavior we balance on destination IP.
-Since PF\_RING does not feature load balancing based only on destination
-IP address, we made a custom implementation of this zbalance policy.
-
-TODO: say it's tested on 20 Gbps
-
-Implementation of the protocol includes 3 components:
-detector, proxy application, and client.
-Detector will parse the traffic, searching for registrations in
-tagged messages. After detector observes a registration, and negotiates with client
-a phantom host IP,
-all packets, that are sent to that phantom host IP,
-will be forwarded into a proxy application.
-
-\subsection{Registration phase}
-
-Each \scheme connection has 2 phases: registration, and usage of a phantom host.
-Registration starts with a handshake that is similar to a TapDance handshake,
-but initial HTTP request is complete.
-This allows a reachable site to provide a genuine response
-to a HTTP GET request of its index page.
-Since station does not need to produce a response,
-which significantly reduces complexity of a detector,
-that does not need to decrypt and inject packets into a TLS connection between
-client and a reachable site, as opposed to original TapDance.
-
-Client begins registration by establishing TLS connection
-to one of the reachable websites,
-path to which passes by our tap.
-Client uses a Chosen-Ciphertext Steganography technique~\cite{tapdance14} to manipulate
-plaintext of a first application data HTTP request
-to get desired ciphertext,
-and exchange keys with the station.
-After client writes Elligator-encoded~\cite{elligator} representative into the ciphertext at a static offset of 92 bytes from the end,
-that could be decoded using station's private key,
-to negotiate a 32 byte Elligator-encoded~\cite{elligator} shared secret between the client and the station.
-That shared secret is used as a seed of SHA-256 based key derivation function (HKDF),
-allowing station and client to derive an unlimited amount of shared secrets.
-
-Elligator representative on the wire is immediately followed by a 6 bytes long AES-GCM-encrypted
-fixed size payload(FSP), that holds flags and the size of the variable size payload(VSP).
-IV and key for encrypted of both FSP and VSP will be derived from HKDF.
-Once FSP is decrypted and the size of VSP is known, station can decrypt the VSP as well.
-VSP itself is a protobuf, which allows us to easily change the contents of VSP without risk of version mismatch, and currently contains 3 fields: version of configuration(which includes list of decoys), SNI of mask site, and a presumably blocked target host that client would like to get connected to.
-
-Client will sleep a short randomized period of time before attempting to establish connection to phantom host.
-This is done for 2 reasons: to break potentially observable interflow dependency with a phantom host connection being established right after a first application layer data packet sent to decoy,
-and to give station time.
-TODO: why does it need time?
-
-\subsection{Application phase}
-Client and station will use HKDF to derive 16 random bytes and use them to
-agree on a phantom host IP address, by applying a simple selection algorithm.
-Algorithm is as follows: first, flatten a list of pre-shared available IP
-addresses in various subnets into a single indexed list, then make a 128-bit
-integer out of 16 random bytes and divide it by the length
-of the flattened list, and use the remainder of this division as an index
-of the list to pick an IP address.
-
-To thwart active probing attacks, this application will then confirm
-that connecting client knows a secret, negotiated during the registration.
-If connecting client does know that secret, application will set up proxying,
-otherwise it may give censor a response, that acts like that this IP address
-is not an open proxy.
-
-TODO: describe MakeConnWithCompleteHandshake?
-
-Note that the detector and proxy application are only loosely coupled with each other,
-making it simple to replace one of them.
-We plan to take advantage of encrypted SNI, when it gets widely adopted,
-and replace our current proxy implementation with one that uses encrypted SNI
-and achieve improved unobservability properties, described in section~\ref{esni}.
-
-\subsection{Languages and LOC counts} % TODO: rename/restructure and complete section
-Client is written in Golang and follows the same API as standard TapDance does,
-which allows us to reuse existing TapDance CLI wrapper and Android application.
-
--Language choice (Rust, Go, minimal C)
--Open source (client, station and application)
-\fi
-
-\section{Evaluation}
-\label{sec:evaluation}
-% 1 page
-
-%\TODO{Write (1 page)}
-
-\FigUpload
-\FigDownload
-
-To evaluate our \scheme implementation, we compare its bandwidth and latency
-to that of TapDance in a realistic ISP setting. We used a 20~Gbps
-network tap at a mid-sized ISP and run both implementations on a 1U server with
-an 8-core Intel Xeon E5-2640 CPU, 64GB of RAM, and a dual-port Intel X710 10GbE SFP+
-network interface. A typical week of bandwidth seen on the tap is
-shown in Figure~\ref{fig:tap-bandwidth}, ranging from 2.4~Gbps to peaks above
-17~Gbps.
-
-We evaluated the performance of a client from an India-based VPS,
-Figures~\ref{fig:upload} and~\ref{fig:download} show the upload and download as
-measured by iperf for TapDance, our \scheme implementation (using the mask site application),
-and a direct connection to our iperf server in the ISP's network.
-
-TapDance must reconnect if the amount of data sent by the client
-exceeds a short TCP window (typically on the order of 32~KBytes) or the
-connection persists until a timeout (18-120 seconds). At each reconnect, the
-TapDance client naively blocks until a new TLS connection to the decoy and
-station has been established. Thus, when uploading files, TapDance has to create
-a new TLS connection for every 32~KBytes of data it sends, limiting its average
-upload bandwidth to around 0.1~Mbps due to the high overhead. In contrast,
-our \scheme implementation is
-able to maintain the same connection during large uploads, and achieves
-performance inline with the direct connection, over 1400 times faster.
-
-During download-only workloads, TapDance is able to better utilize the network,
-but must still reconnect before the decoy times out. In our tests, we see
-TapDance reconnect every 25 seconds, which can negatively impact the performance of
-downloads or any real-time streaming applications. Again, our \scheme
-implementation is able to maintain a single connection and provide the maximum
-download rate without interruption, 14\% faster than TapDance.
-
-We also measure the latency of repeated small requests. In both \scheme (using
-the OSSH protocol) and
-TapDance we establish a single session tunnel using our integrated Psiphon
-client, and make 1000 requests through each using Apache Benchmark (ab). We find
-that our India-based VPS throttles TLS but not OSSH, making TapDance twice as slow as
-\scheme. We repeated these tests on a US-based VPS which does not have such
-throttling, and show results in Figure~\ref{fig:latency}. TapDance's frequent
-reconnects adds significant latency to about 10\% of requests. In addition, the
-median latency of \scheme is about 19\% faster, due to the added
-overhead of TLS and the complex path that TapDance data packets take through
-the station compared to \scheme.
-
-\FigLatency
-
-%Compare to TapDance performance:
-%-Connection setup time
-%-Connection/session lifetime
-%-Throughput (especially upload vs download)
-%-Security considerations
-
-%\section{Discussion}
 
@@
 \paragraph{Client-side applications}
-On the application side, \scheme provides an interesting opportunity to explore
+\TODO{On the application side}, \scheme provides an interesting opportunity to explore
 \emph{client mimicking} phantom hosts. Rather than pretend to be a server (e.g.,

### 2019-09-02 paper/figures.tex
Implementation pass for content structure and clarification

@@
     \centering
-    \includegraphics[width=0.7\linewidth,clip]{figures/dark-decoy-flow1.png}
+    \includegraphics[width=0.7\linewidth,clip]{figures/dark-decoy-impl1.png}
     \caption{\textbf{Station Architecture}\,---\,\rm%
-        We used PF\_RING to receive packets from a 20~Gbps packet tap, which we load balance
-        across 4~CPU cores. The detector process identifies registrations, notifying all
-        cores when a new registration is received (green dashed registration flow). The detector also
-        identifies packets associated with registered flows (by connection 4-tuple) and diverts them
-        to a local application which handles proxying connections(purple dotted flow). The local 
-        application determines which proxy the flow should use based on a parameter specified by 
-        the client in the registration and initializes a goroutine to handle forwarding. 
+        We used PF\_RING to receive packets from a 20~Gbps tap which we load balance
+        across 4~CPU cores. The detector processes identify registrations, sending notification to
+        all other cores via redis and to the local application 
+        via ZMQ when a new registration is received . The detector also
+        identifies packets associated with registered flows and diverts them
+        to the local application which handles proxying connections. The local 
+        application determines which transport the flow should use based on a parameter specified in
+        the client's registration and initializes a goroutine to handle forwarding. 
         \\\hspace{\textwidth}
         A censor trying to interfere in this
-        connection would need to co-opt the clients IP address in a precise window (after the 
-        registration but before the client connects to the phantom) and correctly guess the phantom hosts 
+        connection would need to take over the clients IP address in a precise window (after the 
+        registration but before the client connects to the phantom) and correctly guess the phantom host's 
         IP address (or connect to all possible phantom IPs) before the active probe traffic gets to the local application. 
-        At this point their connection will fail in a manor specific to the proxy that the client specified
-        in the registration (e.g. connecting to OSSH without knowledge of the preshared secret).}
+        At this point their connection will fail in a manor specific to the transport that the client specified
+        in the registration (e.g. connecting to OSSH without knowledge of the pre-shared secret).}
     \label{fig:implementation}

### 2019-09-02 paper/paper.tex
Implementation pass for content structure and clarification

@@
 
-We implemented the \scheme protocol and deployed a station at a
-20~Gbps router in a mid-sized transit ISP. We used PF\_RING to
+We implemented \scheme and deployed a station at a mid-sized transit ISP tapping 
+traffic from a 20~Gbps router. We used PF\_RING to
 consume the 20~Gbps link, and feed it to a custom \textbf{detector} written in Rust. The
-detector processes all packets and watches for new registrations. It also
-forwards all packets sent to a (registered) phantom host address to the local
-\textbf{application} via an \texttt{iptables} DNAT rule that rewrites the destination IP,
-allowing the application to accept and respond to connections using the native
+detector processes all packets and watches for new registrations. Once a registration 
+is detected the local application is notified via an 
+out-of-band ZMQ~\cite{zmq} connection, which provides the
+registering client's IP address, the seed, and other configuration
+information. We note that this is not along a critical timing path for 
+proxying connections and no client packets are sent over ZMQ.
+
+The detectors forwards all packets destined for a (registered) phantom host address to the local
+\textbf{application} via tun interfaces and \texttt{iptables} DNAT rules that rewrite the destination IP,
+allowing the local application to accept and respond to connections using the native
 operating system's interface. Figure~\ref{fig:implementation} shows the overall
@@
 
-Our detector is a modified fork of the open source TapDance
-implementation~\cite{tapdance-source}.
+% Our detector is a modified fork of the open source TapDance
+% implementation~\cite{tapdance-source}.
 We implemented our detector in approximately 1,800 lines of Rust (compared to
@@
 registrations, but only one core will be ultimately responsible for processing all of
-the packets sent to a given phantom host, regardless of who or when it is sent.
-
-\subsection{Application}
-
-We implemented our application in about 500~lines of Golang. Though we note
-other protocols (e.g. obfsproxy or WebRTC) could be used as the application, we
-implemented a mask site mimicking application, that pretends to be a mask site
-when actively probed by the censor.
-
-The application accepts connections to phantom host addresses forwarded by the
-detector and rewritten to the local address using \texttt{iptables}.
-The application also receives out-of-band information about registrations from the
-detector via a ZMQ~\cite{zmq} connection, which informs the application of the
-registering client's IP address, the secret seed, and other configuration
-information passed by the client.
-
-Once the application accepts a connection, it initially acts as a transparent
-proxy to the mask site specified by the client during registration. The
-application parses the handshake, forwarding packets back and forth between
-client and mask site without modification, and extracting the server and client
-randoms. The application attempts to decrypt the first application data record
-from the client using a key derived from the secret seed, and client and server
-randoms. We use the uTLS library~\cite{utls} on both the application and client
-to allow us to change the TLS secrets being used after the handshake.
-
-\FigTapBandwidth
-
-If the decryption is successful, the application switches to forwarding
-(decrypted) data back and forth with a client-specified endpoint, such as a
-SOCKS proxy, which can multiplex multiple client connections over the single
-connection to the phantom host.
+the packets sent to a given phantom host, regardless of who sends it or when it is sent.
 
@@
 
-Our \scheme client is written in Golang, and uses the TapDance-like protocol
-(Section~\ref{sec:registration}) for
-registration. We note that this protocol should be harder for censors to observe
+Our \scheme client is written in Golang, and uses the refraction networking tagging
+schema (Section~\ref{sec:registration}) for
+registration. We note that this protocol will be more difficult for censors to observe
 than normal TapDance because it consists of only a single (complete) request, and the station does
-not have to spoof packets as the decoy used during registration, only passively
+not have to spoof packets as the decoy during registration, only passively
 observe them.
 
-We implemented two of the applications in our client: Obfuscated SSH used by
-Psiphon
-(Section~\ref{sec:ossh}) and our Mask Site protocol
-(Section~\ref{sec:mask-sites}). Our client signals which application it will use
-in the registration tag. The client also sends a flag that indicates if the
-client supports IPv6, to allow IPv4-only clients to only derive IPv4 phantom
-hosts.
+We implemented support for two of the transports in our client: Obfuscated SSH used by
+Psiphon (Section~\ref{sec:ossh}) and our TLS Mask Site protocol
+(Section~\ref{sec:mask-sites}). Our client signals which transport it will use
+in the registration tag along with a flag indicating whether the
+client supports IPv6, allowing IPv4-only clients to derive exclusively IPv4 phantom hosts.
 After registration, the client connects to the derived
-phantom host address, and speaks the specified application protocol, which
-tunnels a SOCKS connection between the client and Psiphon's backend servers,
-which proxy the client's connections.
-
-\if0
-In order to scale up to 20Gbps and beyond,
-one has to utilize multiple cores and employ load balancing.
-We use PF\_RING built-in load balancer \emph{zbalance} to efficiently
-distribute load between 4 cores.
-Our timeout is based on last IP address usage time, which prevents us from
-balancing load based on source IP address,
-as censor would be able to observe
-same destination IP address picking or not picking up
-depending on source IP address.
-To avoid such unusual behavior we balance on destination IP.
-Since PF\_RING does not feature load balancing based only on destination
-IP address, we made a custom implementation of this zbalance policy.
-
-TODO: say it's tested on 20 Gbps
-
-Implementation of the protocol includes 3 components:
-detector, proxy application, and client.
-Detector will parse the traffic, searching for registrations in
-tagged messages. After detector observes a registration, and negotiates with client
-a phantom host IP,
-all packets, that are sent to that phantom host IP,
-will be forwarded into a proxy application.
-
-\subsection{Registration phase}
-
-Each \scheme connection has 2 phases: registration, and usage of a phantom host.
-Registration starts with a handshake that is similar to a TapDance handshake,
-but initial HTTP request is complete.
-This allows a reachable site to provide a genuine response
-to a HTTP GET request of its index page.
-Since station does not need to produce a response,
-which significantly reduces complexity of a detector,
-that does not need to decrypt and inject packets into a TLS connection between
-client and a reachable site, as opposed to original TapDance.
-
-Client begins registration by establishing TLS connection
-to one of the reachable websites,
-path to which passes by our tap.
-Client uses a Chosen-Ciphertext Steganography technique~\cite{tapdance14} to manipulate
-plaintext of a first application data HTTP request
-to get desired ciphertext,
-and exchange keys with the station.
-After client writes Elligator-encoded~\cite{elligator} representative into the ciphertext at a static offset of 92 bytes from the end,
-that could be decoded using station's private key,
-to negotiate a 32 byte Elligator-encoded~\cite{elligator} shared secret between the client and the station.
-That shared secret is used as a seed of SHA-256 based key derivation function (HKDF),
-allowing station and client to derive an unlimited amount of shared secrets.
-
-Elligator representative on the wire is immediately followed by a 6 bytes long AES-GCM-encrypted
-fixed size payload(FSP), that holds flags and the size of the variable size payload(VSP).
-IV and key for encrypted of both FSP and VSP will be derived from HKDF.
-Once FSP is decrypted and the size of VSP is known, station can decrypt the VSP as well.
-VSP itself is a protobuf, which allows us to easily change the contents of VSP without risk of version mismatch, and currently contains 3 fields: version of configuration(which includes list of decoys), SNI of mask site, and a presumably blocked target host that client would like to get connected to.
-
-Client will sleep a short randomized period of time before attempting to establish connection to phantom host.
-This is done for 2 reasons: to break potentially observable interflow dependency with a phantom host connection being established right after a first application layer data packet sent to decoy,
-and to give station time.
-TODO: why does it need time?
-
-\subsection{Application phase}
-Client and station will use HKDF to derive 16 random bytes and use them to
-agree on a phantom host IP address, by applying a simple selection algorithm.
-Algorithm is as follows: first, flatten a list of pre-shared available IP
-addresses in various subnets into a single indexed list, then make a 128-bit
-integer out of 16 random bytes and divide it by the length
-of the flattened list, and use the remainder of this division as an index
-of the list to pick an IP address.
-
-To thwart active probing attacks, this application will then confirm
-that connecting client knows a secret, negotiated during the registration.
-If connecting client does know that secret, application will set up proxying,
-otherwise it may give censor a response, that acts like that this IP address
-is not an open proxy.
-
-TODO: describe MakeConnWithCompleteHandshake?
-
-Note that the detector and proxy application are only loosely coupled with each other,
-making it simple to replace one of them.
-We plan to take advantage of encrypted SNI, when it gets widely adopted,
-and replace our current proxy implementation with one that uses encrypted SNI
-and achieve improved unobservability properties, described in section~\ref{esni}.
-
-\subsection{Languages and LOC counts} % TODO: rename/restructure and complete section
-Client is written in Golang and follows the same API as standard TapDance does,
-which allows us to reuse existing TapDance CLI wrapper and Android application.
-
--Language choice (Rust, Go, minimal C)
--Open source (client, station and application)
-\fi
+phantom host address, and speaks the specified transport protocol, which
+tunnels between the client and either the mask site transport local to the 
+station or Psiphon's backend servers. A SOCKS connection can be initiated through
+this tunnel to allow for connection multiplexing.
+
+\subsection{Application \& Transports}
+
+We implemented our station-side application in about 500~lines of Golang. This includes
+support for OSSH (via integration with Psiphon) and Mask Sites, both specifiable by the client
+during registration. We note that support for other transport protocols (e.g. Obfs4 or WebRTC)
+can be added as development continues.
+
+\subsubsection{OSSH}
+
+Our \scheme implementation includes support for OSSH through integration with Psiphon. 
+Client traffic is forwarded to a Psiphon server by using  \scheme as a  
+transparent proxy. This symbiotic relationship provides \scheme with active 
+and passive probe resistance, while preventing censors from being able to inexpensively
+block Psiphon's backend servers individually.
+
+\subsubsection{Mask Sites}
+
+We implemented a mask site mimicking proxy, that pretends to be a mask site
+when actively probed by the censor. Once the station accepts accepts a connection 
+for a registered flow, it initially acts as a transparent
+proxy to a mask site specified by the client during registration. The
+application parses the handshake, forwarding packets back and forth between
+client and mask site without modification, extracting the server and client
+randoms. The application attempts to decrypt the first application data record
+from the client using a key derived from the secret seed, client, and server
+randoms. We use the uTLS library~\cite{utls} on both the application and client
+to allow us to change the TLS secrets being used after the handshake.
+
+\FigTapBandwidth
+
+If the decryption is successful, the application switches to forwarding
+(decrypted) data back and forth with a client-specified endpoint, such as a
+SOCKS proxy, which can provide multiple secure connections over the single
+connection to the phantom host.
 

### 2019-09-02 paper/paper.tex
Pass on Abstract, Introduction, and Conclusion.

@@
 deploying ISPs. Instead of using real websites as the decoy destinations
-for proxy connections, our scheme creates seemingly legitimate hosts
-on demand, at IP addresses where no web server exists.
+for proxy connections, our scheme connects to IP addresses where no 
+web server exists leveraging proxy functionality from the core of the network.
 These phantom hosts are difficult for a censor to distinguish from
@@
 
-\TODO{Phantom hosts are cheap to create, allowing for discardable or even one-time-use
-proxy servers}. This greatly increases the cost for censors to
+Phantom hosts are cheap to connect to, and greatly expand the 
+number of viable proxy endpoints that a censor must consider. This increases the cost for censors to
 block, as they must detect and block in real time. Meanwhile, even a censor that
-can detect 90\% of phantom hosts does not significantly increase the cost to the
-circumvention system, giving \scheme an advantage in the censor/circumventor
+could theoretically detect 90\% of phantom hosts with confidence does not significantly reduce the
+effectiveness of a circumvention system, giving \scheme an advantage in the censor/circumventor
 cat-and-mouse game.
-%TODO: don't need to hedge on IPv4 anymore..? could cut
+
 \scheme supports both IPv4 and IPv6,
@@
 ahead of time to identify addresses that change behavior.
-Because we fully control the transport connection, connections can live as
+Because we fully control the proxy transport, connections can live as
 long as needed, without the complexity faced by TapDance.
@@
 Refraction Networking schemes. Due to its modular design, different registration
-protocols and applications can be used. One obvious direction is to further
-study such alternatives. For instance, while we use a TapDance-like
-covert channel for registration, we could potentially cut down on the overhead of one-time
-registration by using port-knocking or using a Telex-style~\cite{telex11} tag (in the Client Hello rather than Application Data).
+protocols and proxy transports can be used interchangeably by the client. The
+flexibility of proxy transports and simplicity of registration allows \scheme to
+incorporate state of the art censorship circumvention tools and resist 
+nation-state censors.
+
+One obvious future direction is to study new options for registration and proxy transport. For instance, while 
+\scheme currently uses a refraction networking covert channel for registration, we could potentially 
+cut down on the overhead of one-time registration by using port-knocking or using a 
+Telex-style~\cite{telex11} tag (in the Client Hello rather than Application Data).
 
 \paragraph{Client-side applications}
-\TODO{On the application side}, \scheme provides an interesting opportunity to explore
+\scheme provides an interesting opportunity to explore
 \emph{client mimicking} phantom hosts. Rather than pretend to be a server (e.g.,
-a mask site), our application could connect back to a client after registration
+a mask site), our transport itself could connect to a newly registered client
 from the phantom host address. Possible protocols could include WebRTC, mentioned in
@@
 observability. While Slitheen offers ideal mimicry of decoys, it comes at a high
-cost of overhead. \scheme applications could implement Slitheen
-in order to perfectly mimic the mask site's latency, packet timings, and payload
+cost of overhead. \scheme transports such as mask site could implement Slitheen
+in order to perfectly mimic the decoy site's latency, packet timings, and payload
 sizes. In addition, careful choice of mask sites may allow for higher
@@
 stations at real ISPs.
-
-%\section{Conclusion}
-%.25 page
-
-%\TODO{Write (0.25 page}
 

### 2019-09-04 application/lib/buffer_conn.go
Moving liveness out of rust to go

@@ -26,9 +26,9 @@ func (bc *bufferedReaderConn) CloseWrite() error {
 		CloseWrite() error
 	}); ok {
 		return closeWriter.CloseWrite()
-	} else {
-		return errors.New("not a CloseWriter")
 	}
+	return errors.New("not a CloseWriter")
+
 }
 
 func (bc *bufferedReaderConn) CloseRead() error {
@@ -36,9 +36,9 @@ func (bc *bufferedReaderConn) CloseRead() error {
 		CloseRead() error
 	}); ok {
 		return closeReader.CloseRead()
-	} else {
-		return errors.New("not a CloseReader")
 	}
+	return errors.New("not a CloseReader")
+
 }
 
 func makeBufferedReaderConn(c net.Conn, r *bufio.Reader) *bufferedReaderConn {

### 2019-09-04 application/lib/conjure.go

@@ -1,0 +1,43 @@
+package lib
+
+import (
+	"crypto/sha256"
+
+	"golang.org/x/crypto/hkdf"
+)
+
+type conjureSharedKeys struct {
+	FspKey, FspIv, VspKey, VspIv, MasterSecret, DarkDecoySeed []byte
+}
+
+func genSharedKeys(sharedSecret []byte) (conjureSharedKeys, error) {
+	tdHkdf := hkdf.New(sha256.New, sharedSecret, []byte("tapdancetapdancetapdancetapdance"), nil)
+	keys := conjureSharedKeys{
+		FspKey:        make([]byte, 16),
+		FspIv:         make([]byte, 12),
+		VspKey:        make([]byte, 16),
+		VspIv:         make([]byte, 12),
+		MasterSecret:  make([]byte, 48),
+		DarkDecoySeed: make([]byte, 16),
+	}
+
+	if _, err := tdHkdf.Read(keys.FspKey); err != nil {
+		return keys, err
+	}
+	if _, err := tdHkdf.Read(keys.FspIv); err != nil {
+		return keys, err
+	}
+	if _, err := tdHkdf.Read(keys.VspKey); err != nil {
+		return keys, err
+	}
+	if _, err := tdHkdf.Read(keys.VspIv); err != nil {
+		return keys, err
+	}
+	if _, err := tdHkdf.Read(keys.MasterSecret); err != nil {
+		return keys, err
+	}
+	if _, err := tdHkdf.Read(keys.DarkDecoySeed); err != nil {
+		return keys, err
+	}
+	return keys, nil
+}

### 2019-09-04 application/lib/registration.go

@@ -1,32 +1,65 @@
 package lib
 
 import (
+	"fmt"
 	"log"
 	"net"
 	"os"
 	"sync"
 	"time"
+
+	"github.com/go-redis/redis"
+	pb "github.com/refraction-networking/gotapdance/protobuf"
 )
 
 type RegistrationManager struct {
 	registeredDecoys *RegisteredDecoys
 	Logger           *log.Logger
+	DDSelector       *DDIpSelector
 }
 
 func NewRegistrationManager() *RegistrationManager {
 	logger := log.New(os.Stdout, "", log.Lmicroseconds)
 
+	d, err := NewDDIpSelector()
+	if err != nil {
+		fmt.Errorf("Failed to create the DDIpSelector Object: %v\n", err)
+		return nil
+	}
 	return &RegistrationManager{
 		Logger:           logger,
 		registeredDecoys: NewRegisteredDecoys(),
+		DDSelector:       d,
 	}
 }
 
-func (regManager *RegistrationManager) AddRegistration(darkDecoyAddr [16]byte, d *DecoyRegistration) {
+func (regManager *RegistrationManager) NewRegistration(c2s *pb.ClientToStation, conjureKeys *conjureSharedKeys, flags [1]byte) (*DecoyRegistration, error) {
+
+	darkDecoyAddr, err := regManager.DDSelector.Select(
+		conjureKeys.DarkDecoySeed, uint(c2s.GetDecoyListGeneration()), c2s.GetV6Support())
+
+	if err != nil {
+		return nil, fmt.Errorf("Failed to select dark decoy IP address: %v", err)
+	}
+
+	reg := DecoyRegistration{
+		DarkDecoy:    darkDecoyAddr,
+		Covert:       c2s.GetCovertAddress(),
+		Mask:         c2s.GetMaskedDecoyServerName(),
+		MasterSecret: conjureKeys.MasterSecret,
+		Flags:        uint8(flags[0]),
+	}
+	return &reg, nil
+}
+func (regManager *RegistrationManager) AddRegistration(d *DecoyRegistration) {
+
+	registerForDetector(&DecoyRegistration)
+
+	darkDecoyAddr := d.DarkDecoy.String()
 	regManager.registeredDecoys.register(darkDecoyAddr, d)
 }
 
-func (regManager *RegistrationManager) CheckRegistration(darkDecoyAddr net.IP) *DecoyRegistration {
[…]

### 2019-09-04 application/lib/registration_test.go

@@ -1,0 +1,89 @@
+package lib 
+
+import (
+	"fmt"
+	"testing"
+	"net"
+	pb "github.com/refraction-networking/gotapdance/protobuf"
+	"github.com/golang/protobuf/proto"
+)
+
+func mockReceiveFromDetector() (pb.ClientToStation, conjureSharedKeys, [1]byte){
+	clientToStationBytes := []byte{ 
+		0x10, 0x9a, 0x04, 0x18, 0x0b, 0xa2, 0x01, 0x0e, 0x35, 0x32, 0x2e, 0x34, 0x34, 0x2e, 0x37,
+		0x33, 0x2e, 0x36, 0x3a, 0x34, 0x34, 0x33, 0xb0, 0x01, 0x00, 0xa2, 0x06, 0x01, 0x00}
+	sharedSecret := []byte{
+		0x54, 0x14, 0xc7, 0x34, 0xad, 0x5d, 0xc5, 0x3e, 0x6b, 0x56, 0xa7, 0xbb, 0x47, 0xce, 0x69, 0x5a, 
+		0x14, 0xa3, 0xef, 0x07, 0x6a, 0x3d, 0x5a, 0xce, 0x9c, 0xbf, 0x3b, 0x4d, 0x12, 0x70, 0x6b, 0x73}
+	flags := [1]byte{0x01}
+
+	clientToStation := &pb.ClientToStation{}
+	err := proto.Unmarshal(clientToStationBytes, clientToStation)
+	if err != nil {
+		fmt.Printf("Failed to unmarshal ClientToStation protobuf\n")
+	}
+
+	conjureKeys, err := genSharedKeys(sharedSecret)
+
+	return *clientToStation, conjureKeys, flags
+}
+
+
+func testEqualRegistrations(reg1 *DecoyRegistration, reg2 *DecoyRegistration) bool {
+	return true
+}
+
+func TestCreateDecoyRegistration(t *testing.T) {
+	rm := NewRegistrationManager()
+
+	c2s, keys, flags := mockReceiveFromDetector()
+
+	newReg, err := rm.NewRegistration(&c2s, &keys, flags)
+	if err != nil {
+		t.Fatalf("Registration failed: %v", err)
+	}
+
+	expectedReg := DecoyRegistration{}
+
+	if !testEqualRegistrations(newReg, &expectedReg) {
+		t.Fatalf("Bad registration Created")
+	}
+}
+
[…]

### 2019-09-04 application/main.go

@@ -1,6 +1,7 @@
 package main
 
 import (
+	"encoding/binary"
 	"bytes"
 	"fmt"
 	"log"
@@ -10,6 +11,8 @@ import (
 
 	dd "./lib"
 	zmq "github.com/pebbe/zmq4"
+	"github.com/golang/protobuf/proto"
+	pb "github.com/refraction-networking/gotapdance/protobuf"
 )
 
 func getOriginalDst(fd uintptr) (net.IP, error) {
@@ -74,21 +77,61 @@ func get_zmq_updates(regManager *dd.RegistrationManager) {
 
 	for {
 
-		ipAddr, reg, err := recieve_zmq_message(sub)
-		if err != nil {
+		newReg, err := recieve_zmq_message(sub, regManager)
+		if err != nil || newReg == nil {
 			continue
 		}
 
-		regManager.AddRegistration(*ipAddr, reg)
-		logger.Printf("new registration: {dark decoy address=%v, covert=%v, mask=%v, flags=0x%02x}\n",
-			net.IP(ipAddr[:]).String(), reg.Covert, reg.Mask, reg.Flags)
+		if !newReg.PhantomIsLive() {
+			regManager.AddRegistration(newReg)
+			logger.Printf("new registration: {dark decoy address=%v, covert=%v, mask=%v, flags=0x%02x}\n",
+				net.IP(ipAddr[:]).String(), reg.Covert, reg.Mask, reg.Flags)
+		}
 	}
 }
 
-func recieve_zmq_message(sub *zmq.Socket) (*[16]byte, *dd.DecoyRegistration, error) {
-	var masterSecret [48]byte
-	var ipAddr [16]byte
-	var covertAddrLen, maskedAddrLen, flags [1]byte
+func recieve_zmq_message(sub *zmq.Socket, regManager *RegistrationManager) (*dd.DecoyRegistration, error) {
+	// var sharedSecret [32]byte
+	// var ipAddr []byte
+	// var covertAddrLen, maskedAddrLen [1]byte
+
+	var sharedSecret [32]byte
+	var fixedSizePayload [6]byte
+	var flags [1]byte
+
+	msg, err := sub.RecvBytes(0)
+	if err != nil {
+		logger.Printf("error reading from ZMQ socket: %v\n", err)
+		return nil, nil, err
+	}
+	if len(msg) < 32 + 6 + 1 + 16 {
+		logger.Printf("short message of size %v\n", len(msg))
[…]

### 2019-09-04 src/elligator.rs

@@ -37,9 +37,120 @@ fn extract_stego_bytes(in_buf: &[u8], out_buf: &mut [u8])
     out_buf[2] = ((x) & 0xff) as u8;
 }
 
+
+// Returns either (Shared Secret, Fixed Size Payload, Variable Size Payload) or Box<Error>
+//      Boxed error becuase size of return isn't known at compile time 
+pub fn extract_payloads(secret_key: &[u8], tls_record: &[u8]) -> (Result<([u8; 32], [u8; FSP::LENGTH], Vec<u8>), Box<Error>>)
+{
+    if tls_record.len() < 112 // (conservatively) smaller than minimum request
+    {
+        let err: Box<Error> = From::from("small tls record".to_string());
+        return Err(err);
+    }
+
+    // This fn indexes a lot of slices with computed offsets; panics possible!
+    let result = panic::catch_unwind(||
+        {
+            // TLS record: 1 byte of 'content type', 2 of 'version', 2 of 'length',
+            //               and then [length] bytes of 'payload'
+            //======================================================================
+            //let content_type = tls_record[0];
+            //let tls_version = u8u8_to_u16(tls_record[1], tls_record[2]);
+
+            let tls_payload = &tls_record[5..tls_record.len()];
+            //======================================================================
+            // Starting from 92 byte from the end of the TLS payload extract
+            // stego'd data from each block of 4 bytes (if the payload length isn't
+            // a multiple of 4, just ignore the tail). Continue until we have run
+            // out of input data, or room in the output buffer.
+            let mut stego_repr_and_fsp: [u8; REPRESENTATIVE_AND_FSP_LEN] = [0; REPRESENTATIVE_AND_FSP_LEN];
+            let mut in_offset: usize = tls_payload.len() as usize - 92;
+            let mut out_offset: usize = 0;
+            while in_offset < (tls_payload.len() - 3) as usize &&
+                out_offset < (REPRESENTATIVE_AND_FSP_LEN - 2) as usize
+                {
+                    extract_stego_bytes(&tls_payload[in_offset..in_offset + 4],
+                                        &mut stego_repr_and_fsp[out_offset..out_offset + 3]);
+                    in_offset += 4;
+                    out_offset += 3;
+                }
+
+            // client should randomize first bit, here we set it back to 0
[…]

### 2019-09-04 src/process_packet.rs

@@ -2,6 +2,7 @@ use libc::size_t;
 use std::os::raw::c_void;
 use std::panic;
 use std::slice;
+use std:: str;
 
 use pnet::packet::Packet;
 use pnet::packet::ethernet::{EthernetPacket, EtherTypes};
@@ -23,6 +24,7 @@ use signalling::ClientToStation;
 
 
 const TLS_TYPE_APPLICATION_DATA: u8 = 0x17;
+const SPECIAL_PACKET_PAYLOAD: &'static str = "'This must be Thursday,' said Arthur to himself, sinking low over his beer. 'I never could get the hang of Thursdays.'";
 //const SQUID_PROXY_ADDR: &'static str = "127.0.0.1";
 //const SQUID_PROXY_PORT: u16 = 1234;
 
@@ -211,15 +213,17 @@ impl PerCoreGlobal
 
         if  is_tls_app_pkt(&tcp_pkt) {
             match self.check_dark_decoy_tag(&flow, &tcp_pkt) {
-                Some(dd_flow) => {
-                    debug!("New Dark Decoy Flow {} negotiated in {},", dd_flow, flow);
-                    self.flow_tracker.mark_dark_decoy(&dd_flow);
+                true => {
+                    debug!("New Dark Decoy registration detected in {},", flow);
+                    // self.flow_tracker.mark_dark_decoy(&dd_flow);
                     // not removing flow from stale_tracked_flows for optimization reasons:
                     // it will be removed later
                 },
-                None => {}
+                false => {}
             };
             self.flow_tracker.stop_tracking_flow(&flow);
+        }else {
+            self.check_connect_test_str(&flow, &tcp_pkt);
         }
     }
 
@@ -250,104 +254,128 @@ impl PerCoreGlobal
 
     fn check_dark_decoy_tag(&mut self,
                             flow: &Flow,
-                            tcp_pkt: &TcpPacket) -> Option<FlowNoSrcPort>
+                            tcp_pkt: &TcpPacket) -> bool
     {
         self.stats.elligator_this_period += 1;
         match elligator::extract_payloads(&self.priv_key, &tcp_pkt.payload()) {
             Ok(res) => {
-                // res.0 => HKDFKeys
+                // res.0 => shared secret
                 // res.1 => Fixed sixe payload
                 // res.2 => variable size paylaod (c2s)
-                let fixed_size_payload: FSP = res.1;
-
-                let mut c2s = match protobuf::parse_from_bytes::<ClientToStation>
-                    (&res.2) {
[…]

### 2019-09-04 src/util.rs

@@ -188,7 +188,7 @@ pub struct FSP {
 impl FSP {
     const UNUSED_BYTES: usize = 3;
     const USED_BYTES: usize = 3;
-    const LENGTH: usize = 6;
+    pub const LENGTH: usize = 6;
     pub const FLAG_PROXY_HEADER: u8 = 0x4;
     pub const FLAG_UPLOAD_ONLY:  u8 = (1 << 7);
 	pub const FLAG_USE_TIL:      u8 = (1 << 0);
@@ -214,6 +214,12 @@ impl FSP {
     pub fn to_vec(&self) -> &Vec<u8> {
         let vec = &self.bytes;
         return vec
+    }
+
+    pub fn to_bytes(&self)-> [u8; FSP::LENGTH] {
+        let mut array = [0; FSP::LENGTH];
+        array.copy_from_slice(&self.bytes);
+        return array
     }
 
     pub fn use_proxy_header(&self) -> bool {

### 2019-09-20 paper/paper.tex
Update ACM format, add authors and acknowledgements

@@
-\documentclass[sigconf,anonymous]{acmart}
-%\usepackage{usenix2019_v3}
-
-\AtBeginDocument{%
-  \providecommand\BibTeX{{%
-    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}
-
-%% Rights management information.  This information is sent to you
-%% when you complete the rights form.  These commands have SAMPLE
-%% values in them; it is your responsibility as an author to replace
-%% the commands and values with those provided to you when you
-%% complete the rights form.
-%% \setcopyright{acmcopyright}
-%% \copyrightyear{2019}
-%% \acmYear{2019}
-%% \acmDOI{10.1145/1122445.1122456}
-
-%% %% These commands are for a PROCEEDINGS abstract or paper.
-%% \acmConference[CCS '19]{CCS '19: ACM Conference on Computer and Communications
-%% Security}{November 11--15, 2019}{London, UK}
-%% \acmBooktitle{CCS '19: ACM Symposium on Computer and Communications Security,
-%%   November 11--15, 2019, London, UK}
-%% \acmPrice{0.00}
-%% \acmISBN{978-1-4503-9999-9/18/06}
-
-\fancyhf{} % Remove fancy page headers                                                                
-\fancyhead[C]{Anonymous submission \#610 to ACM CCS 2019}
-\fancyfoot[C]{\thepage}
-
-\setcopyright{none} % No copyright notice required for submissions                                     
-\acmConference[Anonymous Submission to ACM CCS 2019]{ACM Conference on Computer and Communications Security}{Due 15 May 2019}{London, TBD}
-\acmYear{2019}
-
-\settopmatter{printacmref=false, printccs=true, printfolios=true}
-
-% to be able to draw some self-contained figs
-\usepackage{tikz}
-%\usepackage{parskip}
-%\usepackage{mathptmx}\renewcommand{\ttdefault}{cmtt}
-\usepackage{amsmath}
+\documentclass[sigconf]{acmart}
+
+\settopmatter{printacmref=true}
+
+\usepackage[utf8]{inputenc}
+\usepackage{microtype}
+\usepackage{enumitem}
+\usepackage{graphicx}
+\usepackage{tabularx}
+\usepackage[font=small]{caption}
+\usepackage{subcaption}
+\usepackage{xspace}
+\usepackage{dblfloatfix} % magic
+\usepackage{balance}
+\usepackage{paralist}
 \usepackage{wasysym}
-%\setlength{\parskip}{1pt} % 1ex plus 0.5ex minus 0.2ex}
-%\setlength\parskip{1pt}
-\usepackage{graphicx} % http://ctan.org/pkg/graphicx
-\usepackage{booktabs} % http://ctan.org/pkg/booktabs
-\usepackage{xparse}   % http://ctan.org/pkg/xparse%don't print date
+\usepackage{xparse}
 \NewDocumentCommand{\rot}{O{45} O{1em} m}{\makebox[#2][l]{\rotatebox{#1}{#3}}}%
-\include{figures}
-\usepackage{subcaption}
-\usepackage{cleveref}
-\usepackage{microtype}
-\SetExtraKerning{encoding=*,font=*}{\textemdash={120,120}} % Add space around emdashes
-\usepackage[font=small]{caption}
-\microtypecontext{spacing=nonfrench}
-%\usepackage{subcaption}
-\usepackage{paralist}
-\usepackage{xspace}
-\usepackage{soul}
-\newcommand{\note}[2]{\hl{[\textbf{#1:} #2]}\xspace}
-\newcommand{\nikita}[1]{\note{nikita}{#1}}
-\newcommand{\TODO}[1]{\hl{TODO: #1}\xspace}
-\newcommand{\TK}{\hl{TK}\xspace}
-
-% Slight JAH fix to stop URLs from breaking after ``http:''
+\urlstyle{rm}
+
+% From CCS template:
+\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08emT\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
+% Fix URL hyphenation (AH 12/2008)
 \def\UrlBreaks{\do-\do\.\do\@\do\\\do\!\do\_\do\|\do\;\do\>\do\]%
@@
 \def\UrlBigBreaks{\do\:\do\/}%
-\urlstyle{rm}
-
-\widowpenalty=10000
-\clubpenalty=10000
+
+\newcommand{\todo}[1]{}
+\renewcommand{\todo}[1]{{\color{red} TODO: {#1}}}
+\newcommand{\TODO}[1]{}
+\renewcommand{\TODO}[1]{{\color{red} TODO: {#1}}}
+\newcommand{\TK}{}
+\renewcommand{\TK}{{\color{red}TK}\xspace}
 
@@
 
+\copyrightyear{2019}
+\acmYear{2019}
+\acmConference[CCS '19]{2019 ACM SIGSAC Conference on Computer and Communications Security}{November 11--15, 2019}{London, United Kingdom}
+\acmBooktitle{2019 ACM SIGSAC Conference on Computer and Communications Security (CCS '19), November 11--15, 2019, London, United Kingdom}
+\acmPrice{15.00}
+\acmDOI{10.1145/3319535.3363218}
+\acmISBN{978-1-4503-6747-9/19/11}
+\setcopyright{rightsretained}
+
+\include{figures}
+
 \begin{document}
 
-\date{}
-
-% make title bold and 14 pt font (Latex default is non-bold, 16 pt)
-%\title{\Large \bf Dark Decoys:
-%  Conjuring Proxies from Unused Address Space}
+\fancyhead{} % From CCS template.
+
 \title{Conjure: Summoning Proxies from Unused Address Space}
 
-%\author{Anonymized for review}
-%for single author (just remove % characters)
-%\author{
-%{\rm Your N.\ Here}\\
-%Your Institution
-%\and
-%{\rm Second Name}\\
-%Second Institution
-%% copy the following lines to add more authors
-%% \and
-%% {\rm Name}\\
-%%Name Institution
-%} % end author
-
-%\newcommand{\scheme}{Dark Decoys\xspace}
+\author{Sergey Frolov}\affiliation{University of Colorado Boulder}
+\author{Jack Wampler}\affiliation{University of Colorado Boulder}
+\author{Sze Chuen Tan}\affiliation{UIUC}
+\author{J. Alex Halderman}\affiliation{University of Michigan}
+\author{Nikita Borisov}\affiliation{UIUC}
+\author{Eric Wustrow}\affiliation{University of Colorado Boulder}
+
 \newcommand{\scheme}{Conjure\xspace}
@@
 \end{abstract}
+
+\begin{CCSXML}
+  <ccs2012>
+  <concept>
+  <concept_id>10003033.10003083.10003014</concept_id>
+  <concept_desc>Networks~Network security</concept_desc>
+  <concept_significance>300</concept_significance>
+  </concept>
+  <concept>
+  <concept_id>10003456.10003462.10003480</concept_id>
+  <concept_desc>Social and professional topics~Censorship</concept_desc>
+  <concept_significance>300</concept_significance>
+  </concept>
+  </ccs2012>
+\end{CCSXML}
+
+\ccsdesc[300]{Networks~Network security}
+\ccsdesc[300]{Social and professional topics~Censorship}
 
@@
 
-\bibliographystyle{plain}
-\small
+\begin{acks}
+  The authors thank the incredible partner organizations that have
+  made deployment of Refraction Networking a reality, especially Merit
+  Network and Psiphon. We also thank \TODO{anyone else?} the
+  University of Colorado IT Security and Network Operations
+  staff. This material is based in part upon work supported by the
+  U.S. National Science Foundation under Awards \TODO{others?}
+  CNS-1518888 and OAC-1925476.
+\end{acks}
+
+\bibliographystyle{ACM-Reference-Format}
+\balance
 \bibliography{biblio}
 
-\appendix
-
-\input{rebuttal}
+%\appendix
+%\input{rebuttal}
 

### 2019-09-24 paper/paper.tex
Update paper.tex

@@
 
+\subsection{Performance}
+
 We evaluated the performance of a client from an India-based VPS,
@@
 \subsubsection{IPv4}
-While \scheme composes well with IPv6, we can also support IPv4, with some
-careful caveats. First, in IPv4, there are substantially fewer addresses,
-allowing censors to easily \textbf{enumerate network prefixes} that pass by the ISP
-station to look for legitimate sites to whitelist. To address this, \scheme
+While \scheme works best with IPv6, it can also support IPv4, with some
+careful caveats.
+
+First, in IPv4, there are substantially fewer addresses,
+allowing censors to potentially \textbf{enumerate all the network prefixes}
+that pass by the ISP station, compose the list of innocuous sites,
+and block other websites, as they are being summoned by \scheme.
+To address this, \scheme
 phantom hosts are firewalled from all IPs other than the client that registered
-them. Thus, censors would not see them in an enumerating scan from a single
-vantage point before registration (when they do not exist), and blocking hosts
-not seen in such a scan would block legitimate hosts that firewalled themselves
-off from all but a few IPs. % Such firewall behavior is a best practice for...
+them, providing a reason why the address hasn't been seen in an enumerating scan,
+conducted by a censor from a single vantage point.
 Censors could attempt to scan the network from \emph{all} potential client
@@
 makes it possible for a censor to \textbf{pre-image the hash} used to derive the phantom
-address from the seed. Even with the /16 of IPs and all 65K ports, a censor need
-only test an expected $2^{32}$ possible seeds to find one that would allow it
-to register for that phantom address. The censor could then register a suspected
+address from the seed. Even with the /16 of IPs and all 65K ports, in order to
+find a seed for any desired address a censor
+needs to only test an expected $2^{32}$ possible seeds.
+The censor could then register a suspected
 address, and see if it provides proxy access. If it does, the censor learns
@@
 registration. This also serves to prevent abuse by attackers that attempt
-to use the \scheme station to interfere with legitimate services.
+to use the \scheme station to interfere with innocuous services.
 
@@
 
-\subsubsection{IPv6 address entropy}
+\subsubsection{IPv6}
 \FigIpBits
 
-In IPv6 \scheme, we no longer need to worry about address enumeration or
-pre-image attacks. Our ISP routes a /32 IPv6 prefix, which provides $2^{96}$ potential
+In IPv6 \scheme address enumeration and pre-image attacks are infeasible due to a large amount of
+potential IP addresses.
+Our ISP routes a /32 IPv6 prefix, which provides $2^{96}$ potential
 phantom host IP addresses. However, IPv6 addresses often have long runs of 0

### 2019-09-25 paper/paper.tex
bib fixes and client github footnote

@@
 Networking protocol that overcomes these challenges while retaining
-TapDance's ISP-friendly deployment requirements.
+TapDance's ISP-friendly deployment requirements~\footnote{
+We have released the open source implementation of the Conjure client at 
+\url{https://github.com/refraction-networking/gotapdance/tree/dark-decoy}.}.
 Our key innovation is an architecture that avoids

### 2019-09-25 application/lib/registration.go
fix ip registration format

@@ -138,7 +138,7 @@ func registerForDetector(reg *DecoyRegistration) {
 	if err != nil {
 		fmt.Printf("couldn't connect to redis")
 	} else {
-		client.Publish(DETECTOR_REG_CHANNEL, reg.DarkDecoy.String())
+		client.Publish(DETECTOR_REG_CHANNEL, string(reg.DarkDecoy.To4()))
 		client.Close()
 	}
 }

### 2019-09-25 application/lib/registration_test.go

@@ -117,8 +117,11 @@ func TestRegisterForDetector(t *testing.T) {
 		t.Logf("Read %s from subscriber\n", msg.Payload)
 	}
 
+	// reconstruct IP from message
+	ip_string := fmt.Sprintf("%d.%d.%d.%d", msg.Payload[0], msg.Payload[1], msg.Payload[2], msg.Payload[3])
+
 	// check IP equality
-	if reg.DarkDecoy.Equal(net.ParseIP(msg.Payload)) == false {
-		t.Fatalf("Expected %v, got %v", reg.DarkDecoy, msg.Payload)
+	if reg.DarkDecoy.Equal(net.ParseIP(ip_string)) == false {
+		t.Fatalf("Expected %v, got %v", reg.DarkDecoy, net.ParseIP(msg.Payload))
 	}
 }

### 2019-09-25 paper/paper.tex
5.1 pass

@@
 
-To achieve high-performance necessary to operate at 20~Gbps, we used
-PF\_RING~\cite{pfring} to load balance incoming packets over 4~CPU cores. PF\_RING
-supports balancing across cores based on flow (5-tuple) or source and
-destination IPs. However, both of these options present engineering challenges
-for \scheme that we must overcome.
-One issue is that registrations could be processed on a
-different core than the packets sent to that specific phantom host address. For
-instance, a client could have its registration handled by Core 1, while its
-packets to the phantom host address end up on Core 3, which doesn't know about the
-original registration.
-
-To address this, we used Redis~\cite{redis} to allow each process to broadcast
+To achieve performance needed to operate at 20~Gbps, we used
+PF\_RING~\cite{pfring} to load balance incoming packets across 4~CPU cores,
+which each run a dedicated detector process.
+PF\_RING supports load balancing packets based on
+either their flow (5-tuple), or their source/destination IPs, which allows
+connections to be processed by a single process without
+requiring communication across independent cores.
+
+However, in \scheme, registration connections and phantom proxy connections
+could end up being load balanced to different cores. In order for an individual
+detector process to forward phantom proxy connections to the application, it must
+know about the original registration, even if that registration was observed by a
+different core.
+To address this, we used Redis~\cite{redis} to allow each core's process to broadcast
 (publish) newly registered decoys to the other cores so they can
-add them to their local list of registered phantom host addresses.
-However, this introduces two new problems. First, a core might add a
-registration \emph{after} it has already received and processed packets destined
-for the specified phantom host. This typically isn't a problem when running on a
-single core, as packets are processed sequentially. Second, each core may
-timeout each phantom host at different times, potentially leading to differing
-behavior that is visible to a censor. For instance, if we used the
-source/destination IPs to load balance, a censor's packets to a phantom host could
-be processed by a different core than the client. If the censor waits for the
-known timeout before sending a probe, its core may have timed out that phantom host, while the client's core has refreshed the timeout of the phantom host due
-to active use.
-
-To address the first issue of asynchronous cores, we force the client to delay sending its connection
-to the phantom host until a short time after registration. In practice, we force
-the client to wait until the registration decoy responds before starting a
-connection with the registered phantom host. While the decoy response is
-unrelated to the station's processing, it serves as a conservative way to know
-the registration has had time to reach the station.
-
-To address the second issue of differing core timeouts, we implemented a new
+add them to their local list of registered phantom host addresses. Broadcasting
+registrations across all cores ensures that each detector process sees all
+registrations, and can forward phantom proxy connections accordingly.
+
+A second problem arises when considering how to \emph{timeout} unused phantom proxies
+in the detector. When a phantom proxy is timed out, it no longer responds to any
+active probes. A naive implementation might simply have each core timeout unused
+phantom proxies after they go unused for a set time. However, this could leave
+one core (that sees active proxy use) forwarding packets to the application, while
+other cores (that do not see use) would timeout the proxy. A censor could probe the
+phantom proxy and observe this behavior: if the censor's packets are processed
+on a forwarding core, the censor can establish a TCP connection with the phantom
+application. Otherwise, if they are processed on a timed out core, the censor's packets
+will be ignored. Through multiple connections, the censor could use this strange
+behavior (of intermittent TCP response) to identify and block potential phantom
+proxies.
+
+To address this issue of differing core timeouts, we implemented a new
 load-balancing algorithm in
-PF\_RING to select the core based solely on the destination IP address of the
-packet. We still must use Redis to tell all of the cores of new
-registrations, but only one core will be ultimately responsible for processing all of
-the packets sent to a given phantom host, regardless of who sends it or when it is sent.
+PF\_RING to select the core based only off the destination IP address of a
+packet. This means that \emph{all} packets sent to a particular phantom proxy address
+are processed by the same detector core, which allows the phantom proxy's timeout state
+to be consistent regardless of what source attempts to connect to it.
+%We still must use Redis to tell all of the cores of new
+%registrations, but only one core will be ultimately responsible for processing all of
+%the packets sent to a given phantom host, regardless of who sends it or when it is sent.
 

### 2019-09-25 paper/paper.tex
remove ack todos

@@
   made deployment of Refraction Networking a reality, especially Merit
-  Network and Psiphon. We also thank \TODO{anyone else?} the
+  Network and Psiphon. We also thank the
   University of Colorado IT Security and Network Operations
   staff. This material is based in part upon work supported by the
-  U.S. National Science Foundation under Awards \TODO{others?}
+  U.S. National Science Foundation under Awards
   CNS-1518888 and OAC-1925476.

### 2019-09-25 paper/background.tex
minor edits from Nikita

@@
 handshake with a destination site, sends an encrypted web request, and
-receives an encrypted response. In refraction routing, at least one direction
+receives an encrypted response. In Refraction Networking, at least one direction
 of this exchange is observed by a \emph{refraction station}, deployed at

### 2019-09-25 paper/figures.tex
minor edits from Nikita

@@
         IP address (or connect to all possible phantom IPs) before the active probe traffic gets to the local application. 
-        At this point their connection will fail in a manor specific to the transport that the client specified
+        At this point their connection will fail in a manner specific to the transport that the client specified
         in the registration (e.g. connecting to OSSH without knowledge of the pre-shared secret).}
@@
 
-    \caption{\textbf{First generation systems}\rm for Refraction Networking, such as Telex and Cirripede, operated as inline network elements, with the ability to observe traffic and block specific flows.
+    \caption{\textbf{First generation systems}\rm\ for Refraction Networking, such as Telex and Cirripede, operated as inline network elements, with the ability to observe traffic and block specific flows.
 ISPs worried that if the inline element failed, it could bring down the network.\looseness=-1}
@@
 
-    \caption{\textbf{TapDance}\rm is a second-generation Refraction Network scheme that operates without flow blocking, needing only to passively observe traffic and inject packets.
+    \caption{\textbf{TapDance}\rm\ is a second-generation Refraction Network scheme that operates without flow blocking, needing only to passively observe traffic and inject packets.
 TapDance has recently been deployed at a mid-size ISP, but the techniques used to silence the decoy site and participate in the client--decoy TCP connection mid-stream add significant complexity, performance bottlenecks, and detection risk.}

### 2019-09-25 paper/paper.tex
minor edits from Nikita

--- 2019-09-25 paper/paper.tex
@@
 Upon recognizing a steganographic signal from the client, the ISP modifies the connection response to return censored content requested by the user.
-Censors cannot easily block access without also blocking legitimate connections to the decoy sites---collateral damage that may be prohibitive for censors if Refraction is widely deployed~\cite{robinson2013collateral}.
+Censors cannot easily block access without also blocking legitimate connections to the decoy sites---collateral damage that may be prohibitive for censors if Refraction Networking is widely deployed~\cite{robinson2013collateral}.
 
@@
 In addition, \scheme provides significantly
-more flexibility than existing Refraction protocols, allowing maintainers to
+more flexibility than existing Refraction Networking protocols, allowing maintainers to
 respond to future censor techniques.
@@
 the addresses that are phantom hosts, and block only those. We note this
-assumption supposes that the deployment is large enough to deter routing around
-decoy attacks~\cite{rad12,true-cost-rad}.
+assumption supposes that the censor does not mount effective routing
+decoy attacks~\cite{rad12,true-cost-rad}; we discuss these attacks further in Section~\ref{sec:placement-rad}.
 
@@
 
-Similar to previous schemes, our design does not require expensive in-line
+Similar to TapDance~\cite{tapdance14}, our design does not require expensive in-line
 flow blocking and is accomplished with only a passive tap at the ISP, imparting
@@
 single vantage point would not reveal hosts that only respond to specific IPs
-(e.g. firewalled subnets).
+(e.g., firewalled subnets).
 
@@
 Censors could still try to actively probe with guesses for the SNI,
-servers could respond with generic ``Unknown SNI'' errors. If such responses
+but servers could respond with generic ``Unknown SNI'' errors. If such responses
 were common for incorrect SNI, the censor's efforts to identify phantom hosts
@@
 
-\textit{Nearby sites --} pick websites that are
+\textit{Nearby sites ---} pick websites that are
 legitimately hosted in or near the network of the phantom host addresses
@@
 
-\textit{Popular sites --} choose mask sites from a list such as the Alexa
+\textit{Popular sites ---} choose mask sites from a list such as the Alexa
 top site~\cite{alexa-top500} list. Although it may be wise to avoid
@@
 
-\textit{Passive observation --} collect sites by passively observing DNS requests, TLS
+\textit{Passive observation ---} collect sites by passively observing DNS requests, TLS
 SNI, or certificates that pass by at the network tap. This would allow for building a realistic set

### 2019-09-26 paper/paper.tex
more minor edits

@@
 \texttt{obfs3}, the more recent probe-resistant \texttt{obfs4} remains a viable
-proxy in the country
+proxy in the country.\footnote{E.g., \url{https://metrics.torproject.org/userstats-bridge-combined.html?start=2019-06-27&end=2019-09-25&country=cn} shows \texttt{obfs4} clients from China successfully using Tor.}
 
@@
 One obvious future direction is to study new options for registration and proxy transport. For instance, while 
-\scheme currently uses a refraction networking covert channel for registration, we could potentially 
+\scheme currently uses a TapDance- style covert channel for registration, we could potentially 
 cut down on the overhead of one-time registration by using port-knocking or using a 
-Telex-style~\cite{telex11} tag (in the Client Hello rather than Application Data).
+Telex-style~\cite{telex11} tag (in the ClientHello rather than Application Data).
 

### 2019-09-26 paper/paper.tex
Refraction Networking

@@
 Networking protocol that overcomes these challenges while retaining
-TapDance's ISP-friendly deployment requirements~\footnote{
+TapDance's ISP-friendly deployment requirements\footnote{
 We have released the open source implementation of the Conjure client at 
@@
 \label{sec:registration}
-We use a form of refraction networking similar to Tapdance to register directly with
+We use a form of Refraction Networking similar to Tapdance to register directly with
 the station, though \scheme registration is significantly simpler and more difficult
@@
 
-Our \scheme client is written in Golang, and uses the refraction networking tagging
+Our \scheme client is written in Golang, and uses the Refraction Networking tagging
 schema (Section~\ref{sec:registration}) for

### 2019-09-26 paper/background.tex
refraction networking -> Refraction Networking

@@
 
-Refraction networking operates by injecting covert communication inside a
+Refraction Networking operates by injecting covert communication inside a
 client's HTTPS connection with a reachable site, also known as a decoy site. In
@@
 
-One of the key challenges for refraction networking is in taking over a session.
+One of the key challenges for Refraction Networking is in taking over a session.
 The station must start responding to the client's traffic as if it were the decoy destination, and at the same time prevent the destination from sending its own responses back to the client.
@@
 
-\paragraph{Registration Signal} In all implementations of refraction networking, a client must send a covert signal to the station to initiate communication.
+\paragraph{Registration Signal} In all implementations of Refraction Networking, a client must send a covert signal to the station to initiate communication.
 This covert signal is  embedded inside communication fields that must be indistinguishable from random by a censor without access to a secret/private key available to the station.

### 2019-09-26 paper/figures.tex
figure caption

@@
     \caption{\textbf{\scheme Operations}\,---\,\rm%
-        A \scheme session is constructed in two pieces. First a client registers by sending a tls connection
-        to the Decoy host (see Figure 2c) with a steganographically tagged payload.
-        This registration contains the true address that the client would like to connect to and a seed 
-        which the \scheme station uses to derive the Phantom IP address for the session(green dashed flow). 
-        Second The client derives the same 
-        Phantom IP address and connects directly to it using the proxy protocol (e.g. OSSH) that they specified in
-        their registration (purple dotted flow). The station identifies registered packets by source IP, destination IP,
-        and destination port (client IP, phantom IP, and phantom port respectively). The traffic is passed 
-        to a proxy server handling the specific proxy specified by the client then redirected to the 
-        covert address that the client indicated in their registration. 
+        A \scheme session is constructed in two pieces. First a client registers by sending a TLS connection
+        to the decoy host (see Figure 2c) with a steganographically tagged payload.
+        This registration contains the true ``covert'' address that the client would like to connect to and a seed 
+        which the \scheme station uses to derive the Phantom IP address for the session (green dashed flow). 
+        Second, the client derives the same 
+        Phantom IP address and connects directly to it using the proxy protocol (e.g. OSSH) specified in
+        the registration (purple dotted flow). The station identifies registered packets by source IP, destination IP,
+        and destination port (client IP, phantom IP and port respectively). The traffic is passed 
+        to a proxy server handling the specific proxy protocol, which ultimately proxies traffic to
+        the covert address.
         \\\hspace{\textwidth}
-        Secrets for the individual proxy services are shared out of band or derived from the shared secret 
-        between the client and the station such that an adversary attempting to probe a connection will be
-        unable to connect to the proxy service. 
+        Secrets for the individual application proxy service are shared out of band or derived from the secret seed shared
+        between client and station during registration, preventing an adversary from being
+        able to successfully connect to the application in follow up probes.
     }

### 2019-09-26 paper/paper.tex
mask site pass

@@
 Any protocol that satisfies these criteria can be used as an effective transport
-with \scheme. In this section, we describe various existing protocols (OSSH and obfuscated Obfs4) as well
+with \scheme. In this section, we describe various existing protocols (OSSH and obfs4) as well
 as introduce our own (Mask sites, TLS 1.3 eSNI, and phantom WebRTC clients) that
@@
 
-Working with currently popular implementations of TLS we overcome the active 
-and passive probing challenges by mimicking an existing mask site. To a censor, this site
-will be difficult to distinguish from the actual site, making it expensive for
+Another option to overcome active and passive probing attacks is to mimic existing TLS sites.
+In this application, we simply forward traffic between any connecting clients
+and a real TLS site. To a censor, our phantom site
+will be difficult to distinguish from the actual ``mask'' site, making it expensive for
 them to block without potentially blocking the real site. TLS connections to the
@@
 respond as a proxy. If not, the application simply continues to forward data
-between the client and the mask site, in case a clients IP was taken over by
+between the client and the mask site, in case a client's IP was taken over by
 a censor after registration. As the censor does not have knowledge of
@@
 would be easy for a censor to block as a likely non-legitimate host. Likewise,
-if a phantom host at an IP address pretends to be a domain (\texttt{example.com}) that
-globally resolves to a single IP address, the censor could also trivially
+if a phantom host at an IP address pretends to be a domain that
+globally resolves to a single (different) IP address, the censor could also trivially
 identify and block the phantom host.

### 2019-09-26 paper/paper.tex
add cite, typo

@@
 from the client using a key derived from the secret seed, client, and server
-randoms. We use the uTLS library~\cite{utls} on both the application and client
+randoms. We use the uTLS library~\cite{utls,tls-fingerprint} on both the application and client
 to allow us to change the TLS secrets being used after the handshake.
@@
 
-We evaluated the performance of a client from an India-based VPS,
-Figures~\ref{fig:upload} and~\ref{fig:download} show the upload and download as
+We evaluated the performance of a client from an India-based VPS.
+Figures~\ref{fig:upload} and~\ref{fig:download} show the upload and download bandwidth as
 measured by iperf for TapDance, our \scheme implementation (using the mask site application),

### 2019-09-28 paper/figures.tex
Cleanup in progress

@@
         the covert address.
-        \\\hspace{\textwidth}
         Secrets for the individual application proxy service are shared out of band or derived from the secret seed shared
-        between client and station during registration, preventing an adversary from being
-        able to successfully connect to the application in follow up probes.
+        between client and station during registration, preventing an adversary from 
+        successfully connecting to the application in follow up probes.
     }
@@
     \centering
-    %\vspace{-0.54in}
     \includegraphics[width=\linewidth,clip]{figures/high-level.png}
@@
     \centering
-    \begin{tabular}{l|ccccc}
+    \begin{tabular}{lccccc}
             & \rot{OSSH~\cite{ossh}} &
@@
               \rot{TLS eSNI} & \rot{WebRTC} \\
-            \hline
+            \toprule
             Active probe resistant  & \yes  & \yes & \yes & \yes & \yes \\
@@
             \scheme implementation  & \yes & \no  & \yes  & \no & \no \\
+            \bottomrule
     \end{tabular}
@@
     \caption{\textbf{\scheme Applications}\,---\,\rm%
-    ``Active probe resistant`` protocols are designed to look innocuous even if scanned by a censor.
-    ``Tunneling`` (T) protocols use another protocol (e.g. TLS) to blend in, while ``Randomized`` (R)
+    ``Active probe resistant'' protocols are designed to look innocuous even if scanned by a censor.
+    ``Tunneling'' (T) protocols use another protocol (e.g. TLS) to blend in, while ``Randomized'' (R)
         ones attempt to have no discernable protocol fingerprint or headers.
@@
         all other cores via redis and to the local application 
-        via ZMQ when a new registration is received . The detector also
+        via ZMQ when a new registration is received. The detector also
         identifies packets associated with registered flows and diverts them
@@
         the client's registration and initializes a goroutine to handle forwarding. 
-        \\\hspace{\textwidth}
         A censor trying to interfere in this
@@
   \begin{subfigure}{\columnwidth}
+    \centering
     \includegraphics[width=\columnwidth]{figures/refraction-v1}
-    \vspace{-3pt}
 
@@
   \end{subfigure}
-  \vspace{16pt}
+  \vspace{12pt}
 
   \begin{subfigure}{\columnwidth}
+    \centering
     \includegraphics[width=\columnwidth]{figures/tapdance}
-    \vspace{-3pt}
 
@@
   \end{subfigure}
-  \vspace{16pt}
+  \vspace{12pt}
 
   \begin{subfigure}{\columnwidth}
-    \label{fig:evolutionconjure}
+    \centering
     \includegraphics[width=\columnwidth]{figures/dark-decoys}
-    \vspace{-3pt}
 
@@
 Second, the client connects to a ``phantom host'' where there is no running server, and the station proxies the connection in its entirety.}
+    \label{fig:evolutionconjure}
     \label{fig:dark-decoys}
   \end{subfigure}
-
-  \vspace{12pt}
   \caption{\textbf{Evolution of Refraction Networking}}

### 2019-09-28 paper/paper.tex
Cleanup in progress

@@
 \usepackage{balance}
-\usepackage{paralist}
+%\usepackage{paralist}
 \usepackage{wasysym}
@@
 Meanwhile, many popular tools and techniques for circumventing such censorship
-have ceased to function, because censors have evolved new ways to block them~\cite{ensafi-tor,great-cannon}
+become ineffective, because censors have evolved new ways to block them~\cite{ensafi-tor,great-cannon}
 or infrastructure they rely on has become unavailable.
@@
 Censors cannot easily block access without also blocking legitimate connections to the decoy sites---collateral damage that may be prohibitive for censors if Refraction Networking is widely deployed~\cite{robinson2013collateral}.
+\looseness=-1
 
@@
 perspective, leads to major challenges when interposing in an ongoing
-client-to--decoy connection:
-\begin{compactitem}
+client-to-decoy connection:
+
+\begin{itemize}
 \item Implementation is complex and error-prone, requiring kernel
@@
   that is challenging to conceal.
-\end{compactitem}
+\end{itemize}
 
@@
 \smallskip
-
-In this paper, we present \textbf{\scheme}, a Refraction
+\noindent\textbf{Conjure}\enskip
+In this paper, we present \scheme, a Refraction
 Networking protocol that overcomes these challenges while retaining
@@
 TapDance, as our design resists active attacks.
+\looseness=1
 
@@
 large IPv6 prefixes (e.g. a /32 IPv6 prefix contains $2^{96}$ addresses).
+\looseness=1
 
@@
 other existing intermittently available proxies to register.
-
-\medskip
 
@@
 \subsection{Transports}
+%\TODO{The organization of this into subsubsections and paragraphs is a mess.  Can we flatten it a bit or divide into two sections?}
 
@@
 
-\paragraph{Encrypted SNI}
-\label{esni}
-
+\paragraph{Encrypted SNI}\label{esni}
 TLS~1.3~\cite{tls13} offers several features that may greatly simplify 
@@
 
-\paragraph{Mask Sites}
-\label{sec:mask-sites}
-
+\paragraph{Mask Sites}\label{sec:mask-sites}
 Another option to overcome active and passive probing attacks is to mimic existing TLS sites.
@@
 \paragraph{Mask Site Selection}
-
 Selecting which sites to masquerade as must be done carefully to avoid censors
@@
 identify and block the phantom host.
-
-\textit{Nearby sites ---} pick websites that are
+Several approaches are possible:
+
+\begin{description}
+\item[\rm\em Nearby sites:] pick websites that are
 legitimately hosted in or near the network of the phantom host addresses
@@
 
-\textit{Popular sites ---} choose mask sites from a list such as the Alexa
+\item[\rm\em Popular sites:] choose mask sites from a list such as the Alexa
 top site~\cite{alexa-top500} list. Although it may be wise to avoid
@@
 
-\textit{Passive observation ---} collect sites by passively observing DNS requests, TLS
+\item[\rm\em Passive observation:] collect sites by passively observing DNS requests, TLS
 SNI, or certificates that pass by at the network tap. This would allow for building a realistic set
@@
 that pass by the tap.
+
+\end{description}
 
@@
 information. We note that this is not along a critical timing path for 
-proxying connections and no client packets are sent over ZMQ.
+proxying connections and no client packets are sent over ZMQ\@.
 
@@
 operating system's interface. Figure~\ref{fig:implementation} shows the overall
-architecture of our implementation, which we describe next.
+architecture of our implementation, which we describe in the following subsections.
 % Along with the client?
@@
 % implementation~\cite{tapdance-source}.
-We implemented our detector in approximately 1,800 lines of Rust (compared to
-over 5,000 lines for TapDance)\footnote{excluding (from both) about 3,000 lines
-of auto-generated protobuf code}.
+We implemented our detector in approximately 1,800 lines of Rust, compared to
+over 5,000 lines for TapDance (excluding from both auto-generated protobuf code).
 
@@
 
-\subsection{Application \& Transports}
+\subsection{Application and Transports}
 
@@
 number of bits set and compares it to the histogram of a uniformly random set of
-addresses.\footnote{The random distribution's center is skewed from 64 due to
-the number of set bits in our fixed /32 network prefix.} Although these
+addresses. (The random distribution's center is skewed from 64 due to
+the number of set bits in our fixed /32 network prefix.) Although these
 distributions are distinguishable, they do have significant overlap. Given

### 2019-09-28 paper/paper.tex
Polish layout

@@
 Networking protocol that overcomes these challenges while retaining
-TapDance's ISP-friendly deployment requirements\footnote{
-We have released the open source implementation of the Conjure client at 
-\url{https://github.com/refraction-networking/gotapdance/tree/dark-decoy}.}.
+TapDance's ISP-friendly deployment requirements
 Our key innovation is an architecture that avoids
@@
 14\% faster download bandwidth, and over 1400 times faster upload bandwidth.
-In addition, \scheme provides significantly
-more flexibility than existing Refraction Networking protocols, allowing maintainers to
-respond to future censor techniques.
-We believe that these advantages
+In addition, \scheme is significantly more
+flexible than existing Refraction Networking protocols, allowing maintainers to
+respond to future censor techniques with greater agility.
+We believe that these advantages will
 make \scheme a strong choice for future Refraction Networking deployments.
+
+We have released the open source implementation of the Conjure client at 
+\url{https://github.com/refraction-networking/gotapdance/tree/dark-decoy}.
 
@@
 TapDance, as our design resists active attacks.
-\looseness=1
 
@@
 large IPv6 prefixes (e.g. a /32 IPv6 prefix contains $2^{96}$ addresses).
-\looseness=1
 
@@
 
-\FigIpEntropy
-
 Prior work by Foremski et al.~\cite{foremski2016entropy} has developed models to
@@
 would produce, this is still a significant amount for phantom hosts to hide in.
+\looseness=-1
 
@@
 (OSSH)~\cite{ossh}, and Shadowsocks~\cite{shadowsocks}. Each of these protocols
-require the client to know a special secret distributed alongside the original
+require the client to know a secret distributed alongside the original
 proxy address. Without knowledge of this secret, active-probing censors will not
@@
 servers with active probing.
+
+\FigIpEntropy
 
@@
 applications (e.g. obfsproxy, WebRTC, etc) that do not have this issue.
+\looseness=-1
 

### 2019-09-28 paper/paper.tex
Small spell fixes

@@
 outside the scope of the censor, but that the censor can send non-disruptive
-probes (such as stale TCP acknowledgements) that would normally
+probes (such as stale TCP acknowledgments) that would normally
 be ignored. We emphasize that TapDance is observable by censors that can send
@@
 \label{sec:registration}
-We use a form of Refraction Networking similar to Tapdance to register directly with
+We use a form of Refraction Networking similar to TapDance to register directly with
 the station, though \scheme registration is significantly simpler and more difficult
-to detect than vanilla Tapdance. This is because registration flows are unidirectional; 
+to detect than vanilla TapDance. This is because registration flows are unidirectional; 
 a client communicates their intent to register to the station without any 
@@
 and sends a normal HTTPS request that embeds a ciphertext tag in the payload. 
-\scheme leverages the same steganographic technique as Tapdance to encode the 
+\scheme leverages the same steganographic technique as TapDance to encode the 
 ciphertext~\cite[\S3]{tapdance14}, however we send a complete request allowing the

### 2019-11-20 application/lib/registration.go
log registration expiration and duration

@@ -77,7 +77,7 @@ func (regManager *RegistrationManager) CountRegistrations(darkDecoyAddr *net.IP)
 }
 
 func (regManager *RegistrationManager) RemoveOldRegistrations() {
-	regManager.registeredDecoys.removeOldRegistrations()
+	regManager.registeredDecoys.removeOldRegistrations(regManager.Logger)
 }
 
 // Note: These must match the order in the client tapdance/conjure.go transports
@@ -252,7 +252,7 @@ func (r *RegisteredDecoys) countRegistrations(darkDecoyAddr *net.IP) int {
 }
 
 // TODO log registration expiration
-func (r *RegisteredDecoys) removeOldRegistrations() {
+func (r *RegisteredDecoys) removeOldRegistrations(logger *log.Logger) {
 	const timeout = -time.Minute * 5
 	cutoff := time.Now().Add(timeout)
 	idx := 0
@@ -265,7 +265,9 @@ func (r *RegisteredDecoys) removeOldRegistrations() {
 		}
 		decoyAddr := r.decoysTimeouts[idx].decoy
 		hmacId := r.decoysTimeouts[idx].hmacId
+		regTime := r.decoysTimeouts[idx].registrationTime
 		delete(r.decoys[decoyAddr], hmacId)
+		logger.Printf("expired registration for %v, %v, duration: %v", decoyAddr, hmacId, time.Now().Sub(regTime))
 		idx += 1
 	}
 	r.decoysTimeouts = r.decoysTimeouts[idx:]

### 2019-11-20 application/lib/registration.go
remove comment

@@ -251,7 +251,6 @@ func (r *RegisteredDecoys) countRegistrations(darkDecoyAddr *net.IP) int {
 	return len(regs)
 }
 
-// TODO log registration expiration
 func (r *RegisteredDecoys) removeOldRegistrations(logger *log.Logger) {
 	const timeout = -time.Minute * 5
 	cutoff := time.Now().Add(timeout)

### 2019-11-21 application/lib/proxies.go
logging proxy duration and bytes transfered at close

@@ -80,14 +80,19 @@ func halfPipe(src, dst net.Conn,
 	oncePrintErr sync.Once,
 	logger *log.Logger) {
 
+	var proxyStartTime = time.Now()
+
 	buf := bufferPool.Get().([]byte)
-	_, err := io.CopyBuffer(dst, src, buf)
+	written, err := io.CopyBuffer(dst, src, buf)
 	oncePrintErr.Do(
 		func() {
+			proxyEndTime := time.Since(proxyStartTime) * time.Millisecond
 			if err == nil {
-				logger.Printf("gracefully stopping forwarding from %v", src.RemoteAddr())
+				logger.Printf("gracefully stopping forwarding from %v {duration; %v, bytes_written: %v}",
+					src.RemoteAddr(), proxyEndTime, written)
 			} else {
-				logger.Printf("stopping forwarding from %v due to error: %v", src.RemoteAddr(), err)
+				logger.Printf("stopping forwarding from %v due to error: %v {duration; %v, bytes_written: %v}",
+					src.RemoteAddr(), err, proxyEndTime, written)
 			}
 		})
 	if closeWriter, ok := dst.(interface {

### 2019-11-21 application/lib/proxies.go
unit fix for logging

@@ -86,7 +86,7 @@ func halfPipe(src, dst net.Conn,
 	written, err := io.CopyBuffer(dst, src, buf)
 	oncePrintErr.Do(
 		func() {
-			proxyEndTime := time.Since(proxyStartTime) * time.Millisecond
+			proxyEndTime := time.Since(proxyStartTime) 
 			if err == nil {
 				logger.Printf("gracefully stopping forwarding from %v {duration; %v, bytes_written: %v}",
 					src.RemoteAddr(), proxyEndTime, written)

### 2019-11-21 application/lib/proxies.go
Added date in output for basic loggers. We should add a logging singleton of some kind to the application

@@ -130,7 +130,7 @@ func MinTransportProxy(regManager *RegistrationManager, clientConn *net.TCPConn,
 	originalDst := originalDstIP.String()
 	originalSrc := clientConn.RemoteAddr().String()
 	flowDescription := fmt.Sprintf("[%s -> %s] ", originalSrc, originalDst)
-	logger := log.New(os.Stdout, "[MIN] "+flowDescription, log.Lmicroseconds)
+	logger := log.New(os.Stdout, "[MIN] "+flowDescription, log.Ldate|log.Lmicroseconds)
 
 	logger.Printf("new connection (%d potential registrations)", regManager.CountRegistrations(&originalDstIP))
 

### 2019-11-21 application/main.go

@@ -62,7 +62,7 @@ func handleNewConn(regManager *dd.RegistrationManager, clientConn *net.TCPConn) 
 }
 
 func get_zmq_updates(regManager *dd.RegistrationManager) {
-	logger := log.New(os.Stdout, "[ZMQ] ", log.Lmicroseconds)
+	logger := log.New(os.Stdout, "[ZMQ] ", log.Ldate|log.Lmicroseconds)
 	sub, err := zmq.NewSocket(zmq.SUB)
 	if err != nil {
 		logger.Printf("could not create new ZMQ socket: %v\n", err)

### 2019-11-22 application/lib/proxies.go
missed some logger declarations

@@ -86,7 +86,7 @@ func halfPipe(src, dst net.Conn,
 	written, err := io.CopyBuffer(dst, src, buf)
 	oncePrintErr.Do(
 		func() {
-			proxyEndTime := time.Since(proxyStartTime) 
+			proxyEndTime := time.Since(proxyStartTime)
 			if err == nil {
 				logger.Printf("gracefully stopping forwarding from %v {duration; %v, bytes_written: %v}",
 					src.RemoteAddr(), proxyEndTime, written)
@@ -180,7 +180,7 @@ func twoWayProxy(reg *DecoyRegistration, clientConn *net.TCPConn, originalDstIP 
 	notReallyOriginalSrc := clientConn.RemoteAddr().String()
 	flowDescription := fmt.Sprintf("[%s -> %s (covert=%s)] ",
 		notReallyOriginalSrc, originalDst, reg.Covert)
-	logger := log.New(os.Stdout, "[2WP] "+flowDescription, log.Lmicroseconds)
+	logger := log.New(os.Stdout, "[2WP] "+flowDescription, log.Ldate|log.Lmicroseconds)
 	logger.Println("new flow")
 
 	covertConn, err := net.Dial("tcp", reg.Covert)
@@ -208,7 +208,7 @@ func twoWayProxy(reg *DecoyRegistration, clientConn *net.TCPConn, originalDstIP 
 }
 
 func writePROXYHeader(conn net.Conn, originalIPPort string) error {
-	logger := log.New(os.Stdout, "[2WP] ", log.Lmicroseconds)
+	logger := log.New(os.Stdout, "[2WP] ", log.Ldate|log.Lmicroseconds)
 	logger.Println("Writing Proxy Header")
 	if len(originalIPPort) == 0 {
 		return errors.New("can't write PROXY header: empty IP")
@@ -235,7 +235,7 @@ func threeWayProxy(reg *DecoyRegistration, clientConn *net.TCPConn, originalDstI
 
 	flowDescription := fmt.Sprintf("[%s -> %s(%v) -> %s] ",
 		notReallyOriginalSrc, originalDst, maskHostPort, targetHostPort)
-	logger := log.New(os.Stdout, "[3WP] "+flowDescription, log.Lmicroseconds)
+	logger := log.New(os.Stdout, "[3WP] "+flowDescription, log.Ldate|log.Lmicroseconds)
 
[…]

### 2019-11-22 paper/figures.tex

@@
     \centering
-    \includegraphics[width=0.95\linewidth,clip]{figures/bandwidth-up.pdf}
+    \includegraphics[width=0.95\linewidth,clip]{figures/bandwidth-up.pdf}\vspace{-2pt}
     \caption{\textbf{Upload Performance}\,---\,\rm%
@@
         As expected, TapDance's upload performance is several orders of magnitude lower than
-        the link capacity, due to the overhead of frequent reconnects to the decoy.
+        the link capacity, due to the overhead of making frequent reconnects to the decoy site.
     }
@@
     \centering
-    \includegraphics[width=0.95\linewidth,clip]{figures/bandwidth-down.pdf}
+    \includegraphics[width=0.95\linewidth,clip]{figures/bandwidth-down.pdf}\vspace{-2pt}
     \caption{\textbf{Download Performance}\,---\,\rm%
         Using iperf, we compare the download performance of a direct connection, TapDance, and \scheme.
-        While TapDance can achieve link capacity download, it still has to occasionally reconnect
+        While TapDance can achieve link-capacity download, it still has to occasionally reconnect
         to the decoy, as seen by the periodic dips. These reconnects are more common the more data
-        the client sends (e.g. requests or any upload data).
+        the client sends (e.g. requests or uploads).
     }
@@
     \caption{\textbf{Tap Bandwidth}\,---\,\rm%
-        We deployed our \scheme implementation in a realistic ISP testbed on a
-        tap of a 20~Gbps router. As shown in a typical week, traffic
-        ranges from 2-17~Gbps.
+        We deployed \scheme in a realistic ISP testbed on a
+        tap of a 20~Gbps router. In a typical week, traffic
+        ranges from 2--17~Gbps.
     }
@@
     %\includegraphics[width=\linewidth,clip]{figures/entropy_curveball_1hr.png}
-    \includegraphics[width=\linewidth,clip]{figures/entropy-ip-16hr.png}
+    \includegraphics[width=0.95\linewidth,clip]{figures/entropy-ip-16hr.png}
     \caption{\textbf{IPv6 Entropy}\,---\,\rm%
@@
         we can also use the Entropy/IP tool to generate addresses from the Bayesian Network
-        model it produces.}
+        model it produces.\vspace{-5pt}}
     \label{fig:ipentropy}
@@
     \includegraphics[width=\linewidth,clip]{figures/ip-bits-set-pdf.pdf}
-    \caption{\textbf{IPv6 bits set}\,---\,\rm%
+    \caption{\textbf{IPv6 Bits Set}\,---\,\rm%
         We measure the number of bits set to 1 in IPv6 addresses in our ISP's /32
@@
     \medskip
-    \caption{\textbf{Comparing Refraction Networking schemes}\,---\,\rm%
+    \caption{\textbf{Comparing Refraction Networking Schemes}\,---\,\rm%
         ``No inline blocking'' corresponds to schemes that can operate as a passive tap on the side
@@
         ``Unlimited Sessions'' shows schemes that do not need to repeatedly reconnect to download
-        or upload arbitrarily large content.}
+        or upload arbitrarily large content.\vspace{-10pt}}
     \label{tab:compare}

### 2019-11-22 paper/related.tex
minor edits from Nikita

@@
 as previously described, this trick comes at a cost: the decoy only stays silent
-for a short timeout (typically 30-120 seconds), and limits the amount of data
+for a short timeout (typically 30--120\,s), and limits the amount of data
 the client can send before it responds. TapDance clients must keep connections
@@
 clients to maintain long-lived connections to the phantom host.
+\looseness=-1
 
@@
 \subsection{Decoy Placement and Routing Attacks}
+\label{sec:placement-rad}
 

### 2019-11-23 application/lib/proxies.go
Updating logging at connection start and end -- easier to parse

@@ -78,7 +78,8 @@ func ProxyFactory(reg *DecoyRegistration, proxyProtocol uint) func(*DecoyRegistr
 func halfPipe(src, dst net.Conn,
 	wg *sync.WaitGroup,
 	oncePrintErr sync.Once,
-	logger *log.Logger) {
+	logger *log.Logger,
+	tag string) {
 
 	var proxyStartTime = time.Now()
 
@@ -88,11 +89,11 @@ func halfPipe(src, dst net.Conn,
 		func() {
 			proxyEndTime := time.Since(proxyStartTime)
 			if err == nil {
-				logger.Printf("gracefully stopping forwarding from %v {duration; %v, bytes_written: %v}",
-					src.RemoteAddr(), proxyEndTime, written)
+				logger.Printf("gracefully stopping forwarding {from: %v duration; %v, bytes_written: %v, tag: %s }",
+					src.RemoteAddr(), int64(proxyEndTime/time.Millisecond), written, tag)
 			} else {
-				logger.Printf("stopping forwarding from %v due to error: %v {duration; %v, bytes_written: %v}",
-					src.RemoteAddr(), err, proxyEndTime, written)
+				logger.Printf("stopping forwarding due to err {from: %v, duration; %v, bytes_written: %v, tag: %v}  error: %v",
+					src.RemoteAddr(), int64(proxyEndTime/time.Millisecond), written, tag, err)
 			}
 		})
 	if closeWriter, ok := dst.(interface {
@@ -129,7 +130,7 @@ func MinTransportProxy(regManager *RegistrationManager, clientConn *net.TCPConn,
 
 	originalDst := originalDstIP.String()
 	originalSrc := clientConn.RemoteAddr().String()
-	flowDescription := fmt.Sprintf("[%s -> %s] ", originalSrc, originalDst)
+	flowDescription := fmt.Sprintf("%s -> %s ", originalSrc, originalDst)
 	logger := log.New(os.Stdout, "[MIN] "+flowDescription, log.Ldate|log.Lmicroseconds)
 
 	logger.Printf("new connection (%d potential registrations)", regManager.CountRegistrations(&originalDstIP))
@@ -137,18 +138,18 @@ func MinTransportProxy(regManager *RegistrationManager, clientConn *net.TCPConn,
 	possibleHmac := make([]byte, 32)
 	n, err := readAtMost(clientConn, possibleHmac)
[…]

### 2019-11-23 application/lib/proxies.go
formatting mistakes

@@ -89,7 +89,7 @@ func halfPipe(src, dst net.Conn,
 		func() {
 			proxyEndTime := time.Since(proxyStartTime)
 			if err == nil {
-				logger.Printf("gracefully stopping forwarding {from: %v duration; %v, bytes_written: %v, tag: %s }",
+				logger.Printf("gracefully stopping forwarding {from: %v, duration; %v, bytes_written: %v, tag: %s}",
 					src.RemoteAddr(), int64(proxyEndTime/time.Millisecond), written, tag)
 			} else {
 				logger.Printf("stopping forwarding due to err {from: %v, duration; %v, bytes_written: %v, tag: %v}  error: %v",
@@ -149,7 +149,7 @@ func MinTransportProxy(regManager *RegistrationManager, clientConn *net.TCPConn,
 	}
 	// If we are here, this is our transport (TODO: signal in output channel for it)
 	logger.Printf("registration found {reg_id: %s, phantom: %s, hmac: %s, covert: %s}\n", reg.IDString(), originalDstIP, hex.EncodeToString(possibleHmac), reg.Covert)
-	logger.SetPrefix(fmt.Sprintf("%s ", reg.IDString()))
+	logger.SetPrefix(fmt.Sprintf("[MIN] %s ", reg.IDString()))
 
 	covertConn, err := net.Dial("tcp", reg.Covert)
 	if err != nil {
